### 2019-09-26 ErrP.tex
Subo una version base del paper sacando la informacion de la tesis.  Falta mucho todavia, depuracion, intro, referencias, escritura, figuras, imagenes formas, etc.

%% bare_jrnl.tex
%% V1.4b
%% 2015/08/26
%% by Michael Shell
%% see http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
%% journal paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/pkg/ieeetran
%% and
%% http://www.ieee.org/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE! 
%% User assumes all risk.
%% In no event shall the IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%*************************************************************************

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. The IEEE's font choices and paper sizes can   ***
% *** trigger bugs that do not appear when using other class files.       ***                          ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

\documentclass[journal]{IEEEtran}
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[journal]{../sty/IEEEtran}

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{subcaption} 
\usepackage{hyperref}
\usepackage{algorithm2e} % For algorithms
\usepackage{amsmath, amssymb, amsthm} % Mathematical packages

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/pkg/ifpdf
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
%\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of the IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off
% such as if a citation ever needs to be enclosed in parenthesis.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 5.0 (2009-03-20) and later if using hyperref.sty.
% The latest version can be obtained at:
% http://www.ctan.org/pkg/cite
% The documentation is contained in the cite.sty file itself.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at: 
% http://www.ctan.org/pkg/graphicx
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/pkg/epslatex
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
%\usepackage{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics.
%
% Note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/amsmath

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/pkg/algorithms
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/pkg/algorithmicx

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/array

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

% *** SUBFIGURE PACKAGES ***
%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false,font=footnotesize]{subfig}
%\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a larger sans serif font
% than the serif footnote size font used in traditional IEEE formatting
% and thus the need to invoke different subfig.sty package options depending
% on whether compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/pkg/subfig

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure.
% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
% corrections already built into the system in which case a warning will
% be issued if an attempt is made to load fixltx2e.sty as it is no longer
% needed.
% The latest version and documentation can be found at:
% http://www.ctan.org/pkg/fixltx2e

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/stfloats
% Do not use the stfloats baselinefloat ability as the IEEE does not allow
% \baselineskip to stretch. Authors submitting work to the IEEE should note
% that the IEEE rarely uses double column equations and that authors should try
% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
% such ways.
% Do not attempt to use stfloats with fixltx2e as they are incompatible.
% Instead, use Morten Hogholm'a dblfloatfix which combines the features
% of both fixltx2e and stfloats:
%
% \usepackage{dblfloatfix}
% The latest version can be found at:
% http://www.ctan.org/pkg/dblfloatfix

%\ifCLASSOPTIONcaptionsoff
%  \usepackage[nomarkers]{endfloat}
% \let\MYoriglatexcaption\caption
% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
%\fi
% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and 
% Axel Sommerfeldt. This package may be useful when used in conjunction with 
% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
% submissions have lists of figures/tables at the end of the paper and that
% figures/tables without any captions are placed on a page by themselves at
% the end of the document. If needed, the draftcls IEEEtran class option or
% \CLASSINPUTbaselinestretch interface can be used to increase the line
% spacing as well. Be sure and use the nomarkers option of endfloat to
% prevent endfloat from "marking" where the figures would have been placed
% in the text. The two hack lines of code above are a slight modification of
% that suggested by in the endfloat docs (section 8.4.1) to ensure that
% the full captions always appear in the list of figures/tables - even if
% the user used the short optional argument of \caption[]{}.
% IEEE papers do not typically make use of \caption[]'s optional argument,
% so this should not be an issue. A similar trick can be used to disable
% captions of packages such as subfig.sty that lack options to turn off
% the subcaptions:
% For subfig.sty:
% \let\MYorigsubfloat\subfloat
% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
% However, the above trick will not work if both optional arguments of
% the \subfloat command are used. Furthermore, there needs to be a
% description of each subfigure *somewhere* and endfloat does not add
% subfigure captions to its list of figures. Thus, the best approach is to
% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
% and instead reference/explain all the subfigures within the main caption.
% The latest version of endfloat.sty and its documentation can obtained at:
% http://www.ctan.org/pkg/endfloat
%
% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
% later in the document, say, to conditionally put the References on a 
% page by themselves.

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/url
% Basically, \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Training an Agent on Brainwaves}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

\author{Bartolomé Francisco, Moreno Juan,  Navas Natalia, Vitali José, \\
Rodrigo~Ramele,~\IEEEmembership{Member,~IEEE,} 
        Juan~Miguel,~Santos% <-this % stops a space
\thanks{R. Ramele and J.M.Santos are with the Department
of Computer Engineering, Instituto Tecnológico de Buenos Aires(ITBA), Argentina,
e-mail: rramele@itba.edu.ar.}% <-this % stops a space
\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}

% note the % following the last \IEEEmembership and also \thanks - 
% these prevent an unwanted space from occurring between the last author name
% and the end of the author line. i.e., if you had this:
% 
% \author{....lastname \thanks{...} \thanks{...} }
%                     ^------------^------------^----Do not want these spaces!
%
% a space would be appended to the last name and could cause every name on that
% line to be shifted left slightly. This is one of those "LaTeX things". For
% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
% "AB" then you have to do: "\textbf{A}\textbf{B}"
% \thanks is no different in this regard, so shield the last } of each \thanks
% that ends a line with a % and do not let a space in before the next \thanks.
% Spaces after \IEEEmembership other than the last one are OK (and needed) as
% you are supposed to have spaces between the names. For what it is worth,
% this is a minor point as most people would not even notice if the said evil
% space somehow managed to creep in.

% The paper headers
\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}
% The only time the second header will appear is for the odd numbered pages
% after the title page when using the twoside option.
% 
% *** Note that you probably will NOT want to include the author's ***
% *** name in the headers of peer review papers.                   ***
% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
% you desire.

% If you want to put a publisher's ID mark on the page you can do it like
% this:
%\IEEEpubid{0000--0000/00\$00.00~\copyright~2015 IEEE}
% Remember, if you use this you must call \IEEEpubidadjcol in the second
% column for its text to clear the IEEEpubid mark.

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
The field of Brain Computer Interfaces has seen a bloom in the past few years. One of its applications is the training of systems using signals originated from the human brain. Out of all the methods used to acquire information from the central nervous system the one that has gained the most popularity is Electroencephalography (EEG), mainly because of its effectiveness, low cost and because it is noninvasive.
Event-related potential (ERP) are brain signals that are time-locked to a particular event. Error-related potential (ErrP) are a particular type of ERP that are can be elicited by a person who attends a recognizable error. When subjects observe an agent who makes a mistake this potential can be discerned when analyzing the signals which are directly related with the cognitive interpretation of an erroneous outcome or decision.
Reinforcement Learning (RL) is an approach to machine learning where an agent tries to maximize the reward obtained while interacting with an unknown environment. This work follow this path by detecting the ErrP potential from subjects witnessing an agent playing the game and improving the agent behavior using RL and obtaining rewards from the subjects.
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
ErrP, BCI, EEG, RL, Agent, AI
\end{IEEEkeywords}

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\section{Introduction}

% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
\IEEEPARstart{T}{he} effectiveness of today's human–machine interaction is limited by a communication bottleneck as operators are required to translate high-level concepts into a machine-mandated sequence of instructions \cite{CURSOR-CONTROL-PAPER}. This work tackles directly this problem by exploring the use of brain signals as an interface between human and computer, overcoming this limitation by enabling the control of the system without explicit communication from the user.

Using reinforcement learning with reward signals based on brain activity, recorded by an EEG-based BCI system during the task execution, in order to train an agent has been explored in previous research. The paper \cite{ROBOT-CONTROL-PAPER} has successfully demonstrated that a robot can be controlled by obtaining the reward from brain activity generated while observing the robot solving a task. The present project applies a similar process for making a virtual agent improve its performance using electroencephalography (EEG) signals as feedback for a reinforcement learning algorithm. The idea is that subjects observing a simple simulated system can train such system using only error-related potentials (ErrP) that can be identified in their brain signals. The detection of ErrP signals has been explored in the publication \cite{EERP-PAPER} which describes the methods that are used in order to identify this specific potential from EEG signals.

In recent years reinforcement learning has seen a come-back. This is mainly because of DeepBrain's AlphaGo who was the first to reach superhuman proficiency in challenging domains, when it won the complex game Go against several world champions. In 2015 AlphaGo won 5 matches against 3-times European Champion, Mr Fan Hui. AlphaGo then went on to compete against Mr Lee Sedol, winner of 18 world titles and considered to be the greatest player until then, and won 4 out of 5 matches in 2016 \cite{ALPHA-GO}.

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure}

% Note that the IEEE typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command,
% and the \label for the overall figure must come after \caption.
% \hfil is used as a separator to get equal spacing.
% Watch out that the combined width of all the subfigures on a 
% line do not exceed the text width or a line break will occur.
%
%\begin{figure*}[!t]
%\centering
%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
%\label{fig_second_case}}
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat[]), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.
% Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
% labels, the optional argument to \subfloat must be present. If a
% subcaption is not desired, just leave its contents blank,
% e.g., \subfloat[].

% An example of a floating table. Note that, for IEEE style tables, the
% \caption command should come BEFORE the table and, given that table
% captions serve much like titles, are usually capitalized except for words
% such as a, an, and, as, at, but, by, for, in, nor, of, on, or, the, to
% and up, which are usually not capitalized unless they are the first or
% last word of the caption. Table text will default to \footnotesize as
% the IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
%\begin{table}[!t]
%% increase table row spacing, adjust to taste
%\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
%\caption{An Example of a Table}
%\label{table_example}
%\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
%\begin{tabular}{|c||c|}
%\hline
%One & Two\\
%\hline
%Three & Four\\
%\hline
%\end{tabular}
%\end{table}

% Note that the IEEE does not put floats in the very first column
% - or typically anywhere on the first page for that matter. Also,
% in-text middle ("here") positioning is typically not used, but it
% is allowed and encouraged for Computer Society conferences (but
% not Computer Society journals). Most IEEE journals/conferences use
% top floats exclusively. 
% Note that, LaTeX2e, unlike IEEE journals/conferences, places
% footnotes above bottom floats. This can be corrected via the
% \fnbelowfloat command of the stfloats package.

In Section I, in Section II and Results and conclusions are exposed at the end.

\section{Materials and Methods}

The project consists of collecting signals from a person's brain while they are watching a game where the agent has knowledge of the way it's played but not how to win it. Hence, the agent can learn using the person's feedback to get better at the game. This section describes the process of obtaining the person's brain signals and how they are used to make the agent improve it's performance.

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.4]{Images/complete_flow.png}
    \caption{Overview of the experimental procedure.}
    \label{diag:complete_flow}
\end{figure}

The experimental procedure is summarized in Figure \ref{diag:complete_flow}. The core of the procedure is the retrieval of the subject's brain activity. This process is called brainwave session. In order to fetch this data, subjects use a wireless digital EEG device during the experiment. Once the subject has the headset on, a set up procedure is executed as described in Section \ref{cognitive_experiment_details} using a program called g.NeedAcceess to do an impedance check and to visually inspect the EEG signals in order to check if it's correctly applied. Subsequently, the OpenVibe Acquisition Server program is launched and configured. This program is part of the OpenVibe platform \cite{OPEN-VIBE-PAPER} and has the responsibility of receiving the signals data from the headset and stimulus information from the game and transfers it to the OpenVibe Designer application. After this step, the Game and the OpenVibe Designer programs are launched and configured to communicate with the previously mentioned acquisition server. Once the subject is ready the computer is positioned in front of them and the brainwave session starts. A brainwave session consists of several experiences, each of them being a game run, and it uses a pseudo-random function to determine the agent's movements. The system is described in more detail in Section \ref{cognitive_experiment_system} and the brainwave session in Section \ref{cognitive_experiment_details}. Once the experimental procedure is completed, the game state information and the signals data with the stimuli channel information of each run are stored. For each run, the signals and stimulus information are then passed to the classification module that uses them to train the classifier. The classification step is covered in detail in Section \ref{signal_processing_and_classification}. After this step is finished, the game movements and the trained classifier are used to update a Q-Table for each experience. Lastly, the calculated Q-Table is used to test if the agent has boosted its performance while playing the game. This module is explained in Section \ref{q_learning_step}.

\subsection{Cognitive Game experiment}
This section details the game system characteristics, the brainwave session process and the retrieval and analysis of the generated data from the subjects interaction with the system.

\label{cognitive_experiment_system}{
The system consists of a $5x5$ grid where there are two lights, one representing the current position of the agent, and the other one representing the goal, shown in figure  \ref{fig:game_representation}. The objective of the system is for the agent to reach the goal. The light representing the goal remains static at the bottom-right position of the grid, while the one representing the position of the agent always starts at the upper-left position of the grid. The grid is represented by circular spots with a black background. The agent's position has a blue light, the goal position has a green light, and the rest of cells are represented with grey spots. When the agent reaches the goal, the position where the agent and the goal are located turns red, showing that the experience has ended. There are four possible movements that the agent can perform: it can go upwards, downwards, towards the left and towards the right, as long as the move doesn't make the agent leave the grid. The movement direction is selected randomly and is executed once every 2 seconds. When the experience ends, there is a pause of 5 seconds before the next experience starts. The experience is designed for it to be evident whenever there is an error (when the agent moves away from the objective) so the subject can notice it immediately after the stimulus is presented, possibly triggering a cognitive response.

\begin{figure}[h!]
\begin{subfigure}{0.5\textwidth}
\includegraphics[width=0.9\linewidth,scale=0.9]{Images/grid_initial_state.png} 
\caption{Initial state of the grid.}
\label{fig:subim1}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
\includegraphics[width=0.9\linewidth,scale=0.9]{Images/grid_end_state.png}
\caption{Final state of the grid.}
\label{fig:subim2}
\end{subfigure}
\caption{Grid system representation used in cognitive experience.}
\label{fig:game_representation}
\end{figure}
}

\section{Calibration}

The first step in order to be able to find ErrP signals is to choose the most efficient algorithm, and the proper calibration. In order to do this different parameters are tested for a set of algorithms and for each individual subject. Initially a sub-selection of experiments is used to define a subset of parameters to test with, and then all the data is tested with this subset of parameters.

\section{Signal Processing and Segmentation}

The goal of this module is to build a classifier that is able to identify whether the action taken by the agent is an error or not. It is developed in Python using the \href{https://mne-tools.github.io/0.11/index.html}{MNE} environment \cite{MNE-PYTHON}, which is a package designed specifically for processing EEG and MEG data, and the machine learning library \href{https://scikit-learn.org/stable/}{Scikit-Learn}.

Many classification methods are considered. The best classifier is selected based on a calibration and selection procedure that is further explained in sections \ref{algorithm_calibration} and \ref{algorithm_comparison}. After an optimal algorithm and a configuration are selected, a classifier is trained for each subject and then epochs from their experiences are classified. These classifications are then used by a reinforcement learning algorithm to train the agent. This last algorithm is explained in detail in section \ref{q_learning_step}.

This step consists of processing the collected signals in order to train a classifier that can decide whether an error potential is triggered or not. Firstly, the output of a brainwave session is read and a band pass filter of 0.1-20.0Hz is applied to the signal, as seen in Figure \ref{fig_psd_band_pass}. Samples that correspond to the start of an event are tagged using the data from the stimuli channel.

After the data is loaded and tagged, epochs are extracted from the raw data. Epochs consist of all the sample points that take place between the start of the event and 2 seconds later (time for each action to take place), resulting in 500 samples per channel, as the sample frequency is 250 Hz.

Samples that do not correspond to an epoch are not used. Also, epochs referring to the start or finish of the experience are excluded. This is done because the start and the end of the experience doesn't involve the agent taking an action, thus giving signals that should not be considered in the classification process.

In this way, the raw data of an entire brainwave session is processed into an array of experiences where each element is an array of epochs tagged with a number specifying if the epoch corresponds to an action that made the agent move further from the goal (hit) or an action that made the agent move closer to the goal (no hit). The ErrP is expected to be found in hits. To get the data ready for classification, the stimuli channel is removed in order to classify the signals using only the EEG data and a mne.decoding.vectorizer \footnote{Link to vectorizer documentation: \href{https://mne.tools/dev/generated/mne.decoding.Vectorizer.html}{https://mne.tools/dev/generated/mne.decoding.Vectorizer.html}} function is applied to transform the data into a single array sample. Lastly, this data is used by the classification module as information to train and test a classifier.

\section{Classification with Logistic Regression}
For the logistic regression algorithm the parameters that are tested are $C$ and the Solver.  The $C$ parameter is the inverse of the regularization strength. The values this parameter can take are 0.001, 0.01, 0.1, 1 and 10. The solver parameter refers to the algorithm that is used in the optimization problem, the ones that are tested are $lbfgs$ and $saga$. The different configurations that resulted as optimal for subjects can be seen in the apendix section \ref{apendix:algorithm_config:lr}.

Raw signals are classified using a vectorizer a minmaxscaler and finally the logistic regression classifier.  Even tough the classification accuracy is low, the information is enough to have valid rewards that can be used to retrieve the information.

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.4]{Images/algorithm_calibration/LR_calib.png}
    \caption{Logistic Regression Algorithm Calibration}
    \label{diag:algorithm_calibration:lr}
\end{figure}

\section{Reinforcement Learning}

The set of experiences of each subject is split into training and testing, so that the results of the classification can then be used to improve the performance of the agent. After training the classifier, the testing experiences are classified. Then, for each experience a reward file is generated. For this purpose, game states files, which are submitted by the game when an experience takes place, are used. These files contain an ordered list of the states of the game throughout an experience. With this file and the classification of the test data of an experience, a reward file is submitted. This file specifies a reward for each movement in the game, based on the classification of the event that corresponds to that movement. The reward can either be -1 when the event is classified as a hit or 0 when it is classified as a no hit. The accuracy of this rewards depends on the performance of the classifier. This reward file is used by the Q-Learning algorithm to improve its performance, as detailed in section \ref{q_learning_step}.

\subsection{Q-Learning}{
\label{q_learning_step}
A Q-Learning algorithm is used to train the agent. It is developed in Python and uses the \href{https://gym.openai.com}{OpenAI Gym} toolkit. Gym is a toolkit for developing and comparing reinforcement learning algorithms. It makes no assumptions about the structure of an agent, and is compatible with any numerical computation library, such as TensorFlow or Theano.

\subsubsection{Algorithm implementation}{
\label{q_learning_step_alg}
The Q-Table is initialized with zeros, unless a preexisting Q-Table is passed as a parameter. In order for the agent to learn from the feedback generated by the subject, the Q-Table is not used to determine the action to take at a given state. Instead, the policy which determines which action to take in a particular state is given by the steps taken from the brainwave session results. This allows to train the Q-Table based on the subject's feedback from the movements the agent took, which are chosen pseudo-randomly, while executing the brainwave session. The previously mentioned feedback is not explicit as it comes from the interpreted brain signal data, which is collected while the agent is executing the brainwave session and then each action is classified as an error or not. This implies that the reward is determined by the subject's brain activity. This is covered in further detail in \ref{q_learning_step_env}.

While using the previously mentioned step function, the Q-Table is updated in each iteration. This is done following the Equation \ref{equ:update_q_table}.

\begin{equation}
    Q(s,a) \leftarrow Q(s,a) + \alpha[r+\gamma* Max(s, a)-Q(s, a) ]
    \label{equ:update_q_table}
\end{equation}

After the algorithm finishes iterating through all the training episodes, the Q-Table is saved. Each experience is one $trainingEpisode$.

The reward function is calculated based on the current distance to the goal, if it has increased compared to the previous step then the rewards is negative, if not it returns zero. In order to test how the Q-Table is trained when the accuracy is not perfect the reward function doesn't always return the correct reward. It calculates a random number between 0 and 1, and if it is larger than the accuracy then it will return 0 even if it should return -1 as the reward.

The reward function is described in algorithm \ref{algorithm:env_rewards}.

\begin{algorithm}
\SetAlgoLined
\DontPrintSemicolon
$reward \leftarrow 0$\\
  \uIf{currentDistanceToGoal > previousDistanceToGoal}{
    $reward \leftarrow -1$ \;
  }
  \uElseIf{random.uniform(0, 1) < accuracy}{
    return reward \;
  }
  \Else{
    return 0 \;
  }
\label{algorithm:env_rewards}
\caption{Reward Calculation for $ChaseEnv$}
\end{algorithm}
}
}

\section{Results}

\subsection{Reinforcement Learning}

\textbf{Average steps to goal}
Figure \ref{fig:avg_steps} shows the average amount of steps it takes to reach the goal as the Q-Table is progressively trained using the reward information obtained for each subject. Each point corresponds to the average amount of steps it takes for the agent to reach the goal for a specific Q-Table in 200 iterations. The first point represents the amount of steps it takes to reach the goal for a Q-Table that hasn't been trained at all, where movements are decided randomly. The next point corresponds to the amount of steps it takes to reach the goal using a Q-Table trained with one experience, and so on.

The results show that as the Q-Table is progressively trained the average amount of steps decreases, meaning that the agent learns. However, the rate at which it learns varies per subject, certain subjects have more effective experiments than others, for example results for subject 1 (fig \ref{fig:avg_steps_1}) show faster learning than those of subject 8 (fig \ref{fig:avg_steps_8}).

In the case for subject 5 and 6, the reward information obtained from the brainwaves is not enough to train the agent effectively. Figures \ref{fig:avg_steps_5} and \ref{fig:avg_steps_6} show no apparent learning, as the amount of steps to reach the goal doesn't decrease when trained. Both subjects have less recorded data from the sessions in comparison to the rest of the subjects. In particular, subject 5 has less recorded experiences, so it is respective graphic shows the amount of steps for an empty Q-Table and for a Q-Table trained with only one experience. These results are consistent with fig. \ref{fig:roc:manuel} and fig. \ref{fig:roc:marta}, which show that the signal classification for these subjects hasn't been particularly successful. The average steps result for these subject are similar to that of fig. \ref{fig:roc:noise} which is constructed from noise, so the generated Q-Table would be similar to one generated with noise.

\begin{figure}[h]
        \centering
        \includegraphics[scale=0.4]{Images/Average_steps/alex.png} 
        \caption{Average steps using Q-table trained with the results of subject 1}
        \label{fig:avg_steps_1}
\end{figure}

\begin{figure}[h]
        \centering
        \includegraphics[scale=0.4]{Images/Average_steps/gonza.png} 
        \caption{Average steps using Q-table trained with the results of subject 2}
        \label{fig:avg_steps_2}
\end{figure}

\begin{figure}[h]
        \centering
        \includegraphics[scale=0.4]{Images/Average_steps/jose.png} 
        \caption{Average steps using Q-table trained with the results of subject 3}
        \label{fig:avg_steps_3}
\end{figure}

\begin{figure}[h]
        \centering
        \includegraphics[scale=0.4]{Images/Average_steps/juan.png} 
        \caption{Average steps using Q-table trained with the results of subject 4}
        \label{fig:avg_steps_4}
\end{figure}

\begin{figure}[h]
        \centering
        \includegraphics[scale=0.4]{Images/Average_steps/manu.png} 
        \caption{Average steps using Q-table trained with the results of subject 5}
        \label{fig:avg_steps_5}
\end{figure}

\begin{figure}[h]
        \centering
        \includegraphics[scale=0.4]{Images/Average_steps/marta.png} 
        \caption{Average steps using Q-table trained with the results of subject 6}
        \label{fig:avg_steps_6}
\end{figure}

\begin{figure}[h]
        \centering
        \includegraphics[scale=0.4]{Images/Average_steps/nati.png} 
        \caption{Average steps using Q-table trained with the results of subject 7}
        \label{fig:avg_steps_7}
\end{figure}

\begin{figure}[h]
        \centering
        \includegraphics[scale=0.4]{Images/Average_steps/santiago.png} 
        \caption{Average steps using Q-table trained with the results of subject 8}
        \label{fig:avg_steps_8}
\end{figure}

\section{Conclusion}
The present research work set out to validate if ErrP signals could be used to train an agent using reinforcement learning. The collected data show that ErrP signals can in fact be classified and used to train an agent effectively.

When classifying, the better performing classifier is Logistic Regression. One important aspect of the classification results is the low percentage of false positives, meaning that it is not common that the agent learns that an action is wrong when in fact it is an action that takes it closer to the goal. On the other hand, the percentage of false negatives is generally higher, but this is not a serious issue since missing out on learning that an action is wrong does not lower the performance of the agent, but only means it will take more experiences to learn a correct path.

Once ErrP signals are identified they can be used to train a reinforcement learning algorithm. However, this can only be achieved by generating a specific classifier for each subject and using it for giving rewards for the corresponding subjects. Results show that training a classifier with data of one subject, but using it to classify the events of experiences of another subject does not lead to an improvement on the performance of the agent, concluding that the experiment is not suited for transfer learning. Despite that, the rewards generated from different subjects can be used to train the same Q-Table to improve its performance.

Brainwave sessions have a low amount of experiences in order to reduce fatigue from the subjects. However data suggests that longer sessions are required in order to reach better classification scores, since more data is available in order to train the classifier. It can be seen that subjects with the largest amounts of data have the best classification. This can also be achieved designing a bigger game system that generates more samples with every session.

Finally, this research verifies that brain signals can be used as an interface between human and computer enabling the control of the system without explicit input from the user.

% if have a single appendix:
%\appendix[Proof of the Zonklar Equations]
% or
%\appendix  % for no appendix heading
% do not use \section anymore after \appendix, only \section*
% is possibly needed

% use appendices with more than one appendix
% then use \section to start each appendix
% you must declare a \section before using any
% \subsection or using \label (\appendices by itself
% starts a section numbered zero.)
%

% use section* for acknowledgment
\section*{Acknowledgment}

The authors would like to thank...

% Can use something like this to put references on a page
% by themselves when using endfloat and the captionsoff option.
\ifCLASSOPTIONcaptionsoff
  \newpage
\fi

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
\bibliographystyle{IEEEtran}
\bibliography{References}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
% biography section
% 
% If you have an EPS/PDF photo (graphicx package needed) extra braces are
% needed around the contents of the optional argument to biography to prevent
% the LaTeX parser from getting confused when it sees the complicated
% \includegraphics command within an optional argument. (You could create
% your own custom macro containing the \includegraphics command to make things
% simpler here.)
%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
% or if you just want to reserve a space for a photo:

\begin{IEEEbiography}{Michael Shell}
Biography text here.
\end{IEEEbiography}

% if you will not have a photo at all:
\begin{IEEEbiographynophoto}{John Doe}
Biography text here.
\end{IEEEbiographynophoto}

% insert where needed to balance the two columns on the last page with
% biographies
%\newpage

\begin{IEEEbiographynophoto}{Jane Doe}
Biography text here.
\end{IEEEbiographynophoto}

% You can push biographies down or up by placing
% a \vfill before or after them. The appropriate
% use of \vfill depends on what kind of text is
% on the last page and whether or not the columns
% are being equalized.

%\vfill

% Can be used to pull up biographies so that the bottom of the last one
% is flush with the other column.
%\enlargethispage{-5in}

% that's all folks
\end{document}

### 2019-09-26 ErrP.tex
Subo una versión más depurada del paper

@@
 
-\begin{figure}[h]
+\begin{figure}[h!]
+\begin{subfigure}{0.5\textwidth}
+\includegraphics[scale=0.2]{Images/Average_steps/alex.png}
+\includegraphics[scale=0.2]{Images/Average_steps/gonza.png}
+\includegraphics[scale=0.2]{Images/Average_steps/jose.png}
+ \includegraphics[scale=0.2]{Images/Average_steps/juan.png} 
+\caption{Initial state of the grid.}
+\label{fig:subim1}
+\end{subfigure}
+\begin{subfigure}{0.5\textwidth}
+ \includegraphics[scale=0.2]{Images/Average_steps/manu.png} 
+  \includegraphics[scale=0.2]{Images/Average_steps/marta.png} 
+  \includegraphics[scale=0.2]{Images/Average_steps/nati.png} 
+  \includegraphics[scale=0.2]{Images/Average_steps/santiago.png} 
+\caption{Final state of the grid.}
+\label{fig:subim2}
+\end{subfigure}
+\caption{Grid system representation used in cognitive experience.}
+\label{fig:game_representation}
+\end{figure}
+
+\begin{figure}[h!]
 \centering
-        \includegraphics[scale=0.4]{Images/Average_steps/alex.png} 
-        \caption{Average steps using Q-table trained with the results of subject 1}
-        \label{fig:avg_steps_1}
+\includegraphics[scale=0.4]{Images/Average_steps/noise.png}
+\caption{Average steps using Q-Table trained with noise.}
+\label{fig:avg_steps_noise}
 \end{figure}
@@
     \centering
-        \includegraphics[scale=0.4]{Images/Average_steps/gonza.png} 
-        \caption{Average steps using Q-table trained with the results of subject 2}
-        \label{fig:avg_steps_2}
-\end{figure}
-
-\begin{figure}[h]
-        \centering
-        \includegraphics[scale=0.4]{Images/Average_steps/jose.png} 
-        \caption{Average steps using Q-table trained with the results of subject 3}
-        \label{fig:avg_steps_3}
-\end{figure}
-
-\begin{figure}[h]
-        \centering
-        \includegraphics[scale=0.4]{Images/Average_steps/juan.png} 
-        \caption{Average steps using Q-table trained with the results of subject 4}
-        \label{fig:avg_steps_4}
-\end{figure}
-
-\begin{figure}[h]
-        \centering
-        \includegraphics[scale=0.4]{Images/Average_steps/manu.png} 
-        \caption{Average steps using Q-table trained with the results of subject 5}
-        \label{fig:avg_steps_5}
-\end{figure}
-
-\begin{figure}[h]
-        \centering
-        \includegraphics[scale=0.4]{Images/Average_steps/marta.png} 
-        \caption{Average steps using Q-table trained with the results of subject 6}
-        \label{fig:avg_steps_6}
-\end{figure}
-
-\begin{figure}[h]
-        \centering
-        \includegraphics[scale=0.4]{Images/Average_steps/nati.png} 
-        \caption{Average steps using Q-table trained with the results of subject 7}
-        \label{fig:avg_steps_7}
-\end{figure}
-
-\begin{figure}[h]
-        \centering
-        \includegraphics[scale=0.4]{Images/Average_steps/santiago.png} 
-        \caption{Average steps using Q-table trained with the results of subject 8}
-        \label{fig:avg_steps_8}
+    \includegraphics[scale=0.4]{Images/algorithm_calibration/Total_calib.png}
+    \caption{Score Obtained With The Optimal Calibration Per Algorithm Per Subject}
+    \label{diag:algorithm_calibration:subject_calib}
 \end{figure}

### 2019-10-18 ErrP.tex
Rewrote intro

@@
 % (should never be an issue)
-\IEEEPARstart{T}{he} effectiveness of today's human–machine interaction is limited by a communication bottleneck as operators are required to translate high-level concepts into a machine-mandated sequence of instructions \cite{CURSOR-CONTROL-PAPER}.
-This work tackles directly this problem by exploring the use of brain signals as an interface between human and computer, overcoming this limitation by enabling the control of the system without explicit communication from the user.
+\IEEEPARstart{T}{he} effectiveness of today's human–machine interaction and artificial intelligence is limited by a communication bottleneck as humans are required to translate high-level concepts into a machine-mandated sequence of instructions \cite{CURSOR-CONTROL-PAPER}.
+This work tackles this problem by exploring the use of brain signals as an interface between human and computer, trying to overcome this limitation by providing information to the system without explicit communication from the user.
+This information is used to make a gaming agent improve its operational performance using electroencephalography (EEG) signals as feedback of the performed task from an observational human critic.
+The idea is that subjects observing a computer game play can train the gaming agent using only electrophisiological signals called Error-related Potentials (ErrP) that can be identified from their brain signals.
 
-Using reinforcement learning with reward signals based on brain activity, recorded by an EEG-based BCI system during the task execution, in order to train an agent has been explored in previous research.
-The paper \cite{ROBOT-CONTROL-PAPER} has successfully demonstrated that a robot can be controlled by obtaining the reward from brain activity generated while observing the robot solving a task.
-The present project applies a similar process for making a virtual agent improve its performance using electroencephalography (EEG) signals as feedback for a reinforcement learning algorithm.
-The idea is that subjects observing a simple simulated system can train such system using only error-related potentials (ErrP) that can be identified in their brain signals.
-The detection of ErrP signals has been explored in the publication \cite{EERP-PAPER} which describes the methods that are used in order to identify this specific potential from EEG signals.
+Error-related Potentials are signal components that can be found on EEG traces and are elicited when a subject is aware of the presence of un unexpected outcome, which she identifies as an error.
+It is currently an extensive area of research in the neuroscience community~\cite{Chavarriaga2014} PAPER NEURO.
+They can detected by signal processing and machine learning techniques~\cite{EERP-PAPER} and they are also used in Brain-Computer Interfaces (BCI) to implement or enhance artificial communication channels~\cite{Chavarriaga2014}.
 
-In recent years reinforcement learning has seen a come-back.
-This is mainly because of DeepBrain's AlphaGo who was the first to reach superhuman proficiency in challenging domains, when it won the complex game Go against several world champions.
-In 2015 AlphaGo won 5 matches against 3-times European Champion, Mr Fan Hui.
+In order to train the agent, a natural solution for this scenario comes handy from the field of Artificial Intelligence: Reinforcement Learning (RL).
+Recently, this technique has seen a come-back.
+Nonneglected is the influence of DeepBrain's AlphaGo project, which was the first to reach superhuman proficiency when it won the complex game Go against several world champions.
+By using variants of this technique, in 2015 AlphaGo won 5 matches against 3-times European Champion, Mr Fan Hui.
 AlphaGo then went on to compete against Mr Lee Sedol, winner of 18 world titles and considered to be the greatest player until then, and won 4 out of 5 matches in 2016 \cite{ALPHA-GO}.
+
+Previous research has explored the usage of RL with reward signals based on brain activity, recorded by an EEG-based BCI system during the task execution.
+The paper \cite{ROBOT-CONTROL-PAPER} has successfully demonstrated that a robot can be controlled by obtaining a reward signal from brain activity of a person which is observing the robot solving a task   OTHERS WORKS.
+In the same line, the objective of this work is to use the information extracted from brainwaves to enhance the performance of a gaming agent, replicating and extending those results.
 
@@
 
-In Section I, in Section II and Results and conclusions are exposed at the end.
+In Section \ref{section:materials} the general layout of the cognitive game experiment is described.
+Section \ref{section:calibration} outlines the processing pipeline used to detect ErrP components.
+The following Section \ref{section:classification} describes the classification algorithm and their parameters.
+Results and conclusions are exposed at the end.
 
 \section{Materials and Methods}
+\label{section:materials}
 
-The project consists of collecting signals from a person's brain while they are watching a game where the agent has knowledge of the way it's played but not how to win it.
-Hence, the agent can learn using the person's feedback to get better at the game.
-This section describes the process of obtaining the person's brain signals and how they are used to make the agent improve it's performance.
+This experiment consists of collecting signals from a person's brain while they are watching a game where the agent knows the game rules but not how to win it.
+Hence, the agent can learn the winning strategy using the person's feedback to improve its own performance.
+This section describes the process of obtaining the person's brain signals and how they are used to make the agent more efficient.
 
@@
 This process is called brainwave session.
-In order to fetch this data, subjects use a wireless digital EEG device during the experiment.
-Once the subject has the headset on, a set up procedure is executed as described in Section \ref{cognitive_experiment_details} using a program called g.NeedAcceess to do an impedance check and to visually inspect the EEG signals in order to check if it's correctly applied.
-Subsequently, the OpenVibe Acquisition Server program is launched and configured.
-This program is part of the OpenVibe platform \cite{OPEN-VIBE-PAPER} and has the responsibility of receiving the signals data from the headset and stimulus information from the game and transfers it to the OpenVibe Designer application.
+In order to fetch this data, subjects use a wireless digital EEG device during the experiment (g.Mobilab, g.Tec, Austria).
+Once the subject has the headset on, a set up procedure is executed to implement an impedance check and to visually inspect the EEG signals in order to verify if it the electrophisiological interface is generating valid data.
+Subsequently, the OpenVibe Acquisition Server, from the OpenVibe platform~\cite{OPEN-VIBE-PAPER}, is launched and configured.
+This program has the responsibility of receiving the signal data from the headset and any event information from the game and transfers it to the OpenVibe Designer application.
 After this step, the Game and the OpenVibe Designer programs are launched and configured to communicate with the previously mentioned acquisition server.
-Once the subject is ready the computer is positioned in front of them and the brainwave session starts.
-A brainwave session consists of several experiences, each of them being a game run, and it uses a pseudo-random function to determine the agent's movements.
+Once the subject is ready, a computer screen is positioned in front of her and the brainwave session starts.
+A brainwave session consists of several experiences, each one being a game run, and it uses a pseudo-random function to determine the agent's movements.
 The system is described in more detail in Section \ref{cognitive_experiment_system} and the brainwave session in Section \ref{cognitive_experiment_details}.
-Once the experimental procedure is completed, the game state information and the signals data with the stimuli channel information of each run are stored.
+Once the experimental procedure is completed, the game state information and the signal data with the game event information of each run are stored.
 For each run, the signals and stimulus information are then passed to the classification module that uses them to train the classifier.
@@
 \subsection{Cognitive Game experiment}
-This section details the game system characteristics, the brainwave session process and the retrieval and analysis of the generated data from the subjects interaction with the system.
+\label{cognitive_experiment_details}
+%This section details the game system characteristics, the brainwave session process and the retrieval and analysis of the generated data from the subjects interaction with the system.
 
 \label{cognitive_experiment_system}{
-The system consists of a $5x5$ grid where there are two lights, one representing the current position of the agent, and the other one representing the goal, shown in figure  \ref{fig:game_representation}.
+The game parsimoniously consists of a $5x5$ grid of grey circular spots with a black background.
+A blue spot indicates current position of the agent whereas a a green spot represents the goal, as shown in figure  \ref{fig:game_representation}.
 The objective of the system is for the agent to reach the goal.
-The light representing the goal remains static at the bottom-right position of the grid, while the one representing the position of the agent always starts at the upper-left position of the grid.
-The grid is represented by circular spots with a black background.
-The agent's position has a blue light, the goal position has a green light, and the rest of cells are represented with grey spots.
+The circular spot representing the goal remains static at the bottom-right position of the grid, while the one representing the position of the agent always starts at the upper-left position of the grid.
 When the agent reaches the goal, the position where the agent and the goal are located turns red, showing that the experience has ended.
-There are four possible movements that the agent can perform: it can go upwards, downwards, towards the left and towards the right, as long as the move doesn't make the agent leave the grid.
+There are four possible movements that the agent can perform: it can go upwards, downwards, towards the left and towards the right, and those moves are bounded to avoid the agent from leaving the grid.
 The movement direction is selected randomly and is executed once every 2 seconds.
 When the experience ends, there is a pause of 5 seconds before the next experience starts.
-The experience is designed for it to be evident whenever there is an error (when the agent moves away from the objective) so the subject can notice it immediately after the stimulus is presented, possibly triggering a cognitive response.
+Each time an agent moves, it is considered as a stimulus to the observational human critic.
+The experience is designed for it to be evident whenever there is an error (i.e.
+the agent moves away from the objective) so the subject can notice it immediately after the stimulus is presented, possibly triggering the expected cognitive response, which can be imprinted as an ErrP component within the EEG stream.
 
@@
 \section{Calibration}
+\label{section:calibration}
 
@@
 
-The goal of this module is to build a classifier that is able to identify whether the action taken by the agent is an error or not.
-It is developed in Python using the \href{https://mne-tools.github.io/0.11/index.html}{MNE} environment \cite{MNE-PYTHON}, which is a package designed specifically for processing EEG and MEG data, and the machine learning library \href{https://scikit-learn.org/stable/}{Scikit-Learn}.
+To aid in detecting the ErrP response, an offline processing pipeline and classifier is constructed to identify whether the action taken by the agent is an error or not.
+It is developed in Python using the \href{https://mne-tools.github.io/0.11/index.html}{MNE} platform \cite{MNE-PYTHON}, which is a package designed specifically for processing EEG and MEG data, and the machine learning library \href{https://scikit-learn.org/stable/}{Scikit-Learn}.
 
@@
 
+Enfatizar la idea de que la mejor métrica de la propia detección está dada por la propia capacidad del agente de minimizar su tarea, que hay un flujo de información que involucra la propia percepción de la persona.
+
 \subsection{Reinforcement Learning}
@@
 The collected data show that ErrP signals can in fact be classified and used to train an agent effectively.
+
+Enfatizar la idea de que la mejor métrica de la propia detección está dada por la propia capacidad del agente de minimizar su tarea, que hay un flujo de información que involucra la propia percepción de la persona.
 

### 2019-10-23 ErrP.tex
Added info about the experiment

@@
 % Do not put math or special symbols in the title.
-\title{Training an Agent on Brainwaves}
+\title{Training a Gaming Agent on Brainwaves}
 %
@@
 This information is used to make a gaming agent improve its operational performance using electroencephalography (EEG) signals as feedback of the performed task from an observational human critic.
-The idea is that subjects observing a computer game play can train the gaming agent using only electrophisiological signals called Error-related Potentials (ErrP) that can be identified from their brain signals.
-
-Error-related Potentials are signal components that can be found on EEG traces and are elicited when a subject is aware of the presence of un unexpected outcome, which she identifies as an error.
-It is currently an extensive area of research in the neuroscience community~\cite{Chavarriaga2014} PAPER NEURO.
+The idea is that subjects observing a computer game play can train the gaming agent using only signals components called Error-related Potentials (ErrP) that can be identified from their brain signals.
+These can be found on EEG traces and are elicited when a subject is aware of the presence of un unexpected outcome, which she identifies as an error.
+It is currently an extensive area of research in the neuroscience community~\cite{Holroyd2009}.
 They can detected by signal processing and machine learning techniques~\cite{EERP-PAPER} and they are also used in Brain-Computer Interfaces (BCI) to implement or enhance artificial communication channels~\cite{Chavarriaga2014}.
@@
 Recently, this technique has seen a come-back.
-Nonneglected is the influence of DeepBrain's AlphaGo project, which was the first to reach superhuman proficiency when it won the complex game Go against several world champions.
-By using variants of this technique, in 2015 AlphaGo won 5 matches against 3-times European Champion, Mr Fan Hui.
+Nonneglected is the influence of DeepBrain's AlphaGo project, which was the first to reach superhuman proficiency when it won the complex game Go against several world champions~\cite{ALPHA-GO}.
+
+%By using variants of this technique, in 2015 AlphaGo won 5 matches against 3-times European Champion, Mr Fan Hui.
 AlphaGo then went on to compete against Mr Lee Sedol, winner of 18 world titles and considered to be the greatest player until then, and won 4 out of 5 matches in 2016 \cite{ALPHA-GO}.
@@
 Previous research has explored the usage of RL with reward signals based on brain activity, recorded by an EEG-based BCI system during the task execution.
-The paper \cite{ROBOT-CONTROL-PAPER} has successfully demonstrated that a robot can be controlled by obtaining a reward signal from brain activity of a person which is observing the robot solving a task   OTHERS WORKS.
-In the same line, the objective of this work is to use the information extracted from brainwaves to enhance the performance of a gaming agent, replicating and extending those results.
+The papers \cite{ROBOT-CONTROL-PAPER,Omedes2013} have successfully demonstrated that a robot can be controlled by obtaining a reward signal from brain activity of a person which is observing the robot solving a task.
+Other approaches has used the signal as an important feedback to identify targets for robots when implementing shared-control strategies~\cite{Schiatti2018}.
+Additionally, ErrPs has been used in the context of games as an additional feedback channel that can be explored to enhance gaming experience~\cite{Plass-OudeBos2010}.
+In this same line, the objective of this work is to use the information extracted from brainwaves to enhance the performance of a gaming agent, replicating and extending those results.
 
@@
 This process is called brainwave session.
-In order to fetch this data, subjects use a wireless digital EEG device during the experiment (g.Mobilab, g.Tec, Austria).
-Once the subject has the headset on, a set up procedure is executed to implement an impedance check and to visually inspect the EEG signals in order to verify if it the electrophisiological interface is generating valid data.
-Subsequently, the OpenVibe Acquisition Server, from the OpenVibe platform~\cite{OPEN-VIBE-PAPER}, is launched and configured.
-This program has the responsibility of receiving the signal data from the headset and any event information from the game and transfers it to the OpenVibe Designer application.
-After this step, the Game and the OpenVibe Designer programs are launched and configured to communicate with the previously mentioned acquisition server.
-Once the subject is ready, a computer screen is positioned in front of her and the brainwave session starts.
+Subjects are recruited voluntarily.
+They are given a consent form with questions regarding their health (previous health issues and particular visual sensitivity), habits (sleeping hours, caffeine and alcohol consumption), as well as an approval petition to collect the required data.
+The brainwave sessions are performed with 8 subjects, 5 males and 3 females, average age 25.125 years, standard deviation 1.54 years, range of 22-28 years.
+All subjects have normal vision, are right-handed and have no history of neurological disorders.
+
+After the form is filled out, a short description of the procedure is given to the subject.
+They are only told that the objective of the agent is to reach the goal and the four movements that the agent can make.
+When this concludes, the subject is introduced to the wireless digital EEG device (g.Nautilus, g.Tec, Austria) that they have to wear during the brainwave session.
+It has eight electrodes (g.LADYbird, g.Tec, Austria) on the positions Fz, Cz, Pz, Oz, P3, P4, PO7 and PO8, identified according to the 10-20 International System, with a reference set to the right ear lobe and ground set as the AFz position.
+The electrodes contact points are adjusted applying conductive gel until the impedance values displayed by the program g.NeedAccess are within the desired range.
+This process takes between 10 and 15 minutes.
+After this step, the subject is instructed to close their eyes and the same program is used to check the live channel values so that there are no dead ones and the expected values are displayed for eye movements or muscle chewing.
+
+Once the headset is correctly applied, the OpenVibe Acquisition Server program, from the OpenVibe platform~\cite{OPEN-VIBE-PAPER}, is launched and configured with a sampling rate of 250Hz and a 50Hz notch filter is applied to filter out power line noise as well as an additional bandpass filter between 0.5Hz and 60Hz.
+Data is handled and processed with the OpenVibe Designer platform using 8 channels for the brain data (one channel per electrode) and an additional channel for the stimuli.
+When everything is connected, the subject is seated in a comfortable chair in front of a computer screen.
+The brightness of the screen is set to the maximum setting to avoid any visual inconvenience in which the subject can not distinguish the components of the game that appear on the screen.
+
+The Acquisition Server has the responsibility of receiving the signal data from the headset and any event information from the game and transfers it to the OpenVibe Designer application.
+When the subject is ready, the Game and the OpenVibe Designer programs are launched and configured to communicate with the previously mentioned acquisition server.
 A brainwave session consists of several experiences, each one being a game run, and it uses a pseudo-random function to determine the agent's movements.
-The system is described in more detail in Section \ref{cognitive_experiment_system} and the brainwave session in Section \ref{cognitive_experiment_details}.
-Once the experimental procedure is completed, the game state information and the signal data with the game event information of each run are stored.
-For each run, the signals and stimulus information are then passed to the classification module that uses them to train the classifier.
-The classification step is covered in detail in Section \ref{signal_processing_and_classification}.
+Once the experimental procedure is completed, the game state information and the signal data with the game event information of each run are saved.
+ACA For each run, the signals and stimulus information are then passed to the classification module that uses them to train the classifier.
 After this step is finished, the game movements and the trained classifier are used to update a Q-Table for each experience.
@@
 The game parsimoniously consists of a $5x5$ grid of grey circular spots with a black background.
-A blue spot indicates current position of the agent whereas a a green spot represents the goal, as shown in figure  \ref{fig:game_representation}.
+A blue spot indicates current position of the agent whereas a green spot represents the goal, as shown in figure  \ref{fig:game_representation}.
 The objective of the system is for the agent to reach the goal.
@@
 
-Many classification methods are considered.
-The best classifier is selected based on a calibration and selection procedure that is further explained in sections \ref{algorithm_calibration} and \ref{algorithm_comparison}.
-After an optimal algorithm and a configuration are selected, a classifier is trained for each subject and then epochs from their experiences are classified.
-These classifications are then used by a reinforcement learning algorithm to train the agent.
-This last algorithm is explained in detail in section \ref{q_learning_step}.
-
-This step consists of processing the collected signals in order to train a classifier that can decide whether an error potential is triggered or not.
-Firstly, the output of a brainwave session is read and a band pass filter of 0.1-20.0Hz is applied to the signal, as seen in Figure \ref{fig_psd_band_pass}.
+This step consists of offline processing the collected signals in order to train a classifier that can decide whether an error potential is triggered or not.
+Firstly, the output of a brainwave session is read and a band pass filter of 0.1-20.0Hz is applied to the signal.
 Samples that correspond to the start of an event are tagged using the data from the stimuli channel.
@@
 
-In this way, the raw data of an entire brainwave session is processed into an array of experiences where each element is an array of epochs tagged with a number specifying if the epoch corresponds to an action that made the agent move further from the goal (hit) or an action that made the agent move closer to the goal (no hit).
+In this way, the raw data of an entire brainwave session is processed into an array of experiences where each element is an array of epochs tagged with a number specifying the prediction of the classifier, i.e.
+if the epoch corresponds to an action that made the agent move further from the goal (hit) or an action that made the agent move closer to the goal (no hit).
 The ErrP is expected to be found in hits.
-To get the data ready for classification, the stimuli channel is removed in order to classify the signals using only the EEG data and a mne.decoding.vectorizer \footnote{Link to vectorizer documentation: \href{https://mne.tools/dev/generated/mne.decoding.Vectorizer.html}{https://mne.tools/dev/generated/mne.decoding.Vectorizer.html}} function is applied to transform the data into a single array sample.
+To get the data ready for classification, the stimuli channel is removed in order to classify the signals using only the EEG data.
+Each epoch is regularized using a MinMaxScaler.
+The eight channels are concatenated using the  MNE Vectorizer function to transform the data into a single array sample.
 Lastly, this data is used by the classification module as information to train and test a classifier.
 
-\section{Classification with Logistic Regression}
-For the logistic regression algorithm the parameters that are tested are $C$ and the Solver.
-The $C$ parameter is the inverse of the regularization strength.
-The values this parameter can take are 0.001, 0.01, 0.1, 1 and 10.
-The solver parameter refers to the algorithm that is used in the optimization problem, the ones that are tested are $lbfgs$ and $saga$.
-The different configurations that resulted as optimal for subjects can be seen in the apendix section \ref{apendix:algorithm_config:lr}.
+\section{Classification}
 
-Raw signals are classified using a vectorizer a minmaxscaler and finally the logistic regression classifier.
-Even tough the classification accuracy is low, the information is enough to have valid rewards that can be used to retrieve the information.
+Vectorized epochs are used in the classification step.
+Four different classification algorithms are used.
+Logistic Regression, Multi-layer Perceptron with a hidden layer of 100000 neurons, Random Forest and finally a Support Vector Classifier (i.e.
+SVM)~\cite{Lotte2018}.
+
+and finally the logistic regression classifier.  Even tough the classification accuracy is low, the information is enough to have valid rewards that can be used to retrieve the information.
+
+a classifier is trained for each subject and then epochs from their experiences are classified.
+These classifications are then used by a reinforcement learning algorithm to train the agent.
+This last algorithm is explained in detail in section \ref{q_learning_step}.
 

### 2019-10-24 ErrP.tex
Added more info

@@
 It is currently an extensive area of research in the neuroscience community~\cite{Holroyd2009}.
-They can detected by signal processing and machine learning techniques~\cite{EERP-PAPER} and they are also used in Brain-Computer Interfaces (BCI) to implement or enhance artificial communication channels~\cite{Chavarriaga2014}.
+They can be detected by signal processing and machine learning techniques~\cite{EERP-PAPER} and they are also used in Brain-Computer Interfaces (BCI) to implement or enhance artificial communication channels~\cite{Chavarriaga2014}.
 
@@
 The papers \cite{ROBOT-CONTROL-PAPER,Omedes2013} have successfully demonstrated that a robot can be controlled by obtaining a reward signal from brain activity of a person which is observing the robot solving a task.
-Other approaches has used the signal as an important feedback to identify targets for robots when implementing shared-control strategies~\cite{Schiatti2018}.
-Additionally, ErrPs has been used in the context of games as an additional feedback channel that can be explored to enhance gaming experience~\cite{Plass-OudeBos2010}.
+Other approaches have used the signal as an important feedback to identify targets for robots when implementing shared-control strategies~\cite{Schiatti2018}.
+Additionally, ErrPs have been used as well in the context of games as an additional feedback channel that can be explored to enhance gaming experience~\cite{Plass-OudeBos2010}.
 In this same line, the objective of this work is to use the information extracted from brainwaves to enhance the performance of a gaming agent, replicating and extending those results.
@@
 Data is handled and processed with the OpenVibe Designer platform using 8 channels for the brain data (one channel per electrode) and an additional channel for the stimuli.
-When everything is connected, the subject is seated in a comfortable chair in front of a computer screen.
+After everything is connected, the subject seats in a comfortable chair in front of a computer screen.
 The brightness of the screen is set to the maximum setting to avoid any visual inconvenience in which the subject can not distinguish the components of the game that appear on the screen.
 
-The Acquisition Server has the responsibility of receiving the signal data from the headset and any event information from the game and transfers it to the OpenVibe Designer application.
+The Acquisition Server has the responsibility of receiving and synchronizing the signal data from the headset and any event information from the game and transfers it to the OpenVibe Designer application.
 When the subject is ready, the Game and the OpenVibe Designer programs are launched and configured to communicate with the previously mentioned acquisition server.
 A brainwave session consists of several experiences, each one being a game run, and it uses a pseudo-random function to determine the agent's movements.
-Once the experimental procedure is completed, the game state information and the signal data with the game event information of each run are saved.
-ACA For each run, the signals and stimulus information are then passed to the classification module that uses them to train the classifier.
+At the end, the game state information and the signal data with the game event information of each run are saved for offline processing.
+
+%ACA For each run, the signals and stimulus information are then passed to the classification module that uses them to train the classifier.
 After this step is finished, the game movements and the trained classifier are used to update a Q-Table for each experience.
@@
 The movement direction is selected randomly and is executed once every 2 seconds.
-When the experience ends, there is a pause of 5 seconds before the next experience starts.
+At the end, there is a pause of 5 seconds before the next experience starts.
 Each time an agent moves, it is considered as a stimulus to the observational human critic.
@@
 
-\section{Calibration}
-\label{section:calibration}
+%\section{Calibration}
+%\label{section:calibration}
 
-The first step in order to be able to find ErrP signals is to choose the most efficient algorithm, and the proper calibration.
+%The first step in order to be able to find ErrP signals is to choose the most efficient algorithm, and the proper calibration.
 In order to do this different parameters are tested for a set of algorithms and for each individual subject.
@@
 
-\section{Signal Processing and Segmentation}
+\section{Signal Processing, Segmentation and Classification}
 
 To aid in detecting the ErrP response, an offline processing pipeline and classifier is constructed to identify whether the action taken by the agent is an error or not.
-It is developed in Python using the \href{https://mne-tools.github.io/0.11/index.html}{MNE} platform \cite{MNE-PYTHON}, which is a package designed specifically for processing EEG and MEG data, and the machine learning library \href{https://scikit-learn.org/stable/}{Scikit-Learn}.
+It is developed in Python using the \href{https://mne-tools.github.io/0.11/index.html}{MNE} platform \cite{MNE-PYTHON}, which is a package designed specifically for processing EEG and Magnetoencephalography (MEG) data, and based on top of the machine learning library \href{https://scikit-learn.org/stable/}{Scikit-Learn}.
 
@@
 
-\section{Classification}
-
-Vectorized epochs are used in the classification step.
+Vectorized epochs are used in the final classification step.
 Four different classification algorithms are used.
@@
 
-and finally the logistic regression classifier.  Even tough the classification accuracy is low, the information is enough to have valid rewards that can be used to retrieve the information.
+%and finally the logistic regression classifier.  Even tough the classification accuracy is low, the information is enough to have valid rewards that can be used to retrieve the information.
 
-a classifier is trained for each subject and then epochs from their experiences are classified.
+%a classifier is trained for each subject and then epochs from their experiences are classified.
 These classifications are then used by a reinforcement learning algorithm to train the agent.
@@
 The accuracy of this rewards depends on the performance of the classifier.
-This reward file is used by the Q-Learning algorithm to improve its performance, as detailed in section \ref{q_learning_step}.
+This reward file is used by the a variant of a Reinforcement Learning algorithm called Q-Learning algorithm.
 
@@
 Gym is a toolkit for developing and comparing reinforcement learning algorithms.
-It makes no assumptions about the structure of an agent, and is compatible with any numerical computation library, such as TensorFlow or Theano.
+It makes no assumptions about the structure of an agent, and is compatible with any numerical computation library, such as TensorFlow or Theano (cites).
 
@@
 This implies that the reward is determined by the subject's brain activity.
-This is covered in further detail in \ref{q_learning_step_env}.
 
@@
 
-The reward function is calculated based on the current distance to the goal, if it has increased compared to the previous step then the rewards is negative, if not it returns zero.
-In order to test how the Q-Table is trained when the accuracy is not perfect the reward function doesn't always return the correct reward.
-It calculates a random number between 0 and 1, and if it is larger than the accuracy then it will return 0 even if it should return -1 as the reward.
-
-The reward function is described in algorithm \ref{algorithm:env_rewards}.
-
-\begin{algorithm}
-\SetAlgoLined
-\DontPrintSemicolon
-$reward \leftarrow 0$\\
-  \uIf{currentDistanceToGoal > previousDistanceToGoal}{
-    $reward \leftarrow -1$ \;
-  }
-  \uElseIf{random.uniform(0, 1) < accuracy}{
-    return reward \;
-  }
-  \Else{
-    return 0 \;
-  }
-\label{algorithm:env_rewards}
-\caption{Reward Calculation for $ChaseEnv$}
-\end{algorithm}
-}
-}
-
 \section{Results}
@@
 \textbf{Average steps to goal}
-Figure \ref{fig:avg_steps} shows the average amount of steps it takes to reach the goal as the Q-Table is progressively trained using the reward information obtained for each subject.
+Figure \ref{fig:avg_steps} shows the average amount of steps it takes to reach the goal as the Q-Table is progressively trained using the reward information obtained from the tested experiences for each subject.
 Each point corresponds to the average amount of steps it takes for the agent to reach the goal for a specific Q-Table in 200 iterations.
 The first point represents the amount of steps it takes to reach the goal for a Q-Table that hasn't been trained at all, where movements are decided randomly.
-The next point corresponds to the amount of steps it takes to reach the goal using a Q-Table trained with one experience, and so on.
+The next point corresponds to the amount of steps it takes to reach the goal using a policy derived from the Q-Table trained with one experience, and so on.
 

### 2019-10-25 ErrP.tex
Many changes

@@
 
-In order to train the agent, a natural solution for this scenario comes handy from the field of Artificial Intelligence: Reinforcement Learning (RL).
+In order to train the agent, a natural solution for this scenario comes handy from the field of Artificial Intelligence: Reinforcement Learning (RL)~\cite{Santos1999}.
 Recently, this technique has seen a come-back.
@@
 To aid in detecting the ErrP response, an offline processing pipeline and classifier is constructed to identify whether the action taken by the agent is an error or not.
-It is developed in Python using the \href{https://mne-tools.github.io/0.11/index.html}{MNE} platform \cite{MNE-PYTHON}, which is a package designed specifically for processing EEG and Magnetoencephalography (MEG) data, and based on top of the machine learning library \href{https://scikit-learn.org/stable/}{Scikit-Learn}.
+It is developed in Python using the MNE platform \cite{MNE-PYTHON}, which is a package designed specifically for processing EEG and Magnetoencephalography (MEG) data, and based on top of the machine learning library Scikit-Learn~\cite{scikit-learn}.
 
@@
 To get the data ready for classification, the stimuli channel is removed in order to classify the signals using only the EEG data.
-Each epoch is regularized using a MinMaxScaler.
+Each epoch is regularized using a MinMaxScaler, i.e.
+substracting the minimun value in the feature and dividing by the signal peak-to-peak amplitude.
 The eight channels are concatenated using the  MNE Vectorizer function to transform the data into a single array sample.
@@
 This last algorithm is explained in detail in section \ref{q_learning_step}.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[scale=0.4]{Images/algorithm_calibration/LR_calib.png}
-    \caption{Logistic Regression Algorithm Calibration}
-    \label{diag:algorithm_calibration:lr}
-\end{figure}
 
@@
 \label{q_learning_step}
-A Q-Learning algorithm is used to train the agent.
-It is developed in Python and uses the \href{https://gym.openai.com}{OpenAI Gym} toolkit.
+
+Q-Learning~\cite{Watkins1992} is a form of model-free reinforcement learning algorithm where an agent tries an action at a particular state and evaluate its consequences in terms of the reward or penalty it receives.
+In order to represent rewards, a matrix is used, where rows correspond to all the possible states, whereas columns represent all possible actions.
+The reward for an action given a state is the value that can be found on the corresponding row and column.
+This matrix is known as a Q-Table.
+The algorithm proceeds by randomly choosing what action to do and updating iteratively the Q-Table by the following equation
+
+\begin{equation}
+    Q(s,a) \leftarrow Q(s,a) + \alpha[r+\gamma* Max(s, a)-Q(s, a) ]
+    \label{equ:update_q_table}
+\end{equation}
+
+\noindent where $s$ is the current state, $a$ is the action, $\alpha$ represents the learning rate between $0$ exploration and $1$ explotation and $\gamma$ represents the discount rate, a value between 0 and 1 that determines the importance of long term results versus immediate rewards.
+Once the environment has been extensively explored and the Q-Table has been obtained, the action chosen is the one that maximizes the expected reward according to the Q-Table matrix.
+
+For this experiment, the algorithm is developed in Python and uses the OpenAI Gym toolkit~\cite{openai}.
 Gym is a toolkit for developing and comparing reinforcement learning algorithms.
-It makes no assumptions about the structure of an agent, and is compatible with any numerical computation library, such as TensorFlow or Theano (cites).
+It makes no assumptions about the structure of an agent, and is compatible with any numerical computation library, such as TensorFlow or Theano~\cite{tensorflow2015-whitepaper}.
 
-\subsubsection{Algorithm implementation}{
+\subsection{Agent Learning}
 \label{q_learning_step_alg}
@@
 
-While using the previously mentioned step function, the Q-Table is updated in each iteration. This is done following the Equation \ref{equ:update_q_table}.
-
-\begin{equation}
-    Q(s,a) \leftarrow Q(s,a) + \alpha[r+\gamma* Max(s, a)-Q(s, a) ]
-    \label{equ:update_q_table}
-\end{equation}
-
-After the algorithm finishes iterating through all the training episodes, the Q-Table is saved. Each experience is one $trainingEpisode$.
+While using the previously mentioned step function, the Q-Table is updated in each iteration.
+This is done following the Equation \ref{equ:update_q_table}.
+After the algorithm finishes iterating through all the training episodes, the Q-Table is saved.
 
@@
 
-\subsection{Reinforcement Learning}
+Figure~\ref{fig:classifiers} show the binary classification accuracy obtained for the eight subjects for the four different classification algorithms using a 10-fold cross validation procedure.
+The best overall performance is obtained using Logistic Regression.
 
-\textbf{Average steps to goal}
-Figure \ref{fig:avg_steps} shows the average amount of steps it takes to reach the goal as the Q-Table is progressively trained using the reward information obtained from the tested experiences for each subject.
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.4]{Images/algorithm_calibration/Total_calib.png}
+    \caption{Binary Classification Accuracy using different classifiers while recognizing ErrP potentials for the eight subjects.}
+    \label{fig:classifiers}
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale=0.4]{Images/algorithm_calibration/LR_calib.png}
+    \caption{Binary Classification Accuracy using Logistic Regression for the eight subjects.}
+    \label{fig:logisticregression}
+\end{figure}
+
+On the other hand, Figure \ref{fig:avg_steps} shows for each subject the average amount of steps it takes to reach the goal as the Q-Table is progressively trained using the reward information obtained from their tested experiences.
 Each point corresponds to the average amount of steps it takes for the agent to reach the goal for a specific Q-Table in 200 iterations.
 The first point represents the amount of steps it takes to reach the goal for a Q-Table that hasn't been trained at all, where movements are decided randomly.
-The next point corresponds to the amount of steps it takes to reach the goal using a policy derived from the Q-Table trained with one experience, and so on.
-
-The results show that as the Q-Table is progressively trained the average amount of steps decreases, meaning that the agent learns.
-However, the rate at which it learns varies per subject, certain subjects have more effective experiments than others, for example results for subject 1 (fig \ref{fig:avg_steps_1}) show faster learning than those of subject 8 (fig \ref{fig:avg_steps_8}).
-
-In the case for subject 5 and 6, the reward information obtained from the brainwaves is not enough to train the agent effectively.
-Figures \ref{fig:avg_steps_5} and \ref{fig:avg_steps_6} show no apparent learning, as the amount of steps to reach the goal doesn't decrease when trained.
-Both subjects have less recorded data from the sessions in comparison to the rest of the subjects.
-In particular, subject 5 has less recorded experiences, so it is respective graphic shows the amount of steps for an empty Q-Table and for a Q-Table trained with only one experience.
-These results are consistent with fig.
-\ref{fig:roc:manuel} and fig.
-\ref{fig:roc:marta}, which show that the signal classification for these subjects hasn't been particularly successful.
-The average steps result for these subject are similar to that of fig.
-\ref{fig:roc:noise} which is constructed from noise, so the generated Q-Table would be similar to one generated with noise.
+The next point corresponds to the amount of steps it takes to reach the goal using a policy derived from a Q-Table trained with one experience, and so on.
 
@@
  \includegraphics[scale=0.2]{Images/Average_steps/juan.png} 
-\caption{Initial state of the grid.}
-\label{fig:subim1}
-\end{subfigure}
-\begin{subfigure}{0.5\textwidth}
   \includegraphics[scale=0.2]{Images/Average_steps/manu.png} 
@@
   \includegraphics[scale=0.2]{Images/Average_steps/santiago.png} 
-\caption{Final state of the grid.}
-\label{fig:subim2}
 \end{subfigure}
-\caption{Grid system representation used in cognitive experience.}
-\label{fig:game_representation}
+\caption{Average number of steps for the agent when trained with experiences from subjects 1,2,3,4,5,6,7 and 8.}
+\label{fig:avg_steps}
 \end{figure}
+
+The results show that as the Q-Table is progressively trained the average amount of steps decreases, meaning that the agent learns.
+However, the rate at which it learns varies per subject, certain subjects have more effective experiments than others, for example results for subject 1 (fig \ref{fig:avg_steps} A) show faster learning than those of subject 8 (fig \ref{fig:avg_steps_8}).
+
+In the case for subject 5 and 6, the reward information obtained from the brainwaves is not enough to train the agent effectively.
+Figures \ref{fig:avg_steps_5} and \ref{fig:avg_steps_6} show no apparent learning, as the amount of steps to reach the goal doesn't decrease when trained.
+These results are also consistent with the ROC curves, shown on Figures~\ref{fig:subject5roc,fig:subject6roc} obtained for both Subjecs, where the area under the curve are close to chance level.
+Both subjects have less recorded data from the sessions in comparison to the rest of the subjects.
+
+\begin{figure}[h!]
+\begin{subfigure}{0.25\textwidth}
+    \centering
+    \includegraphics[scale=0.2]{Images/Classification_test/roc_manuel.png}
+    \caption{ROC Curve for Subject 5.}
+    \label{fig:subject5roc}
+\end{subfigure}
+\begin{subfigure}{0.25\textwidth}
+    \centering
+    \includegraphics[scale=0.2]{Images/Classification_test/roc_marta.png}
+    \caption{ROC Curve for Subject 5.}
+    \label{fig:subject6roc}
+\end{subfigure}
+\end{figure}
+
+%These results are consistent with fig. \ref{fig:roc:manuel} and fig. \ref{fig:roc:marta}, which show that the signal classification for these subjects hasn't been particularly successful.
+
+Figure~\ref{fig:avg_steps_noise} show the result of an agent successively trained with experiences obtained from a brainwave session, generated with sham signals.
+In this case, random EEG signals were generated using OpenVibe for all channels, as if they were generated from a human observer.
+As it can be seen, the agent learns nothing, and regardless of the amount of experiences that are used to train the Q-Table, the number of steps required to reach the goal does not decrease.
+This pattern is also obtained when the experiences from Subjects 5 and 6 are used, showing that the amount reward labeling implemented by the trained classifier for those subjects worked like a random classifier.
 
@@
 \includegraphics[scale=0.4]{Images/Average_steps/noise.png}
-\caption{Average steps using Q-Table trained with noise.}
+\caption{Average steps using Q-Table trained with a noisy signal.}
 \label{fig:avg_steps_noise}
@@
 
-\begin{figure}[h]
+It is a known fact in BCI that EEG signals have high inter-subject variability.
+This is evidenced in Figure~\ref{fig:transferlearning} were the agent training is performed by using a classifier trained with experiences from one subject,  but tagging the experiences from a different subject using the predicted classification.
+As the agent learns nothing, not performance gain is evidenced.
+
+\begin{figure}[h!]
+\begin{subfigure}{0.25\textwidth}
     \centering
-    \includegraphics[scale=0.4]{Images/algorithm_calibration/Total_calib.png}
-    \caption{Score Obtained With The Optimal Calibration Per Algorithm Per Subject}
-    \label{diag:algorithm_calibration:subject_calib}
+    \includegraphics[scale=0.2]{Images/Average_steps/marta_santiago.png}
+    \caption{Average steps using Q-table trained with experiences from subject 8 classified with a classifier trained with data from subject 6.}
+    \label{fig:subject5roc}
+\end{subfigure}
+\begin{subfigure}{0.25\textwidth}
+    \centering
+    \includegraphics[scale=0.2]{Images/Average_steps/alex_jose.png}
+    \caption{Average steps using Q-table trained with experiences from subject 1 classified with a classifier trained with data from subject 3}
+    \label{fig:subject6roc}
+\end{subfigure}
+\label{fig:transferlearning}
+\end{figure}
+
+Finally, Figure~\ref{fig:avg_steps_all} show the result of training an agent with accumulative experiences from subjects 1,2,3,4,7, and 8.
+
+\begin{figure}[h!]
+\centering
+\includegraphics[scale=0.4]{Images/Average_steps/all.png}
+\caption{Average steps using Q-Table trained with one experience per subject.}
+\label{fig:avg_steps_all}
 \end{figure}
@@
 \section{Conclusion}
-The present research work set out to validate if ErrP signals could be used to train an agent using reinforcement learning.
+The present research work aims to reproduce similar results that states whether ErrP signals could be used to train a gaming agent using reinforcement learning.
 The collected data show that ErrP signals can in fact be classified and used to train an agent effectively.
 
-Enfatizar la idea de que la mejor métrica de la propia detección está dada por la propia capacidad del agente de minimizar su tarea, que hay un flujo de información que involucra la propia percepción de la persona.
+This work aimed to keep the system as simple as possible, emphasizing the flow of information from the subjective error perception of the human critic, through the reward generation using the signal processing and classification pipeline, and finally the updating of the Q-Table to enhance the performance of the gaming agent.
 
-When classifying, the better performing classifier is Logistic Regression.
+%Enfatizar la idea de que la mejor métrica de la propia detección está dada por la propia capacidad del agente de minimizar su tarea, que hay un flujo de información que involucra la propia percepción de la persona.
+
+While classifying, the better performing classifier is Logistic Regression.
 One important aspect of the classification results is the low percentage of false positives, meaning that it is not common that the agent learns that an action is wrong when in fact it is an action that takes it closer to the goal.
@@
 
-Finally, this research verifies that brain signals can be used as an interface between human and computer enabling the control of the system without explicit input from the user.
+Finally, this research verifies that brain signals can be used as an interface between human and a gaming computer enabling an alternative communication with the system without explicit input from the user.
 

### 2019-10-28 ErrP.tex
Subo un montón de datos de versiones

@@
 \begin{abstract}
-The field of Brain Computer Interfaces has seen a bloom in the past few years.
+The field of Brain Computer Interfaces (BCI) has seen a bloom in the past few years.
 One of its applications is the training of systems using signals originated from the human brain.
@@
 Reinforcement Learning (RL) is an approach to machine learning where an agent tries to maximize the reward obtained while interacting with an unknown environment.
-This work follow this path by detecting the ErrP potential from subjects witnessing an agent playing the game and improving the agent behavior using RL and obtaining rewards from the subjects.
+How much a gaming agent can be trained by the rewards obtained from human critics that watch their actions ?
+This work implements a parsimonious application of this idea, to train an agent to solve a simple game using exclusively the information obtained from human critics that observe how to agent plays.
+
 \end{abstract}
@@
 In order to train the agent, a natural solution for this scenario comes handy from the field of Artificial Intelligence: Reinforcement Learning (RL)~\cite{Santos1999}.
+An algorithmic learning strategy can be established by mimicking how biological agents learn from the environment by exploring it and getting feedback, which can be a negative or positive reinforcement.
+This strategy aims to maximize the amount of positive rewards while keeping low the number of negative feedback.
+This allow to pose the learning problem as a mere stochastic optimization strategy~\cite{sutton2018reinforcement}.
 Recently, this technique has seen a come-back.
@@
 Other approaches have used the signal as an important feedback to identify targets for robots when implementing shared-control strategies~\cite{Schiatti2018}.
-Additionally, ErrPs have been used as well in the context of games as an additional feedback channel that can be explored to enhance gaming experience~\cite{Plass-OudeBos2010}.
+Additionally, ErrPs have been used as well in the context of games as an additional feedback channel that can be explored to enhance gaming experience~\cite{Plass-OudeBos2010,kober2018bci}.
 In this same line, the objective of this work is to use the information extracted from brainwaves to enhance the performance of a gaming agent, replicating and extending those results.
@@
 Section \ref{section:calibration} outlines the processing pipeline used to detect ErrP components.
-The following Section \ref{section:classification} describes the classification algorithm and their parameters.
-Results and conclusions are exposed at the end.
+The following Section \ref{learning} describes the agent learning phase.
+Results \ref{results} and conclusions \ref{conclusions} are exposed at the last two sections.
 
@@
 It has eight electrodes (g.LADYbird, g.Tec, Austria) on the positions Fz, Cz, Pz, Oz, P3, P4, PO7 and PO8, identified according to the 10-20 International System, with a reference set to the right ear lobe and ground set as the AFz position.
-The electrodes contact points are adjusted applying conductive gel until the impedance values displayed by the program g.NeedAccess are within the desired range.
+The electrodes contact points are adjusted applying conductive gel until the impedance values displayed by the program g.NeedAccess (g.Tec, Austria) are within the desired range.
 This process takes between 10 and 15 minutes.
@@
 
-Once the headset is correctly applied, the OpenVibe Acquisition Server program, from the OpenVibe platform~\cite{OPEN-VIBE-PAPER}, is launched and configured with a sampling rate of 250Hz and a 50Hz notch filter is applied to filter out power line noise as well as an additional bandpass filter between 0.5Hz and 60Hz.
-Data is handled and processed with the OpenVibe Designer platform using 8 channels for the brain data (one channel per electrode) and an additional channel for the stimuli.
+Once the headset is correctly applied, the OpenVibe Acquisition Server program, from the OpenVibe platform~\cite{OPEN-VIBE-PAPER}, is launched and configured with a sampling rate of $250$ Hz.
+A $50$ Hz notch filter is applied to filter out power line.
+An additional bandpass filter between $0.5$ Hz and $60$ Hz is applied as well.
+Data is handled and processed with the OpenVibe Designer, from the same platform, using 8 channels for the brain data (one channel per electrode) and an additional channel for the stimuli.
 After everything is connected, the subject seats in a comfortable chair in front of a computer screen.
@@
 When the subject is ready, the Game and the OpenVibe Designer programs are launched and configured to communicate with the previously mentioned acquisition server.
-A brainwave session consists of several experiences, each one being a game run, and it uses a pseudo-random function to determine the agent's movements.
+A brainwave session consists of several experiences, each one being a game run.
 At the end, the game state information and the signal data with the game event information of each run are saved for offline processing.
@@
 The game parsimoniously consists of a $5x5$ grid of grey circular spots with a black background.
-A blue spot indicates current position of the agent whereas a green spot represents the goal, as shown in figure  \ref{fig:game_representation}.
+A blue spot indicates current position of the agent whereas a green spot represents the goal, as shown in Figure  \ref{fig:game_representation}.
 The objective of the system is for the agent to reach the goal.
@@
 At the end, there is a pause of 5 seconds before the next experience starts.
-Each time an agent moves, it is considered as a stimulus to the observational human critic.
+Each time an agent moves, the Game Manager program sends an event marker to the Acquisition Server.
+This is considered as a stimulus to the observational human critic.
 The experience is designed for it to be evident whenever there is an error (i.e.
@@
 \begin{subfigure}{0.5\textwidth}
-\includegraphics[width=0.9\linewidth,scale=0.9]{Images/grid_initial_state.png} 
-\caption{Initial state of the grid.}
-\label{fig:subim1}
+\centering 
+\includegraphics[scale=0.2]{Images/grid_initial_state.png}
+\includegraphics[scale=0.2]{Images/grid_end_state.png}
 \end{subfigure}
-\begin{subfigure}{0.5\textwidth}
-\includegraphics[width=0.9\linewidth,scale=0.9]{Images/grid_end_state.png}
-\caption{Final state of the grid.}
-\label{fig:subim2}
-\end{subfigure}
-\caption{Grid system representation used in cognitive experience.}
+\centering 
+\caption{Grid system representation used in the Cognitive Game Experience.}
 \label{fig:game_representation}
 \end{figure}
-}
 
@@
 \section{Signal Processing, Segmentation and Classification}
+\label{section:calibration}
 
@@
 This step consists of offline processing the collected signals in order to train a classifier that can decide whether an error potential is triggered or not.
-Firstly, the output of a brainwave session is read and a band pass filter of 0.1-20.0Hz is applied to the signal.
+Firstly, the output of a brainwave session is read and an additional band pass filter of 0.1-20.0Hz is applied to the signal.
 Samples that correspond to the start of an event are tagged using the data from the stimuli channel.
@@
 Epochs consist of all the sample points that take place between the start of the event and 2 seconds later (time for each action to take place), resulting in 500 samples per channel, as the sample frequency is 250 Hz.
+Thus, each epoch is composed of a matrix $500$ x $8$.
 
@@
 substracting the minimun value in the feature and dividing by the signal peak-to-peak amplitude.
-The eight channels are concatenated using the  MNE Vectorizer function to transform the data into a single array sample.
+The eight channels are concatenated using the  MNE Vectorizer function to transform the data matrix into a single array sample.
 Lastly, this data is used by the classification module as information to train and test a classifier.
@@
 \section{Reinforcement Learning}
+\label{learning}
 
@@
 These files contain an ordered list of the states of the game throughout an experience.
-With this file and the classification of the test data of an experience, a reward file is submitted.
+With this file and the classification of the test data of an experience, a reward file is composed.
 This file specifies a reward for each movement in the game, based on the classification of the event that corresponds to that movement.
@@
 This matrix is known as a Q-Table.
-The algorithm proceeds by randomly choosing what action to do and updating iteratively the Q-Table by the following equation
+The algorithm proceeds by randomly choosing what action to do and updating iteratively the Q-Table based on the received reward $r$ by the following equation
 
@@
 This is done following the Equation \ref{equ:update_q_table}.
-After the algorithm finishes iterating through all the training episodes, the Q-Table is saved.
+After the algorithm finishes iterating through all the training episodes, the Q-Table is stored to test the performance of the agent.
 
 \section{Results}
-
-Enfatizar la idea de que la mejor métrica de la propia detección está dada por la propia capacidad del agente de minimizar su tarea, que hay un flujo de información que involucra la propia percepción de la persona.
+\label{results}
 
@@
 
-On the other hand, Figure \ref{fig:avg_steps} shows for each subject the average amount of steps it takes to reach the goal as the Q-Table is progressively trained using the reward information obtained from their tested experiences.
+On the other hand, Figure \ref{fig:avg_steps} shows for each subject the average amount of steps the agent takes to reach the goal as the Q-Table is progressively trained using the reward information obtained from their tested experiences.
 Each point corresponds to the average amount of steps it takes for the agent to reach the goal for a specific Q-Table in 200 iterations.
@@
 \end{subfigure}
-\caption{Average number of steps for the agent when trained with experiences from subjects 1,2,3,4,5,6,7 and 8.}
+\caption{Average number of steps for the agent when trained with experiences from subjects 1-8.}
 \label{fig:avg_steps}
@@
 The results show that as the Q-Table is progressively trained the average amount of steps decreases, meaning that the agent learns.
-However, the rate at which it learns varies per subject, certain subjects have more effective experiments than others, for example results for subject 1 (fig \ref{fig:avg_steps} A) show faster learning than those of subject 8 (fig \ref{fig:avg_steps_8}).
+However, the rate at which it learns varies per subject, certain subjects have more effective experiments than others, for example results for subject 1 (fig \ref{fig:avg_steps} A) show faster learning than those of subject 8 (fig \ref{fig:avg_steps} H).
 
 In the case for subject 5 and 6, the reward information obtained from the brainwaves is not enough to train the agent effectively.
-Figures \ref{fig:avg_steps_5} and \ref{fig:avg_steps_6} show no apparent learning, as the amount of steps to reach the goal doesn't decrease when trained.
-These results are also consistent with the ROC curves, shown on Figures~\ref{fig:subject5roc,fig:subject6roc} obtained for both Subjecs, where the area under the curve are close to chance level.
+Figures \ref{fig:avg_steps} E and \ref{fig:avg_steps} F show no apparent learning, as the amount of steps to reach the goal doesn't decrease when trained.
+These results are also consistent with the ROC curves, shown on Figures~\ref{fig:subject5roc} and~\ref{fig:subject6roc} obtained for both Subjecs, where the area under the curve are close to chance level.
 Both subjects have less recorded data from the sessions in comparison to the rest of the subjects.
@@
 As it can be seen, the agent learns nothing, and regardless of the amount of experiences that are used to train the Q-Table, the number of steps required to reach the goal does not decrease.
-This pattern is also obtained when the experiences from Subjects 5 and 6 are used, showing that the amount reward labeling implemented by the trained classifier for those subjects worked like a random classifier.
+This pattern is also obtained when the experiences from Subjects 5 and 6 are used, showing that the reward labeling predicted by the trained classifier for those subjects worked like a random classifier.
 
@@
 
-It is a known fact in BCI that EEG signals have high inter-subject variability.
-This is evidenced in Figure~\ref{fig:transferlearning} were the agent training is performed by using a classifier trained with experiences from one subject,  but tagging the experiences from a different subject using the predicted classification.
-As the agent learns nothing, not performance gain is evidenced.
+Electroencephalographic signals have high inter-subject variability~\cite{Chavarriaga2014}.
+This is evidenced in Figure~\ref{fig:transferlearning} where the agent training is performed by using a classifier trained with experiences from one subject,  but tagging the experiences from a different subject using the predicted classification.
+Not performance gain is evidenced, the agents learn nothing which implies that the reward information is useless.
+
+%\begin{figure*}[ht!]
+%    \centering
+%    \begin{subfigure}[t]{0.5\textwidth}
+%        \centering
+%        \includegraphics[height=1.2in]{Images/Average_steps/marta_santiago.png}
+%        \caption{Lorem ipsum}
+%    \end{subfigure}%
+%    ~ 
+%    \begin{subfigure}[t]{0.5\textwidth}
+%        \centering
+%        \includegraphics[height=1.2in]{Images/Average_steps/alex_jose.png}
+%        \caption{Lorem ipsum, lorem ipsum,Lorem ipsum, lorem ipsum,Lorem ipsum}
+%    \end{subfigure}
+%    \caption{Caption place holder}
+%\end{figure*}
 
 \begin{figure}[h!]
-\begin{subfigure}{0.25\textwidth}
-    \centering
+\begin{subfigure}{0.5\textwidth}
 \includegraphics[scale=0.2]{Images/Average_steps/marta_santiago.png}
-    \caption{Average steps using Q-table trained with experiences from subject 8 classified with a classifier trained with data from subject 6.}
-    \label{fig:subject5roc}
+\includegraphics[scale=0.2]{Images/Average_steps/alex_jose.png}
 \end{subfigure}
-\begin{subfigure}{0.25\textwidth}
-    \centering
-    \includegraphics[scale=0.2]{Images/Average_steps/alex_jose.png}
-    \caption{Average steps using Q-table trained with experiences from subject 1 classified with a classifier trained with data from subject 3}
-    \label{fig:subject6roc}
-\end{subfigure}
+\caption{Average steps using Q-table trained with experiences from subject 8 classified with a classifier trained with data from subject 6.
+Average steps using Q-table trained with experiences from subject 1 classified with a classifier trained with data from subject 3.}
 \label{fig:transferlearning}
@@
 \includegraphics[scale=0.4]{Images/Average_steps/all.png}
-\caption{Average steps using Q-Table trained with one experience per subject.}
+\caption{Average steps using Q-Table trained with 6 experiences from different subjects.}
 \label{fig:avg_steps_all}
@@
 \section{Conclusion}
+\label{conclusions}
+
+%Enfatizar la idea de que la mejor métrica de la propia detección está dada por la propia capacidad del agente de minimizar su tarea, que hay un flujo de información que involucra la propia percepción de la persona.
+
 The present research work aims to reproduce similar results that states whether ErrP signals could be used to train a gaming agent using reinforcement learning.
@@
 
-This work aimed to keep the system as simple as possible, emphasizing the flow of information from the subjective error perception of the human critic, through the reward generation using the signal processing and classification pipeline, and finally the updating of the Q-Table to enhance the performance of the gaming agent.
+This work aims to keep the system as simple as possible, emphasizing the flow of information from the subjective error perception of the human critic, through the reward generation using the signal processing and classification pipeline, and finally the updating of the Q-Table to enhance the performance of the gaming agent.
 
@@
 Once ErrP signals are identified they can be used to train a reinforcement learning algorithm.
-However, this can only be achieved by generating a specific classifier for each subject and using it for giving rewards for the corresponding subjects.
-Results show that training a classifier with data of one subject, but using it to classify the events of experiences of another subject does not lead to an improvement on the performance of the agent, concluding that the experiment is not suited for transfer learning.
-Despite that, the rewards generated from different subjects can be used to train the same Q-Table to improve its performance.
-
 Brainwave sessions have a low amount of experiences in order to reduce fatigue from the subjects.
@@
 This can also be achieved designing a bigger game system that generates more samples with every session.
+
+At the same time, the training depends strictly on the subject's data that was used to train it.
+Results show that training a classifier with data of one subject, but using it to classify the events of experiences of another subject does not lead to an improvement on the performance of the agent.
+Despite that, the rewards generated from different subjects can be used to train the same Q-Table to improve its performance, which may lead to strategies where the overall performance is improved based on the information on different human critics at the same time.
+
+One additional aspect to remark is the robustness of RL implementation.
+General accuracy is in general low.
+Even with that lower accuracy values, the RL algorithm was able to extract meaningful information from rewards files that were pointing to improve the agent performance.
+The complexity of the game should be tackled to allow at least the possibility that the target position be dynamically especified.
+In that case the agent would start to learn to follow the target, instead of learning to go to a specific static destination (which is actually learning now).
 

### 2019-10-29 ErrP.tex
Agrego mas toques
Subo una version bastante cerrada.

@@
 % (should never be an issue)
-\IEEEPARstart{T}{he} effectiveness of today's human–machine interaction and artificial intelligence is limited by a communication bottleneck as humans are required to translate high-level concepts into a machine-mandated sequence of instructions \cite{CURSOR-CONTROL-PAPER}.
+\IEEEPARstart{T}{he} effectiveness of today's human–machine interaction and artificial intelligence is limited by a communication bottleneck as humans are required to translate high-level concepts into a machine-mandated sequence of instructions~\cite{CURSOR-CONTROL-PAPER}.
 This work tackles this problem by exploring the use of brain signals as an interface between human and computer, trying to overcome this limitation by providing information to the system without explicit communication from the user.
@@
 
-In order to train the agent, a natural solution for this scenario comes handy from the field of Artificial Intelligence: Reinforcement Learning (RL)~\cite{Santos1999}.
-An algorithmic learning strategy can be established by mimicking how biological agents learn from the environment by exploring it and getting feedback, which can be a negative or positive reinforcement.
+In order to train the agent, Reinforcement Learning (RL)~\cite{Santos1999} comes as natural solution for this scenario from the field of Artificial Intelligence.
+RL is an algorithmic learning strategy that can be established by mimicking how biological agents learn from the environment by exploring it and getting feedback rewards, either negative or positive.
 This strategy aims to maximize the amount of positive rewards while keeping low the number of negative feedback.
-This allow to pose the learning problem as a mere stochastic optimization strategy~\cite{sutton2018reinforcement}.
+Thus, the learning problem is  posed as a mere stochastic optimization strategy~\cite{sutton2018reinforcement}.
 Recently, this technique has seen a come-back.
@@
 
-Previous research has explored the usage of RL with reward signals based on brain activity, recorded by an EEG-based BCI system during the task execution.
+Previous research has explored the usage of RL with reward signals based on brain activity, recorded by an EEG-based BCI system during task execution.
 The papers \cite{ROBOT-CONTROL-PAPER,Omedes2013} have successfully demonstrated that a robot can be controlled by obtaining a reward signal from brain activity of a person which is observing the robot solving a task.
@@
 The following Section \ref{learning} describes the agent learning phase.
-Results \ref{results} and conclusions \ref{conclusions} are exposed at the last two sections.
+Results and Conclusions are exposed in Sections \ref{results} and \ref{conclusions}.
 
@@
 Hence, the agent can learn the winning strategy using the person's feedback to improve its own performance.
-This section describes the process of obtaining the person's brain signals and how they are used to make the agent more efficient.
+This section describes the process of obtaining the person's brain signals that are used to make the agent more efficient.
 
@@
 
-After the form is filled out, a short description of the procedure is given to the subject.
+After the form is filled out, a short description of the procedure is given to each subject.
 They are only told that the objective of the agent is to reach the goal and the four movements that the agent can make.
@@
 
-In this way, the raw data of an entire brainwave session is processed into an array of experiences where each element is an array of epochs tagged with a number specifying the prediction of the classifier, i.e.
+In this way, the raw data of an brainwave session is processed into an array of experiences where each element is an array of epochs tagged with a number specifying the prediction of the classifier, i.e.
 if the epoch corresponds to an action that made the agent move further from the goal (hit) or an action that made the agent move closer to the goal (no hit).
@@
 The set of experiences of each subject is split into training and testing, so that the results of the classification can then be used to improve the performance of the agent.
-After training the classifier, the testing experiences are classified.
+After training, the testing experiences are classified.
 Then, for each experience a reward file is generated.
@@
 On the other hand, Figure \ref{fig:avg_steps} shows for each subject the average amount of steps the agent takes to reach the goal as the Q-Table is progressively trained using the reward information obtained from their tested experiences.
-Each point corresponds to the average amount of steps it takes for the agent to reach the goal for a specific Q-Table in 200 iterations.
+Each point corresponds to the average number of steps in 200 iterations that it takes for the agent to reach the goal for a specific Q-Table.
 The first point represents the amount of steps it takes to reach the goal for a Q-Table that hasn't been trained at all, where movements are decided randomly.
@@
     \includegraphics[scale=0.2]{Images/Classification_test/roc_manuel.png}
-    \caption{ROC Curve for Subject 5.}
+    \caption{ }
     \label{fig:subject5roc}
@@
     \includegraphics[scale=0.2]{Images/Classification_test/roc_marta.png}
-    \caption{ROC Curve for Subject 5.}
+    \caption{ }    
     \label{fig:subject6roc}
 \end{subfigure}
+\caption{ROC Curve for Subjects 5 and 6}
 \end{figure}
@@
 
-This work aims to keep the system as simple as possible, emphasizing the flow of information from the subjective error perception of the human critic, through the reward generation using the signal processing and classification pipeline, and finally the updating of the Q-Table to enhance the performance of the gaming agent.
+This work aims to keep the system as simple as possible, emphasizing the flow of information from the subjective error perception of the human critic, through the reward generation using the signal processing and classification pipeline, and finally Q-Table updating  to enhance the performance of the gaming agent.
 
@@
 
-While classifying, the better performing classifier is Logistic Regression.
-One important aspect of the classification results is the low percentage of false positives, meaning that it is not common that the agent learns that an action is wrong when in fact it is an action that takes it closer to the goal.
+While classifying, the obtained better performing classifier is Logistic Regression.
+One important aspect of the classification results is the low percentage of false positives (Figure~\ref{fig:confusionmatrix}), meaning that it is not common that the agent learns that an action is wrong when in fact it is an action that takes it closer to the goal.
 On the other hand, the percentage of false negatives is generally higher, but this is not a serious issue since missing out on learning that an action is wrong does not lower the performance of the agent, but only means it will take more experiences to learn a correct path.
+
+\begin{figure}[h!]
+\begin{subfigure}{0.5\textwidth}
+\centering
+\includegraphics[scale=0.12]{Images/Classification_test/matrix_alex.png}
+\includegraphics[scale=0.12]{Images/Classification_test/matrix_jose.png}\\
+\includegraphics[scale=0.12]{Images/Classification_test/matrix_juan.png}
+\includegraphics[scale=0.12]{Images/Classification_test/matrix_santiago.png}
+\end{subfigure}
+\caption{Confusion Matrix for subjects 1,3,4 and 8.}
+\label{fig:confusionmatrix}
+\end{figure}
 
@@
 Results show that training a classifier with data of one subject, but using it to classify the events of experiences of another subject does not lead to an improvement on the performance of the agent.
-Despite that, the rewards generated from different subjects can be used to train the same Q-Table to improve its performance, which may lead to strategies where the overall performance is improved based on the information on different human critics at the same time.
+Despite that, the rewards generated from different subjects can be used to train the same Q-Table to improve its performance, which may lead to strategies where the overall performance is improved based on the information from different human critics at the same time.
 
-One additional aspect to remark is the robustness of RL implementation.
-General accuracy is in general low.
-Even with that lower accuracy values, the RL algorithm was able to extract meaningful information from rewards files that were pointing to improve the agent performance.
-The complexity of the game should be tackled to allow at least the possibility that the target position be dynamically especified.
-In that case the agent would start to learn to follow the target, instead of learning to go to a specific static destination (which is actually learning now).
+One additional aspect to remark is the robustness of the learning strategy based on Q-Learning~\cite{Bauer2015,Rubin2012}.
+The obtained accuracy to discriminate ErrPs is low.
+However, even with such a lower accuracy values, the RL algorithm was able to extract meaningful information from rewards files that were helpful to improve the agent performance.
+
+Further work could be conducted in order to increase the complexity of the game to allow at least the possibility that the target position be dynamically changed.
+In that case the agent would start to learn to follow the target, instead of learning to go to a specific static destination spot.
+Additionally, the classifier could be enhanced to recognize more effectively the Error Potential.
 

### 2019-10-29 ErrP.tex
Varios cambios

@@
 
-Further work could be conducted in order to increase the complexity of the game to allow at least the possibility that the target position be dynamically changed.
+Further work could be conducted in order to increase the complexity of the game to allow  the possibility that the target position be dynamically changed.
 In that case the agent would start to learn to follow the target, instead of learning to go to a specific static destination spot.

### 2019-11-19 ErrP.tex
Updated all the images that show the number of steps to reach the target for each subject.  Changes in the text here and there.

--- 2019-10-29 ErrP.tex
@@
 \usepackage{amsmath, amssymb, amsthm} % Mathematical packages
+\hypersetup{hidelinks=true}
 
@@
 Rodrigo~Ramele,~\IEEEmembership{Member,~IEEE,} 
-        Juan~Miguel,~Santos% <-this % stops a space
+        Juan~Miguel~Santos% <-this % stops a space
 \thanks{R. Ramele and J.M.Santos are with the Department
@@
 One of its applications is the training of systems using signals originated from the human brain.
-Out of all the methods used to acquire information from the central nervous system the one that has gained the most popularity is Electroencephalography (EEG), mainly because of its effectiveness, low cost and because it is noninvasive.
+Out of all the methods used to acquire information from the central nervous system, the one that has gained most popularity is Electroencephalography (EEG), mainly because of its effectiveness, low cost and its noninvasive characteristic.
 Event-related potential (ERP) are brain signals that are time-locked to a particular event.
-Error-related potential (ErrP) are a particular type of ERP that are can be elicited by a person who attends a recognizable error.
-When subjects observe an agent who makes a mistake this potential can be discerned when analyzing the signals which are directly related with the cognitive interpretation of an erroneous outcome or decision.
+Error-related potential (ErrP) are a particular type of ERP that  can be elicited by a person who attends a recognizable error.
+When subjects observe an agent who makes a mistake this potential can be discerned by analyzing the signals which are directly related with the cognitive interpretation of an erroneous outcome or decision.
 Reinforcement Learning (RL) is an approach to machine learning where an agent tries to maximize the reward obtained while interacting with an unknown environment.
-How much a gaming agent can be trained by the rewards obtained from human critics that watch their actions ?
-This work implements a parsimonious application of this idea, to train an agent to solve a simple game using exclusively the information obtained from human critics that observe how to agent plays.
-
+In this work, a gaming agent is trained using Reinforcement Learning, and using the feedback obtained from human critic observers.
+Results show that there is an effective transfer of information and that the agent learns successfully to solve the game efficiently.
 \end{abstract}
@@
 This work tackles this problem by exploring the use of brain signals as an interface between human and computer, trying to overcome this limitation by providing information to the system without explicit communication from the user.
-This information is used to make a gaming agent improve its operational performance using electroencephalography (EEG) signals as feedback of the performed task from an observational human critic.
+This information is used to make a gaming agent improve its operational performance using electroencephalography (EEG) signals as feedback of the performed task, obtained from an observational human critic.
 The idea is that subjects observing a computer game play can train the gaming agent using only signals components called Error-related Potentials (ErrP) that can be identified from their brain signals.
@@
 
-\begin{figure}[h]
+\begin{figure*}
     \centering
-    \includegraphics[scale=0.4]{Images/complete_flow.png}
+    \includegraphics[width=\textwidth]{Images/complete_flow.png}
     \caption{Overview of the experimental procedure.}
     \label{diag:complete_flow}
-\end{figure}
+\end{figure*}
 
 The experimental procedure is summarized in Figure \ref{diag:complete_flow}.
-The core of the procedure is the retrieval of the subject's brain activity.
+The central part is the retrieval of the subject's brain activity.
 This process is called brainwave session.
@@
 
-The Acquisition Server has the responsibility of receiving and synchronizing the signal data from the headset and any event information from the game and transfers it to the OpenVibe Designer application.
+The Acquisition Server has the responsibility of receiving and synchronizing the signal data from the headset and any event information from the game, and transfers it to the OpenVibe Designer application.
 When the subject is ready, the Game and the OpenVibe Designer programs are launched and configured to communicate with the previously mentioned acquisition server.
@@
 \centering 
-\caption{Grid system representation used in the Cognitive Game Experience.}
+\caption{Grid system representation used in the Cognitive Game Experience. The blue spot represents the initial location while the green spot represents the target location. }
 \label{fig:game_representation}
@@
 Four different classification algorithms are used.
-Logistic Regression, Multi-layer Perceptron with a hidden layer of 100000 neurons, Random Forest and finally a Support Vector Classifier (i.e.
+Logistic Regression, Multi-layer Perceptron with a hidden layer of 100 neurons (i.e.
+default values for the Scikit-Learn MLPClassifier), Random Forest and finally a Support Vector Classifier (i.e.
 SVM)~\cite{Lotte2018}.
@@
 
+ARREGLAR !!!
 The set of experiences of each subject is split into training and testing, so that the results of the classification can then be used to improve the performance of the agent.
-After training, the testing experiences are classified.
+After training, testing experiences are classified.
 Then, for each experience a reward file is generated.
@@
 In order to represent rewards, a matrix is used, where rows correspond to all the possible states, whereas columns represent all possible actions.
-The reward for an action given a state is the value that can be found on the corresponding row and column.
+The reward for an action given a state, is the value that can be found on the corresponding row and column.
 This matrix is known as a Q-Table.
@@
 \begin{equation}
-    Q(s,a) \leftarrow Q(s,a) + \alpha[r+\gamma* Max(s, a)-Q(s, a) ]
+    Q(s,a) \leftarrow Q(s,a) + \alpha[r+\gamma* \max Q(s, a)-Q(s, a) ]
     \label{equ:update_q_table}
@@
 
-Figure~\ref{fig:classifiers} show the binary classification accuracy obtained for the eight subjects for the four different classification algorithms using a 10-fold cross validation procedure.
+Figures~\ref{fig:classifiers} and~\ref{fig:logisticregression} show the binary classification accuracy obtained for the eight subjects for the four different classification algorithms using a 10-fold cross validation procedure.
 The best overall performance is obtained using Logistic Regression.
@@
 \begin{subfigure}{0.5\textwidth}
-\includegraphics[scale=0.2]{Images/Average_steps/alex.png}
-\includegraphics[scale=0.2]{Images/Average_steps/gonza.png}
-\includegraphics[scale=0.2]{Images/Average_steps/jose.png}
- \includegraphics[scale=0.2]{Images/Average_steps/juan.png} 
-  \includegraphics[scale=0.2]{Images/Average_steps/manu.png} 
-  \includegraphics[scale=0.2]{Images/Average_steps/marta.png} 
-  \includegraphics[scale=0.2]{Images/Average_steps/nati.png} 
-  \includegraphics[scale=0.2]{Images/Average_steps/santiago.png} 
+\centering
+\includegraphics[scale=0.27]{Images/Average_steps/a.png}
+\includegraphics[scale=0.27]{Images/Average_steps/b.png}
+\centering
+\includegraphics[scale=0.27]{Images/Average_steps/c.png}
+ \includegraphics[scale=0.27]{Images/Average_steps/d.png} 
+ \centering
+  \includegraphics[scale=0.27]{Images/Average_steps/e.png} 
+  \includegraphics[scale=0.27]{Images/Average_steps/f.png} 
+  \centering
+  \includegraphics[scale=0.27]{Images/Average_steps/g.png} 
+  \includegraphics[scale=0.27]{Images/Average_steps/h.png} 
 \end{subfigure}
-\caption{Average number of steps for the agent when trained with experiences from subjects 1-8.}
+\caption{Average number of steps for the agent when trained with experiences from subjects 1(A)-8(H).
+Y axis show the averaged number of steps, while x axis show the number of experiences used to accumulative train the Q-Table.}
 \label{fig:avg_steps}
@@
 The results show that as the Q-Table is progressively trained the average amount of steps decreases, meaning that the agent learns.
-However, the rate at which it learns varies per subject, certain subjects have more effective experiments than others, for example results for subject 1 (fig \ref{fig:avg_steps} A) show faster learning than those of subject 8 (fig \ref{fig:avg_steps} H).
+However, the rate at which it learns varies per subject, certain subjects have more effective experiments than others.
+For example results for subject 1 (fig \ref{fig:avg_steps} A) show faster learning than those of subject 8 (fig \ref{fig:avg_steps} H).
 
@@
 Figures \ref{fig:avg_steps} E and \ref{fig:avg_steps} F show no apparent learning, as the amount of steps to reach the goal doesn't decrease when trained.
-These results are also consistent with the ROC curves, shown on Figures~\ref{fig:subject5roc} and~\ref{fig:subject6roc} obtained for both Subjecs, where the area under the curve are close to chance level.
+These results are also consistent with their ROC curves, shown on Figures~\ref{fig:rocsubjects} obtained for both Subjecs, where the area under the curve are close to chance level.
 Both subjects have less recorded data from the sessions in comparison to the rest of the subjects.
@@
 \begin{figure}[h!]
+\captionsetup[subfigure]{justification=centering}
 \begin{subfigure}{0.25\textwidth}
@@
     \includegraphics[scale=0.2]{Images/Classification_test/roc_manuel.png}
-    \caption{ }
-    \label{fig:subject5roc}
 \end{subfigure}
@@
     \includegraphics[scale=0.2]{Images/Classification_test/roc_marta.png}  
-    \caption{ }    
-    \label{fig:subject6roc}
 \end{subfigure}
-\caption{ROC Curve for Subjects 5 and 6}
+\caption{ROC Curves for Subjects 5 (up) and 6 (down)}
+\label{fig:rocsubjects}
 \end{figure}
@@
 
-Figure~\ref{fig:avg_steps_noise} show the result of an agent successively trained with experiences obtained from a brainwave session, generated with sham signals.
+Figure~\ref{fig:avg_steps_noise} shows the result of an agent successively trained with experiences obtained from a brainwave session, generated with sham signals.
 In this case, random EEG signals were generated using OpenVibe for all channels, as if they were generated from a human observer.
@@
 \begin{subfigure}{0.5\textwidth}
-\includegraphics[scale=0.2]{Images/Average_steps/marta_santiago.png}
-\includegraphics[scale=0.2]{Images/Average_steps/alex_jose.png}
+\includegraphics[scale=0.27]{Images/Average_steps/Ax.png}
+\includegraphics[scale=0.27]{Images/Average_steps/Bx.png}
 \end{subfigure}
-\caption{Average steps using Q-table trained with experiences from subject 8 classified with a classifier trained with data from subject 6.
-Average steps using Q-table trained with experiences from subject 1 classified with a classifier trained with data from subject 3.}
+\caption{(A) Average steps using Q-table trained with experiences from subject 8 classified with a classifier trained with data from subject 6.
+(B) Average steps using Q-table trained with experiences from subject 1 classified with a classifier trained with data from subject 3.}
 \label{fig:transferlearning}
@@
 
-Finally, Figure~\ref{fig:avg_steps_all} show the result of training an agent with accumulative experiences from subjects 1,2,3,4,7, and 8.
+Finally, Figure~\ref{fig:avg_steps_all} shows the result of training an agent with accumulative experiences from subjects 1,2,3,4,7, and 8.
 
@@
 \end{subfigure}
-\caption{Confusion Matrix for subjects 1,3,4 and 8.}
+\caption{Confusion Matrix for subjects 1,3,4 and 8. Darker colors show higher values.  It can be seen the lower percentage of false positives (upper left corner of each chart).}
 \label{fig:confusionmatrix}
@@
 
-Finally, this research verifies that brain signals can be used as an interface between human and a gaming computer enabling an alternative communication with the system without explicit input from the user.
+Finally, in line with other results, this research verifies that brain signals can be used as an interface between human and a gaming computer enabling an alternative communication with the system without explicit input from the user.
 
@@
 
-\begin{IEEEbiography}{Michael Shell}
-Biography text here.
-\end{IEEEbiography}
+%\begin{IEEEbiography}{Michael Shell}
+%Biography text here.
+%\end{IEEEbiography}
 
 % if you will not have a photo at all:
-\begin{IEEEbiographynophoto}{John Doe}
-Biography text here.
-\end{IEEEbiographynophoto}
+%\begin{IEEEbiographynophoto}{John Doe}
+%Biography text here.
+%\end{IEEEbiographynophoto}
 
@@
 
-\begin{IEEEbiographynophoto}{Jane Doe}
-Biography text here.
-\end{IEEEbiographynophoto}
+%\begin{IEEEbiographynophoto}{Jane Doe}
+%Biography text here.
+%\end{IEEEbiographynophoto}
 

### 2019-11-19 ErrP.tex
Fixed image sizes.  Only two remains.  Passed IEEE latex analyzer.

--- 2019-11-19 ErrP.tex
@@
 The Acquisition Server has the responsibility of receiving and synchronizing the signal data from the headset and any event information from the game, and transfers it to the OpenVibe Designer application.
-When the subject is ready, the Game and the OpenVibe Designer programs are launched and configured to communicate with the previously mentioned acquisition server.
+When the subject is ready, the Game Manager and the OpenVibe Designer programs are launched and configured to communicate with the previously mentioned acquisition server.
 A brainwave session consists of several experiences, each one being a game run.
@@
 In this way, the raw data of an brainwave session is processed into an array of experiences where each element is an array of epochs tagged with a number specifying the prediction of the classifier, i.e.
-if the epoch corresponds to an action that made the agent move further from the goal (hit) or an action that made the agent move closer to the goal (no hit).
+if the epoch corresponds to an action that made the agent move further from the goal (hit) or an action that made the agent move closer to the goal (no-hit).
 The ErrP is expected to be found in hits.
@@
 
-ARREGLAR !!!
 The set of experiences of each subject is split into training and testing, so that the results of the classification can then be used to improve the performance of the agent.
-After training, testing experiences are classified.
-Then, for each experience a reward file is generated.
-For this purpose, game states files, which are submitted by the game when an experience takes place, are used.
-These files contain an ordered list of the states of the game throughout an experience.
-With this file and the classification of the test data of an experience, a reward file is composed.
-This file specifies a reward for each movement in the game, based on the classification of the event that corresponds to that movement.
-The reward can either be -1 when the event is classified as a hit or 0 when it is classified as a no hit.
+Each experience includes an ordered list of extracted epochs for each movement that the agent triggered plus the game state information, i.e.
+the movement specification.
+After a classifier is trained, the epochs of the experience are classified as hit or no-hit.
+With the game state information and the classification of the test data of an experience, a reward file is composed.
+This file specifies a reward for each movement in the game run, based on the classification of the event that corresponds to that movement.
+The reward can either be -1 when the event is classified as a hit or 0 when it is classified as a no-hit.
 The accuracy of this rewards depends on the performance of the classifier.
@@
 
-\begin{figure}[h]
+\begin{figure}[ht]
     \centering
@@
 \caption{Average number of steps for the agent when trained with experiences from subjects 1(A)-8(H).
-Y axis show the averaged number of steps, while x axis show the number of experiences used to accumulative train the Q-Table.}
+Y axis show the averaged number of steps, while x axis show the number of experiences used to cumulative train the Q-Table.}
 \label{fig:avg_steps}
@@
 Figure~\ref{fig:avg_steps_noise} shows the result of an agent successively trained with experiences obtained from a brainwave session, generated with sham signals.
-In this case, random EEG signals were generated using OpenVibe for all channels, as if they were generated from a human observer.
+In this case, random EEG signals were generated using OpenVibe Acquisition Server signal generator for all channels, as if they were generated from a human observer.
 As it can be seen, the agent learns nothing, and regardless of the amount of experiences that are used to train the Q-Table, the number of steps required to reach the goal does not decrease.
@@
 While classifying, the obtained better performing classifier is Logistic Regression.
-One important aspect of the classification results is the low percentage of false positives (Figure~\ref{fig:confusionmatrix}), meaning that it is not common that the agent learns that an action is wrong when in fact it is an action that takes it closer to the goal.
+One important aspect of the classification results is the low percentage of false positives (Figure~\ref{fig:confusionmatrix}), showing a high specificity.
+It is not common that the agent learns that an action is wrong when in fact it is an action that takes it closer to the goal.
 On the other hand, the percentage of false negatives is generally higher, but this is not a serious issue since missing out on learning that an action is wrong does not lower the performance of the agent, but only means it will take more experiences to learn a correct path.
@@
 \end{subfigure}
-\caption{Confusion Matrix for subjects 1,3,4 and 8. Darker colors show higher values.  It can be seen the lower percentage of false positives (upper left corner of each chart).}
+\caption{Confusion Matrix for subjects 1,3,4 and 8. Darker colors show higher values.  It can be seen the lower percentage of false positives (upper right corner of each chart).}
 \label{fig:confusionmatrix}
@@
 
-At the same time, the training depends strictly on the subject's data that was used to train it.
+At the same time, the effective agent training depends on the subject's data that was used to train it.
 Results show that training a classifier with data of one subject, but using it to classify the events of experiences of another subject does not lead to an improvement on the performance of the agent.

### 2019-12-03 ErrP.tex
Subo una version mas pulida con casi todos los cambios

@@
 \author{Bartolomé Francisco, Moreno Juan,  Navas Natalia, Vitali José, \\
-Rodrigo~Ramele,~\IEEEmembership{Member,~IEEE,} 
-        Juan~Miguel~Santos% <-this % stops a space
+Ramele~Rodrigo,~\IEEEmembership{Member,~IEEE,} 
+        Santos~Juan~Miguel% <-this % stops a space
 \thanks{R. Ramele and J.M.Santos are with the Department
@@
 When subjects observe an agent who makes a mistake this potential can be discerned by analyzing the signals which are directly related with the cognitive interpretation of an erroneous outcome or decision.
-Reinforcement Learning (RL) is an approach to machine learning where an agent tries to maximize the reward obtained while interacting with an unknown environment.
-In this work, a gaming agent is trained using Reinforcement Learning, and using the feedback obtained from human critic observers.
+Reinforcement Learning (RL) is an Artificial Intelligence approach where an agent tries to maximize rewards obtained while interacting with an unknown environment.
+In this work, a gaming agent is trained using RL, and the feedback obtained from human critic observers.
 Results show that there is an effective transfer of information and that the agent learns successfully to solve the game efficiently.
@@
 This work tackles this problem by exploring the use of brain signals as an interface between human and computer, trying to overcome this limitation by providing information to the system without explicit communication from the user.
-This information is used to make a gaming agent improve its operational performance using electroencephalography (EEG) signals as feedback of the performed task, obtained from an observational human critic.
-The idea is that subjects observing a computer game play can train the gaming agent using only signals components called Error-related Potentials (ErrP) that can be identified from their brain signals.
-These can be found on EEG traces and are elicited when a subject is aware of the presence of un unexpected outcome, which she identifies as an error.
+This information is used to make a gaming agent improves its operational performance using electroencephalography (EEG) signals as feedback of the performed task, obtained from an observational human critic.
+The idea is that subjects observing a computer game playing, can train the gaming agent using only signals components called Error-related Potentials (ErrP) that can be identified from their brain signals.
+These can be found on EEG traces and are elicited when a subject is aware of the presence of an unexpected outcome, which she/he identifies as an error.
 It is currently an extensive area of research in the neuroscience community~\cite{Holroyd2009}.
-They can be detected by signal processing and machine learning techniques~\cite{EERP-PAPER} and they are also used in Brain-Computer Interfaces (BCI) to implement or enhance artificial communication channels~\cite{Chavarriaga2014}.
+Error-related Potentials can be detected by signal processing and machine learning techniques~\cite{EERP-PAPER} and they are also used in Brain-Computer Interfaces (BCI) to implement or enhance artificial communication channels~\cite{Chavarriaga2014}.
 
-In order to train the agent, Reinforcement Learning (RL)~\cite{Santos1999} comes as natural solution for this scenario from the field of Artificial Intelligence.
-RL is an algorithmic learning strategy that can be established by mimicking how biological agents learn from the environment by exploring it and getting feedback rewards, either negative or positive.
-This strategy aims to maximize the amount of positive rewards while keeping low the number of negative feedback.
+In order to train the agent, RL~\cite{Santos1999} comes as a natural solution for this scenario from the field of Artificial Intelligence.
+RL is an algorithmic learning strategy that can be established by mimicking how biological agents learn from its environment by exploring it and getting feedback rewards, either negative or positive.
+This strategy aims to maximize the amount of positive rewards while keeping the number of negative feedback low.
 Thus, the learning problem is  posed as a mere stochastic optimization strategy~\cite{sutton2018reinforcement}.
 Recently, this technique has seen a come-back.
-Nonneglected is the influence of DeepBrain's AlphaGo project, which was the first to reach superhuman proficiency when it won the complex game Go against several world champions~\cite{ALPHA-GO}.
+Nonneglected is the influence of DeepBrain's AlphaGo project, which was the first to reach a very high proficiency when it won the complex game Go against several world champions~\cite{ALPHA-GO}.
 
@@
 Previous research has explored the usage of RL with reward signals based on brain activity, recorded by an EEG-based BCI system during task execution.
-The papers \cite{ROBOT-CONTROL-PAPER,Omedes2013} have successfully demonstrated that a robot can be controlled by obtaining a reward signal from brain activity of a person which is observing the robot solving a task.
-Other approaches have used the signal as an important feedback to identify targets for robots when implementing shared-control strategies~\cite{Schiatti2018}.
-Additionally, ErrPs have been used as well in the context of games as an additional feedback channel that can be explored to enhance gaming experience~\cite{Plass-OudeBos2010,kober2018bci}.
-In this same line, the objective of this work is to use the information extracted from brainwaves to enhance the performance of a gaming agent, replicating and extending those results.
+The papers \cite{ROBOT-CONTROL-PAPER,Kim2017,Omedes2013} have successfully demonstrated that a robot can be controlled by obtaining a reward signal from a person's brain activity which is observing the robot solve a task.
+Other approaches have used the signal as an important feedback for human-robot interaction or to implement shared-control strategies~\cite{Schiatti2018}.
+Additionally, ErrPs have also been used in the context of games as an additional feedback channel that can be explored to enhance gaming experience~\cite{Plass-OudeBos2010,kober2018bci}.
+In this same line, the objective of this work is to use the information extracted from brainwaves to enhance the performance of a gaming agent, replicating and extending the usage of this signal.
 
@@
 
-In Section \ref{section:materials} the general layout of the cognitive game experiment is described.
+In Section \ref{section:materials} the general layout of the cognitive game is described.
 Section \ref{section:calibration} outlines the processing pipeline used to detect ErrP components.
@@
 
-This experiment consists of collecting signals from a person's brain while they are watching a game where the agent knows the game rules but not how to win it.
+This first part consists in collecting signals from a person's brainwaves while they are watching a game where the agent knows the game rules but not how to win it.
 Hence, the agent can learn the winning strategy using the person's feedback to improve its own performance.
@@
     \includegraphics[width=\textwidth]{Images/complete_flow.png}
-    \caption{Overview of the experimental procedure.}
+    \caption{Overview of the experimental procedure.
+Brainwaves are obtained by the OpenVibe Acquisition Server.
+The Game Manager is responsible for generating the game screen and is connected to the Acquisition Server to send stimulus information.
+The captured information is stored by the OpenVibe Designer.
+Offline, EEG signals are classified and they are linked to each game movement calculated by the Game Manager to determine proper rewards for each action.
+This information is used by a Reinforcement Learning algorithm to learn a Q-Table to improve the performance of the agent that plays the game.}
     \label{diag:complete_flow}
@@
 It has eight electrodes (g.LADYbird, g.Tec, Austria) on the positions Fz, Cz, Pz, Oz, P3, P4, PO7 and PO8, identified according to the 10-20 International System, with a reference set to the right ear lobe and ground set as the AFz position.
-The electrodes contact points are adjusted applying conductive gel until the impedance values displayed by the program g.NeedAccess (g.Tec, Austria) are within the desired range.
+The electrode contact points are adjusted applying conductive gel until the impedance values displayed by the program g.NeedAccess (g.Tec, Austria) are within the desired range.
 This process takes between 10 and 15 minutes.
@@
 Once the headset is correctly applied, the OpenVibe Acquisition Server program, from the OpenVibe platform~\cite{OPEN-VIBE-PAPER}, is launched and configured with a sampling rate of $250$ Hz.
-A $50$ Hz notch filter is applied to filter out power line.
+A $50$ Hz notch filter is applied to filter out power line noise.
 An additional bandpass filter between $0.5$ Hz and $60$ Hz is applied as well.
-Data is handled and processed with the OpenVibe Designer, from the same platform, using 8 channels for the brain data (one channel per electrode) and an additional channel for the stimuli.
+Data is handled and processed with the OpenVibe Designer, from the same platform, using 8 channels for the brain data (one channel per electrode) and an additional channel for the stimulus, which corresponds to a game movement performed by the agent.
 After everything is connected, the subject seats in a comfortable chair in front of a computer screen.
 The brightness of the screen is set to the maximum setting to avoid any visual inconvenience in which the subject can not distinguish the components of the game that appear on the screen.
+The dataset is published on the IEEE DataPort initiative~\cite{6emh-wb46-19}.
 
 The Acquisition Server has the responsibility of receiving and synchronizing the signal data from the headset and any event information from the game, and transfers it to the OpenVibe Designer application.
-When the subject is ready, the Game Manager and the OpenVibe Designer programs are launched and configured to communicate with the previously mentioned acquisition server.
+When the subject is ready, the Game Manager and the OpenVibe Designer programs are launched and configured to communicate with the previously mentioned Acquisition Server.
 A brainwave session consists of several experiences, each one being a game run.
@@
 
-\subsection{Cognitive Game experiment}
+\subsection{Cognitive Game Procedure}
 \label{cognitive_experiment_details}
@@
 When the agent reaches the goal, the position where the agent and the goal are located turns red, showing that the experience has ended.
-There are four possible movements that the agent can perform: it can go upwards, downwards, towards the left and towards the right, and those moves are bounded to avoid the agent from leaving the grid.
+There are four possible movements that the agent can perform: it can go upwards, downwards, towards the left and towards the right, and those movements are bounded to avoid the agent from leaving the grid.
 The movement direction is selected randomly and is executed once every 2 seconds.
@@
 \centering 
-\caption{Grid system representation used in the Cognitive Game Experience. The blue spot represents the initial location while the green spot represents the target location. }
+\caption{Grid system representation used in the Cognitive Game Experience.
+The blue spot represents the initial location while the green spot represents the target location.
+Once the agent reaches the target spot, its color turns to red to indicate the end of the play.}
 \label{fig:game_representation}
@@
 To aid in detecting the ErrP response, an offline processing pipeline and classifier is constructed to identify whether the action taken by the agent is an error or not.
-It is developed in Python using the MNE platform \cite{MNE-PYTHON}, which is a package designed specifically for processing EEG and Magnetoencephalography (MEG) data, and based on top of the machine learning library Scikit-Learn~\cite{scikit-learn}.
+It is developed in Python using the MNE platform \cite{MNE-PYTHON}, which is a package designed specifically for processing EEG and Magnetoencephalography data, and built upon the machine learning library Scikit-Learn~\cite{scikit-learn}.
 
-This step consists of offline processing the collected signals in order to train a classifier that can decide whether an error potential is triggered or not.
+This pipeline consists of offline processing the collected signals in order to train a classifier that can decide whether an error potential is triggered.
 Firstly, the output of a brainwave session is read and an additional band pass filter of 0.1-20.0Hz is applied to the signal.
-Samples that correspond to the start of an event are tagged using the data from the stimuli channel.
+Samples that correspond to the start of an event are tagged using the data from the stimulus channel.
 
@@
 
-Samples that do not correspond to an epoch are not used.
+Samples that do not correspond to an epoch (located beyond the 2 seconds frame after the onset of the event) are not used.
 Also, epochs referring to the start or finish of the experience are excluded.
-This is done because the start and the end of the experience doesn't involve the agent taking an action, thus giving signals that should not be considered in the classification process.
+This is done because the start and the end of the experience doesn't involve the agent taking an action.
 
@@
 The ErrP is expected to be found in hits.
-To get the data ready for classification, the stimuli channel is removed in order to classify the signals using only the EEG data.
+To get the data ready for classification, the stimulus channel is removed in order to classify the signals using only the EEG data.
 Each epoch is regularized using a MinMaxScaler, i.e.
@@
 Lastly, this data is used by the classification module as information to train and test a classifier.
-
-Vectorized epochs are used in the final classification step.
 Four different classification algorithms are used.
 Logistic Regression, Multi-layer Perceptron with a hidden layer of 100 neurons (i.e.
-default values for the Scikit-Learn MLPClassifier), Random Forest and finally a Support Vector Classifier (i.e.
+default values for the Scikit-Learn MLPClassifier), Random Forest and finally a linear kernel Support Vector Classifier (i.e.
 SVM)~\cite{Lotte2018}.
+
+%Vectorized epochs are used in the final classification step.
 
@@
 
-The set of experiences of each subject is split into training and testing, so that the results of the classification can then be used to improve the performance of the agent.
-Each experience includes an ordered list of extracted epochs for each movement that the agent triggered plus the game state information, i.e.
+Each experience consists of a list of game movement configuration and the associated epoch obtained from subject's brainwaves.
+The set of experiences of each subject is split into training and testing.
+Training experiences are used to train the classifier, whereas test experiences are used to test its performance.
+After a classifier is trained, the epochs of the experience are classified as hit or no-hit.
+A reward for each movement in the game run is produced, based on the classification of the event that correspond to that movement.
+The reward can either be -1 when the event is classified as a hit or 0 when it is classified as a no-hit.
+The accuracy of this rewards depends on the performance of the classifier.
+The list of game movements and their associated reward information are used to train the agent by a variant of Reinforcement Learning called Q-Learning algorithm.
+
+%The set of experiences of each subject is split into training and testing, so that the results of the classification can then be used to improve the performance of the agent.
+Each experience includes an ordered list of extracted epochs for each movement that the agent carried out plus the game state information, i.e.
 the movement specification.
-After a classifier is trained, the epochs of the experience are classified as hit or no-hit.
+
+%After a classifier is trained, the epochs of the experience are classified as hit or no-hit.
 With the game state information and the classification of the test data of an experience, a reward file is composed.
@@
 \begin{equation}
-    Q(s,a) \leftarrow Q(s,a) + \alpha[r+\gamma* \max Q(s, a)-Q(s, a) ]
+    Q(s,a) \leftarrow Q(s,a) + \alpha[r+\gamma* \max_{\tilde{a}} Q(s, \tilde{a})-Q(s, a) ]
     \label{equ:update_q_table}
@@
 
-\noindent where $s$ is the current state, $a$ is the action, $\alpha$ represents the learning rate between $0$ exploration and $1$ explotation and $\gamma$ represents the discount rate, a value between 0 and 1 that determines the importance of long term results versus immediate rewards.
+\noindent where $s$ is the current state, $a$ is the action, $\alpha$ represents the learning rate and $\gamma$ represents the discount factor, a value between 0 and 1 that determines the importance of long term results versus immediate rewards.
 Once the environment has been extensively explored and the Q-Table has been obtained, the action chosen is the one that maximizes the expected reward according to the Q-Table matrix.
 
-For this experiment, the algorithm is developed in Python and uses the OpenAI Gym toolkit~\cite{openai}.
+The algorithm is developed in Python and uses the OpenAI Gym toolkit~\cite{openai}.
 Gym is a toolkit for developing and comparing reinforcement learning algorithms.
@@
 Instead, the policy which determines which action to take in a particular state is given by the steps taken from the brainwave session results.
-This allows to train the Q-Table based on the subject's feedback from the movements the agent took, which are chosen pseudo-randomly, while executing the brainwave session.
+This allows to learn the Q-Table based on the subject's feedback from the movements the agent took, which are chosen pseudo-randomly, while executing the brainwave session.
 The previously mentioned feedback is not explicit as it comes from the interpreted brain signal data, which is collected while the agent is executing the brainwave session and then each action is classified as an error or not.
@@
 
-While using the previously mentioned step function, the Q-Table is updated in each iteration.
-This is done following the Equation \ref{equ:update_q_table}.
+Hence, following the iterative procedure based on Equation~\ref{equ:update_q_table}, the Q-Table is updated in each iteration.
 After the algorithm finishes iterating through all the training episodes, the Q-Table is stored to test the performance of the agent.
@@
     \includegraphics[scale=0.4]{Images/algorithm_calibration/Total_calib.png}
-    \caption{Binary Classification Accuracy using different classifiers while recognizing ErrP potentials for the eight subjects.}
+    \caption{Binary Classification Score using different classifiers while recognizing ErrP potentials for the eight subjects.}
     \label{fig:classifiers}
@@
     \includegraphics[scale=0.4]{Images/algorithm_calibration/LR_calib.png}
-    \caption{Binary Classification Accuracy using Logistic Regression for the eight subjects.}
+    \caption{Binary Classification Score using Logistic Regression for the eight subjects.}
     \label{fig:logisticregression}
@@
 On the other hand, Figure \ref{fig:avg_steps} shows for each subject the average amount of steps the agent takes to reach the goal as the Q-Table is progressively trained using the reward information obtained from their tested experiences.
-Each point corresponds to the average number of steps in 200 iterations that it takes for the agent to reach the goal for a specific Q-Table.
-The first point represents the amount of steps it takes to reach the goal for a Q-Table that hasn't been trained at all, where movements are decided randomly.
+Each point corresponds to the average number of steps in 200 repetitions that it takes for the agent to reach the goal for a specific Q-Table.
+The first point represents the amount of steps the agent takes to reach the goal for a Q-Table that hasn't been trained at all, where movements are decided randomly.
 The next point corresponds to the amount of steps it takes to reach the goal using a policy derived from a Q-Table trained with one experience, and so on.
@@
 The results show that as the Q-Table is progressively trained the average amount of steps decreases, meaning that the agent learns.
-However, the rate at which it learns varies per subject, certain subjects have more effective experiments than others.
+However, the rate at which it learns varies per subject, depending on the classification accuracy of the extracted brainwaves.
 For example results for subject 1 (fig \ref{fig:avg_steps} A) show faster learning than those of subject 8 (fig \ref{fig:avg_steps} H).
@@
 Figures \ref{fig:avg_steps} E and \ref{fig:avg_steps} F show no apparent learning, as the amount of steps to reach the goal doesn't decrease when trained.
-These results are also consistent with their ROC curves, shown on Figures~\ref{fig:rocsubjects} obtained for both Subjecs, where the area under the curve are close to chance level.
+These results are also consistent with their ROC curves, shown on Figures~\ref{fig:rocsubjects} obtained for both subjects, where the area under the curve are close to chance level.
 Both subjects have less recorded data from the sessions in comparison to the rest of the subjects.
+This variation in performance for different subjects has been studied extensively in BCI.
+Besides low data samples there could be other reasons that may be affecting the classification accuracy:  it may be due to cognitive reasons, this being the subject not paying extensively attention to the game dynamics, very low Signal-To-Noise Ratio (SNR) of the ErrP component or even the BCI-illiteracy phenomena where the specific subject's signals do not contain the expected component response~\cite{Yousefi2019}.
 
@@
 \end{subfigure}
-\caption{ROC Curves for Subjects 5 (up) and 6 (down)}
+\caption{ROC Curves for subjects 5 (up) and 6 (down)}
 \label{fig:rocsubjects}
@@
 Figure~\ref{fig:avg_steps_noise} shows the result of an agent successively trained with experiences obtained from a brainwave session, generated with sham signals.
-In this case, random EEG signals were generated using OpenVibe Acquisition Server signal generator for all channels, as if they were generated from a human observer.
-As it can be seen, the agent learns nothing, and regardless of the amount of experiences that are used to train the Q-Table, the number of steps required to reach the goal does not decrease.
-This pattern is also obtained when the experiences from Subjects 5 and 6 are used, showing that the reward labeling predicted by the trained classifier for those subjects worked like a random classifier.
+In this case, random EEG signals were generated using OpenVibe Acquisition Server signal generator for all channels, as if they were generated from a human observer who doesn't pay attention to the game.
+As it can be seen, the agent learns nothing, and regardless of the amount of experiences that are used to learn the Q-Table, the number of steps required to reach the goal does not decrease.
+This pattern is also obtained when the experiences from subjects 5 and 6 are used, showing that the reward labeling predicted by the trained classifier for those subjects worked like a random classifier.
 
@@
 Electroencephalographic signals have high inter-subject variability~\cite{Chavarriaga2014}.
-This is evidenced in Figure~\ref{fig:transferlearning} where the agent training is performed by using a classifier trained with experiences from one subject,  but tagging the experiences from a different subject using the predicted classification.
+This is evidenced in Figure~\ref{fig:transferlearning} where the agent training is performed by using rewards obtained by classifying epochs from one subject, but using a classifier which was trained using the brainwaves from a different subject.
 Not performance gain is evidenced, the agents learn nothing which implies that the reward information is useless.
@@
 Finally, Figure~\ref{fig:avg_steps_all} shows the result of training an agent with accumulative experiences from subjects 1,2,3,4,7, and 8.
+It can be seen that the overall performance of the agent improves as long as there are more experiences to be used to train it, regardless if they were generated from the brainwaves classification from different subjects.
 
@@
 
-The present research work aims to reproduce similar results that states whether ErrP signals could be used to train a gaming agent using reinforcement learning.
+This work aims to to state whether ErrP signals could be used to train a gaming agent using reinforcement learning.
 The collected data show that ErrP signals can in fact be classified and used to train an agent effectively.
 
-This work aims to keep the system as simple as possible, emphasizing the flow of information from the subjective error perception of the human critic, through the reward generation using the signal processing and classification pipeline, and finally Q-Table updating  to enhance the performance of the gaming agent.
+This proposal tries to keep the system as simple as possible, emphasizing information flow from the subjective error perception of the human critic, through the reward generation using the signal processing and classification pipeline, and finally the Q-Table updating  to enhance the performance of the gaming agent.
 
@@
 
-While classifying, the obtained better performing classifier is Logistic Regression.
+%While classifying, the better performing classifier is Logistic Regression.
 One important aspect of the classification results is the low percentage of false positives (Figure~\ref{fig:confusionmatrix}), showing a high specificity.
@@
 On the other hand, the percentage of false negatives is generally higher, but this is not a serious issue since missing out on learning that an action is wrong does not lower the performance of the agent, but only means it will take more experiences to learn a correct path.
+
+While classifying, the better performing classifier is Logistic Regression.
+One important aspect of the classification results is the low percentage of false positives (Figure~\ref{fig:confusionmatrix}), showing a high specificity.
+It is not common that the agent learns that an action is wrong when in fact it is an action that takes it closer to the goal.
+On the other hand, the percentage of false negatives is generally higher.
+However, even though this imply that the agent misses frequently that an action taken is wrong, this do not seems to be a serious issue because the agent improves its performance.
 
@@
 Once ErrP signals are identified they can be used to train a reinforcement learning algorithm.
-Brainwave sessions have a low amount of experiences in order to reduce fatigue from the subjects.
+Brainwave sessions have a low amount of experiences in order to reduce fatigue from subjects.
 However data suggests that longer sessions are required in order to reach better classification scores, since more data is available in order to train the classifier.
@@
 
-At the same time, the effective agent training depends on the subject's data that was used to train it.
+At the same time, effective agent training depends on the subject's data that was used to train it.
 Results show that training a classifier with data of one subject, but using it to classify the events of experiences of another subject does not lead to an improvement on the performance of the agent.
@@
 
-Finally, in line with other results, this research verifies that brain signals can be used as an interface between human and a gaming computer enabling an alternative communication with the system without explicit input from the user.
+Concluding, this research show evidence that brain signals can be used as an interface between human and a gaming computer enabling an alternative communication with the system without explicit input from the user.
 
@@
 
-The authors would like to thank...
+The authors would like to thank the Laboratory Centro de Inteligencia Computacional and to ITBA University
+
+\section*{Funding}
+This work was supported by the grant ITBACyT-15 issued by ITBA University.
 

### 2019-12-04 ErrP.tex
Actualizo algunos nombres de archivos

@@
 Out of all the methods used to acquire information from the central nervous system, the one that has gained most popularity is Electroencephalography (EEG), mainly because of its effectiveness, low cost and its noninvasive characteristic.
-Event-related potential (ERP) are brain signals that are time-locked to a particular event.
+Event-related potential (ERP) are brain signals found on EEG that are time-locked to a particular event.
 Error-related potential (ErrP) are a particular type of ERP that  can be elicited by a person who attends a recognizable error.
@@
 Reinforcement Learning (RL) is an Artificial Intelligence approach where an agent tries to maximize rewards obtained while interacting with an unknown environment.
-In this work, a gaming agent is trained using RL, and the feedback obtained from human critic observers.
+In this work, a gaming agent is trained using RL, and the feedback obtained from brainwaves of human critic observers.
 Results show that there is an effective transfer of information and that the agent learns successfully to solve the game efficiently.
@@
 The electrode contact points are adjusted applying conductive gel until the impedance values displayed by the program g.NeedAccess (g.Tec, Austria) are within the desired range.
-This process takes between 10 and 15 minutes.
+This process takes between 10 to 15 minutes.
 After this step, the subject is instructed to close their eyes and the same program is used to check the live channel values so that there are no dead ones and the expected values are displayed for eye movements or muscle chewing.
 
-Once the headset is correctly applied, the OpenVibe Acquisition Server program, from the OpenVibe platform~\cite{OPEN-VIBE-PAPER}, is launched and configured with a sampling rate of $250$ Hz.
-A $50$ Hz notch filter is applied to filter out power line noise.
-An additional bandpass filter between $0.5$ Hz and $60$ Hz is applied as well.
+Once the headset is correctly applied, the OpenVibe Acquisition Server program, from the OpenVibe platform~\cite{OPEN-VIBE-PAPER}, is launched and configured with a sampling rate of $250$~Hz.
+A $50$~Hz notch filter is applied to filter out power line noise.
+An additional bandpass filter between $0.5$~Hz and $60$~Hz is applied as well.
 Data is handled and processed with the OpenVibe Designer, from the same platform, using 8 channels for the brain data (one channel per electrode) and an additional channel for the stimulus, which corresponds to a game movement performed by the agent.
@@
 The brightness of the screen is set to the maximum setting to avoid any visual inconvenience in which the subject can not distinguish the components of the game that appear on the screen.
-The dataset is published on the IEEE DataPort initiative~\cite{6emh-wb46-19}.
+This dataset has been published on the IEEE DataPort initiative~\cite{6emh-wb46-19}.
 
@@
 This variation in performance for different subjects has been studied extensively in BCI.
-Besides low data samples there could be other reasons that may be affecting the classification accuracy:  it may be due to cognitive reasons, this being the subject not paying extensively attention to the game dynamics, very low Signal-To-Noise Ratio (SNR) of the ErrP component or even the BCI-illiteracy phenomena where the specific subject's signals do not contain the expected component response~\cite{Yousefi2019}.
+Besides low data samples there are other reasons affecting the classification accuracy:  cognitive reasons, this being the subject not paying extensively attention to the game dynamics, very low Signal-To-Noise Ratio (SNR) of the ErrP component or even the BCI-illiteracy phenomena where the specific subject's signals do not contain the expected component response~\cite{Yousefi2019}.
 
@@
     \centering
-    \includegraphics[scale=0.2]{Images/Classification_test/roc_manuel.png}
+    \includegraphics[scale=0.2]{Images/Classification_test/roc_e.png}
 \end{subfigure}
@@
     \centering
-    \includegraphics[scale=0.2]{Images/Classification_test/roc_marta.png}  
+    \includegraphics[scale=0.2]{Images/Classification_test/roc_f.png}  
 \end{subfigure}
@@
 
-%These results are consistent with fig. \ref{fig:roc:manuel} and fig. \ref{fig:roc:marta}, which show that the signal classification for these subjects hasn't been particularly successful.
+%These results are consistent with fig. \ref{fig:roc:e} and fig. \ref{fig:roc:f}, which show that the signal classification for these subjects hasn't been particularly successful.
 
@@
 Not performance gain is evidenced, the agents learn nothing which implies that the reward information is useless.
-
-%\begin{figure*}[ht!]
-%    \centering
-%    \begin{subfigure}[t]{0.5\textwidth}
-%        \centering
-%        \includegraphics[height=1.2in]{Images/Average_steps/marta_santiago.png}
-%        \caption{Lorem ipsum}
-%    \end{subfigure}%
-%    ~ 
-%    \begin{subfigure}[t]{0.5\textwidth}
-%        \centering
-%        \includegraphics[height=1.2in]{Images/Average_steps/alex_jose.png}
-%        \caption{Lorem ipsum, lorem ipsum,Lorem ipsum, lorem ipsum,Lorem ipsum}
-%    \end{subfigure}
-%    \caption{Caption place holder}
-%\end{figure*}
 
@@
 
-This work aims to to state whether ErrP signals could be used to train a gaming agent using reinforcement learning.
+This work aims to state whether ErrP signals could be used to train a gaming agent using reinforcement learning.
 The collected data show that ErrP signals can in fact be classified and used to train an agent effectively.
@@
 On the other hand, the percentage of false negatives is generally higher.
-However, even though this imply that the agent misses frequently that an action taken is wrong, this do not seems to be a serious issue because the agent improves its performance.
+However, even though this implies that the agent misses frequently that an action taken is wrong, this is not hindering the overall performance and the agent is still learning.
+
+%However, even though this imply that the agent misses frequently that an action taken is wrong, this do not seems to be a serious issue because the agent improves its performance.
 
@@
 \centering
-\includegraphics[scale=0.12]{Images/Classification_test/matrix_alex.png}
-\includegraphics[scale=0.12]{Images/Classification_test/matrix_jose.png}\\
-\includegraphics[scale=0.12]{Images/Classification_test/matrix_juan.png}
-\includegraphics[scale=0.12]{Images/Classification_test/matrix_santiago.png}
+\includegraphics[scale=0.12]{Images/Classification_test/matrix_a.png}
+\includegraphics[scale=0.12]{Images/Classification_test/matrix_c.png}\\
+\includegraphics[scale=0.12]{Images/Classification_test/matrix_d.png}
+\includegraphics[scale=0.12]{Images/Classification_test/matrix_h.png}
 \end{subfigure}

### 2019-12-09 coverletter.tex
Version manuscrita lista

Dear Editor,

We are submitting a Full Paper, titled "Training a Gaming Agent on Brainwaves" which we believe is within the scope of IEEE Transactions on Games.  This article encompass work performed at CiC Laboratory of the ITBA University in Buenos Aires, Argentina, in the context of research on Brain Computer Interfaces and Artificial Intelligence.  This is original work, which has not been submitted for publication elsewhere.

This work details an experiment performed by 8 subjects that watched a gaming agent playing a simple game. Subjects used a wireless EEG device to capture brainwaves.  We detected Error-Potentials (ErrP) which are signal components that can be found on EEG traces that are triggered when the subject subjectively determines an erroneous outcome.  By classifying the signals we derived rewards penalizing the agent movements that the person considered as an error.  Using that information, the gaming agent was trained using Q-Learning, a Reinforcement Learning algorithm.  We show that the agent learns a policy that improves its operational performance.

We believe this is an interesting work that explore a novel interaction scheme, where the interaction between a game and a person is not explicit.  Instead, the information is sent surreptitiously, or extracted from the person to derive information for the gaming agent.  This is a challenging area of research and our work shows how to implement a simple game that triggered this action potential from users.

Additionally, for the sake of reproducibility we used open source libraries for our software implementation and uploaded the obtained dataset to the IEEE Dataport initiative.

Yours truly
Rodrigo Ramele
ITBA University 
Argentina

### 2020-07-07 review/response.letter.tex
Ok, hay que ver todos los puntos de la revisión.

\documentclass[journal,onecolumn,12pt]{IEEEtran}

\usepackage{amsmath,amssymb,bm}
\usepackage{amsthm, amsfonts}	
\usepackage{bm,bbm}
\usepackage[normalem]{ulem}
\usepackage{color}
\usepackage{fancybox}
\usepackage{url,booktabs}
\usepackage[round]{natbib}

\usepackage{xr}

\title{Reply to Reviewer's Comments on\\
``Training a gaming agent on brainwaves''}
\author{}

\begin{document}

\maketitle
\pagenumbering{roman}
\setcounter{page}{1}

We are grateful to the reviewer for pointing out relevant issues in our manuscript.

In the following, we discuss how we dealt with each raised issue.

\vskip+1ex
\noindent \dotfill

\section*{\fbox{Reviewer \#1 Transcript:}}

This paper proposes the use of a gaming agent to be trained using Reinforcement Learning (RL) as well as the feedback obtained from EEG brainwaves of human critic observers. The idea of using brain patterns for boosting ML is highly interesting and well suited for the journal. Although it is not a new concept, it is nicely re-purposed for online use-case.

However, I am not sure if there is something new in the paper compared to the 2010 proof-of-concept (Iturrate et al.: Robot Reinforcement Learning using EEG-based reward signals). The presentation style seems a bit confusing and needs serious improvements. Background is very limited (some are incorporated in the introduction) and substantial work is required. There has been a lot of work in BCIs over the past decade and some in the area of games.

From the scientific part, the results are not so convincing. In particular, the proposed idea does not seem to be too practical method. The classification does not provide something significant as it stands at the moment. The sample used is also quite small and the complexity of the game is limited.

Nevertheless, the paper could be improved in many ways. An obvious point would be to improve the classifiers. Apart from this, I would suggest that authors would look at ways of manipulating the stimulus, stimulus presentation or giving out incentives to participants.

\section*{\fbox{Reviewer \#2 Transcript:}}

The paper is interesting and relevant. However in my opinion it needs revision for purposes of clarification and to improve the contribution.
Please see attached document for my comments.

Training a Gaming Agent on Brainwaves
There are too many grammatical errors to list individually.
//Does the header refer to a general template?
JOURNAL OF LATEX CLASS FILES, VOL. 14, NO. 8, AUGUST 2015
//The abstract read more like an introduction, rather than an indication of the work undertaken for the paper.
25 “Results show that there is an effective transfer of information and that
the agent learns successfully to solve the game efficiently.”
//This is too vague. What are the outcomes of the study?
39 This information is used to make a gaming agent improves its operational performance using electroencephalography (EEG) signals as feedback of the performed task, obtained from an observational human critic.
//There is a grammar issue. I don’t understand this sentence.
54 RL should be defined in main body of the paper. Also the term ‘agent’ needs to be defined/clarified. How does it relate to the Game Manager from Figure 1?
17 col 2 Recently, this technique has seen a come-back. //this is not scientific language
58 col 3 The precision of 25.125 is inappropriate P2, 46 col 2 What is “state information”?
P3, 2 red normally indicates an error
P3, 11 I assume that the “observational human critic” is the player/participant/subject/human observer. This role should be clarified and terminology used consistently.
P3, 41 define MNE
P3, 56 Thus, each epoch is composed of a matrix 500 x 8. // add channels
P4, 32 Hence, following the iterative procedure based on Equation 1, the Q-Table is updated in each iteration. After the algorithm finishes iterating through all the training episodes, the Q-Table is stored to test the performance of the agent.
// Will the game always terminate? How long does the game take? Does smooth progression toward finish affect the err potential?
P4 Fig 3. Is the chance score = 0.5?
P4 the labels referred to in Fig 5 should correlate with the test here, i.e., A= subject 1 etc.
P4 referring to Fig 6; a comparison ROC curve with subject 1 would be more interesting

P5, 34 what is meant by “experiences”?
P5, 29 col 2 – remove Average steps per Q-Table legend.
P5 50, col 2 The collected data show that ErrP signals can in fact be classified and used to train an agent effectively.
// how has effectiveness been determined here?
Page 6 Fig 10 the text is not legible, it should be improved.
Page 6, 40
“However, even though this implies that the agent misses frequently that an action taken is wrong, this is not hindering the overall performance and the agent is still learning.”
// Your results show that this is subject dependent
P6, 56
Results show that training a classifier with data of one subject, but using it
to classify the events of experiences of another subject does
not lead to an improvement on the performance of the agent.
// could a pre-trained generic classifier provide a better initial state, subsequently trained with observer data to converge more quickly?
Are there differential err potential for up, down, left, right?

\section*{\fbox{Reviewer \#3 Transcript:}}

Comments to the Author
The following work shows the usage of ErrPs for training a gaming agent using reinforcement learning. Authors attempt different conventional classification approaches, as well as intersubject classification.

It is unclear to me the benefit of evaluating single subject to single subject offline classification accuracy. Please elaborate on this. Since different subjects attained different performance, all combinations of subjects used for training and testing should be inspected for the 1:1 evaluation setup. Maybe classification accuracy could be reported at different steps (depending on the amount of training data – gradual increasing the number of subjects)
What is the ratio of hit/no hit segments of action (epochs)?
Page 3, column 2, lines 4-9. It is unclear at this stage what action from the starting point would generate an ErrP.
moves-> move
Page 3, column 2, lines 11-13. Has the MinMax Scaler been applied in any other BCI related study or elsewhere? I think including a reference would be useful.
Page 4. Figure 3. I would suggest adding another set of bars for the grand average classification scores.
Page 4, Figure 4. This figure is redundant and could be removed.
Page 5, Figure 5. The titles of the subplots would be more descriptive when replacing the letters with the corresponding subjects number.
Page 5, column 1, line 52, Not ->no
Page 5, column1, line 55, accumulative->cumulative
Page 6, Figure 8. It is unclear to me what is the benefit of showing both A and B. Since the behavior is similar in both cases.
Page 6, Figure 10. This figure is, in my opinion, incomplete. What is the reason for showing this subset of subjects? I suggest showing the confusion matrices of all subjects and/or their average.
Page 6, column 2, line 40. show -> shows

\subsection*{\ovalbox{Reviewer 1 General Comments}}

This paper proposes the use of a gaming agent to be trained using Reinforcement Learning (RL) as well as the feedback obtained from EEG brainwaves of human critic observers. The idea of using brain patterns for boosting ML is highly interesting and well suited for the journal. Although it is not a new concept, it is nicely re-purposed for online use-case.

However, I am not sure if there is something new in the paper compared to the 2010 proof-of-concept (Iturrate et al.: Robot Reinforcement Learning using EEG-based reward signals). The presentation style seems a bit confusing and needs serious improvements. Background is very limited (some are incorporated in the introduction) and substantial work is required. There has been a lot of work in BCIs over the past decade and some in the area of games.

\begin{quotation}
{\color{blue}
We conducted a literature review and updated the introduction accordingly.  We highlighted what we think is our contribution, which is a simple game that can be used to trigger the ErrP response in a very simple scenario that can be used to train.  Additionally, regarding the results that we got, we think it is important to emphasize the cumulative contribution of different subjects enhances the performance of an agent even though the classification is not good.
}
\end{quotation}

From the scientific part, the results are not so convincing. In particular, the proposed idea does not seem to be too practical method. The classification does not provide something significant as it stands at the moment. The sample used is also quite small and the complexity of the game is limited.

\begin{quotation}
{\color{blue}
Issues raised by the Reviewer are accurate and timely described.  We aim to find a suitable game that at the same time can be implemented by RL and that triggered the ErrP response.  AFAIK we do didnt find any experiment that tackles the generation of ErrP for games in this way.  Most of the work replicates the structure of Iturrate experiment in robotics but none on a simple game plataform as the one described here.
}
\end{quotation}

Nevertheless, the paper could be improved in many ways. An obvious point would be to improve the classifiers. Apart from this, I would suggest that authors would look at ways of manipulating the stimulus, stimulus presentation or giving out incentives to participants.

\begin{quotation}
{\color{blue}
Due to COVID crisis we are unable to perform further experimentation.  
}
\end{quotation}

\subsection*{\ovalbox{Reviewer 2 General Comments}}
The paper is interesting and relevant. However in my opinion it needs revision for purposes of clarification and to improve the contribution.
Please see attached document for my comments.

Training a Gaming Agent on Brainwaves
There are too many grammatical errors to list individually.

\begin{quotation}
{\color{blue}
We truly appreciate this level of detail in all the comments and the requests for information.  The value provided by the comments in huge.  Thanks !!
}
\end{quotation}

//Does the header refer to a general template?
JOURNAL OF LATEX CLASS FILES, VOL. 14, NO. 8, AUGUST 2015

\begin{quotation}
{\color{blue}
This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
}
\end{quotation}

//The abstract read more like an introduction, rather than an indication of the work undertaken for the paper.
25 “Results show that there is an effective transfer of information and that
the agent learns successfully to solve the game efficiently.”
//This is too vague. What are the outcomes of the study?

\begin{quotation}
{\color{blue}
We need to change the abstract according to all the changes that we have to do.
}
\end{quotation}

39 This information is used to make a gaming agent improves its operational performance using electroencephalography (EEG) signals as feedback of the performed task, obtained from an observational human critic.
//There is a grammar issue. I don’t understand this sentence.

\begin{quotation}
{\color{blue}
We modified the sentence.
}
\end{quotation}

54 RL should be defined in main body of the paper. Also the term ‘agent’ needs to be defined/clarified. How does it relate to the Game Manager from Figure 1?

\begin{quotation}
{\color{blue}
The acronym was revised and we also verified all the other acronyms used in the text.  The term agent was defined, and their relation with the Game Manager in Figure 1 was established.
}
\end{quotation}

17 col 2 Recently, this technique has seen a come-back. // this is not scientific language

\begin{quotation}
{\color{blue}
This mistake has been corrected.
}
\end{quotation}

58 col 3 The precision of 25.125 is inappropriate P2, 46 col 2 What is “state information”?

\begin{quotation}
{\color{blue}
The precision for this information was adjusted to two decimals for the age mean and standard deviation.  We removed the "state information" and replaced the wording of the phrase in order to clarify more clearly the information that we wanted to convey.
}
\end{quotation}

P3, 2 red normally indicates an error

\begin{quotation}
{\color{blue}
We understand the Reviewers point, and we agree with him that red is not the right color to represent the completion of a task in the game.  However, we do not want to change it this point because is not trivial the screen configuration that we used in the experiments that elicited the ErrP response, which may be affected by colors and shapes~\cite{REF}.
}
\end{quotation}

P3, 11 I assume that the “observational human critic” is the player/participant/subject/human observer. This role should be clarified and terminology used consistently.

\begin{quotation}
{\color{blue}
Absolutely.  I didn't decide if use OHC "observational human critic" or subject throughtout all the text.
}
\end{quotation}

P3, 41 define MNE

\begin{quotation}
{\color{blue}
Historically MNE standed for Miimun Error Estimate, a software package developed in Martinos Center of Harvard University.  Now MNE  is the name of the entire software platform to perform analysis of several type of brain signals like Magnetoencephalograpy and Electroencephalography.
}
\end{quotation}

P3, 56 Thus, each epoch is composed of a matrix 500 x 8. // add channels

\begin{quotation}
{\color{blue}
Excellent.
}
\end{quotation}

P4, 32 Hence, following the iterative procedure based on Equation 1, the Q-Table is updated in each iteration. After the algorithm finishes iterating through all the training episodes, the Q-Table is stored to test the performance of the agent.
// Will the game always terminate? How long does the game take? Does smooth progression toward finish affect the err potential?

\begin{quotation}
{\color{blue}

If the gaming agent moves randomly on the board of Figure 2, it takes on average 100 steps to arrive to the final location on the grid.  Each step, the movement direction is selected from the Q-Table once every 2 seconds, so on average it takes around 200 seconds to finish the game.  After some training, the Q-Table could potentially end up in loops so if the steps count arrives to 200 the game is interrupted and it starts all over again (and in that case no reward is received).

We didn't test if the err potential was affected by the smooth progression toward the end.  It's something interesting to test.

We added all this information in the paper.

}
\end{quotation}

P4 Fig 3. Is the chance score = 0.5?

\begin{quotation}
{\color{blue}
Yes, it is.  We added that information in the Figure caption.
}
\end{quotation}

P4 the labels referred to in Fig 5 should correlate with the test here, i.e., A= subject 1 etc.

\begin{quotation}
{\color{blue}
The figure labels were modified to reflect which graph references which subject, in a more clearly way.
}
\end{quotation}

P4 referring to Fig 6; a comparison ROC curve with subject 1 would be more interesting

\begin{quotation}
{\color{blue}
We added the ROC Curve for subject 1.
}
\end{quotation}

P5, 34 what is meant by “experiences”?

\begin{quotation}
{\color{blue}
This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
}
\end{quotation}

P5, 29 col 2 – remove Average steps per Q-Table legend.

\begin{quotation}
{\color{blue}
This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
}
\end{quotation}

P5 50, col 2 The collected data show that ErrP signals can in fact be classified and used to train an agent effectively.
// how has effectiveness been determined here?

\begin{quotation}
{\color{blue}
This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
}
\end{quotation}

Page 6 Fig 10 the text is not legible, it should be improved.

\begin{quotation}
{\color{blue}
This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
}
\end{quotation}

Page 6, 40
“However, even though this implies that the agent misses frequently that an action taken is wrong, this is not hindering the overall performance and the agent is still learning.”
// Your results show that this is subject dependent
P6, 56
Results show that training a classifier with data of one subject, but using it
to classify the events of experiences of another subject does
not lead to an improvement on the performance of the agent.

\begin{quotation}
{\color{blue}
This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
}
\end{quotation}

// could a pre-trained generic classifier provide a better initial state, subsequently trained with observer data to converge more quickly?
Are there differential err potential for up, down, left, right?

\begin{quotation}
{\color{blue}
This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
}
\end{quotation}

\vskip+1ex
\noindent \dotfill
\vskip+1ex

\subsection*{\ovalbox{Reviewer 3 General Comments}}

Comments to the Author
The following work shows the usage of ErrPs for training a gaming agent using reinforcement learning. Authors attempt different conventional classification approaches, as well as intersubject classification.

\begin{quotation}
{\color{blue}
This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
}
\end{quotation}

It is unclear to me the benefit of evaluating single subject to single subject offline classification accuracy. Please elaborate on this.

\begin{quotation}
{\color{blue}
This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
}
\end{quotation}

Since different subjects attained different performance, all combinations of subjects used for training and testing should be inspected for the 1:1 evaluation setup.

\begin{quotation}
{\color{blue}
This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
}
\end{quotation}

Maybe classification accuracy could be reported at different steps (depending on the amount of training data – gradual increasing the number of subjects)

\begin{quotation}
{\color{blue}
This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
}
\end{quotation}

What is the ratio of hit/no hit segments of action (epochs)?

\begin{quotation}
{\color{blue}
This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
}
\end{quotation}

Page 3, column 2, lines 4-9. It is unclear at this stage what action from the starting point would generate an ErrP.
moves-> move

\begin{quotation}
{\color{blue}
This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
}
\end{quotation}

Page 3, column 2, lines 11-13. Has the MinMax Scaler been applied in any other BCI related study or elsewhere? I think including a reference would be useful.

\begin{quotation}
{\color{blue}
This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
}
\end{quotation}

Page 4. Figure 3. I would suggest adding another set of bars for the grand average classification scores.

\begin{quotation}
{\color{blue}
This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
}
\end{quotation}

Page 4, Figure 4. This figure is redundant and could be removed.

\begin{quotation}
{\color{blue}
This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
}
\end{quotation}

Page 5, Figure 5. The titles of the subplots would be more descriptive when replacing the letters with the corresponding subjects number.

\begin{quotation}
{\color{blue}
This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
}
\end{quotation}

Page 5, column 1, line 52, Not ->no

\begin{quotation}
{\color{blue}
This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
}
\end{quotation}

Page 5, column1, line 55, accumulative->cumulative

\begin{quotation}
{\color{blue}
This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
}
\end{quotation}

Page 6, Figure 8. It is unclear to me what is the benefit of showing both A and B. Since the behavior is similar in both cases.

\begin{quotation}
{\color{blue}
This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
}
\end{quotation}

Page 6, Figure 10. This figure is, in my opinion, incomplete. What is the reason for showing this subset of subjects? I suggest showing the confusion matrices of all subjects and/or their average.

\begin{quotation}
{\color{blue}
This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
}
\end{quotation}

Page 6, column 2, line 40. show -> shows

\begin{quotation}
{\color{blue}
This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
}
\end{quotation}

\vskip+1ex
\noindent \dotfill
\vskip+1ex
\bibliographystyle{mdpi}
\bibliography{article}

\end{document}

### 2020-07-07 ErrP.tex
Ok, hay que ver todos los puntos de la revisión.

@@
 % The paper headers
-\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
+\markboth{IEEE Transactions on Games}%
 {Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}
@@
 \IEEEPARstart{T}{he} effectiveness of today's human–machine interaction and artificial intelligence is limited by a communication bottleneck as humans are required to translate high-level concepts into a machine-mandated sequence of instructions~\cite{CURSOR-CONTROL-PAPER}.
-This work tackles this problem by exploring the use of brain signals as an interface between human and computer, trying to overcome this limitation by providing information to the system without explicit communication from the user.
-This information is used to make a gaming agent improves its operational performance using electroencephalography (EEG) signals as feedback of the performed task, obtained from an observational human critic.
-The idea is that subjects observing a computer game playing, can train the gaming agent using only signals components called Error-related Potentials (ErrP) that can be identified from their brain signals.
-These can be found on EEG traces and are elicited when a subject is aware of the presence of an unexpected outcome, which she/he identifies as an error.
+This work tackles this problem by exploring the use of brain signals as an interface between human and computer, trying to provide information to the system without explicit communication from the user.
+To perform this task, a computer game is used as a means to simplify the task at hand.
+
+Games has been used extensively as tools to test new means of interactions\cite{REF}.
+Agents are computer programs that can sense the environment, process information, and act upon them modifying their environment.
+Gaming agents are instances of these programs that can interact with a computer game, behaving like a real user playing the game.
+They are required to understand how to proceed in this context so they need to have enough information to understand first how to play (the game mechanics) and which strategy can they use to effectively win the game.
+
+In this work, this information is obtained from an observational human critic in the form of electroencephalographic (EEG) signals.
+These are used as feedback to evaluate the operational performance of the gaming agent.
+Observational human critics are subjects observing a computer gaming agent playing the game.
+These subjects can train the gaming agent using only signals components called Error-related Potentials (ErrP) that can be identified from their brain signals.
+This type of signals can be found on EEG traces and are elicited when a subject is aware of the presence of an unexpected outcome, which she/he identifies as an error.
 It is currently an extensive area of research in the neuroscience community~\cite{Holroyd2009}.
@@
 
-In order to train the agent, RL~\cite{Santos1999} comes as a natural solution for this scenario from the field of Artificial Intelligence.
-RL is an algorithmic learning strategy that can be established by mimicking how biological agents learn from its environment by exploring it and getting feedback rewards, either negative or positive.
+In order to train the agent, Reinforcement Learning (RL)~\cite{Santos1999} comes as a natural solution for this scenario from the field of Artificial Intelligence.
+This is an algorithmic learning strategy that can be established by mimicking how biological agents learn from its environment by exploring it and getting feedback rewards, either negative or positive.
 This strategy aims to maximize the amount of positive rewards while keeping the number of negative feedback low.
 Thus, the learning problem is  posed as a mere stochastic optimization strategy~\cite{sutton2018reinforcement}.
-Recently, this technique has seen a come-back.
+Recently, this technique has been used extensively in the context of recent advances in artificial intelligence~\cite{REF}.
 Nonneglected is the influence of DeepBrain's AlphaGo project, which was the first to reach a very high proficiency when it won the complex game Go against several world champions~\cite{ALPHA-GO}.
@@
 Brainwaves are obtained by the OpenVibe Acquisition Server.
-The Game Manager is responsible for generating the game screen and is connected to the Acquisition Server to send stimulus information.
+The Game Manager is responsible for generating the game screen, the game mechanics, and the game movements performed by the gaming agent.
+It is also connected to the Acquisition Server to send stimulus information.
 The captured information is stored by the OpenVibe Designer.
@@
 The experimental procedure is summarized in Figure \ref{diag:complete_flow}.
-The central part is the retrieval of the subject's brain activity.
+The central part is the retrieval of the observation human critic's brain activity.
 This process is called brainwave session.
@@
 They are given a consent form with questions regarding their health (previous health issues and particular visual sensitivity), habits (sleeping hours, caffeine and alcohol consumption), as well as an approval petition to collect the required data.
-The brainwave sessions are performed with 8 subjects, 5 males and 3 females, average age 25.125 years, standard deviation 1.54 years, range of 22-28 years.
+The brainwave sessions are performed with 8 subjects, 5 males and 3 females, average age 25.12 years, standard deviation 1.54 years, range of 22-28 years.
 All subjects have normal vision, are right-handed and have no history of neurological disorders.
@@
 They are only told that the objective of the agent is to reach the goal and the four movements that the agent can make.
-When this concludes, the subject is introduced to the wireless digital EEG device (g.Nautilus, g.Tec, Austria) that they have to wear during the brainwave session.
+When this concludes, the subject is introduced to the wireless digital EEG device (g.Nautilus, g.Tec, Austria) that she/he has to wear during the brainwave session.
 It has eight electrodes (g.LADYbird, g.Tec, Austria) on the positions Fz, Cz, Pz, Oz, P3, P4, PO7 and PO8, identified according to the 10-20 International System, with a reference set to the right ear lobe and ground set as the AFz position.
@@
 A brainwave session consists of several experiences, each one being a game run.
-At the end, the game state information and the signal data with the game event information of each run are saved for offline processing.
+At the end, all the sequence of game movements and the signal data of each run are saved for offline processing.
 
@@
 A blue spot indicates current position of the agent whereas a green spot represents the goal, as shown in Figure  \ref{fig:game_representation}.
-The objective of the system is for the agent to reach the goal.
+The agent's objective is to reach the goal.
 The circular spot representing the goal remains static at the bottom-right position of the grid, while the one representing the position of the agent always starts at the upper-left position of the grid.
@@
 The blue spot represents the initial location while the green spot represents the target location.
-Once the agent reaches the target spot, its color turns to red to indicate the end of the play.}
+Once the agent reaches the target spot, its color turns red to indicate the end of the play.}
 \label{fig:game_representation}
@@
 
-To aid in detecting the ErrP response, an offline processing pipeline and classifier is constructed to identify whether the action taken by the agent is an error or not.
-It is developed in Python using the MNE platform \cite{MNE-PYTHON}, which is a package designed specifically for processing EEG and Magnetoencephalography data, and built upon the machine learning library Scikit-Learn~\cite{scikit-learn}.
+To aid in detecting the ErrP response, an offline processing pipeline and classifier is constructed to identify whether the action taken by the agent is an error or not, from the human observer point of view.
+It is developed in Python using the "MNE" software platform \cite{MNE-PYTHON}, which is a package designed specifically for processing EEG and Magnetoencephalography data, and built upon the machine learning library Scikit-Learn~\cite{scikit-learn}.
 
-This pipeline consists of offline processing the collected signals in order to train a classifier that can decide whether an error potential is triggered.
+This pipeline consists of the offline processing of the collected signals in order to train a classifier that can decide whether an error potential is triggered.
 Firstly, the output of a brainwave session is read and an additional band pass filter of 0.1-20.0Hz is applied to the signal.
@@
 Epochs consist of all the sample points that take place between the start of the event and 2 seconds later (time for each action to take place), resulting in 500 samples per channel, as the sample frequency is 250 Hz.
-Thus, each epoch is composed of a matrix $500$ x $8$.
+Thus, each epoch is composed of a matrix $500$ x $8$ channels.
 
@@
 
-In this way, the raw data of an brainwave session is processed into an array of experiences where each element is an array of epochs tagged with a number specifying the prediction of the classifier, i.e.
-if the epoch corresponds to an action that made the agent move further from the goal (hit) or an action that made the agent move closer to the goal (no-hit).
+In this way, the raw data of a brainwave session is processed into an array of experiences where each element is an array of epochs tagged with a number specifying the prediction of the classifier, i.e.
+if the epoch corresponds to an action that made the agent moves further from the goal (hit) or an action that made the agent moves closer to the goal (no-hit).
 The ErrP is expected to be found in hits.
@@
 Each epoch is regularized using a MinMaxScaler, i.e.
-substracting the minimun value in the feature and dividing by the signal peak-to-peak amplitude.
+substracting the minimun value in the epoch and dividing by the signal peak-to-peak amplitude.
 The eight channels are concatenated using the  MNE Vectorizer function to transform the data matrix into a single array sample.
@@
 
-Each experience consists of a list of game movement configuration and the associated epoch obtained from subject's brainwaves.
+Each experience consists of a list of game movement configurations and the associated epochs obtained from subject's brainwaves.
 The set of experiences of each subject is split into training and testing.
@@
 After a classifier is trained, the epochs of the experience are classified as hit or no-hit.
-A reward for each movement in the game run is produced, based on the classification of the event that correspond to that movement.
+A reward for each movement in the game run is produced, based on the classification of the epoch that correspond to that movement.
 The reward can either be -1 when the event is classified as a hit or 0 when it is classified as a no-hit.
@@
 Q-Learning~\cite{Watkins1992} is a form of model-free reinforcement learning algorithm where an agent tries an action at a particular state and evaluate its consequences in terms of the reward or penalty it receives.
-In order to represent rewards, a matrix is used, where rows correspond to all the possible states, whereas columns represent all possible actions.
-The reward for an action given a state, is the value that can be found on the corresponding row and column.
+In order to represent rewards, a matrix $Q(s,a)$ is used, where rows correspond to all the possible states, whereas columns represent all possible actions.
 This matrix is known as a Q-Table.
@@
 \begin{equation}
-    Q(s,a) \leftarrow Q(s,a) + \alpha[r+\gamma* \max_{\tilde{a}} Q(s, \tilde{a})-Q(s, a) ]
+    Q(s,a) \leftarrow Q(s,a) + \alpha[r+\gamma* \max_{\tilde{a}} Q(\tilde{s}, \tilde{a})-Q(s, a) ]
     \label{equ:update_q_table}
@@
 \noindent where $s$ is the current state, $a$ is the action, $\alpha$ represents the learning rate and $\gamma$ represents the discount factor, a value between 0 and 1 that determines the importance of long term results versus immediate rewards.
-Once the environment has been extensively explored and the Q-Table has been obtained, the action chosen is the one that maximizes the expected reward according to the Q-Table matrix.
+Hence,  $Q(s,a)$  is the expected value of the sum of discounted rewards that the agent will receive if in the $s$ state, it takes the action $a$ according to this policy.
+Once the environment has been extensively explored and the Q-Table has been obtained, the action chosen for a given state is the one that maximizes the expected reward according to the Q-Table matrix.
 
@@
 The Q-Table is initialized with zeros, unless a preexisting Q-Table is passed as a parameter.
-In order for the agent to learn from the feedback generated by the subject, the Q-Table is not used to determine the action to take at a given state.
-Instead, the policy which determines which action to take in a particular state is given by the steps taken from the brainwave session results.
+For the agent, in order to learn from the feedback generated by the subject, the Q-Table is not used to determine the action to take at a given state.
+Instead, the policy which determines which action to take in a particular state is given by the agent's actions taken from the brainwave session results.
 This allows to learn the Q-Table based on the subject's feedback from the movements the agent took, which are chosen pseudo-randomly, while executing the brainwave session.
-The previously mentioned feedback is not explicit as it comes from the interpreted brain signal data, which is collected while the agent is executing the brainwave session and then each action is classified as an error or not.
+The previously mentioned feedback is not explicit as it comes from the interpreted brain signal data.
 This implies that the reward is determined by the subject's brain activity.
@@
     \includegraphics[scale=0.4]{Images/algorithm_calibration/Total_calib.png}
-    \caption{Binary Classification Score using different classifiers while recognizing ErrP potentials for the eight subjects.}
+    \caption{Binary classification score using different classifiers while recognizing ErrP potentials for the eight subjects.  Chance Level is 0.5.}
     \label{fig:classifiers}
@@
 
-On the other hand, Figure \ref{fig:avg_steps} shows for each subject the average amount of steps the agent takes to reach the goal as the Q-Table is progressively trained using the reward information obtained from their tested experiences.
+On the other hand, Figure \ref{fig:avg_steps} shows for each subject the average amount of steps the agent takes to reach the goal as the Q-Table is progressively trained using the reward information obtained from their classified experiences.
 Each point corresponds to the average number of steps in 200 repetitions that it takes for the agent to reach the goal for a specific Q-Table.
@@
 \end{subfigure}
-\caption{Average number of steps for the agent when trained with experiences from subjects 1(A)-8(H).
+\caption{Average number of steps for the agent when trained with experiences from subjects 1-8.
 Y axis show the averaged number of steps, while x axis show the number of experiences used to cumulative train the Q-Table.}
@@
 However, the rate at which it learns varies per subject, depending on the classification accuracy of the extracted brainwaves.
-For example results for subject 1 (fig \ref{fig:avg_steps} A) show faster learning than those of subject 8 (fig \ref{fig:avg_steps} H).
+For example results for subject 1 show faster learning than those of subject 8 (Figure \ref{fig:avg_steps}).
 
@@
 Figures \ref{fig:avg_steps} E and \ref{fig:avg_steps} F show no apparent learning, as the amount of steps to reach the goal doesn't decrease when trained.
-These results are also consistent with their ROC curves, shown on Figures~\ref{fig:rocsubjects} obtained for both subjects, where the area under the curve are close to chance level.
+These results are also consistent with their classification ROC curves, shown on Figures~\ref{fig:rocsubjects} obtained for both subjects, where the area under the curve are close to chance level.
 Both subjects have less recorded data from the sessions in comparison to the rest of the subjects.
@@
 
-Once ErrP signals are identified they can be used to train a reinforcement learning algorithm.
+Once ErrP signals are identified they can be used to train an agent using a reinforcement learning algorithm.
 Brainwave sessions have a low amount of experiences in order to reduce fatigue from subjects.
@@
 The obtained accuracy to discriminate ErrPs is low.
-However, even with such a lower accuracy values, the RL algorithm was able to extract meaningful information from rewards files that were helpful to improve the agent performance.
+However, even with such a lower accuracy values, the RL algorithm was able to extract meaningful information from rewards that were helpful to improve the agent performance.
 
-Further work could be conducted in order to increase the complexity of the game to allow at least the possibility that the target position be dynamically changed.
+Further work will be conducted in order to increase the complexity of the game to allow the possibility that the target position be dynamically changed.
 In that case the agent would start to learn to follow the target, instead of learning to go to a specific static destination spot.
-Additionally, the classifier could be enhanced to recognize more effectively the Error Potential.
+Additionally, the classifier could be enhanced to recognize more effectively the Error Potential~\cite{Iwane2017}.
 
@@
 
-The authors would like to thank the Laboratory Centro de Inteligencia Computacional and to ITBA University
+The authors would like to thank the Laboratory Centro de Inteligencia Computacional and to ITBA University.
 

### 2020-07-07 review/response.letter.tex
Primera iteración de la carta de respuesta.

@@
 {\color{blue}
-This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
+HAY QUE REVISAR BIEN QUE QUEREMOS DECIR CON ESTO.
 }
@@
 {\color{blue}
-This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
+ESTO LO PODEMOS HACER ES ELIMINAR ESO DEL GRAFICO
 }
@@
 {\color{blue}
-This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
+EN ESTA LA IDEA SERIA RESPONDER QUE ES POSIBLE HACERLO PORQUE EL AGENTE SI NO LO ENTRENAS NO MEJORA Y SI LO ENTRENAS AUN CON DATOS POBRES SI MEJORA.
 }
@@
 {\color{blue}
-This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
+TIENEN USTEDES EL CODIGO PARA GENERAR ESTAS FIGURAS?  SERIA PARA AGRANDAR EL TEXTO
 }
@@
 // Your results show that this is subject dependent
+
+\begin{quotation}
+{\color{blue}
+This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
+}
+\end{quotation}
+
 P6, 56
@@
 {\color{blue}
-This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
+ACA NO ESTOY SEGURO QUE QUISO DECIR
 }
@@
 {\color{blue}
-This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
+We appreciate a lot the time dedicated to review our manuscript.
 }
@@
 {\color{blue}
-This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
+ErrP detection and experimentation is not an straightforward.
+We tested many variants of the game and none could produce the ErrP.
+We aimed to have a simple solution, a simple game.
+The single subject accuracy that we show on Figure 6 are illustrative that the level of ErrP single trial identification that we achieved for different subjects (which is low).
+We wanted to emphasize the finding that even with such low levels of identification (which is a common issue in BCI research \cite{REF}, it was possible for the agent to learn an efficient strategy.
 }
@@
 {\color{blue}
-This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
+ESTE SERIA UN GRAFICO EN UNA TABLA DE 8X8 DONDE SE MUESTRAN TODAS LAS COMBINACIONES POSIBLES. CREEN QUE ESTO SERIA ALGO FACTIBLE ?
 }
@@
 {\color{blue}
-This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
+CREO QUE APUNTA A ARMAR ALGUN GRAFICO QUE MUESTRE COMO VA MEJORANDO LA CLASIFICACION A MEDIDA QUE SE VA VARIANDO LOS CONJUNTOS DE TRAINING/TESTING.  NO TIENEN ALGO ASI NO ?
 }
@@
 {\color{blue}
-This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
+PARA CADA EXPERIENCIA, SE ACUERDAN CUAL ES LA RELACION HIT (TIENE ERRP)/NO HIT DE TODOS LOS MOVIMIENTOS QUE SE HACEN EN UNA SOLA CORRIDA ?
 }
@@
 {\color{blue}
-This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
+MMMMMMM
 }
@@
 {\color{blue}
-This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
+AGREGAR REFERENCIAS DE ALGUN OTRO ESTUDIO QUE USE MINMAX SCALER PARA BCI
 }
@@
 {\color{blue}
-This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
+LO QUE PIDE ACA EL REVISOR ES AGREGAR UNA BARRA MAS A CADA SUJETO CON LA CLASIFICACION HACIENDO PROMEDIO DE TODAS LAS SENALES.  MMMM Cre que esto sería dificil tenerlo....
 }
@@
 {\color{blue}
-This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
+YO CREO QUE SERIA MEJOR REEMPLAZAR LA FIGURA 3 CON UNA FIGURA QUE MUESTRE LO MISMO PERO MAS CLARA.  TIENEN USTEDES ALGUNA FIGURA ASI ?
 }
@@
 {\color{blue}
-This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
+We agree with Reviewer's comment.  We removed the letters and replace them with subject's numbers.
 }
@@
 {\color{blue}
-This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
+Fixed.  Thank you very much !
 }
@@
 {\color{blue}
-This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
+Fixed.
 }
@@
 {\color{blue}
-This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
+TIENE RAZON.  ACA PODEMOS MOSTRAR TODAS LAS CURVAS RESUMIDAS.  EL TEMA ES QUE HAY QUE CAMBIAR LOS LABELS PARA QUE PUEDAN AJUSTARSE COMO SI FUESEN GRAFICOS CHICOS, QUEDARIA DE 4X4.
 }
@@
 {\color{blue}
-This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
+HAY QUE MOSTRAR TODAS LAS MATRICES DE CONFUSION.
 }

### 2020-07-07 ErrP.tex
Primera iteración de la carta de respuesta.

@@
 This is evidenced in Figure~\ref{fig:transferlearning} where the agent training is performed by using rewards obtained by classifying epochs from one subject, but using a classifier which was trained using the brainwaves from a different subject.
-Not performance gain is evidenced, the agents learn nothing which implies that the reward information is useless.
+No performance gain is evidenced, the agents learn nothing which implies that the reward information is useless.
 
@@
 
-Finally, Figure~\ref{fig:avg_steps_all} shows the result of training an agent with accumulative experiences from subjects 1,2,3,4,7, and 8.
+Finally, Figure~\ref{fig:avg_steps_all} shows the result of training an agent with cumulative experiences from subjects 1,2,3,4,7, and 8.
 It can be seen that the overall performance of the agent improves as long as there are more experiences to be used to train it, regardless if they were generated from the brainwaves classification from different subjects.
@@
 
-Concluding, this research show evidence that brain signals can be used as an interface between human and a gaming computer enabling an alternative communication with the system without explicit input from the user.
+Concluding, this research shows evidence that brain signals can be used as an interface between human and a gaming computer enabling an alternative communication with the system without explicit input from the user.
 

### 2020-07-25 ErrP.tex
Subo ultimos cambios

@@
 % (should never be an issue)
-\IEEEPARstart{T}{he} effectiveness of today's human–machine interaction and artificial intelligence is limited by a communication bottleneck as humans are required to translate high-level concepts into a machine-mandated sequence of instructions~\cite{CURSOR-CONTROL-PAPER}.
-This work tackles this problem by exploring the use of brain signals as an interface between human and computer, trying to provide information to the system without explicit communication from the user.
-To perform this task, a computer game is used as a means to simplify the task at hand.
+\IEEEPARstart{T}{he} effectiveness of today's human–machine interaction and artificial intelligence is limited by a communication bottleneck as humans are required to translate high-level concepts into a machine-mandated sequence of instructions~\cite{Xu2020,CURSOR-CONTROL-PAPER}.
+This work tackles this problem by exploring the use of brain signals as an interface between humans and computers, trying to provide information to the system without explicit communication from the user.
 
-Games has been used extensively as tools to test new means of interactions\cite{REF}.
-Agents are computer programs that can sense the environment, process information, and act upon them modifying their environment.
-Gaming agents are instances of these programs that can interact with a computer game, behaving like a real user playing the game.
-They are required to understand how to proceed in this context so they need to have enough information to understand first how to play (the game mechanics) and which strategy can they use to effectively win the game.
+On the other hand, video games has been used widely as tools to test new means of interactions\cite{REF}.
+Gaming agents are computer programs that can sense the game environment, process information, and interact with a computer game, behaving like a real user playing the game.
 
-In this work, this information is obtained from an observational human critic in the form of electroencephalographic (EEG) signals.
-These are used as feedback to evaluate the operational performance of the gaming agent.
-Observational human critics are subjects observing a computer gaming agent playing the game.
-These subjects can train the gaming agent using only signals components called Error-related Potentials (ErrP) that can be identified from their brain signals.
+In this work, the feedback obtained from an observational human critic (OHC) in the form of electroencephalographic (EEG) signals is used to evaluate the operational performance of a gaming agent.
+Observational human critics are silent subjects observing a computer gaming agent playing the game.
+In this set up, gaming agents can be trained using only signals components called Error-related Potentials (ErrP) that can be identified from their brain signals.
 This type of signals can be found on EEG traces and are elicited when a subject is aware of the presence of an unexpected outcome, which she/he identifies as an error.
 It is currently an extensive area of research in the neuroscience community~\cite{Holroyd2009}.
+
 Error-related Potentials can be detected by signal processing and machine learning techniques~\cite{EERP-PAPER} and they are also used in Brain-Computer Interfaces (BCI) to implement or enhance artificial communication channels~\cite{Chavarriaga2014}.
 
-In order to train the agent, Reinforcement Learning (RL)~\cite{Santos1999} comes as a natural solution for this scenario from the field of Artificial Intelligence.
+In order to train the agent, Reinforcement Learning (RL)~\cite{Santos1999,Sutton2018} comes as a natural solution for this scenario from the field of Artificial Intelligence.
 This is an algorithmic learning strategy that can be established by mimicking how biological agents learn from its environment by exploring it and getting feedback rewards, either negative or positive.
@@
 
+Expandir todos los trabajos que se hacen en BCI que es cierto que son muchísimo.s
+
+To assess air traffic controllers decissions~\cite{Goh2019}.  to categorise actions as errors
+
+In the context of Brain Computer Interfaces a growing number of studies have demonstrated the feasibility of using ErrPs as detection for RL tasks.\cite{Wirth2020}.
+To enhance robotic behaviour\cite{Luo2019}.
+
 Previous research has explored the usage of RL with reward signals based on brain activity, recorded by an EEG-based BCI system during task execution.
@@
 In this same line, the objective of this work is to use the information extracted from brainwaves to enhance the performance of a gaming agent, replicating and extending the usage of this signal.
+
+Therefore, the two contributions of this work are (1) bla bla bla bla bla bla bla bla, (2)
 
@@
 Each epoch is regularized using a MinMaxScaler, i.e.
-substracting the minimun value in the epoch and dividing by the signal peak-to-peak amplitude.
+substracting the minimun value in the epoch and dividing by the signal peak-to-peak amplitude~\cite{Zhou2019}.
 The eight channels are concatenated using the  MNE Vectorizer function to transform the data matrix into a single array sample.

### 2020-07-29 ErrP.tex
Sigo escribiendo parte de la introducción.

@@
 e-mail: rramele@itba.edu.ar.}% <-this % stops a space
-\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}
+\thanks{Manuscript received December 9, 2019; revised August 20, 2020.}}
 
@@
 
+%n this study into the player’s emotional theory of mind (ToM) of gameplaying agents, we investigate how an agent’s behaviour and the player’s own performance and emotions shape the recognition of a frustrated behaviour.
+We focus on the perception of frustration as it is a prevalent affective experience in human-computer interaction.
+We present a testbed game tailored towards this end, in which a player competes against an agent with a frustration model based on theory.
+We collect gameplay data, an annotated ground truth about the player’s appraisal of the agent’s frustration, and apply face recognition to estimate the player’s emotional state.
+We examine the collected data through correlation analysis and predictive machine learning models, and find that the player’s observable emotions are not correlated highly with the perceived frustration of the agent.
+This suggests that our subject’s ToM is a cognitive process based on the gameplay context.
+Our predictive models—using ranking support vector machines—corroborate these results, yielding moderately accurate predictors of players’ ToM.
+
 % For peer review papers, you can put extra information on the cover
@@
 This work tackles this problem by exploring the use of brain signals as an interface between humans and computers, trying to provide information to the system without explicit communication from the user.
-
-On the other hand, video games has been used widely as tools to test new means of interactions\cite{REF}.
-Gaming agents are computer programs that can sense the game environment, process information, and interact with a computer game, behaving like a real user playing the game.
-
+In this respect, video games has been used widely as tools to test new means of interactions~\cite{Carter2014,Barr2007}.
+Gaming agents are computer programs that can sense the computer game environment, process information, and interact with it, behaving like a real user playing the game.
+They are used in the context of testing and evaluating artificial intelligence algorithms and procedures that aim to win the game or to behave like a real user player~\cite{Zhao2020}.
 In this work, the feedback obtained from an observational human critic (OHC) in the form of electroencephalographic (EEG) signals is used to evaluate the operational performance of a gaming agent.
@@
 Error-related Potentials can be detected by signal processing and machine learning techniques~\cite{EERP-PAPER} and they are also used in Brain-Computer Interfaces (BCI) to implement or enhance artificial communication channels~\cite{Chavarriaga2014}.
+
+The appealing idea of a direct interface between the human brain and an artificial system, called Brain Computer Interface (BCI) or Brain Machine Interfaces (BMI), has proved the feasibility of a distinct non-biological communication channel to transmit information from the Central Nervous System (CNS) to a computer device~\cite{Vasiljevic2020}.
+
+BCI is a new input modality to explicitely transfer informtion that can be used in the context of a computer game~\cite{Scherer2012} and their relevance in gaming environments was quickly recognized~\cite{Nijholt2007}.
+and are relevant in the context of the accessibility for video games~\cite{Aguado-Delgado2020}. and in the growing area of e-sports~\cite{Yakovlev2020}.
 
@@
 
-Therefore, the two contributions of this work are (1) bla bla bla bla bla bla bla bla, (2)
+Therefore, the four contributions of this work are (1) a very simple game that can elicit the ErrP potential, (2) the EEG brainwaves from observational human observers, (3) that even when classification accuracy is low and produces a noisy reward signal is enough for an agent to learn the optimal policy to solve this simple game and (4) the collaborative rewards from multiple observational human observers can compensate the lack of accuracy obtained from specific subjects.
 
@@
 
-Each experience consists of a list of game movement configurations and the associated epochs obtained from subject's brainwaves.
-The set of experiences of each subject is split into training and testing.
+Each experience consists of a list of game movement configurations and the associated epochs obtained from OHC's brainwaves.
+The set of experiences of each OHC is split into training and testing.
 Training experiences are used to train the classifier, whereas test experiences are used to test its performance.
@@
 The Q-Table is initialized with zeros, unless a preexisting Q-Table is passed as a parameter.
-For the agent, in order to learn from the feedback generated by the subject, the Q-Table is not used to determine the action to take at a given state.
+For the agent, in order to learn from the feedback generated by the OHC, the Q-Table is not used to determine the action to take at a given state.
 Instead, the policy which determines which action to take in a particular state is given by the agent's actions taken from the brainwave session results.
-This allows to learn the Q-Table based on the subject's feedback from the movements the agent took, which are chosen pseudo-randomly, while executing the brainwave session.
+This allows to learn the Q-Table based on the OHC's feedback from the movements the agent took, which are chosen pseudo-randomly, while executing the brainwave session.
 The previously mentioned feedback is not explicit as it comes from the interpreted brain signal data.
-This implies that the reward is determined by the subject's brain activity.
+This implies that the reward is determined by the OHC's brain activity.
 
@@
 
-Figures~\ref{fig:classifiers} and~\ref{fig:logisticregression} show the binary classification accuracy obtained for the eight subjects for the four different classification algorithms using a 10-fold cross validation procedure.
+Figures~\ref{fig:classifiers} and~\ref{fig:logisticregression} show the binary classification accuracy obtained for the eight OHCs for the four different classification algorithms using a 10-fold cross validation procedure.
 The best overall performance is obtained using Logistic Regression.
@@
     \includegraphics[scale=0.4]{Images/algorithm_calibration/Total_calib.png}
-    \caption{Binary classification score using different classifiers while recognizing ErrP potentials for the eight subjects.  Chance Level is 0.5.}
+    \caption{Binary classification score using different classifiers while recognizing ErrP potentials for the eight OHCs.  Chance Level is 0.5.}
     \label{fig:classifiers}
@@
     \includegraphics[scale=0.4]{Images/algorithm_calibration/LR_calib.png}
-    \caption{Binary Classification Score using Logistic Regression for the eight subjects.}
+    \caption{Binary Classification Score using Logistic Regression for the eight OHCs.}
     \label{fig:logisticregression}
@@
 
-On the other hand, Figure \ref{fig:avg_steps} shows for each subject the average amount of steps the agent takes to reach the goal as the Q-Table is progressively trained using the reward information obtained from their classified experiences.
+On the other hand, Figure \ref{fig:avg_steps} shows for each OHC the average amount of steps the agent takes to reach the goal as the Q-Table is progressively trained using the reward information obtained from their classified experiences.
 Each point corresponds to the average number of steps in 200 repetitions that it takes for the agent to reach the goal for a specific Q-Table.
@@
 \end{subfigure}
-\caption{Average number of steps for the agent when trained with experiences from subjects 1-8.
+\caption{Average number of steps for the agent when trained with experiences from OHCs 1-8.
 Y axis show the averaged number of steps, while x axis show the number of experiences used to cumulative train the Q-Table.}
@@
 The results show that as the Q-Table is progressively trained the average amount of steps decreases, meaning that the agent learns.
-However, the rate at which it learns varies per subject, depending on the classification accuracy of the extracted brainwaves.
-For example results for subject 1 show faster learning than those of subject 8 (Figure \ref{fig:avg_steps}).
+However, the rate at which it learns varies per OHC, depending on the classification accuracy of the extracted brainwaves.
+For example results for OHC 1 show faster learning than those of OHC 8 (Figure \ref{fig:avg_steps}).
 
-In the case for subject 5 and 6, the reward information obtained from the brainwaves is not enough to train the agent effectively.
+In the case for OHC 5 and 6, the reward information obtained from the brainwaves is not enough to train the agent effectively.
 Figures \ref{fig:avg_steps} E and \ref{fig:avg_steps} F show no apparent learning, as the amount of steps to reach the goal doesn't decrease when trained.
-These results are also consistent with their classification ROC curves, shown on Figures~\ref{fig:rocsubjects} obtained for both subjects, where the area under the curve are close to chance level.
-Both subjects have less recorded data from the sessions in comparison to the rest of the subjects.
-This variation in performance for different subjects has been studied extensively in BCI.
-Besides low data samples there are other reasons affecting the classification accuracy:  cognitive reasons, this being the subject not paying extensively attention to the game dynamics, very low Signal-To-Noise Ratio (SNR) of the ErrP component or even the BCI-illiteracy phenomena where the specific subject's signals do not contain the expected component response~\cite{Yousefi2019}.
+These results are also consistent with their classification ROC curves, shown on Figures~\ref{fig:rocsubjects} obtained for both OHCs, where the area under the curve are close to chance level.
+Both OHCs have less recorded data from the sessions in comparison to the rest of the OHCs.
+This variation in performance for different OHCs has been studied extensively in BCI.
+Besides low data samples there are other reasons affecting the classification accuracy:  cognitive reasons, this being the OHC not paying extensively attention to the game dynamics, very low Signal-To-Noise Ratio (SNR) of the ErrP component or even the BCI-illiteracy phenomena where the specific OHC's signals do not contain the expected component response~\cite{Yousefi2019}.
 
@@
 \end{subfigure}
-\caption{ROC Curves for subjects 5 (up) and 6 (down)}
+\caption{ROC Curves for OHCs 5 (up) and 6 (down)}
 \label{fig:rocsubjects}
@@
 As it can be seen, the agent learns nothing, and regardless of the amount of experiences that are used to learn the Q-Table, the number of steps required to reach the goal does not decrease.
-This pattern is also obtained when the experiences from subjects 5 and 6 are used, showing that the reward labeling predicted by the trained classifier for those subjects worked like a random classifier.
+This pattern is also obtained when the experiences from OHCs 5 and 6 are used, showing that the reward labeling predicted by the trained classifier for those OHCs worked like a random classifier.
 
@@
 Electroencephalographic signals have high inter-subject variability~\cite{Chavarriaga2014}.
-This is evidenced in Figure~\ref{fig:transferlearning} where the agent training is performed by using rewards obtained by classifying epochs from one subject, but using a classifier which was trained using the brainwaves from a different subject.
+This is evidenced in Figure~\ref{fig:transferlearning} where the agent training is performed by using rewards obtained by classifying epochs from one OHC, but using a classifier which was trained using the brainwaves from a different OHC.
 No performance gain is evidenced, the agents learn nothing which implies that the reward information is useless.
@@
 \end{subfigure}
-\caption{(A) Average steps using Q-table trained with experiences from subject 8 classified with a classifier trained with data from subject 6.
-(B) Average steps using Q-table trained with experiences from subject 1 classified with a classifier trained with data from subject 3.}
+\caption{(A) Average steps using Q-table trained with experiences from OHC 8 classified with a classifier trained with data from OHC 6.
+(B) Average steps using Q-table trained with experiences from OHC 1 classified with a classifier trained with data from OHC 3.}
 \label{fig:transferlearning}
@@
 
-Finally, Figure~\ref{fig:avg_steps_all} shows the result of training an agent with cumulative experiences from subjects 1,2,3,4,7, and 8.
-It can be seen that the overall performance of the agent improves as long as there are more experiences to be used to train it, regardless if they were generated from the brainwaves classification from different subjects.
+Finally, Figure~\ref{fig:avg_steps_all} shows the result of training an agent with cumulative experiences from OHCs 1,2,3,4,7, and 8.
+It can be seen that the overall performance of the agent improves as long as there are more experiences to be used to train it, regardless if they were generated from the brainwaves classification from different OHCs.
 
@@
 \includegraphics[scale=0.4]{Images/Average_steps/all.png}
-\caption{Average steps using Q-Table trained with 6 experiences from different subjects.}
+\caption{Average steps using Q-Table trained with 6 experiences from different OHCs.}
 \label{fig:avg_steps_all}
@@
 \end{subfigure}
-\caption{Confusion Matrix for subjects 1,3,4 and 8. Darker colors show higher values.  It can be seen the lower percentage of false positives (upper right corner of each chart).}
+\caption{Confusion Matrix for OHCs 1,3,4 and 8. Darker colors show higher values.  It can be seen the lower percentage of false positives (upper right corner of each chart).}
 \label{fig:confusionmatrix}
@@
 Once ErrP signals are identified they can be used to train an agent using a reinforcement learning algorithm.
-Brainwave sessions have a low amount of experiences in order to reduce fatigue from subjects.
+Brainwave sessions have a low amount of experiences in order to reduce fatigue from OHCs.
 However data suggests that longer sessions are required in order to reach better classification scores, since more data is available in order to train the classifier.
-It can be seen that subjects with the largest amounts of data have the best classification.
+It can be seen that OHCs with the largest amounts of data have the best classification.
 This can also be achieved designing a bigger game system that generates more samples with every session.
 
-At the same time, effective agent training depends on the subject's data that was used to train it.
-Results show that training a classifier with data of one subject, but using it to classify the events of experiences of another subject does not lead to an improvement on the performance of the agent.
+At the same time, effective agent training depends on the OHC's data that was used to train it.
+Results show that training a classifier with data of one OHC, but using it to classify the events of experiences of another OHC does not lead to an improvement on the performance of the agent.
 Despite that, the rewards generated from different subjects can be used to train the same Q-Table to improve its performance, which may lead to strategies where the overall performance is improved based on the information from different human critics at the same time.

### 2020-07-31 ErrP.tex
Subo algunos de los cambios que pidieron los revisores.

@@
 
+%In this work, we propose a Dynamic Difficulty Adjustment methodology to achieve automatic video game balance.
+The balance task is modeled as a meta game, a game where actions change the rules of another base game.
+Based on the model of Reinforcement Learning (RL), an agent assumes the role of a game master and learns its optimal policy by playing the meta game.
+In this new methodology we extend traditional RL by adding the existence of a meta environment whose state transition depends on the evolution of a base environment.
+In addition, we propose a Multi Agent System training model for the game master agent, where it plays against multiple agent opponents, each with a distinct behavior and proficiency level while playing the base game.
+Our experiment is conducted on an adaptive grid-world environment in singleplayer and multiplayer scenarios.
+Our results are expressed in twofold: (i) the resulting decision making by the game master through gameplay, which must comply in accordance to an established balance objective by the game designer; (ii) the initial conception of a framework for automatic game balance, where the balance task design is reduced to the modulation of a reward function (balance reward), an action space (balance strategies) and the definition of a balance space state.
+
 % For peer review papers, you can put extra information on the cover
@@
 
+%This work tackles this problem by exploring the use of brain signals as an interface between humans and computers, trying to provide information to the system without explicit communication from the user.
+
 % You must have at least 2 lines in the paragraph with the drop letter
@@
 \IEEEPARstart{T}{he} effectiveness of today's human–machine interaction and artificial intelligence is limited by a communication bottleneck as humans are required to translate high-level concepts into a machine-mandated sequence of instructions~\cite{Xu2020,CURSOR-CONTROL-PAPER}.
-This work tackles this problem by exploring the use of brain signals as an interface between humans and computers, trying to provide information to the system without explicit communication from the user.
-In this respect, video games has been used widely as tools to test new means of interactions~\cite{Carter2014,Barr2007}.
-Gaming agents are computer programs that can sense the computer game environment, process information, and interact with it, behaving like a real user playing the game.
-They are used in the context of testing and evaluating artificial intelligence algorithms and procedures that aim to win the game or to behave like a real user player~\cite{Zhao2020}.
+Hence, new interaction methods are required to increase the communication bandwidth between computers and human, or to produce alternative communications systems to increase the efficiency of this channel.
+In this respect, video games has been widely used as tools to test new means of interactions~\cite{Carter2014,Barr2007}.
+Video gaming agents are computer programs that can sense the computer game environment, process information, and interact with it, behaving like a real user playing the game.
+They are used in the context of testing and evaluating artificial intelligence algorithms that aim to win the game or to behave like a real user player~\cite{Zhao2020}.
 In this work, the feedback obtained from an observational human critic (OHC) in the form of electroencephalographic (EEG) signals is used to evaluate the operational performance of a gaming agent.
 Observational human critics are silent subjects observing a computer gaming agent playing the game.
-In this set up, gaming agents can be trained using only signals components called Error-related Potentials (ErrP) that can be identified from their brain signals.
+
+Concurrently, the appealing idea of a direct interface between the human brain and an artificial system, called Brain Computer Interface (BCI) or Brain Machine Interfaces (BMI), has proved the feasibility of a distinct non-biological communication channel to transmit information from the Central Nervous System (CNS) to a computer device~\cite{Vasiljevic2020}.
+BCI systems provide a new input modality that can be used in the context of a computer game~\cite{Scherer2012} and their relevance in gaming environments was quickly recognized~\cite{Nijholt2007}, is relevant in the context of the accessibility for video games~\cite{Aguado-Delgado2020} and in the growing area of e-sports~\cite{Yakovlev2020}.
+
+In this proposal, gaming agents can be trained using only signals components called Error-related Potentials (ErrP) that can be identified from their brain signals.
 This type of signals can be found on EEG traces and are elicited when a subject is aware of the presence of an unexpected outcome, which she/he identifies as an error.
 It is currently an extensive area of research in the neuroscience community~\cite{Holroyd2009}.
-
 Error-related Potentials can be detected by signal processing and machine learning techniques~\cite{EERP-PAPER} and they are also used in Brain-Computer Interfaces (BCI) to implement or enhance artificial communication channels~\cite{Chavarriaga2014}.
-
-The appealing idea of a direct interface between the human brain and an artificial system, called Brain Computer Interface (BCI) or Brain Machine Interfaces (BMI), has proved the feasibility of a distinct non-biological communication channel to transmit information from the Central Nervous System (CNS) to a computer device~\cite{Vasiljevic2020}.
-
-BCI is a new input modality to explicitely transfer informtion that can be used in the context of a computer game~\cite{Scherer2012} and their relevance in gaming environments was quickly recognized~\cite{Nijholt2007}.
-and are relevant in the context of the accessibility for video games~\cite{Aguado-Delgado2020}. and in the growing area of e-sports~\cite{Yakovlev2020}.
 
@@
 
-Expandir todos los trabajos que se hacen en BCI que es cierto que son muchísimo.s
-
-To assess air traffic controllers decissions~\cite{Goh2019}.  to categorise actions as errors
-
+Previous research has explored the usage of RL with reward signals based on brain activity, recorded by an EEG-based BCI system during task execution.
+The papers \cite{ROBOT-CONTROL-PAPER,Kim2017,Omedes2013} have successfully demonstrated that a robot can be controlled by obtaining a reward signal from a person's brain activity which is observing the robot solve a task.
 In the context of Brain Computer Interfaces a growing number of studies have demonstrated the feasibility of using ErrPs as detection for RL tasks.\cite{Wirth2020}.
 To enhance robotic behaviour\cite{Luo2019}.
-
-Previous research has explored the usage of RL with reward signals based on brain activity, recorded by an EEG-based BCI system during task execution.
-The papers \cite{ROBOT-CONTROL-PAPER,Kim2017,Omedes2013} have successfully demonstrated that a robot can be controlled by obtaining a reward signal from a person's brain activity which is observing the robot solve a task.
+To assess air traffic controllers decissions~\cite{Goh2019}.
+to categorise actions as errors.
 Other approaches have used the signal as an important feedback for human-robot interaction or to implement shared-control strategies~\cite{Schiatti2018}.
@@
 
-Therefore, the four contributions of this work are (1) a very simple game that can elicit the ErrP potential, (2) the EEG brainwaves from observational human observers, (3) that even when classification accuracy is low and produces a noisy reward signal is enough for an agent to learn the optimal policy to solve this simple game and (4) the collaborative rewards from multiple observational human observers can compensate the lack of accuracy obtained from specific subjects.
+Therefore, the four contributions of this work are (1) a very simple game that can elicit the ErrP potential, (2) the EEG brainwaves dataset from observational human observers, (3) results that confirm that even when ErrP classification accuracy is low and produces a noisy reward signal, that provides enough information for an agent to learn the optimal policy to solve the simple game and (4) that collaborative rewards from multiple observational human observers can compensate the lack of accuracy obtained from specific subjects.
 

### 2020-08-10 ErrP.tex
Otra vuelta. Quedaron muy bien los gráficos.

@@
 Hence, new interaction methods are required to increase the communication bandwidth between computers and human, or to produce alternative communications systems to increase the efficiency of this channel.
-In this respect, video games has been widely used as tools to test new means of interactions~\cite{Carter2014,Barr2007}.
-Video gaming agents are computer programs that can sense the computer game environment, process information, and interact with it, behaving like a real user playing the game.
+In this respect, video games has been widely used as test tools to assess new means of interactions~\cite{Carter2014,Barr2007}.
+Video gaming agents are computer programs that can sense the computer game environment, process information, and interact with it.
 They are used in the context of testing and evaluating artificial intelligence algorithms that aim to win the game or to behave like a real user player~\cite{Zhao2020}.
@@
 Concurrently, the appealing idea of a direct interface between the human brain and an artificial system, called Brain Computer Interface (BCI) or Brain Machine Interfaces (BMI), has proved the feasibility of a distinct non-biological communication channel to transmit information from the Central Nervous System (CNS) to a computer device~\cite{Vasiljevic2020}.
-BCI systems provide a new input modality that can be used in the context of a computer game~\cite{Scherer2012} and their relevance in gaming environments was quickly recognized~\cite{Nijholt2007}, is relevant in the context of the accessibility for video games~\cite{Aguado-Delgado2020} and in the growing area of e-sports~\cite{Yakovlev2020}.
-
-In this proposal, gaming agents can be trained using only signals components called Error-related Potentials (ErrP) that can be identified from their brain signals.
+BCI systems provide a new input modality that can be used in the context of a computer game~\cite{Scherer2012,Nijholt2007}, is relevant in the context of the accessibility for video games~\cite{Aguado-Delgado2020} and in the growing area of e-sports~\cite{Yakovlev2020}.
+
+In this proposal, gaming agents are trained using only signals components called Error-related Potentials (ErrP) that can be identified from their brain signals.
 This type of signals can be found on EEG traces and are elicited when a subject is aware of the presence of an unexpected outcome, which she/he identifies as an error.
 It is currently an extensive area of research in the neuroscience community~\cite{Holroyd2009}.
-Error-related Potentials can be detected by signal processing and machine learning techniques~\cite{EERP-PAPER} and they are also used in Brain-Computer Interfaces (BCI) to implement or enhance artificial communication channels~\cite{Chavarriaga2014}.
-
-In order to train the agent, Reinforcement Learning (RL)~\cite{Santos1999,Sutton2018} comes as a natural solution for this scenario from the field of Artificial Intelligence.
-This is an algorithmic learning strategy that can be established by mimicking how biological agents learn from its environment by exploring it and getting feedback rewards, either negative or positive.
+Error-related Potentials can be detected by signal processing and machine learning techniques~\cite{EERP-PAPER} and they are also used in Brain-Computer Interfaces to implement or enhance artificial communication channels~\cite{Chavarriaga2014}.
+
+In order to train the agent, Reinforcement Learning (RL)~\cite{Sutton2018} comes as a natural solution for this scenario from the field of Artificial Intelligence.
+This is an algorithmic learning strategy inspired on how biological agents learn by exploring their environment, and getting negative or positive feedback rewards.
 This strategy aims to maximize the amount of positive rewards while keeping the number of negative feedback low.
-Thus, the learning problem is  posed as a mere stochastic optimization strategy~\cite{sutton2018reinforcement}.
-Recently, this technique has been used extensively in the context of recent advances in artificial intelligence~\cite{REF}.
+Thus, the learning problem is  posed as a stochastic optimization strategy~\cite{Santos1999}.
+Recently, this technique has been used extensively in the context of  advances in artificial intelligence~\cite{Nguyen2020}.
 Nonneglected is the influence of DeepBrain's AlphaGo project, which was the first to reach a very high proficiency when it won the complex game Go against several world champions~\cite{ALPHA-GO}.
@@
 The papers \cite{ROBOT-CONTROL-PAPER,Kim2017,Omedes2013} have successfully demonstrated that a robot can be controlled by obtaining a reward signal from a person's brain activity which is observing the robot solve a task.
-In the context of Brain Computer Interfaces a growing number of studies have demonstrated the feasibility of using ErrPs as detection for RL tasks.\cite{Wirth2020}.
-To enhance robotic behaviour\cite{Luo2019}.
-To assess air traffic controllers decissions~\cite{Goh2019}.
-to categorise actions as errors.
+In the context of Brain Computer Interfaces a growing number of studies have demonstrated the feasibility of using ErrPs as rewards for RL schemes such as to enhance robotic behaviour\cite{Luo2019}, to assess air traffic controllers decissions~\cite{Goh2019} or  to categorise actions as errors~\cite{Wirth2020}.
 Other approaches have used the signal as an important feedback for human-robot interaction or to implement shared-control strategies~\cite{Schiatti2018}.
-Additionally, ErrPs have also been used in the context of games as an additional feedback channel that can be explored to enhance gaming experience~\cite{Plass-OudeBos2010,kober2018bci}.
-In this same line, the objective of this work is to use the information extracted from brainwaves to enhance the performance of a gaming agent, replicating and extending the usage of this signal.
-
-Therefore, the four contributions of this work are (1) a very simple game that can elicit the ErrP potential, (2) the EEG brainwaves dataset from observational human observers, (3) results that confirm that even when ErrP classification accuracy is low and produces a noisy reward signal, that provides enough information for an agent to learn the optimal policy to solve the simple game and (4) that collaborative rewards from multiple observational human observers can compensate the lack of accuracy obtained from specific subjects.
+Additionally, ErrPs have also been used in the context of games as an additional feedback channel that can be explored to improve gaming experience~\cite{Plass-OudeBos2010,kober2018bci}.
+
+Therefore, in this work, we aim to use the information extracted from brainwaves to enhance the performance of a gaming agent.
+The four contributions of are (1) a very simple game that can elicit the ErrP potential, (2) the EEG brainwaves dataset from observational human observers, (3) results that confirm that even when ErrP classification accuracy is low and produces a noisy reward signal, that provides enough information for an agent to learn the optimal policy to solve the simple game and (4) that collaborative rewards from multiple observational human observers can compensate the lack of accuracy obtained from specific subjects.
 
@@
 \captionsetup[subfigure]{justification=centering}
-\begin{subfigure}{0.25\textwidth}
-    \centering
-    \includegraphics[scale=0.2]{Images/Classification_test/roc_e.png}
+\begin{subfigure}{0.5\textwidth}
+\centering
+\includegraphics[scale=0.09]{revisedimages/roc_1.eps}   \hspace{-1.5em}
+\includegraphics[scale=0.09]{revisedimages/roc_2.eps} \\
+\vspace{-1.3em}
+\centering
+\includegraphics[scale=0.09]{revisedimages/roc_3.eps}   \hspace{-1.5em}
+ \includegraphics[scale=0.09]{revisedimages/roc_4.eps} \\
+ \centering
+  \includegraphics[scale=0.09]{revisedimages/roc_5.eps}   \hspace{-1.5em}
+  \includegraphics[scale=0.09]{revisedimages/roc_6.eps} \\
+  \centering
+  \includegraphics[scale=0.09]{revisedimages/roc_7.eps}    \hspace{-1.5em}
+  \includegraphics[scale=0.09]{revisedimages/roc_8.eps} \\
 \end{subfigure}
-\begin{subfigure}{0.25\textwidth}
-    \centering
-    \includegraphics[scale=0.2]{Images/Classification_test/roc_f.png}  
-\end{subfigure}
-\caption{ROC Curves for OHCs 5 (up) and 6 (down)}
+\caption{ROC Curves for OHCs 1-8. True positive rate is on the vertical axis and false positive rate on the horizontal axis.}
 \label{fig:rocsubjects}
@@
 \centering
-\includegraphics[scale=0.12]{Images/Classification_test/matrix_a.png}
-\includegraphics[scale=0.12]{Images/Classification_test/matrix_c.png}\\
-\includegraphics[scale=0.12]{Images/Classification_test/matrix_d.png}
-\includegraphics[scale=0.12]{Images/Classification_test/matrix_h.png}
+\includegraphics[scale=0.12]{revisedimages/matrix_1.eps}
+\includegraphics[scale=0.12]{revisedimages/matrix_2.eps}\\
+\includegraphics[scale=0.12]{revisedimages/matrix_3.eps}
+\includegraphics[scale=0.12]{revisedimages/matrix_4.eps}\\
+\includegraphics[scale=0.12]{revisedimages/matrix_5.eps}
+\includegraphics[scale=0.12]{revisedimages/matrix_6.eps}\\
+\includegraphics[scale=0.12]{revisedimages/matrix_7.eps}
+\includegraphics[scale=0.12]{revisedimages/matrix_8.eps}\\
 \end{subfigure}
-\caption{Confusion Matrix for OHCs 1,3,4 and 8. Darker colors show higher values.  It can be seen the lower percentage of false positives (upper right corner of each chart).}
+\caption{Confusion Matrix for OHCs 1-8. Darker colors show higher values.  It can be seen the lower percentage of false positives (upper right corner of each chart).}
 \label{fig:confusionmatrix}

### 2020-08-18 review/response.letter.tex
Update a modification to the response letter.

@@
 We conducted a literature review and updated the introduction accordingly.
-We highlighted what we think is our contribution, which is a simple game that can be used to trigger the ErrP response in a very simple scenario that can be used to train.
-Additionally, regarding the results that we got, we think it is important to emphasize the cumulative contribution of different subjects enhances the performance of an agent even though the classification is not good.
+We highlighted what we think is our contribution, which is a simple game that can be used to trigger the ErrP response in a very simple scenario that can be used to train the agent.
+Additionally, regarding the results that we got, we think it is important to emphasize that the cumulative contribution of different subjects enhances the performance of an agent even though the classification accuracy of ErrP signals is not good.
 }
@@
 We aim to find a suitable game that at the same time can be implemented by RL and that triggered the ErrP response.
-AFAIK we do didnt find any experiment that tackles the generation of ErrP for games in this way.
-Most of the work replicates the structure of Iturrate experiment in robotics but none on a simple game plataform as the one described here.
+As far as we are aware of, we couldn't find any experiment that tackles the generation of ErrP for games in this way.
+Most of the work replicates the structure of robot learning in robotics but none on a simple game platform as the one described here.
 }
@@
 {\color{blue}
-Due to COVID crisis we are unable to perform further experimentation.  
+In this context we are completely limited to perform further experimentation.  However, we added two more classification schemes.
 }

### 2020-08-18 ErrP.tex
Subo la nueva imágen de la clasificación, ajusto otras dos imágenes y actualicé el texto.

@@
 Therefore, in this work, we aim to use the information extracted from brainwaves to enhance the performance of a gaming agent.
-The four contributions of are (1) a very simple game that can elicit the ErrP potential, (2) the EEG brainwaves dataset from observational human observers, (3) results that confirm that even when ErrP classification accuracy is low and produces a noisy reward signal, that provides enough information for an agent to learn the optimal policy to solve the simple game and (4) that collaborative rewards from multiple observational human observers can compensate the lack of accuracy obtained from specific subjects.
+The four contributions  are (1) a very simple game that can elicit the ErrP potential, (2) the EEG brainwaves dataset from observational human observers, (3) results that confirm that even when ErrP classification accuracy is low and produces a noisy reward signal, that provides enough information for an agent to learn the optimal policy and solve the simple game and (4) that collaborative rewards from multiple observational human observers can compensate the lack of accuracy obtained from specific subjects.
 
@@
 Logistic Regression, Multi-layer Perceptron with a hidden layer of 100 neurons (i.e.
-default values for the Scikit-Learn MLPClassifier), Random Forest and finally a linear kernel Support Vector Classifier (i.e.
+default values for the Scikit-Learn MLPClassifier), Random Forest, KNeighbours with k=3 and finally a linear kernel Support Vector Classifier (i.e.
 SVM)~\cite{Lotte2018}.
@@
 
-Figures~\ref{fig:classifiers} and~\ref{fig:logisticregression} show the binary classification accuracy obtained for the eight OHCs for the four different classification algorithms using a 10-fold cross validation procedure.
+Figure~\ref{fig:classifiers} show the binary classification accuracy obtained for the eight OHCs for the four different classification algorithms using a 10-fold cross validation procedure.
 The best overall performance is obtained using Logistic Regression.
@@
     \centering
-    \includegraphics[scale=0.4]{Images/algorithm_calibration/Total_calib.png}
+    \includegraphics[scale=0.14]{revisedimages/cross_val.eps}
     \caption{Binary classification score using different classifiers while recognizing ErrP potentials for the eight OHCs.  Chance Level is 0.5.}
     \label{fig:classifiers}
-\end{figure}
-
-\begin{figure}[ht]
-    \centering
-    \includegraphics[scale=0.4]{Images/algorithm_calibration/LR_calib.png}
-    \caption{Binary Classification Score using Logistic Regression for the eight OHCs.}
-    \label{fig:logisticregression}
 \end{figure}
@@
 \end{subfigure}
-\caption{Average number of steps for the agent when trained with experiences from OHCs 1-8.
+\caption{Average number of steps for the agent to reach the goal when trained with experiences from OHCs 1-8.
 Y axis show the averaged number of steps, while x axis show the number of experiences used to cumulative train the Q-Table.}
@@
 In the case for OHC 5 and 6, the reward information obtained from the brainwaves is not enough to train the agent effectively.
-Figures \ref{fig:avg_steps} E and \ref{fig:avg_steps} F show no apparent learning, as the amount of steps to reach the goal doesn't decrease when trained.
+Figures \ref{fig:avg_steps} for subjects 5 and 6 show no apparent learning, as the amount of steps to reach the goal doesn't decrease when trained.
 These results are also consistent with their classification ROC curves, shown on Figures~\ref{fig:rocsubjects} obtained for both OHCs, where the area under the curve are close to chance level.
@@
 \includegraphics[scale=0.09]{revisedimages/roc_2.eps} \\
-\vspace{-1.3em}
+%\vspace{-1.3em}
 \centering
@@
 \centering
-\includegraphics[scale=0.4]{Images/Average_steps/noise.png}
+\includegraphics[scale=0.4]{Images/Average_steps/noise.eps}
 \caption{Average steps using Q-Table trained with a noisy signal.}
@@
 \centering
-\includegraphics[scale=0.4]{Images/Average_steps/all.png}
+\includegraphics[scale=0.4]{Images/Average_steps/all.eps}
 \caption{Average steps using Q-Table trained with 6 experiences from different OHCs.}
@@
 \centering
-\includegraphics[scale=0.12]{revisedimages/matrix_1.eps}
-\includegraphics[scale=0.12]{revisedimages/matrix_2.eps}\\
-\includegraphics[scale=0.12]{revisedimages/matrix_3.eps}
-\includegraphics[scale=0.12]{revisedimages/matrix_4.eps}\\
-\includegraphics[scale=0.12]{revisedimages/matrix_5.eps}
-\includegraphics[scale=0.12]{revisedimages/matrix_6.eps}\\
-\includegraphics[scale=0.12]{revisedimages/matrix_7.eps}
-\includegraphics[scale=0.12]{revisedimages/matrix_8.eps}\\
+\includegraphics[scale=0.14]{revisedimages/matrix_1.eps}
+\includegraphics[scale=0.14]{revisedimages/matrix_2.eps}\\
+\includegraphics[scale=0.14]{revisedimages/matrix_3.eps}
+\includegraphics[scale=0.14]{revisedimages/matrix_4.eps}\\
+\includegraphics[scale=0.14]{revisedimages/matrix_5.eps}
+\includegraphics[scale=0.14]{revisedimages/matrix_6.eps}\\
+\includegraphics[scale=0.14]{revisedimages/matrix_7.eps}
+\includegraphics[scale=0.14]{revisedimages/matrix_8.eps}\\
 \end{subfigure}

### 2020-08-19 ErrP.tex
Subo una nueva versión ya con todos los gráficos.
Subo algunos cambios adicionales.

@@
 The experimental procedure is summarized in Figure \ref{diag:complete_flow}.
-The central part is the retrieval of the observation human critic's brain activity.
+The central part is the retrieval of the OHC's brain activity.
 This process is called brainwave session.
@@
 \begin{subfigure}{0.5\textwidth}
-\includegraphics[scale=0.27]{Images/Average_steps/Ax.png}
-\includegraphics[scale=0.27]{Images/Average_steps/Bx.png}
+\includegraphics[scale=0.60]{revisedimages/transfer_learning_heatmap.eps}
 \end{subfigure}

### 2020-08-20 review/response.letter.tex
Subo una nueva versión con varias modificacones en el TEX en base a la carta de respuesta para los revisores.  Nos faltó un tema importante que era armar la clasificación grand-average que uno de los revisores pedía.  Esta clasificación implicaba en vez de tomar los segmentos uno a uno (single trial) tomar de a 10, promedirlos, y clasificar con eso.

--- 2020-07-07 review/response.letter.tex
@@
 {\color{blue}
-We conducted a literature review and updated the introduction accordingly.
-We highlighted what we think is our contribution, which is a simple game that can be used to trigger the ErrP response in a very simple scenario that can be used to train.
-Additionally, regarding the results that we got, we think it is important to emphasize the cumulative contribution of different subjects enhances the performance of an agent even though the classification is not good.
+We conducted a new BCI and games literature review and updated the introduction accordingly, adding more updated background.
+We highlighted what we think is our contribution, which is a simple game that can be used to trigger the ErrP response in a simple scenario that can be used to train an agent.
+We were unable to find a similar work from that same perspective.
 }
@@
 Issues raised by the Reviewer are accurate and timely described.
-We aim to find a suitable game that at the same time can be implemented by RL and that triggered the ErrP response.
-AFAIK we do didnt find any experiment that tackles the generation of ErrP for games in this way.
-Most of the work replicates the structure of Iturrate experiment in robotics but none on a simple game plataform as the one described here.
+We aimed to find a suitable game that at the same time can be trained with a Reinforcement Learning technique and that triggered the ErrP response as well.
+We modified the manuscript, emphasized three results of our experiments.
+First we show that the basic Q-Learning algorithm is robust to noisy signals.
+Additionally,  we showed the futility of transfer learning approaches using the brainwaves signals, and finally that the cumulative contribution of the rewards obtained from different subjects enhances the performance of an agent.
 }
@@
 {\color{blue}
-Due to COVID crisis we are unable to perform further experimentation.  
+We rewrote the classification scheme and performed two more experiments.
+First we included kNeighbours as a new classification algorithm.
+This can be seen in Section B and in Figure 3.
+Moreover, we performed a complete transfer learning experiment, verifying if it was possible to improve the efficiency of the gaming agent  and verified that the best results for the improvement (i.e.
+reduction) on the average number of steps required to reach the target in 200 plays is achieved when a classifier is trained with ErrP signals from the same subject that is used to identify the ErrP and to provide the rewards.
+This is added in Section V and in Figure 7.
 }
@@
 {\color{blue}
-We need to change the abstract according to all the changes that we have to do.
+We performed several changes in the manuscript.  We modified the introduction describing those changes and emphasizing what we think may be our main contributions.
 }
@@
 {\color{blue}
-We modified the sentence.
+We modified the sentence.  We thanks the reviewer for pointing out this issue.
 }
@@
 {\color{blue}
-The acronym was revised and we also verified all the other acronyms used in the text.  The term agent was defined, and their relation with the Game Manager in Figure 1 was established.
+The acronym was revised and we also verified all the other acronyms used in the text.  The term "agent" was defined, and their relation with the Game Manager in Figure 1 was established.
 }
@@
 {\color{blue}
-This mistake has been corrected.
+This mistake has been corrected.  We apologize for the bad choice of words.
 }
@@
 {\color{blue}
-The precision for this information was adjusted to two decimals for the age mean and standard deviation.
-We removed the "state information" and replaced the wording of the phrase in order to clarify more clearly the information that we wanted to convey.
+The precision was adjusted to two decimals for the age mean and the standard deviation.
+We removed  "state information" and replaced the wording of the phrase in order to clarify more clearly the information that we wanted to convey:  we refer to state information to the sequence of movement that the gaming performs on the game.
 }
@@
 {\color{blue}
-We understand the Reviewers point, and we agree with him that red is not the right color to represent the completion of a task in the game.
-However, we do not want to change it this point because is not trivial the screen configuration that we used in the experiments that elicited the ErrP response, which may be affected by colors and shapes~\cite{REF}.
+We understand the Reviewer's point, and we agree with her/him that red is not the right color to represent the completion of a task in the game, and in this case it may have cognitive implications regarding the generalized concept that red indicates an error.
+It is known that the ErrP response may be affected by colors and shapes~\cite{EIMER1997143}.
+The experiments that we performed were implemented with the board showed on Figure 2 of the manuscript.
+We added this very important issue at the conclusions in relation with possible future works.
 }
@@
 {\color{blue}
-Absolutely.  I didn't decide if use OHC "observational human critic" or subject throughtout all the text.
+Absolutely.  We preferred to use OHC "observational human critic" to emphasize what the subject is actually doing while using the system.
 }
@@
 {\color{blue}
-Historically MNE standed for Miimun Error Estimate, a software package developed in Martinos Center of Harvard University.
-Now MNE  is the name of the entire software platform to perform analysis of several type of brain signals like Magnetoencephalograpy and Electroencephalography.
+Historically MNE standed for Minimum Error Estimate, a software package developed in Martinos Center of Harvard University.
+Now MNE  is the name of a entire software platform to perform analysis of several type of brain signals like Magnetoencephalograpy and Electroencephalography.
 }
@@
 {\color{blue}
-Excellent.
+Excellent.  We added that information.
 }
@@
 P4, 32 Hence, following the iterative procedure based on Equation 1, the Q-Table is updated in each iteration.
-After the algorithm finishes iterating through all the training episodes, the Q-Table is stored to test the performance of the agent.
+After the algorithm finishes iterating throughout all the training episodes, the Q-Table is stored to test the performance of the agent.
 // Will the game always terminate? How long does the game take? Does smooth progression toward finish affect the err potential?
@@
 Each step, the movement direction is selected from the Q-Table once every 2 seconds, so on average it takes around 200 seconds to finish the game.
-After some training, the Q-Table could potentially end up in loops so if the steps count arrives to 200 the game is interrupted and it starts all over again (and in that case no reward is received).
-
-We didn't test if the err potential was affected by the smooth progression toward the end.  It's something interesting to test.
-
-We added all this information in the paper.
+After some training, the Q-Table could potentially end up in loops so if the steps count arrives to 200 the game is interrupted and it starts all over again.
+So far we didn't test if the Error Potential is affected by the smooth progression toward the end, which is indeed something interesting to verify in this simple scenario.
+We added this very interesting extension in Section 6.
 
@@
 {\color{blue}
-Yes, it is.  We added that information in the Figure caption.
+Yes, it is.  We added that information in the Figure's caption.
 }
@@
 {\color{blue}
-The figure labels were modified to reflect which graph references which subject, in a more clearly way.
+The figure labels on Figure 4(now) were modified to reflect which graph references which subject.  Additionally, we use the same notation on the new Figure 5.
 }
@@
 {\color{blue}
-We added the ROC Curve for subject 1.
+We added on Figure 5(now) all the ROC curves that we obtained for all the different subjects, including the one for Subject 1.  
 }
@@
 {\color{blue}
-This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
+Each experience is defined by.....
 }
@@
 {\color{blue}
-This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
+This was modified in all the Figures, adjusting fonts and labels.  We appreciate a lot the time to point out this feature to enhance the quality of the manuscript.
 }
@@
 {\color{blue}
-This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
+Each time the gaming agent plays this simple game, it takes on average around 100 steps to reach the target spot.
+We asked an observational human critic to watch the gaming agent play the game, while we recorded their brainwaves.
+We trained first a classifier to be able to recognize Error Potentials from these brainwaves.
+We started the game again, and the gaming agent started to move around the board, but this time each time an Error Potential was identified from the brainwaves, it was used as a negative reward to train a new Q-Table for the agent.
+We performed another experience, but this time the gaming agent used the Q-Table that was updated in the previous experience.
+We verified that by doing this experiment, the agent required less and less steps on average to reach the goal until it arrives to the optimal number of around 10 steps.
+We found that although the number of training sessions depended on the accuracy of the classifier, even with very low values (just above chance level), the agent learns and the number of average number of steps is reduced.
+We verified that if trained the agent with noise signals, completely uncorrelated with the reward, the agent learned nothing, and the average number of steps was not reduced at all.
+Finally, we also verified that if we train a classifier with Error Potentials from one subject and used that classifier to provide the rewards for the experiment, the number of steps is not reduced, and that do not depend on the subjects, is an instrinsical result which is produced when mixing the clasifiers.
+Only the usage of a classifier from the same subject produces this improvement.
+Finally, we verified that rewards obtained from different subjects, can be used to improve the performance of the gaming agent.
 }
@@
 {\color{blue}
-This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
+This is now Figure 9, we increased the fontsize, added a colormap and included the confusion matrices for all the subjects.
 }
@@
 // Your results show that this is subject dependent
+
+\begin{quotation}
+{\color{blue}
+Yes, the Reviewer is correct.  We modified this sentence to state more clearly the message that we wanted to convey, which is, that results are completely subject dependent, but that 
+}
+\end{quotation}
+
 P6, 56
@@
 not lead to an improvement on the performance of the agent.
-
-\begin{quotation}
-{\color{blue}
-This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
-}
-\end{quotation}
 
@@
 {\color{blue}
-This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
+The statement is absolutely right.
+We extended this experience per Reviewer's suggestion and we verified that effectively the only combination of training/testing in the recognition of ErrP that produces an improvement on the performance of the agent is the one that uses information from the same subject (check new Figure 7).
+We think a generic-clasiffier to identify ErrP potentials for any subject (i.e.
+without calibration) is a very research goal of the BCI community because it will allow to have more robust, and easier to use, with shorter setups, BCI devices.
+If such a generic pre-trained classifier could be conceived, this simple game can be used to verify if the number of training sessions required is reduced and this will confirm that the pre-trained classifier is helping to do it more quickly.
+We didn't verify if the error potential for up down left right per se produces a different error potential, though we verified that in general getting farther from the target (in Manhattan distance) produces a signal which is slightly different from the one that is produced when the gaming agent moves closer to the target.
+We added these very interesting experiences to perform in Section 6.
 }
@@
 {\color{blue}
-This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
+We tested many variants of the game and we found that not so many could produce the ErrP.
+We aimed to have a simple solution, a simple game.
+The single subject accuracy that we show on Figure 5(now) show the level of ErrP single trial identification that we achieved for different subjects (which is low).
+We wanted to emphasize the finding that even with such low levels of identification, it was possible for the agent to learn an efficient strategy.
 }
@@
 {\color{blue}
-This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
+This is an excellent idea that we now explored with a new experiment.
+We showed the results on Figure 7, where a classifier is trained to recognized ErrP signals using the information obtained from one Trainer subject and used to generate rewards for a gaming agent on a different Tester subject.
+We added information about this on Section 5.
 }
@@
 {\color{blue}
-This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
+The classification accuracy obtained for all subject is now being shown on Figure 5 with ROC curves.
+What is shown progressively is the experiment itself, where after each training session, a new Q-Table is generated based on rewards obtained from the previous training session and the agent improves their efficiency by reaching the target in a progressively less number of steps on average.
 }
@@
 {\color{blue}
-This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
+The initial ratio hit/no-hit segments is 50/50, so for each training session, as the average number of steps is around 100, it will be 50 segments of hit (ErrP when the gaming agent moves away from the target in terms of getting a higher module in manhatan distance) or no hit on the contrary.
+When the Q-Table is being updated, the number of hit segments starts to decrease.
 }
@@
 {\color{blue}
-This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
+The Reviewer is absolutely right in that there isn't any possible action that the gaming agent can perform at the beginning of the experience (the game agent is located at the upper-left corner).
+We modified the phrase to emphasize the message that we wanted to convey, and that there is a very important caveat of the experiment in terms that the gaming agent always has a 5\% chance of wandering and selecting an action randomly, regardless of their Q-Train (whether it is updated or not).
+This is precisely to avoid loops or deadlocks situations.
 }
@@
 {\color{blue}
-This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
+We added a reference where the MinMaxScaler is used in a BCI application (new page 3, second column).
 }
@@
 {\color{blue}
-This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
+This figure was removed, thank you very much for your comment.
 }
@@
 {\color{blue}
-This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
+We included now all the ROC curves for all the subjects, where the difference in AUCs can be seen more clearly.
 }
@@
 {\color{blue}
-This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
+Absolutely right.
+We included all the confusion matrices for all the subjects.
+The reason for this is that we wanted to convey the message that our hypothesis is that as false positives are low, those ErrP that are triggered are indeed good "rewards" that are useful for the training algorithm and the gaming agent is using that information, tough scarce, in a useful way to learn and improve it performance.
 }
@@
 \bibliographystyle{mdpi}
-\bibliography{article}
+\bibliography{Reference}
 

### 2020-08-20 ErrP.tex
Subo una nueva versión con varias modificacones en el TEX en base a la carta de respuesta para los revisores.  Nos faltó un tema importante que era armar la clasificación grand-average que uno de los revisores pedía.  Esta clasificación implicaba en vez de tomar los segmentos uno a uno (single trial) tomar de a 10, promedirlos, y clasificar con eso.

@@
 
-Further work will be conducted in order to increase the complexity of the game to allow the possibility that the target position be dynamically changed.
+The simple setup of the game and board allows to further experimentation, using the reduction of the number of steps as a validation of the achieved information transfer.
+It will be interesting to verify if the smooth progression towards the end alter the shape of the ErrP response.
+REF
+
+Further work will be conducted in order to increase the complexity of the game to allow the possibility that the target position be dynamically changed, or to consider how the ErrP response is triggered in relation with shapes and colors of the board markers~\cite{EIMER1997143}.
 In that case the agent would start to learn to follow the target, instead of learning to go to a specific static destination spot.

### 2020-08-21 review/response.letter.tex
Casi lista.

@@
 {\color{blue}
-We tested many variants of the game and we found that not so many could produce the ErrP.
-We aimed to have a simple solution, a simple game.
-The single subject accuracy that we show on Figure 5(now) show the level of ErrP single trial identification that we achieved for different subjects (which is low).
+We tested many variants of simple games and we found that only the one proposed here produced a distinctive  ErrP response.
+The single subject accuracy that is presented on Figure 5(now) shows the level of ErrP single trial identification that we achieved for different subjects (which is low).
 We wanted to emphasize the finding that even with such low levels of identification, it was possible for the agent to learn an efficient strategy.
@@
 This is an excellent idea that we now explored with a new experiment.
-We showed the results on Figure 7, where a classifier is trained to recognized ErrP signals using the information obtained from one Trainer subject and used to generate rewards for a gaming agent on a different Tester subject.
+We showed the results on Figure 7, where a classifier is trained to recognize ErrP signals using the information obtained from one Trainer subject and used to generate rewards for a gaming agent on a different Tester subject.
 We added information about this on Section 5.
@@
 {\color{blue}
-The initial ratio hit/no-hit segments is 50/50, so for each training session, as the average number of steps is around 100, it will be 50 segments of hit (ErrP when the gaming agent moves away from the target in terms of getting a higher module in manhatan distance) or no hit on the contrary.
-When the Q-Table is being updated, the number of hit segments starts to decrease.
+The initial ratio hit/no-hit segments is 50/50, so for each training session, as the average number of steps is around 100, it will be 50 segments of hit (moving further from the target) or no-hit (moving closer).
+As the Q-Table is being updated, the number of hit segments slightly decreases.
 }
@@
 This is precisely to avoid loops or deadlocks situations.
+On the other hand, we fixed the pointed out grammatical error as well.
 }

### 2020-08-21 review/response.letter.tex
Una versión un poco más cerrada con todos los cambios pero le falta algo de lectura.

@@
 
-We are grateful to the reviewer for pointing out relevant issues in our manuscript.
+We are grateful to all the reviewers for their tremendously helpful feedback.
 
@@
 {\color{blue}
-We conducted a new BCI and games literature review and updated the introduction accordingly, adding more updated background.
-We highlighted what we think is our contribution, which is a simple game that can be used to trigger the ErrP response in a simple scenario that can be used to train an agent.
+We conducted a new BCI and games literature review and updated the Introduction accordingly, adding more updated background.
+We highlight now what we think is our contribution, which is a simple game that can be used to trigger the ErrP response in a simple scenario that can be used to train an agent.
 We were unable to find a similar work from that same perspective.
@@
 First we show that the basic Q-Learning algorithm is robust to noisy signals.
-Additionally,  we showed the futility of transfer learning approaches using the brainwaves signals, and finally that the cumulative contribution of the rewards obtained from different subjects enhances the performance of an agent.
+Additionally,  we show the futility of transfer learning approaches using the brainwaves signals, and finally that the cumulative contribution of the rewards obtained from different subjects enhances the performance of an agent.
 }
@@
 This can be seen in Section B and in Figure 3.
+In that same Figure, we also added results obtained while performing signal averaging to enhance the SNR of the ErrP component.
 Moreover, we performed a complete transfer learning experiment, verifying if it was possible to improve the efficiency of the gaming agent and verified that the best results for the improvement (i.e.
-reduction) on the average number of steps required to reach the target in 200 plays is achieved when a classifier is trained with ErrP signals from the same subject that is used to identify the ErrP and to provide the rewards.
+reduction) on the average number of steps, required to reach the target in 200 plays, is achieved when a classifier is trained with ErrP signals from the same subject that is used to identify the ErrP and to provide the rewards.
 This is added in Section V and in Figure 7.
@@
 
+\vspace{2em}
 \begin{quotation}
 {\color{blue}
-We truly appreciate this level of detail in all the comments and the requests for information.  The value provided by the comments in huge.  Thanks !!
+We truly appreciate this level of detail in all the comments and the requests for information. 
 }
 \end{quotation}
+\vspace{2em}
 
@@
 
+\vspace{2em}
 \begin{quotation}
 {\color{blue}
-This is a shameful mistake, we are terrible sorry.  We thought this was going to be replaced by the platform automatically. Thanks for pointing out this error.
+This error has been fixed.  Thanks for pointing it out.
 }
 \end{quotation}
+\vspace{2em}
 
@@
 
+\vspace{2em}
 \begin{quotation}
 {\color{blue}
-We performed several changes in the manuscript.  We modified the introduction describing those changes and emphasizing what we think may be our main contributions.
+We performed several changes in the manuscript.  We modified the Introduction describing those changes and emphasizing what we think may be our main contributions.
 }
 \end{quotation}
+\vspace{2em}
 
@@
 
+\vspace{2em}
 \begin{quotation}
@@
 \end{quotation}
+\vspace{2em}
 
@@
 The precision was adjusted to two decimals for the age mean and the standard deviation.
-We removed  "state information" and replaced the wording of the phrase in order to clarify more clearly the information that we wanted to convey:  we refer to state information to the sequence of movement that the gaming performs on the game.
+We removed  "state information" and replaced the wording of the phrase in order to clarify more clearly the information that we wanted to convey:  we refer to state information to the sequence of movement that the gaming agent performs on the game.
 }
 \end{quotation}
+\vspace{2em}
 
@@
 We understand the Reviewer's point, and we agree with her/him that red is not the right color to represent the completion of a task in the game, and in this case it may have cognitive implications regarding the generalized concept that red indicates an error.
-It is known that the ErrP response may be affected by colors and shapes~\cite{EIMER1997143}.
+It is known that the ErrP response may be affected by colors and shapes (Eimer 1997, \textit{An event-related potential (ERP) study of transient and sustained visual attention to color and form}).
 The experiments that we performed were implemented with the board showed on Figure 2 of the manuscript.
@@
 
+\vspace{2em}
 \begin{quotation}
 {\color{blue}
-Absolutely.  We preferred to use OHC "observational human critic" to emphasize what the subject is actually doing while using the system.
+Absolutely.  We preferred to use OHC "observational human critic" to emphasize what the subject is actually doing while using the system.  We clarified this notation along the manuscript.
 }
 \end{quotation}
+\vspace{2em}
 
@@
 Now MNE  is the name of a entire software platform to perform analysis of several type of brain signals like Magnetoencephalograpy and Electroencephalography.
+We added a clarification about this on Section III.
 }
 \end{quotation}
+\vspace{2em}
 
@@
 Each step, the movement direction is selected from the Q-Table once every 2 seconds, so on average it takes around 200 seconds to finish the game.
-After some training, the Q-Table could potentially end up in loops so if the steps count arrives to 200 the game is interrupted and it starts all over again.
+After training, the Q-Table could potentially end up in loops so if the steps count arrives to 200 the game is interrupted and it starts all over again.
 So far we didn't test if the Error Potential is affected by the smooth progression toward the end, which is indeed something interesting to verify in this simple scenario.
@@
 
+\vspace{2em}
 \begin{quotation}
 {\color{blue}
-The figure labels on Figure 4(now) were modified to reflect which graph references which subject.  Additionally, we use the same notation on the new Figure 5.
+The figure labels on Figure 4(now) were modified to reflect which subfigure references which subject.  Additionally, we use the same notation on the new Figure 5.
 } 
 \end{quotation}
+\vspace{2em}
 
@@
 
+\vspace{2em}
 \begin{quotation}
 {\color{blue}
-This was modified in all the Figures, adjusting fonts and labels.  We appreciate a lot the time to point out this feature to enhance the quality of the manuscript.
+This was modified in all the Figures, adjusting fonts and labels.  We appreciate a lot the time to point out this issue.
 }
 \end{quotation}
+\vspace{2em}
 
@@
 We trained first a classifier to be able to recognize Error Potentials from these brainwaves.
-We started the game again, and the gaming agent started to move around the board, but this time each time an Error Potential was identified from the brainwaves, it was used as a negative reward to train a new Q-Table for the agent.
-We performed another experience, but this time the gaming agent used the Q-Table that was updated in the previous experience.
+We started the game again, and the gaming agent started to move around the board, but this time once an Error Potential was identified from the brainwaves, it was used as a negative reward to train a new Q-Table for the agent.
+The game was iteratively repeated, but the gaming agent used the Q-Table that was updated in the previous experience.
 We verified that by doing this experiment, the agent required less and less steps on average to reach the goal until it arrives to the optimal number of around 10 steps.
@@
 We verified that if trained the agent with noise signals, completely uncorrelated with the reward, the agent learned nothing, and the average number of steps was not reduced at all.
-Finally, we also verified that if we train a classifier with Error Potentials from one subject and used that classifier to provide the rewards for the experiment, the number of steps is not reduced, and that do not depend on the subjects, is an instrinsical result which is produced when mixing the clasifiers.
+Finally, we also verified that if we train a classifier with Error Potentials from one subject and used that classifier to provide the rewards for the experiment, the number of steps is not reduced, and that do not depend on the subjects, is an intrinsic result which is produced when mixing the classifiers.
 Only the usage of a classifier from the same subject produces this improvement.
-Finally, we verified that rewards obtained from different subjects, can be used to improve the performance of the gaming agent.
+Finally, we verified that rewards obtained from different subjects, can be used to improve the performance of the gaming agent collaboratively.
 }
 \end{quotation}
+\vspace{2em}
 
@@
 
+\vspace{2em}
 \begin{quotation}
 {\color{blue}
-Yes, the Reviewer is correct.  We modified this sentence to state more clearly the message that we wanted to convey, which is, that results are completely subject dependent, but that 
+Yes, the Reviewer is correct.
+We modified this sentence to state more clearly the message that we wanted to convey, which is, that results are completely subject dependent.
+But that even when many action should be tagged as "wrong" (triggering an ErrP) only with a few of them right, it is enough to train the agent towards the optimal solution.
 }
 \end{quotation}
+\vspace{2em}
 
@@
 {\color{blue}
-LO QUE PIDE ACA EL REVISOR ES AGREGAR UNA BARRA MAS A CADA SUJETO CON LA CLASIFICACION HACIENDO PROMEDIO DE TODAS LAS SENALES.  MMMM Cre que esto sería dificil tenerlo....
+We added a new bar on the Figure 4 where we added the obtained classification accuracy when 5 segments are ensemble averaged to produce a signal (with an improved SNR in terms of the ErrP).
+For some subjects we do not have enough segments to
 }
@@
 \vskip+1ex
-\bibliographystyle{mdpi}
+\bibliographystyle{IEEEtran}
 \bibliography{Reference}

### 2020-08-21 ErrP.tex
Una versión un poco más cerrada con todos los cambios pero le falta algo de lectura.

--- 2020-08-19 ErrP.tex
@@
 \begin{abstract}
-The field of Brain Computer Interfaces (BCI) has seen a bloom in the past few years.
-One of its applications is the training of systems using signals originated from the human brain.
-Out of all the methods used to acquire information from the central nervous system, the one that has gained most popularity is Electroencephalography (EEG), mainly because of its effectiveness, low cost and its noninvasive characteristic.
-Event-related potential (ERP) are brain signals found on EEG that are time-locked to a particular event.
-Error-related potential (ErrP) are a particular type of ERP that  can be elicited by a person who attends a recognizable error.
-When subjects observe an agent who makes a mistake this potential can be discerned by analyzing the signals which are directly related with the cognitive interpretation of an erroneous outcome or decision.
-Reinforcement Learning (RL) is an Artificial Intelligence approach where an agent tries to maximize rewards obtained while interacting with an unknown environment.
-In this work, a gaming agent is trained using RL, and the feedback obtained from brainwaves of human critic observers.
-Results show that there is an effective transfer of information and that the agent learns successfully to solve the game efficiently.
+In this study, we propose a simple game scenario that can be used to trigger a feedback response embedded in the Electroencephalographic (EEG) signals of an observation human critic that observes an agent playing a game.
+Based on the model of Reinforcement Learning (RL), the gaming agent receives rewards for their actions on the game and learns its optimal policy.
+These rewards are obtained by implementing a Brain-Computer Interface (BCI) system that identifies signal components called Error-related Potentials (ErrP).
+These are brain signals found on EEG that can be elicited by a person who attends a recognizable error.
+When subjects observe the agent making a mistake this potential can be discerned by analyzing the signals which are directly related with the cognitive interpretation of an erroneous outcome or decision.
+We perform an iteratively incremental experiment where the agent plays, receives rewards from an observational human critic, and updates its policy for the next match.
+Our results are expressed in threefold: (i) the structure of a simple grid-based game that can elicit the ErrP signal component; (ii) low classification accuracy just above chance level that produces noisy rewards is enough to allow an agent to learn the optimal policy and solve the game; (iii) collaborative rewards from multiple observational human critics can compensate the lack of accuracy obtained from specific subjects or the difficulty of transfer learning solutions.
 \end{abstract}
@@
 Our results are expressed in twofold: (i) the resulting decision making by the game master through gameplay, which must comply in accordance to an established balance objective by the game designer; (ii) the initial conception of a framework for automatic game balance, where the balance task design is reduced to the modulation of a reward function (balance reward), an action space (balance strategies) and the definition of a balance space state.
+
+%In this study, we propose a simple game scenario that can be used to trigger a feedback response embedded in the Electroencephalographic (EEG) signals of an observation human critic that observes an agent playing a game.
+Based on the model of Reinforcement Learning (RL), a gaming agent receives rewards based on their actions on the game and learns its optimal policy.
+These rewards are obtained by implementing a Brain-Computer Interface (BCI) system that identifies signal components called Error-related Potentials (ErrP).
+These are brain signals found on EEG that can be elicited by a person who attends a recognizable error.
+When subjects observe the agent making a mistake this potential can be discerned by analyzing the signals which are directly related with the cognitive interpretation of an erroneous outcome or decision.
+Our experiment
+
+%In addition, we verified that the effective tagging of rewards could only be performed by using information from the same subject.
+
+%Our results are expressed in threefold: (i) a simple grid-based game can elicit the ErrP signal component; (ii) though ErrP identification accuracy is low and produces a noisy reward, an agent can learn the optimal policy and solve the simple game; (iii) collaborative rewards from multiple observational human observers can compensate the lack of accuracy obtained from specific subjects.
+
+%Therefore, in this work, we aim to use the information extracted from brainwaves to enhance the performance of a gaming agent.
+The three contributions  are (1) a very simple game that can elicit the ErrP potential, (2) results that confirm that even when ErrP classification accuracy is low and produces a noisy reward signal, that provides enough information for an agent to learn the optimal policy and solve the simple game and (3) that collaborative rewards from multiple observational human observers can compensate the lack of accuracy obtained from specific subjects.
+
+%Each time the gaming agent plays this simple game, it takes on average around 100 steps to reach the target spot.
+We asked an observational human critic to watch the gaming agent play the game, while we recorded their brainwaves.
+We trained first a classifier to be able to recognize Error Potentials from these brainwaves.
+We started the game again, and the gaming agent started to move around the board, but this time once an Error Potential was identified from the brainwaves, it was used as a negative reward to train a new Q-Table for the agent.
+The game was iteratively repeated, but the gaming agent used the Q-Table that was updated in the previous experience.
+%We verified that by doing this experiment, the agent required less and less steps on average to reach the goal until it arrives to the optimal number of around 10 steps.
+We found that although the number of training sessions depended on the accuracy of the classifier, even with very low values (just above chance level), the agent learns and the number of average number of steps is reduced.
+%We verified that if trained the agent with noise signals, completely uncorrelated with the reward, the agent learned nothing, and the average number of steps was not reduced at all.
+%Finally, we also verified that if we train a classifier with Error Potentials from one subject and used that classifier to provide the rewards for the experiment, the number of steps is not reduced, and that do not depend on the subjects, is an intrinsic result which is produced when mixing the classifiers.
+Only the usage of a classifier from the same subject produces this improvement.
+%Finally, we verified that rewards obtained from different subjects, can be used to improve the performance of the gaming agent collaboratively.
 
@@
 The papers \cite{ROBOT-CONTROL-PAPER,Kim2017,Omedes2013} have successfully demonstrated that a robot can be controlled by obtaining a reward signal from a person's brain activity which is observing the robot solve a task.
-In the context of Brain Computer Interfaces a growing number of studies have demonstrated the feasibility of using ErrPs as rewards for RL schemes such as to enhance robotic behaviour\cite{Luo2019}, to assess air traffic controllers decissions~\cite{Goh2019} or  to categorise actions as errors~\cite{Wirth2020}.
+In the context of Brain Computer Interfaces a growing number of studies have demonstrated the feasibility of using ErrPs as rewards for RL schemes such as to enhance robotic behaviour~\cite{Luo2019}, to assess air traffic controllers decissions~\cite{Goh2019} or  to categorise actions as errors~\cite{Wirth2020}.
 Other approaches have used the signal as an important feedback for human-robot interaction or to implement shared-control strategies~\cite{Schiatti2018}.
@@
 Therefore, in this work, we aim to use the information extracted from brainwaves to enhance the performance of a gaming agent.
-The four contributions  are (1) a very simple game that can elicit the ErrP potential, (2) the EEG brainwaves dataset from observational human observers, (3) results that confirm that even when ErrP classification accuracy is low and produces a noisy reward signal, that provides enough information for an agent to learn the optimal policy and solve the simple game and (4) that collaborative rewards from multiple observational human observers can compensate the lack of accuracy obtained from specific subjects.
+The three contributions  are (1) a very simple game that can elicit the ErrP potential, (2) results that confirm that even when ErrP classification accuracy is low and produces a noisy reward signal, that provides enough information for an agent to learn the optimal policy and solve the simple game and (3) that collaborative rewards from multiple observational human observers can compensate the lack of accuracy obtained from specific subjects.
 
@@
 When the subject is ready, the Game Manager and the OpenVibe Designer programs are launched and configured to communicate with the previously mentioned Acquisition Server.
-A brainwave session consists of several experiences, each one being a game run.
-At the end, all the sequence of game movements and the signal data of each run are saved for offline processing.
+A brainwave session consists of several matches, each one being a game run.
+At the end, all the sequence of game movements and the signal data generated for each match are saved for offline processing.
 
@@
 The circular spot representing the goal remains static at the bottom-right position of the grid, while the one representing the position of the agent always starts at the upper-left position of the grid.
-When the agent reaches the goal, the position where the agent and the goal are located turns red, showing that the experience has ended.
+When the agent reaches the goal, the position where the agent and the goal are located turns red, showing that the match has ended.
 There are four possible movements that the agent can perform: it can go upwards, downwards, towards the left and towards the right, and those movements are bounded to avoid the agent from leaving the grid.
 The movement direction is selected randomly and is executed once every 2 seconds.
-At the end, there is a pause of 5 seconds before the next experience starts.
+At the end, there is a pause of 5 seconds before the next match starts.
 Each time an agent moves, the Game Manager program sends an event marker to the Acquisition Server.
 This is considered as a stimulus to the observational human critic.
-The experience is designed for it to be evident whenever there is an error (i.e.
+The game is designed for it to be evident whenever there is an error (i.e.
 the agent moves away from the objective) so the subject can notice it immediately after the stimulus is presented, possibly triggering the expected cognitive response, which can be imprinted as an ErrP component within the EEG stream.
@@
 \centering 
-\caption{Grid system representation used in the Cognitive Game Experience.
+\caption{Grid system representation used in the cognitive game.
 The blue spot represents the initial location while the green spot represents the target location.
@@
 This pipeline consists of the offline processing of the collected signals in order to train a classifier that can decide whether an error potential is triggered.
-Firstly, the output of a brainwave session is read and an additional band pass filter of 0.1-20.0Hz is applied to the signal.
+Firstly, the output of a brainwave session is read and an additional band pass filter of 0.1-20.0 Hz is applied to the signal.
 Samples that correspond to the start of an event are tagged using the data from the stimulus channel.
@@
 
-Samples that do not correspond to an epoch (located beyond the 2 seconds frame after the onset of the event) are not used.
-Also, epochs referring to the start or finish of the experience are excluded.
-This is done because the start and the end of the experience doesn't involve the agent taking an action.
-
-In this way, the raw data of a brainwave session is processed into an array of experiences where each element is an array of epochs tagged with a number specifying the prediction of the classifier, i.e.
+Samples that do not correspond to an epoch (located beyond the 2 seconds frame after the onset of the event) are not used. Also, epochs referring to the start or finish of each match are excluded.
+
+In this way, the raw data of a brainwave session is processed into an array of matches where each element is an array of epochs tagged with a number specifying the prediction of the classifier, i.e.
 if the epoch corresponds to an action that made the agent moves further from the goal (hit) or an action that made the agent moves closer to the goal (no-hit).
@@
 Lastly, this data is used by the classification module as information to train and test a classifier.
-Four different classification algorithms are used.
-Logistic Regression, Multi-layer Perceptron with a hidden layer of 100 neurons (i.e.
+Five different classification algorithms are used:  Logistic Regression, Multi-layer Perceptron with a hidden layer of 100 neurons (i.e.
 default values for the Scikit-Learn MLPClassifier), Random Forest, KNeighbours with k=3 and finally a linear kernel Support Vector Classifier (i.e.
@@
 
-Each experience consists of a list of game movement configurations and the associated epochs obtained from OHC's brainwaves.
-The set of experiences of each OHC is split into training and testing.
-Training experiences are used to train the classifier, whereas test experiences are used to test its performance.
-After a classifier is trained, the epochs of the experience are classified as hit or no-hit.
-A reward for each movement in the game run is produced, based on the classification of the epoch that correspond to that movement.
+Each match consists of a list of game movement configurations and the associated epochs obtained from OHC's brainwaves.
+The set of matches of each OHC is split into training and testing.
+Training matches are used to train the classifier to identify the ErrP signal.
+After a classifier is trained, the epochs extracted from the test matches are classified as hit or no-hit.
+A reward for each movement in the game run is produced, based on the prediction from the classifier that correspond to that movement.
 The reward can either be -1 when the event is classified as a hit or 0 when it is classified as a no-hit.
@@
 \label{q_learning_step_alg}
-The Q-Table is initialized with zeros, unless a preexisting Q-Table is passed as a parameter.
-For the agent, in order to learn from the feedback generated by the OHC, the Q-Table is not used to determine the action to take at a given state.
-Instead, the policy which determines which action to take in a particular state is given by the agent's actions taken from the brainwave session results.
-This allows to learn the Q-Table based on the OHC's feedback from the movements the agent took, which are chosen pseudo-randomly, while executing the brainwave session.
+
+The Q-Table is initialized with zeros, so the initial policy for the agent is randomized.
+In order for the agent to learn from the feedback generated by the OHC,  the policy which determines which action to take in a particular state is given by the agent's actions taken from the previous brainwave session match.
+This allows to learn the Q-Table based on the OHC's feedback from the movements the agent took, which are initially chosen pseudo-randomly, while executing the brainwave session.
 The previously mentioned feedback is not explicit as it comes from the interpreted brain signal data.
@@
 Hence, following the iterative procedure based on Equation~\ref{equ:update_q_table}, the Q-Table is updated in each iteration.
-After the algorithm finishes iterating through all the training episodes, the Q-Table is stored to test the performance of the agent.
+After the algorithm finishes iterating through all the training episodes, the Q-Table is stored and used by the agent in the next match.
 
@@
 The best overall performance is obtained using Logistic Regression.
+In addition, the classification accuracy obtained averaging 5 epochs is shown as well.
+Although the signal averaging procedures improves the Signal-To-Noise-Radio (SNR) of the ErrP response, it reduces the number of data samples and produces a clear improvement only for the subjects that contain more samples (5, 3 and 7).
 
@@
     \centering
-    \includegraphics[scale=0.14]{revisedimages/cross_val.eps}
-    \caption{Binary classification score using different classifiers while recognizing ErrP potentials for the eight OHCs.  Chance Level is 0.5.}
+    \includegraphics[scale=0.12]{revisedimages/cross_val.eps}
+    \caption{Binary single trial classification score using four different classifiers while recognizing ErrP potentials for the eight OHCs.
+The classification score using an ensemble average of 5 epochs is shown as well (GrandAvg).
+Chance Level is 0.5.}
     \label{fig:classifiers}
@@
 
-On the other hand, Figure \ref{fig:avg_steps} shows for each OHC the average amount of steps the agent takes to reach the goal as the Q-Table is progressively trained using the reward information obtained from their classified experiences.
-Each point corresponds to the average number of steps in 200 repetitions that it takes for the agent to reach the goal for a specific Q-Table.
+On the other hand, Figure \ref{fig:avg_steps} shows for each OHC the average amount of steps the agent takes to reach the goal as the Q-Table is progressively trained using the reward information obtained from the prediction performed by the trained classifier.
+Each point corresponds to the average number of steps, in 200 repetitions, that it takes for the agent to reach the goal for a specific Q-Table.
 The first point represents the amount of steps the agent takes to reach the goal for a Q-Table that hasn't been trained at all, where movements are decided randomly.
-The next point corresponds to the amount of steps it takes to reach the goal using a policy derived from a Q-Table trained with one experience, and so on.
+The next point corresponds to the amount of steps it takes to reach the goal using a policy derived from a Q-Table trained with one game match, and so on.
 
@@
 \end{subfigure}
-\caption{Average number of steps for the agent to reach the goal when trained with experiences from OHCs 1-8.
-Y axis show the averaged number of steps, while x axis show the number of experiences used to cumulative train the Q-Table.}
+\caption{Average number of steps for the agent to reach the goal when trained with rewards generated from brainwaves from OHCs 1-8.
+Y axis show the averaged number of steps, while x axis show the number of game matches used to cumulative train the Q-Table.}
 \label{fig:avg_steps}
@@
 In the case for OHC 5 and 6, the reward information obtained from the brainwaves is not enough to train the agent effectively.
-Figures \ref{fig:avg_steps} for subjects 5 and 6 show no apparent learning, as the amount of steps to reach the goal doesn't decrease when trained.
+Figures \ref{fig:avg_steps} for OHC 5 and 6 show no apparent learning, as the amount of steps to reach the goal doesn't decrease when trained.
 These results are also consistent with their classification ROC curves, shown on Figures~\ref{fig:rocsubjects} obtained for both OHCs, where the area under the curve are close to chance level.
 Both OHCs have less recorded data from the sessions in comparison to the rest of the OHCs.
-This variation in performance for different OHCs has been studied extensively in BCI.
-Besides low data samples there are other reasons affecting the classification accuracy:  cognitive reasons, this being the OHC not paying extensively attention to the game dynamics, very low Signal-To-Noise Ratio (SNR) of the ErrP component or even the BCI-illiteracy phenomena where the specific OHC's signals do not contain the expected component response~\cite{Yousefi2019}.
+This variation in performance for different OHCs has been studied extensively in BCI~\cite{Chavarriaga2014}.
+Besides low data samples there are other reasons affecting the classification accuracy:  cognitive reasons (i.e.
+the OHC not paying extensively attention to the game dynamics), very low SNR of the ErrP component or even the BCI-illiteracy phenomena where the specific OHC's signals do not contain the expected component response~\cite{Yousefi2019}.
 
@@
 
-Figure~\ref{fig:avg_steps_noise} shows the result of an agent successively trained with experiences obtained from a brainwave session, generated with sham signals.
-In this case, random EEG signals were generated using OpenVibe Acquisition Server signal generator for all channels, as if they were generated from a human observer who doesn't pay attention to the game.
-As it can be seen, the agent learns nothing, and regardless of the amount of experiences that are used to learn the Q-Table, the number of steps required to reach the goal does not decrease.
-This pattern is also obtained when the experiences from OHCs 5 and 6 are used, showing that the reward labeling predicted by the trained classifier for those OHCs worked like a random classifier.
+Figure~\ref{fig:avg_steps_noise} shows the result of an agent successively trained with brainwave session matches where the EEG is generated with sham signals.
+In this case, random EEG signals are generated using OpenVibe Acquisition Server signal generator for all channels, as if they were produced by an OHC who doesn't pay attention to the game.
+As it can be seen, the agent learns nothing, and regardless of the amount of matches that are used to learn the Q-Table, the number of steps required to reach the goal does not decrease.
+This pattern is also obtained when the game matches from OHCs 5 and 6 are used, showing that the reward labeling predicted by the trained classifier for those cases worked like a random classifier.
 
@@
 Electroencephalographic signals have high inter-subject variability~\cite{Chavarriaga2014}.
-This is evidenced in Figure~\ref{fig:transferlearning} where the agent training is performed by using rewards obtained by classifying epochs from one OHC, but using a classifier which was trained using the brainwaves from a different OHC.
-No performance gain is evidenced, the agents learn nothing which implies that the reward information is useless.
+This is evidenced in Figure~\ref{fig:transferlearning} where the agent training is performed by using rewards obtained by classifying epochs from one Tester OHC, but using a classifier which was trained using the brainwaves from a different Trainer OHC.
+The figure shows the variation on the average number of steps required to reach the goal after training the agent with all the available matches.
+An improvement is shown as negative values.
+Only the diagonal of the heatmap matrix shows a clear improvement in terms of the reduction of the required number of steps to reach the goal (averaged per 200 runs) and it represents the improvement shown for each OHC in Figure~\ref{fig:avg_steps}).
+For this Transfer Learning experiment~\cite{Wu2016}, no performance gain is evidenced, the agents learn nothing and this implies that the reward information is useless.
 
@@
 \end{subfigure}
-\caption{(A) Average steps using Q-table trained with experiences from OHC 8 classified with a classifier trained with data from OHC 6.
-(B) Average steps using Q-table trained with experiences from OHC 1 classified with a classifier trained with data from OHC 3.}
+\caption{Heatmap for the transfer learning experiment.  }
 \label{fig:transferlearning}
@@
 
-Finally, Figure~\ref{fig:avg_steps_all} shows the result of training an agent with cumulative experiences from OHCs 1,2,3,4,7, and 8.
-It can be seen that the overall performance of the agent improves as long as there are more experiences to be used to train it, regardless if they were generated from the brainwaves classification from different OHCs.
+Finally, Figure~\ref{fig:avg_steps_all} shows the result of training an agent with cumulative brainwave session matches from OHCs 1,2,3,4,7, and 8.
+It can be seen that the overall performance of the agent improves as long as there are information to produce rewards, regardless if they were generated from the brainwaves classification from different OHCs.
 
@@
 \includegraphics[scale=0.4]{Images/Average_steps/all.eps}
-\caption{Average steps using Q-Table trained with 6 experiences from different OHCs.}
+\caption{Average steps using Q-Table trained with brainwave session matches from six different OHCs.}
 \label{fig:avg_steps_all}
@@
 
-This work aims to state whether ErrP signals could be used to train a gaming agent using reinforcement learning.
-The collected data show that ErrP signals can in fact be classified and used to train an agent effectively.
+This work aims to propose a simple game that can elicit the ErrP component and that can be used to train a gaming agent using the RL model.
+The collected data shows that ErrP signals can in fact be classified and used to train an agent effectively.
 
@@
 
-%Enfatizar la idea de que la mejor métrica de la propia detección está dada por la propia capacidad del agente de minimizar su tarea, que hay un flujo de información que involucra la propia percepción de la persona.
-
-%While classifying, the better performing classifier is Logistic Regression.
-One important aspect of the classification results is the low percentage of false positives (Figure~\ref{fig:confusionmatrix}), showing a high specificity.
-It is not common that the agent learns that an action is wrong when in fact it is an action that takes it closer to the goal.
-On the other hand, the percentage of false negatives is generally higher, but this is not a serious issue since missing out on learning that an action is wrong does not lower the performance of the agent, but only means it will take more experiences to learn a correct path.
-
-While classifying, the better performing classifier is Logistic Regression.
-One important aspect of the classification results is the low percentage of false positives (Figure~\ref{fig:confusionmatrix}), showing a high specificity.
+One additional aspect to remark is the robustness of the learning strategy based on Q-Learning~\cite{Bauer2015,Rubin2012}.
+The obtained accuracy to discriminate ErrPs is low.
+However, even with such a lower accuracy values, the RL algorithm was able to extract meaningful information from rewards that were helpful to improve the agent performance.
+Additionally, one important aspect of the classification results is the low percentage of false positives (Figure~\ref{fig:confusionmatrix}), showing a high specificity.
 It is not common that the agent learns that an action is wrong when in fact it is an action that takes it closer to the goal.
@@
 However, even though this implies that the agent misses frequently that an action taken is wrong, this is not hindering the overall performance and the agent is still learning.
-
+\textit{A little bit of accurate rewards is very useful for the RL algorithm}.
 %However, even though this imply that the agent misses frequently that an action taken is wrong, this do not seems to be a serious issue because the agent improves its performance.
@@
 
-Once ErrP signals are identified they can be used to train an agent using a reinforcement learning algorithm.
-Brainwave sessions have a low amount of experiences in order to reduce fatigue from OHCs.
+%Brainwave sessions have a low amount of matches in order to reduce fatigue from OHCs.
 However data suggests that longer sessions are required in order to reach better classification scores, since more data is available in order to train the classifier.
-It can be seen that OHCs with the largest amounts of data have the best classification.
+Matches from OHCs with the largest amounts of data have the best classification scores and produced more accurate rewards.
 This can also be achieved designing a bigger game system that generates more samples with every session.
+While classifying, the better performing classifier is Logistic Regression.
 
 At the same time, effective agent training depends on the OHC's data that was used to train it.
-Results show that training a classifier with data of one OHC, but using it to classify the events of experiences of another OHC does not lead to an improvement on the performance of the agent.
-Despite that, the rewards generated from different subjects can be used to train the same Q-Table to improve its performance, which may lead to strategies where the overall performance is improved based on the information from different human critics at the same time.
-
-One additional aspect to remark is the robustness of the learning strategy based on Q-Learning~\cite{Bauer2015,Rubin2012}.
-The obtained accuracy to discriminate ErrPs is low.
-However, even with such a lower accuracy values, the RL algorithm was able to extract meaningful information from rewards that were helpful to improve the agent performance.
+Results confirm the futility or complexity of using Transfer Learning~\cite{Wu2016}: training a classifier with data obtained from one OHC, but using it to identify ErrPs to produce rewards for the brainwave session match of another OHC does not increases the performance of the agent.
+Despite that, the rewards generated from different subjects can be used to train the same Q-Table to improve its performance, which may lead to strategies where the overall performance is enhanced based on the information from different human critics at the same time.
+
+The simple setup of the grid-based game allows to further experimentation, using the reduction of the number of steps as a validation of the achieved information transfer.
+It will be of research interest to verify if the smooth progression towards the end alter the shape of the ErrP response, or how the ErrP response is triggered in relation with different shapes and colors of the board markers~\cite{EIMER1997143}.
 
 Further work will be conducted in order to increase the complexity of the game to allow the possibility that the target position be dynamically changed.
-In that case the agent would start to learn to follow the target, instead of learning to go to a specific static destination spot.
-Additionally, the classifier could be enhanced to recognize more effectively the Error Potential~\cite{Iwane2017}.
+Although we found that the better performing classifier is Logistic Regression, there is clearly more room from improvement and the classifier could be enhanced to recognize more effectively the Error Potential~\cite{Iwane2017}.
 

### 2020-08-22 review/response.letter.tex
Subo la versión lista para subir.

@@
 First we show that the basic Q-Learning algorithm is robust to noisy signals.
-Additionally,  we show the futility of transfer learning approaches using the brainwaves signals, and finally that the cumulative contribution of the rewards obtained from different subjects enhances the performance of an agent.
+Additionally,  we show the futility of transfer learning approaches using the brainwave signals, and finally that the cumulative contribution of the rewards obtained from different subjects enhances the performance of an agent.
 }
@@
 {\color{blue}
-We rewrote the classification scheme and performed two more experiments.
+We added a new classifier and performed two more experiments.
 First we included kNeighbours as a new classification algorithm.
-This can be seen in Section B and in Figure 3.
+This can be seen in Section C and in Figure 3.
 In that same Figure, we also added results obtained while performing signal averaging to enhance the SNR of the ErrP component.
 Moreover, we performed a complete transfer learning experiment, verifying if it was possible to improve the efficiency of the gaming agent and verified that the best results for the improvement (i.e.
-reduction) on the average number of steps, required to reach the target in 200 plays, is achieved when a classifier is trained with ErrP signals from the same subject that is used to identify the ErrP and to provide the rewards.
-This is added in Section V and in Figure 7.
+reduction) on the average number of steps, required to reach the target in 200 plays, is achieved when a classifier is trained with ErrP signals from the same subject that is used to identify the ErrP.
+This is added in Section IV and in Figure 7.
+On the other hand, the structure of the game scenario allows to easily extend the experiments to verify what is the outcome of manipulating the stimulus, their presentation or the influence on the results if incentives are given to participants.
+We added this compelling ideas to the Section IV.
 }
@@
 {\color{blue}
-We performed several changes in the manuscript.  We modified the Introduction describing those changes and emphasizing what we think may be our main contributions.
+We performed several changes in the manuscript.  We modified the Introduction describing those changes and emphasizing what we think may be our main contributions.  We rewrote the Abstract completely.
 }
@@
 {\color{blue}
-The acronym was revised and we also verified all the other acronyms used in the text.  The term "agent" was defined, and their relation with the Game Manager in Figure 1 was established.
+The acronym was revised and we also verified all the other acronyms used in the text.
+The term "agent" was defined and presented in the Introduction, and their relation with the Game Manager in Figure 1 was established.
 }
@@
 The precision was adjusted to two decimals for the age mean and the standard deviation.
-We removed  "state information" and replaced the wording of the phrase in order to clarify more clearly the information that we wanted to convey:  we refer to state information to the sequence of movement that the gaming agent performs on the game.
+We removed  "state information" and replaced the wording of the phrase in order to clarify more clearly the information that we wanted to convey:  we refer to state information to the sequence of movements that the gaming agent performs on the game.
 }
@@
 {\color{blue}
-Absolutely.  We preferred to use OHC "observational human critic" to emphasize what the subject is actually doing while using the system.  We clarified this notation along the manuscript.
+Absolutely.
+We preferred to use OHC "observational human critic" to emphasize what the subject is actually doing while using the system.
+We clarified this notation at the Introduction and along the manuscript.
 }
@@
 Now MNE  is the name of a entire software platform to perform analysis of several type of brain signals like Magnetoencephalograpy and Electroencephalography.
-We added a clarification about this on Section III.
+We added a clarification about this on Section II.C.
 }
@@
 
-If the gaming agent moves randomly on the board of Figure 2, it takes on average 100 steps to arrive to the final location on the grid.
-Each step, the movement direction is selected from the Q-Table once every 2 seconds, so on average it takes around 200 seconds to finish the game.
-After training, the Q-Table could potentially end up in loops so if the steps count arrives to 200 the game is interrupted and it starts all over again.
+When the gaming agent moves randomly on the board of Figure 2, it takes on average 100 steps to arrive to the final location on the grid.
+Each step, the movement direction is performed once every 2 seconds, so on average it takes around 200 seconds to finish the game.
+After training during \textit{run sessions} (check new Section II.F), the agent starts to use the Q-Table to decide the next movement.
+However, the Q-Table could potentially end up producing endless loops or deadlocks so if the steps count arrives to 200 the game is interrupted and it starts all over again.
 So far we didn't test if the Error Potential is affected by the smooth progression toward the end, which is indeed something interesting to verify in this simple scenario.
-We added this very interesting extension in Section 6.
+We added this very interesting extension in Section IV.
 
@@
 {\color{blue}
-Each experience is defined by.....
+We added a new Section II.F to clarify this part of the experiment which was not explained at all.
+First we rewrote how we separated the two parts of the experiment, the "Cognitive Game Procedure" and the "Gaming Agent Learning Procedure".
+We replaced "experiences" with \textit{run session}.
+This all is explained in the above-mentioned section.
 }
@@
 We started the game again, and the gaming agent started to move around the board, but this time once an Error Potential was identified from the brainwaves, it was used as a negative reward to train a new Q-Table for the agent.
-The game was iteratively repeated, but the gaming agent used the Q-Table that was updated in the previous experience.
+The game was iteratively repeated, but the gaming agent used the Q-Table that was updated in the previous run session.
 We verified that by doing this experiment, the agent required less and less steps on average to reach the goal until it arrives to the optimal number of around 10 steps.
-We found that although the number of training sessions depended on the accuracy of the classifier, even with very low values (just above chance level), the agent learns and the number of average number of steps is reduced.
-We verified that if trained the agent with noise signals, completely uncorrelated with the reward, the agent learned nothing, and the average number of steps was not reduced at all.
-Finally, we also verified that if we train a classifier with Error Potentials from one subject and used that classifier to provide the rewards for the experiment, the number of steps is not reduced, and that do not depend on the subjects, is an intrinsic result which is produced when mixing the classifiers.
-Only the usage of a classifier from the same subject produces this improvement.
-Finally, we verified that rewards obtained from different subjects, can be used to improve the performance of the gaming agent collaboratively.
+We found that although the effectiveness of this improvement depended on the accuracy of the classifier, even with very low values (just above chance level), the agent learns and the number of average number of steps is reduced.
+We verified that if trained the agent with sham signals, completely uncorrelated with the reward, the agent learned nothing, and the average number of steps was not reduced at all.
+Finally, we also verified that if we train a classifier with Error Potentials from one subject and used that classifier to provide the rewards for the experiment, the number of steps is not reduced, and that do not depend on the subjects, is an intrinsic result which is produced when intermixing the OHCs.
+Only the usage of a trained classifier from the same OHC produces this improvement.
+Finally, we verified that rewards obtained from different OHCs, can be used to improve the performance of the gaming agent collaboratively.
 }
@@
 We extended this experience per Reviewer's suggestion and we verified that effectively the only combination of training/testing in the recognition of ErrP that produces an improvement on the performance of the agent is the one that uses information from the same subject (check new Figure 7).
-We think a generic-clasiffier to identify ErrP potentials for any subject (i.e.
-without calibration) is a very research goal of the BCI community because it will allow to have more robust, and easier to use, with shorter setups, BCI devices.
+We think a generic-classifier to identify ErrP potentials for any subject (i.e.
+without calibration) is a research goal of the BCI community because this will allow to have more robust, easier to use, with shorter setups  BCI devices (Suller 2012,\textit{Online use of error-related potentials in healthy users and people with severe motor impairment increases performance of a P300-BCI}).
 If such a generic pre-trained classifier could be conceived, this simple game can be used to verify if the number of training sessions required is reduced and this will confirm that the pre-trained classifier is helping to do it more quickly.
-We didn't verify if the error potential for up down left right per se produces a different error potential, though we verified that in general getting farther from the target (in Manhattan distance) produces a signal which is slightly different from the one that is produced when the gaming agent moves closer to the target.
-We added these very interesting experiences to perform in Section 6.
+We didn't verify if the error potential for up, down, left, right per se produces a different error potential, though we verified that in general getting farther from the target (in Manhattan distance) produces a signal which is slightly different from the one that is produced when the gaming agent moves closer to the target.
+We added these very interesting lines of further exploration in Section IV.
 }
@@
 We showed the results on Figure 7, where a classifier is trained to recognize ErrP signals using the information obtained from one Trainer subject and used to generate rewards for a gaming agent on a different Tester subject.
-We added information about this on Section 5.
+We added information about this on Section IV.
 }
@@
 The classification accuracy obtained for all subject is now being shown on Figure 5 with ROC curves.
-What is shown progressively is the experiment itself, where after each training session, a new Q-Table is generated based on rewards obtained from the previous training session and the agent improves their efficiency by reaching the target in a progressively less number of steps on average.
+What is shown progressively is the experiment itself, where after each gaming agent training match, a new Q-Table is generated based on the rewards tagged from the brainwave session.
+The agent improves their efficiency by reaching the target in a progressively less number of steps on average for each run session.
 }
@@
 {\color{blue}
-The initial ratio hit/no-hit segments is 50/50, so for each training session, as the average number of steps is around 100, it will be 50 segments of hit (moving further from the target) or no-hit (moving closer).
-As the Q-Table is being updated, the number of hit segments slightly decreases.
+The ratio hit/no-hit segments is 50/50, so for each brainwave session match, as the average number of steps is around 100, it will be 50 segments of hit (moving further from the target) and 50 of no-hit (moving closer).
 }
@@
 {\color{blue}
-The Reviewer is absolutely right in that there isn't any possible action that the gaming agent can perform at the beginning of the experience (the game agent is located at the upper-left corner).
-We modified the phrase to emphasize the message that we wanted to convey, and that there is a very important caveat of the experiment in terms that the gaming agent always has a 5\% chance of wandering and selecting an action randomly, regardless of their Q-Train (whether it is updated or not).
+The Reviewer is absolutely right in that there isn't any possible action that the gaming agent can perform at the beginning of the experience (the game agent is located at the upper-left corner) that may trigger an ErrP response.
+We modified the phrase to emphasize the message that we wanted to convey.
+Additionally, there is a very important caveat of the experiment.
+The gaming agent always has a 5\% chance of wandering and selecting an action randomly, regardless of their Q-Train.
 This is precisely to avoid loops or deadlocks situations.
+
 On the other hand, we fixed the pointed out grammatical error as well.
@@
 {\color{blue}
-We added a new bar on the Figure 4 where we added the obtained classification accuracy when 5 segments are ensemble averaged to produce a signal (with an improved SNR in terms of the ErrP).
-For some subjects we do not have enough segments to
+We added a new bar on the Figure 3 where we included the obtained classification accuracy when 5 segments are ensemble averaged to produce an averaged signal (with an improved SNR in terms of the ErrP).
+These scores are reported in the Figure 4 as "GrandAvg".
+There is a balance to be considered because adding more segments to the averaged signal reduces the number of available samples used for training the classifier.
 }
@@
 {\color{blue}
-This figure was removed, thank you very much for your comment.
+The figure was removed, thank you very much for your comment.
 }
@@
 {\color{blue}
-We agree with Reviewer's comment.  We removed the letters and replace them with subject's numbers.
+We agree with Reviewer's comment.  We removed the letters and replace them with subject's numbers in Figures 4 and 5.
 }
@@
 {\color{blue}
-We included now all the ROC curves for all the subjects, where the difference in AUCs can be seen more clearly.
+We included now all the ROC curves for all the subjects.
 }

### 2020-08-22 ErrP.tex
Subo la versión lista para subir.

@@
 \begin{abstract}
-In this study, we propose a simple game scenario that can be used to trigger a feedback response embedded in the Electroencephalographic (EEG) signals of an observation human critic that observes an agent playing a game.
-Based on the model of Reinforcement Learning (RL), the gaming agent receives rewards for their actions on the game and learns its optimal policy.
+In this study, we propose a simple game scenario that can be used to trigger a feedback response embedded in Electroencephalographic (EEG) signals of an observation human critic that observes an agent playing a game.
+Based on a Reinforcement Learning (RL) model, the gaming agent receives rewards for their actions on the game and learns its optimal policy.
 These rewards are obtained by implementing a Brain-Computer Interface (BCI) system that identifies signal components called Error-related Potentials (ErrP).
 These are brain signals found on EEG that can be elicited by a person who attends a recognizable error.
-When subjects observe the agent making a mistake this potential can be discerned by analyzing the signals which are directly related with the cognitive interpretation of an erroneous outcome or decision.
-We perform an iteratively incremental experiment where the agent plays, receives rewards from an observational human critic, and updates its policy for the next match.
-Our results are expressed in threefold: (i) the structure of a simple grid-based game that can elicit the ErrP signal component; (ii) low classification accuracy just above chance level that produces noisy rewards is enough to allow an agent to learn the optimal policy and solve the game; (iii) collaborative rewards from multiple observational human critics can compensate the lack of accuracy obtained from specific subjects or the difficulty of transfer learning solutions.
+We perform an experiment where rewards are obtained from observational human critics watching an agent playing randomly a game.
+This information is used to iteratively train the agent which receives these rewards and updates its policy improving its overall performance.
+Our results are expressed in threefold: (i) the structure of a simple grid-based game that can elicit the ErrP signal component; (ii) the verification that  low classification accuracy of just above chance level that produces noisy rewards is enough to allow an agent to learn the optimal policy; (iii) collaborative rewards from multiple observational human critics can compensate the lack of accuracy or the limited scope of transfer learning schemes.
 \end{abstract}
+
+%When subjects observe the agent making a mistake this potential can be discerned by analyzing the signals which are directly related with the cognitive interpretation of an erroneous outcome or decision.
 
@@
 \IEEEPARstart{T}{he} effectiveness of today's human–machine interaction and artificial intelligence is limited by a communication bottleneck as humans are required to translate high-level concepts into a machine-mandated sequence of instructions~\cite{Xu2020,CURSOR-CONTROL-PAPER}.
-Hence, new interaction methods are required to increase the communication bandwidth between computers and human, or to produce alternative communications systems to increase the efficiency of this channel.
+Hence, new interaction methods are required to increase the communication bandwidth between computers and humans, or to produce alternative communications systems to increase the efficiency of this channel.
 In this respect, video games has been widely used as test tools to assess new means of interactions~\cite{Carter2014,Barr2007}.
@@
 
-In order to train the agent, Reinforcement Learning (RL)~\cite{Sutton2018} comes as a natural solution for this scenario from the field of Artificial Intelligence.
+In order to train the agent, Reinforcement Learning (RL)~\cite{Sutton2018} stands as a natural solution for this scenario from the field of Artificial Intelligence.
 This is an algorithmic learning strategy inspired on how biological agents learn by exploring their environment, and getting negative or positive feedback rewards.
@@
 The papers \cite{ROBOT-CONTROL-PAPER,Kim2017,Omedes2013} have successfully demonstrated that a robot can be controlled by obtaining a reward signal from a person's brain activity which is observing the robot solve a task.
-In the context of Brain Computer Interfaces a growing number of studies have demonstrated the feasibility of using ErrPs as rewards for RL schemes such as to enhance robotic behaviour~\cite{Luo2019}, to assess air traffic controllers decissions~\cite{Goh2019} or  to categorise actions as errors~\cite{Wirth2020}.
+Moreover, a growing number of studies have demonstrated the feasibility of using ErrPs as rewards for RL schemes such as to enhance robotic behaviour~\cite{Luo2019}, to assess air traffic controllers decissions~\cite{Goh2019} or  to categorise actions as errors~\cite{Wirth2020}.
 Other approaches have used the signal as an important feedback for human-robot interaction or to implement shared-control strategies~\cite{Schiatti2018}.
@@
 Therefore, in this work, we aim to use the information extracted from brainwaves to enhance the performance of a gaming agent.
-The three contributions  are (1) a very simple game that can elicit the ErrP potential, (2) results that confirm that even when ErrP classification accuracy is low and produces a noisy reward signal, that provides enough information for an agent to learn the optimal policy and solve the simple game and (3) that collaborative rewards from multiple observational human observers can compensate the lack of accuracy obtained from specific subjects.
+The three contributions  are (1) a simple game that can elicit the ErrP potential, (2) results that confirm that even when ErrP classification accuracy is low and produces a noisy reward signal, this provides enough information for an agent to learn the optimal policy and solve the simple game and (3) collaborative rewards from multiple observational human observers can compensate the lack of classification accuracy or the inefficacy of transfer learning procedures for brainwaves signals.
 
@@
 In Section \ref{section:materials} the general layout of the cognitive game is described.
-Section \ref{section:calibration} outlines the processing pipeline used to detect ErrP components.
-The following Section \ref{learning} describes the agent learning phase.
-Results and Conclusions are exposed in Sections \ref{results} and \ref{conclusions}.
+Sections \ref{brainwavesession} and \ref{cognitive_experiment_details} outlines the cognitive game procedure used to obtain rewards in the form of ErrP components.
+Section \ref{q_learning_step_alg} describes the gaming agent learning procedure.
+Lastly, results and conclusions are exposed in Sections \ref{results} and \ref{conclusions}.
 
@@
 
-This first part consists in collecting signals from a person's brainwaves while they are watching a game where the agent knows the game rules but not how to win it.
-Hence, the agent can learn the winning strategy using the person's feedback to improve its own performance.
-This section describes the process of obtaining the person's brain signals that are used to make the agent more efficient.
+The experimental procedure is summarized in Figure \ref{diag:complete_flow}.
+The proposed system has two distinct parts.
+This first part consists in collecting signals from a person's brainwaves while they are watching an agent playing a game.
+The agent knows the game rules but not how to win it.
+The second part, the gaming agent learning phase, is where the agent can learn the winning strategy using the person's feedback to improve its own performance.
 
@@
 Offline, EEG signals are classified and they are linked to each game movement calculated by the Game Manager to determine proper rewards for each action.
-This information is used by a Reinforcement Learning algorithm to learn a Q-Table to improve the performance of the agent that plays the game.}
+This information is used by a Reinforcement Learning algorithm to learn iteratively a Q-Table to improve the performance of the agent that plays the game.}
     \label{diag:complete_flow}
@@
 
-The experimental procedure is summarized in Figure \ref{diag:complete_flow}.
+\subsection{Brainwave Session}
+\label{brainwavesession}
+
 The central part is the retrieval of the OHC's brain activity.
@@
 When the subject is ready, the Game Manager and the OpenVibe Designer programs are launched and configured to communicate with the previously mentioned Acquisition Server.
-A brainwave session consists of several matches, each one being a game run.
+A brainwave session consists of several matches, each one being a game play.
 At the end, all the sequence of game movements and the signal data generated for each match are saved for offline processing.
@@
 
-\section{Signal Processing, Segmentation and Classification}
+\subsection{Signal Processing, Segmentation and Classification}
 \label{section:calibration}
@@
 
-\section{Reinforcement Learning}
+\subsection{Reinforcement Learning}
 \label{learning}
@@
 After a classifier is trained, the epochs extracted from the test matches are classified as hit or no-hit.
-A reward for each movement in the game run is produced, based on the prediction from the classifier that correspond to that movement.
+A reward for each movement in the match is generated based on the prediction from the classifier that correspond to that movement.
 The reward can either be -1 when the event is classified as a hit or 0 when it is classified as a no-hit.
@@
 
-\subsection{Agent Learning}
+\subsection{Gaming Agent Learning Procedure}
 \label{q_learning_step_alg}
 
-The Q-Table is initialized with zeros, so the initial policy for the agent is randomized.
-In order for the agent to learn from the feedback generated by the OHC,  the policy which determines which action to take in a particular state is given by the agent's actions taken from the previous brainwave session match.
-This allows to learn the Q-Table based on the OHC's feedback from the movements the agent took, which are initially chosen pseudo-randomly, while executing the brainwave session.
+This procedure uses the testing matches from brainwave sessions produced during the cognitive game procedure phase, and their components are schematized in Figure~\ref{diag:complete_flow}.
+
+This phase is divided in a sequence of a run session, and a gaming agent training match.
+During the run session, the agent plays 200 matches guided by a specific Q-Table with a remaining 5\% chance of a randomly selected movement left out to reduce deadlocks and loops.
+Following the run session, the agent performs a single gaming agent training match.
+The gaming agent starts with a Q-Table initialized with zeros, so the initial policy for the agent is randomized.
+In order for the agent to learn from the feedback generated by the OHC,  the policy which determines which action to take in a particular state is given by the agent's actions taken from one brainwave session match.
+This allows to learn the Q-Table based on the OHC's feedback from the movements the agent took, which are chosen pseudo-randomly while executing the brainwave session.
 The previously mentioned feedback is not explicit as it comes from the interpreted brain signal data.
@@
 
-Hence, following the iterative procedure based on Equation~\ref{equ:update_q_table}, the Q-Table is updated in each iteration.
-After the algorithm finishes iterating through all the training episodes, the Q-Table is stored and used by the agent in the next match.
+Hence, following the iterative procedure based on Equation~\ref{equ:update_q_table}, the Q-Table is updated in each gaming agent training match.
+After the algorithm finishes replicating all the steps from the brainwave session match, the Q-Table is stored and used by the agent in the next run session.
 
@@
 
-Figure~\ref{fig:classifiers} show the binary classification accuracy obtained for the eight OHCs for the four different classification algorithms using a 10-fold cross validation procedure.
+Figure~\ref{fig:classifiers} show the binary classification accuracy obtained for the eight OHCs for the five different classification algorithms using a 10-fold cross validation procedure.
 The best overall performance is obtained using Logistic Regression.
 In addition, the classification accuracy obtained averaging 5 epochs is shown as well.
-Although the signal averaging procedures improves the Signal-To-Noise-Radio (SNR) of the ErrP response, it reduces the number of data samples and produces a clear improvement only for the subjects that contain more samples (5, 3 and 7).
+Although the signal averaging procedures improves the Signal-To-Noise-Radio (SNR) of the ErrP response, it reduces the number of data samples.
+It produces a clear improvement only for the OHCs that contain more samples (1, 3 and 7).
 
@@
     \includegraphics[scale=0.12]{revisedimages/cross_val.eps}
-    \caption{Binary single trial classification score using four different classifiers while recognizing ErrP potentials for the eight OHCs.
+    \caption{Binary single trial classification score using five different classifiers while recognizing ErrP potentials for the eight OHCs.
 The classification score using an ensemble average of 5 epochs is shown as well (GrandAvg).
@@
 On the other hand, Figure \ref{fig:avg_steps} shows for each OHC the average amount of steps the agent takes to reach the goal as the Q-Table is progressively trained using the reward information obtained from the prediction performed by the trained classifier.
-Each point corresponds to the average number of steps, in 200 repetitions, that it takes for the agent to reach the goal for a specific Q-Table.
-The first point represents the amount of steps the agent takes to reach the goal for a Q-Table that hasn't been trained at all, where movements are decided randomly.
-The next point corresponds to the amount of steps it takes to reach the goal using a policy derived from a Q-Table trained with one game match, and so on.
+Each point corresponds to a run session where the average number of steps, in 200 repetitions, that it takes for the agent to reach the goal for a specific Q-Table, is specified.
+The first point at 0 represents the amount of steps the agent takes to reach the goal for a Q-Table that hasn't been trained at all, where movements are decided randomly.
+The next point corresponds to the amount of steps it takes to reach the goal using a policy derived from a Q-Table trained after one brainwave session match, and so on.
 
@@
 \caption{Average number of steps for the agent to reach the goal when trained with rewards generated from brainwaves from OHCs 1-8.
-Y axis show the averaged number of steps, while x axis show the number of game matches used to cumulative train the Q-Table.}
+Y axis show the averaged number of steps for a run session, while x axis show the number of game matches used to cumulative train the Q-Table.}
 \label{fig:avg_steps}
@@
 This variation in performance for different OHCs has been studied extensively in BCI~\cite{Chavarriaga2014}.
-Besides low data samples there are other reasons affecting the classification accuracy:  cognitive reasons (i.e.
+Besides low data samples, there are other reasons affecting the classification accuracy:  cognitive reasons (i.e.
 the OHC not paying extensively attention to the game dynamics), very low SNR of the ErrP component or even the BCI-illiteracy phenomena where the specific OHC's signals do not contain the expected component response~\cite{Yousefi2019}.
@@
 \includegraphics[scale=0.4]{Images/Average_steps/noise.eps}
-\caption{Average steps using Q-Table trained with a noisy signal.}
+\caption{Average number of steps for the agent to reach the goal when trained with a classifier produced from sham EEG signals.
+X axis show the number of gaming agent training matches used to train the Q-Table.}
 \label{fig:avg_steps_noise}
@@
 This is evidenced in Figure~\ref{fig:transferlearning} where the agent training is performed by using rewards obtained by classifying epochs from one Tester OHC, but using a classifier which was trained using the brainwaves from a different Trainer OHC.
-The figure shows the variation on the average number of steps required to reach the goal after training the agent with all the available matches.
-An improvement is shown as negative values.
-Only the diagonal of the heatmap matrix shows a clear improvement in terms of the reduction of the required number of steps to reach the goal (averaged per 200 runs) and it represents the improvement shown for each OHC in Figure~\ref{fig:avg_steps}).
-For this Transfer Learning experiment~\cite{Wu2016}, no performance gain is evidenced, the agents learn nothing and this implies that the reward information is useless.
+The figure shows the cumulative variation for all run session on the average number of steps required to reach the goal after training the agent with all the available matches from the brainwave session.
+Enhancements are shown as negative values.
+Only the diagonal of the heatmap matrix shows a clear improvement in terms of the reduction of the required number of steps to reach the goal (averaged per 200 runs) which corresponds to the same information for each OHC shown in Figure~\ref{fig:avg_steps}.
+For the transfer learning experiment~\cite{Wu2016}, no performance gain is evidenced, the agents learn nothing and this implies that the reward information is useless.
 
@@
 Additionally, one important aspect of the classification results is the low percentage of false positives (Figure~\ref{fig:confusionmatrix}), showing a high specificity.
-It is not common that the agent learns that an action is wrong when in fact it is an action that takes it closer to the goal.
 On the other hand, the percentage of false negatives is generally higher.
 However, even though this implies that the agent misses frequently that an action taken is wrong, this is not hindering the overall performance and the agent is still learning.
-\textit{A little bit of accurate rewards is very useful for the RL algorithm}.
+\textit{Though scarce, accurate rewards are very useful for the RL algorithm}.
 %However, even though this imply that the agent misses frequently that an action taken is wrong, this do not seems to be a serious issue because the agent improves its performance.
@@
 Despite that, the rewards generated from different subjects can be used to train the same Q-Table to improve its performance, which may lead to strategies where the overall performance is enhanced based on the information from different human critics at the same time.
-
-The simple setup of the grid-based game allows to further experimentation, using the reduction of the number of steps as a validation of the achieved information transfer.
-It will be of research interest to verify if the smooth progression towards the end alter the shape of the ErrP response, or how the ErrP response is triggered in relation with different shapes and colors of the board markers~\cite{EIMER1997143}.
+There seems to be an agreement in terms of the subjective interpretation of what may be an appropriate movement to reach the goal.
+
+The simple setup of the grid-based game allows to further experimentation, using the reduction on the number of average steps to reach the goal as a validation of the achieved information transfer.
+It will be of research interest to verify if the smooth progression towards the end alter the shape of the ErrP response, how the ErrP response is triggered in relation with different shapes and colors of the board markers~\cite{EIMER1997143}, or if there is a differential ErrP signal component in relation to up,down, left and right movements.
+In addition, the outcome of manipulating the stimulus could be further studied as well as the influence on the results if incentives are given to participants.
 
 Further work will be conducted in order to increase the complexity of the game to allow the possibility that the target position be dynamically changed.
-Although we found that the better performing classifier is Logistic Regression, there is clearly more room from improvement and the classifier could be enhanced to recognize more effectively the Error Potential~\cite{Iwane2017}.
-
-Concluding, this research shows evidence that brain signals can be used as an interface between human and a gaming computer enabling an alternative communication with the system without explicit input from the user.
+Although we found that the better performing classifier is Logistic Regression, there is  more room from improvement.
+The classifier could be enhanced to recognize more effectively the Error Potential~\cite{Iwane2017}, or pre-trained to allow higher accuracy~\cite{Spuler2012}.
+
+%Concluding, this research shows evidence that brain signals can be used as an interface between human and a gaming computer enabling an alternative communication with the system without explicit input from the user.
 

### 2020-08-23 ErrP.tex
Paper editing and proof reading

@@
 Based on a Reinforcement Learning (RL) model, the gaming agent receives rewards for their actions on the game and learns its optimal policy.
-These rewards are obtained by implementing a Brain-Computer Interface (BCI) system that identifies signal components called Error-related Potentials (ErrP).
-These are brain signals found on EEG that can be elicited by a person who attends a recognizable error.
-We perform an experiment where rewards are obtained from observational human critics watching an agent playing randomly a game.
-This information is used to iteratively train the agent which receives these rewards and updates its policy improving its overall performance.
+These rewards are obtained by implementing a Brain-Computer Interface (BCI) system that identifies signal components called Error-related Potentials (ErrP), which occur when a person witnesses a recognizable error.
+We perform an experiment where rewards are obtained from the ErrP signals from observational human critics watching an agent randomly play a game.
+An agent is iteratively trained by receiving these rewards and updating its policy, improving its overall performance.
 Our results are expressed in threefold: (i) the structure of a simple grid-based game that can elicit the ErrP signal component; (ii) the verification that low classification accuracy of just above chance level that produces noisy rewards is enough to allow an agent to learn the optimal policy; (iii) collaborative rewards from multiple observational human critics can compensate the lack of accuracy or the limited scope of transfer learning schemes.
@@
 % (should never be an issue)
-\IEEEPARstart{T}{he} effectiveness of today's human–machine interaction and artificial intelligence is limited by a communication bottleneck as humans are required to translate high-level concepts into a machine-mandated sequence of instructions~\cite{Xu2020,CURSOR-CONTROL-PAPER}.
-Hence, new interaction methods are required to increase the communication bandwidth between computers and humans, or to produce alternative communications systems to increase the efficiency of this channel.
-In this respect, video games has been widely used as test tools to assess new means of interactions~\cite{Carter2014,Barr2007}.
-Video gaming agents are computer programs that can sense the computer game environment, process information, and interact with it.
+\IEEEPARstart{T}{he} effectiveness of today's human–machine interaction and artificial intelligence is limited by a communication bottleneck, as humans are required to translate high-level concepts into a machine-mandated sequence of instructions~\cite{Xu2020,CURSOR-CONTROL-PAPER}.
+Hence, new interaction methods are required to increase the communication bandwidth between computers and humans or to produce alternative communications systems to increase the efficiency of this channel.
+In this respect, video games have been widely used as test tools to assess new means of interactions~\cite{Carter2014,Barr2007}.
+Video gaming agents are computer programs that can sense the computer game environment, process information, and react accordingly within the environment.
 They are used in the context of testing and evaluating artificial intelligence algorithms that aim to win the game or to behave like a real user player~\cite{Zhao2020}.
@@
 
-Concurrently, the appealing idea of a direct interface between the human brain and an artificial system, called Brain Computer Interface (BCI) or Brain Machine Interfaces (BMI), has proved the feasibility of a distinct non-biological communication channel to transmit information from the Central Nervous System (CNS) to a computer device~\cite{Vasiljevic2020}.
-BCI systems provide a new input modality that can be used in the context of a computer game~\cite{Scherer2012,Nijholt2007}, is relevant in the context of the accessibility for video games~\cite{Aguado-Delgado2020} and in the growing area of e-sports~\cite{Yakovlev2020}.
-
-In this proposal, gaming agents are trained using only signals components called Error-related Potentials (ErrP) that can be identified from their brain signals.
-This type of signals can be found on EEG traces and are elicited when a subject is aware of the presence of an unexpected outcome, which she/he identifies as an error.
-It is currently an extensive area of research in the neuroscience community~\cite{Holroyd2009}.
-Error-related Potentials can be detected by signal processing and machine learning techniques~\cite{EERP-PAPER} and they are also used in Brain-Computer Interfaces to implement or enhance artificial communication channels~\cite{Chavarriaga2014}.
-
-In order to train the agent, Reinforcement Learning (RL)~\cite{Sutton2018} stands as a natural solution for this scenario from the field of Artificial Intelligence.
-This is an algorithmic learning strategy inspired on how biological agents learn by exploring their environment, and getting negative or positive feedback rewards.
-This strategy aims to maximize the amount of positive rewards while keeping the number of negative feedback low.
+% Reescribí la primera oración porque el sujeto no tenía sentido con el predicado.  TODO
+The feasibility of a distinct non-biological communication channel between the Central Nervous System (CNS) and a computer device has been previously proven with Brain Computer Interfaces (BCI) or Brain Machine Interfaces (BMI).~\cite{Vasiljevic2020}.
+BCI systems provide a new input modality that can be used in the context of a computer game~\cite{Scherer2012,Nijholt2007}.
+This advancement is relevant in the context of the accessibility for video games~\cite{Aguado-Delgado2020} and the growing area of e-sports~\cite{Yakovlev2020}.
+
+% Observation human critic? Suena raro acá, puse Subject pero chequear! TODO
+In this study, gaming agents are trained using only signal components called Error-related Potentials (ErrP) that can be identified in the observer's brain signals.
+These types of signals can be found on EEG traces and are elicited when subjects are aware of the presence of an unexpected outcome, which they identify as an error.
+The analysis of ErrP signals is currently an extensive area of research in the neuroscience community~\cite{Holroyd2009}.
+Error-related Potentials can be detected by signal processing and machine learning techniques~\cite{EERP-PAPER} and are also used in Brain-Computer Interfaces to implement or enhance artificial communication channels~\cite{Chavarriaga2014}.
+
+Given the scenario, Reinforcement Learning (RL)~\cite{Sutton2018} stands out as a natural method to train the agent.
+Reinforcement Learning refers to an algorithmic learning strategy inspired on how biological agents learn by exploring their environment while getting negative or positive feedback rewards.
+The method aims to maximize positive rewards while minimizing negative feedback.
 Thus, the learning problem is posed as a stochastic optimization strategy~\cite{Santos1999}.
 Recently, this technique has been used extensively in the context of advances in artificial intelligence~\cite{Nguyen2020}.
-Nonneglected is the influence of DeepBrain's AlphaGo project, which was the first to reach a very high proficiency when it won the complex game Go against several world champions~\cite{ALPHA-GO}.
+The influence of DeepBrain's AlphaGo project cannot be neglected, since it was the first to reach a very high proficiency when it won the complex game Go against several world champions~\cite{ALPHA-GO}.
 
@@
 Previous research has explored the usage of RL with reward signals based on brain activity, recorded by an EEG-based BCI system during task execution.
-The papers \cite{ROBOT-CONTROL-PAPER,Kim2017,Omedes2013} have successfully demonstrated that a robot can be controlled by obtaining a reward signal from a person's brain activity which is observing the robot solve a task.
-Moreover, a growing number of studies have demonstrated the feasibility of using ErrPs as rewards for RL schemes such as to enhance robotic behaviour~\cite{Luo2019}, to assess air traffic controllers decissions~\cite{Goh2019} or  to categorise actions as errors~\cite{Wirth2020}.
-Other approaches have used the signal as an important feedback for human-robot interaction or to implement shared-control strategies~\cite{Schiatti2018}.
+The papers \cite{ROBOT-CONTROL-PAPER,Kim2017,Omedes2013} have successfully demonstrated that a robot can be controlled with brain signals from a person that is observing a robot solve a task.
+Moreover, a growing number of studies have demonstrated the feasibility of using ErrPs as rewards for RL schemes such as to enhance robotic behaviour~\cite{Luo2019}, to assess air traffic controller's decisions~\cite{Goh2019} or to categorize actions as errors~\cite{Wirth2020}.
+Other approaches have used these signals as important feedback for human-robot interaction or to implement shared-control strategies~\cite{Schiatti2018}.
 Additionally, ErrPs have also been used in the context of games as an additional feedback channel that can be explored to improve gaming experience~\cite{Plass-OudeBos2010,kober2018bci}.
 
-Therefore, in this work, we aim to use the information extracted from brainwaves to enhance the performance of a gaming agent.
-The three contributions  are (1) a simple game that can elicit the ErrP potential, (2) results that confirm that even when ErrP classification accuracy is low and produces a noisy reward signal, this provides enough information for an agent to learn the optimal policy and solve the simple game and (3) collaborative rewards from multiple observational human observers can compensate the lack of classification accuracy or the inefficacy of transfer learning procedures for brainwaves signals.
+In this work, we aim to use the information extracted from brainwaves to enhance the performance of a gaming agent.
+The three contributions are (1) a simple game that can elicit the ErrP potential, (2) results that confirm that even when ErrP classification accuracy is low and produces a noisy reward signal, enough information is generated as for an agent to learn the optimal policy and solve a simple game and (3) collaborative rewards from multiple observational human observers can compensate the lack of classification accuracy or the inefficacy of transfer learning procedures for brainwaves signals.
 
@@
 In Section \ref{section:materials} the general layout of the cognitive game is described.
-Sections \ref{brainwavesession} and \ref{cognitive_experiment_details} outlines the cognitive game procedure used to obtain rewards in the form of ErrP components.
+Sections \ref{brainwavesession} and \ref{cognitive_experiment_details} outline the cognitive game procedure used to obtain rewards in the form of ErrP components.
 Section \ref{q_learning_step_alg} describes the gaming agent learning procedure.
@@
 The proposed system has two distinct parts.
-This first part consists in collecting signals from a person's brainwaves while they are watching an agent playing a game.
+This first part consists of the collection of brainwave signals from a person that is watching an agent play a game.
 The agent knows the game rules but not how to win it.
@@
 
-The central part is the retrieval of the OHC's brain activity.
-This process is called brainwave session.
-Subjects are recruited voluntarily.
-They are given a consent form with questions regarding their health (previous health issues and particular visual sensitivity), habits (sleeping hours, caffeine and alcohol consumption), as well as an approval petition to collect the required data.
-The brainwave sessions are performed with 8 subjects, 5 males and 3 females, average age 25.12 years, standard deviation 1.54 years, range of 22-28 years.
-All subjects have normal vision, are right-handed and have no history of neurological disorders.
+The retrieval of the OHC's brain activity, called the brainwave session, is one of the most critical parts of the study.
+Subjects are recruited voluntarily and given a form with questions regarding their health (previous health issues and particular visual sensitivity), habits (sleeping hours, caffeine and alcohol consumption), and a consent petition to collect the required data.
+The brainwave sessions are performed with 8 subjects, 5 males and 3 females, with an average age of 25.12 years, a standard deviation of 1.54 years, and a range of 22-28 years.
+All subjects have normal vision, are right-handed and no history of neurological disorders.
 
@@
 When this concludes, the subject is introduced to the wireless digital EEG device (g.Nautilus, g.Tec, Austria) that she/he has to wear during the brainwave session.
-It has eight electrodes (g.LADYbird, g.Tec, Austria) on the positions Fz, Cz, Pz, Oz, P3, P4, PO7 and PO8, identified according to the 10-20 International System, with a reference set to the right ear lobe and ground set as the AFz position.
+It has eight electrodes (g.LADYbird, g.Tec, Austria) on the positions Fz, Cz, Pz, Oz, P3, P4, PO7, and PO8, identified according to the 10-20 International System, with a reference set to the right ear lobe and ground set as the AFz position.
 The electrode contact points are adjusted applying conductive gel until the impedance values displayed by the program g.NeedAccess (g.Tec, Austria) are within the desired range.
 This process takes between 10 to 15 minutes.
-After this step, the subject is instructed to close their eyes and the same program is used to check the live channel values so that there are no dead ones and the expected values are displayed for eye movements or muscle chewing.
+After this step, the subject is instructed to close their eyes, make eye movements and muscle chew in order to check the program and guarantee that the live channel values are accurate.
 
@@
 A $50$~Hz notch filter is applied to filter out power line noise.
-An additional bandpass filter between $0.5$~Hz and $60$~Hz is applied as well.
-Data is handled and processed with the OpenVibe Designer, from the same platform, using 8 channels for the brain data (one channel per electrode) and an additional channel for the stimulus, which corresponds to a game movement performed by the agent.
-After everything is connected, the subject seats in a comfortable chair in front of a computer screen.
+An additional bandpass filter between $0.5$~Hz and $60$~Hz is applied.
+Data is handled and processed with the OpenVibe Designer, from the same platform, using 8 channels for the brain data (one channel per electrode) and an additional channel to record the stimulus, which corresponds to a game movement performed by the agent.
+After everything is connected, the subject is seated in a comfortable chair in front of a computer screen.
 The brightness of the screen is set to the maximum setting to avoid any visual inconvenience in which the subject can not distinguish the components of the game that appear on the screen.
@@
 
-The Acquisition Server has the responsibility of receiving and synchronizing the signal data from the headset and any event information from the game, and transfers it to the OpenVibe Designer application.
+The Acquisition Server receives and synchronizes the signal data from the headset and any event information from the game, and transfers it to the OpenVibe Designer application.
 When the subject is ready, the Game Manager and the OpenVibe Designer programs are launched and configured to communicate with the previously mentioned Acquisition Server.
-A brainwave session consists of several matches, each one being a game play.
-At the end, all the sequence of game movements and the signal data generated for each match are saved for offline processing.
+A brainwave session consists of several matches, each one being a gameplay.
+In the end, the sequence of game movements and the signal data generated for each match are saved for offline processing.
 
@@
 The game parsimoniously consists of a $5x5$ grid of grey circular spots with a black background.
-A blue spot indicates current position of the agent whereas a green spot represents the goal, as shown in Figure  \ref{fig:game_representation}.
+A blue spot indicates the current position of the agent and a green spot represents the goal, as shown in Figure  \ref{fig:game_representation}.
 The agent's objective is to reach the goal.
-The circular spot representing the goal remains static at the bottom-right position of the grid, while the one representing the position of the agent always starts at the upper-left position of the grid.
+The circular spot representing the goal remains static at the bottom-right position of the grid, while the one representing the position of the agent starts at the upper-left position of the grid and moves in each iteration.
 When the agent reaches the goal, the position where the agent and the goal are located turns red, showing that the match has ended.
-There are four possible movements that the agent can perform: it can go upwards, downwards, towards the left and towards the right, and those movements are bounded to avoid the agent from leaving the grid.
+There are four possible movements that the agent can perform: it can go upwards, downwards, towards the left and the right, and those movements are bounded to avoid the agent from leaving the grid.
 The movement direction is selected randomly and is executed once every 2 seconds.
-At the end, there is a pause of 5 seconds before the next match starts.
+After each gameplay, there is a pause of 5 seconds until the next match starts.
 Each time an agent moves, the Game Manager program sends an event marker to the Acquisition Server.
-This is considered as a stimulus to the observational human critic.
-The game is designed for it to be evident whenever there is an error (i.e.
+This is considered a stimulus to the observational human critic.
+The game is designed as to be evident whenever there is an error (i.e.
 the agent moves away from the objective) so the subject can notice it immediately after the stimulus is presented, possibly triggering the expected cognitive response, which can be imprinted as an ErrP component within the EEG stream.
@@
 
-To aid in detecting the ErrP response, an offline processing pipeline and classifier is constructed to identify whether the action taken by the agent is an error or not, from the human observer point of view.
+To aid the detection of the ErrP response, an offline processing pipeline and classifier is constructed to identify whether the action taken by the agent is an error or not, from the human observer's point of view.
 It is developed in Python using the "MNE" software platform \cite{MNE-PYTHON}, which is a package designed specifically for processing EEG and Magnetoencephalography data, and built upon the machine learning library Scikit-Learn~\cite{scikit-learn}.
 
-This pipeline consists of the offline processing of the collected signals in order to train a classifier that can decide whether an error potential is triggered.
-Firstly, the output of a brainwave session is read and an additional band pass filter of 0.1-20.0 Hz is applied to the signal.
+This pipeline consists of the offline processing of the collected signals used to train a classifier that can decide whether an error potential is triggered.
+Firstly, the output of a brainwave session is read and an additional band-pass filter of 0.1-20.0 Hz is applied to the signal.
 Samples that correspond to the start of an event are tagged using the data from the stimulus channel.
 
-After the data is loaded and tagged, epochs are extracted from the raw data.
-Epochs consist of all the sample points that take place between the start of the event and 2 seconds later (time for each action to take place), resulting in 500 samples per channel, as the sample frequency is 250 Hz.
+After the raw data is loaded and tagged, epochs are extracted.
+Epochs consist of all the sample points that take place during the 2 seconds from the start of the event, 2 seconds corresponding to the time it takes for each action to take place, resulting in 500 samples per channel, as the sampling frequency is 250 Hz.
 Thus, each epoch is composed of a matrix $500$ x $8$ channels.
@@
 In this way, the raw data of a brainwave session is processed into an array of matches where each element is an array of epochs tagged with a number specifying the prediction of the classifier, i.e.
-if the epoch corresponds to an action that made the agent moves further from the goal (hit) or an action that made the agent moves closer to the goal (no-hit).
+if the epoch corresponds to an action that made the agent move further from the goal (hit) or an action that made the agent moves closer to the goal (no-hit).
 The ErrP is expected to be found in hits.
-To get the data ready for classification, the stimulus channel is removed in order to classify the signals using only the EEG data.
+To get the data ready for classification, the stimulus channel is removed to classify the signals using only the EEG data.
 Each epoch is regularized using a MinMaxScaler, i.e.
-substracting the minimun value in the epoch and dividing by the signal peak-to-peak amplitude~\cite{Zhou2019}.
-The eight channels are concatenated using the  MNE Vectorizer function to transform the data matrix into a single array sample.
+subtracting the minimum value in the epoch and dividing by the signal peak-to-peak amplitude~\cite{Zhou2019}.
+The eight channels are concatenated using the MNE Vectorizer function, which transforms the data matrix into a single array sample.
 Lastly, this data is used by the classification module as information to train and test a classifier.
-Five different classification algorithms are used:  Logistic Regression, Multi-layer Perceptron with a hidden layer of 100 neurons (i.e.
+Five different classification algorithms are used:  Logistic Regression, Multilayer Perceptron with a hidden layer of 100 neurons (i.e.
 default values for the Scikit-Learn MLPClassifier), Random Forest, KNeighbours with k=3 and finally a linear kernel Support Vector Classifier (i.e.
@@
 After a classifier is trained, the epochs extracted from the test matches are classified as hit or no-hit.
-A reward for each movement in the match is generated based on the prediction from the classifier that correspond to that movement.
+A reward for each movement in the match is generated based on the prediction from the classifier for that movement.
 The reward can either be -1 when the event is classified as a hit or 0 when it is classified as a no-hit.
-The accuracy of this rewards depends on the performance of the classifier.
-The list of game movements and their associated reward information are used to train the agent by a variant of Reinforcement Learning called Q-Learning algorithm.
+The accuracy of these rewards depends on the performance of the classifier.
+The list of game movements and their associated reward information is used to train the agent by a variant of Reinforcement Learning called Q-Learning algorithm.
 
@@
 
-Q-Learning~\cite{Watkins1992} is a form of model-free reinforcement learning algorithm where an agent tries an action at a particular state and evaluate its consequences in terms of the reward or penalty it receives.
-In order to represent rewards, a matrix $Q(s,a)$ is used, where rows correspond to all the possible states, whereas columns represent all possible actions.
-This matrix is known as a Q-Table.
-The algorithm proceeds by randomly choosing what action to do and updating iteratively the Q-Table based on the received reward $r$ by the following equation
+Q-Learning~\cite{Watkins1992} is a form of model-free reinforcement learning, where an agent tries an action at a particular state and evaluates its consequences in terms of the reward or penalty it receives.
+To represent rewards, a matrix $Q(s,a)$ is used, where rows correspond to all the possible states, and columns represent all possible actions.
+This matrix is known as the Q-Table.
+The algorithm proceeds by randomly choosing what action to do and iteratively updating the Q-Table based on the received reward $r$ by the following equation
 
@@
 
-\noindent where $s$ is the current state, $a$ is the action, $\alpha$ represents the learning rate and $\gamma$ represents the discount factor, a value between 0 and 1 that determines the importance of long term results versus immediate rewards.
+\noindent where $s$ is the current state, $a$ the action, $\alpha$ the learning rate and $\gamma$ the discount factor, a value between 0 and 1 that determines the importance of long term results versus immediate rewards.
 Hence, $Q(s,a)$ is the expected value of the sum of discounted rewards that the agent will receive if in the $s$ state, it takes the action $a$ according to this policy.
-Once the environment has been extensively explored and the Q-Table has been obtained, the action chosen for a given state is the one that maximizes the expected reward according to the Q-Table matrix.
+Once the environment has been extensively explored and the Q-Table has been optimized, the action chosen for a given state is the one that maximizes the expected reward according to the Q-Table matrix.
 
@@
 
-This procedure uses the testing matches from brainwave sessions produced during the cognitive game procedure phase, and their components are schematized in Figure~\ref{diag:complete_flow}.
-
-This phase is divided in a sequence of a run session, and a gaming agent training match.
-During the run session, the agent plays 200 matches guided by a specific Q-Table with a remaining 5\% chance of a randomly selected movement left out to reduce deadlocks and loops.
+The gaming agent learning procedure uses the testing matches from brainwave sessions produced during the cognitive game procedure phase, and their components are schematized in Figure~\ref{diag:complete_flow}.
+
+This phase is divided into a sequence of run sessions and a gaming agent training match.
+During the run session, the agent plays 200 matches guided by a specific Q-Table with a 5\% chance of a randomly selecting a movement, to reduce deadlocks and loops.
 Following the run session, the agent performs a single gaming agent training match.
 The gaming agent starts with a Q-Table initialized with zeros, so the initial policy for the agent is randomized.
-In order for the agent to learn from the feedback generated by the OHC,  the policy which determines which action to take in a particular state is given by the agent's actions taken from one brainwave session match.
-This allows to learn the Q-Table based on the OHC's feedback from the movements the agent took, which are chosen pseudo-randomly while executing the brainwave session.
+For the agent to learn from the feedback generated by the OHC, the next step, given a current state, will be determined by the agent's actions taken from one brainwave session match.
+This allows the Q-Table to be built based on the OHC's feedback from the movements the agent took, which are executed pseudo-randomly while executing the brainwave session.
 The previously mentioned feedback is not explicit as it comes from the interpreted brain signal data.
@@
 
-Figure~\ref{fig:classifiers} show the binary classification accuracy obtained for the eight OHCs for the five different classification algorithms using a 10-fold cross validation procedure.
+Figure~\ref{fig:classifiers} shows the binary classification accuracy obtained for the eight OHCs using the five different classification algorithms using a 10-fold cross-validation procedure.
 The best overall performance is obtained using Logistic Regression.
 In addition, the classification accuracy obtained averaging 5 epochs is shown as well.
-Although the signal averaging procedures improves the Signal-To-Noise-Radio (SNR) of the ErrP response, it reduces the number of data samples.
-It produces a clear improvement only for the OHCs that contain more samples (1, 3 and 7).
+Although the signal averaging procedures improves the Signal-To-Noise-Radio (SNR) of the ErrP response, it reduces the number of data samples, only producing a clear improvement for the OHCs that contain more samples (1, 3 and 7).
 
@@
 
-On the other hand, Figure \ref{fig:avg_steps} shows for each OHC the average amount of steps the agent takes to reach the goal as the Q-Table is progressively trained using the reward information obtained from the prediction performed by the trained classifier.
-Each point corresponds to a run session where the average number of steps, in 200 repetitions, that it takes for the agent to reach the goal for a specific Q-Table, is specified.
-The first point at 0 represents the amount of steps the agent takes to reach the goal for a Q-Table that hasn't been trained at all, where movements are decided randomly.
+On the other hand, Figure \ref{fig:avg_steps} shows the average amount of steps it takes for the agent to reach the goal for each OHC, as the Q-Table is progressively trained using the reward information obtained from the prediction of the trained classifier.
+Each point corresponds to a run session where the average number of steps for the agent to reach the goal using a specific Q-Table is specified, for 200 repetitions.
+The first point, at the x-value 0, represents the number of steps the agent takes to reach the goal with an untrained Q-Table, where movements are decided randomly.
 The next point corresponds to the amount of steps it takes to reach the goal using a policy derived from a Q-Table trained after one brainwave session match, and so on.
@@
 
-Figure~\ref{fig:avg_steps_noise} shows the result of an agent successively trained with brainwave session matches where the EEG is generated with sham signals.
+Figure~\ref{fig:avg_steps_noise} shows the result of an agent successively trained with brainwave session matches where the EEG is generated with random signals.
 In this case, random EEG signals are generated using OpenVibe Acquisition Server signal generator for all channels, as if they were produced by an OHC who doesn't pay attention to the game.
-As it can be seen, the agent learns nothing, and regardless of the amount of matches that are used to learn the Q-Table, the number of steps required to reach the goal does not decrease.
+The agent learns nothing, and regardless of the number of matches that are used to learn the Q-Table, the number of steps required to reach the goal does not decrease.
 This pattern is also obtained when the game matches from OHCs 5 and 6 are used, showing that the reward labeling predicted by the trained classifier for those cases worked like a random classifier.
@@
 Electroencephalographic signals have high inter-subject variability~\cite{Chavarriaga2014}.
-This is evidenced in Figure~\ref{fig:transferlearning} where the agent training is performed by using rewards obtained by classifying epochs from one Tester OHC, but using a classifier which was trained using the brainwaves from a different Trainer OHC.
-The figure shows the cumulative variation for all run session on the average number of steps required to reach the goal after training the agent with all the available matches from the brainwave session.
+This is evidenced in Figure~\ref{fig:transferlearning} where the agent training is performed with rewards obtained by classifying epochs from one Tester OHC and a classifier that was trained using the brainwaves from a different Trainer OHC.
+The figure shows the cumulative variation for all run sessions on the average number of steps required to reach the goal after training the agent with all the available matches from the brainwave session.
 Enhancements are shown as negative values.
@@
 
-Finally, Figure~\ref{fig:avg_steps_all} shows the result of training an agent with cumulative brainwave session matches from OHCs 1,2,3,4,7, and 8.
-It can be seen that the overall performance of the agent improves as long as there are information to produce rewards, regardless if they were generated from the brainwaves classification from different OHCs.
+Finally, Figure~\ref{fig:avg_steps_all} shows the result of training an agent with cumulative brainwave session matches from OHCs 1, 2, 3, 4, 7, and 8.
+It can be seen that the overall performance of the agent improves as long as there is information to produce rewards, regardless of the fact that they were generated from classifiers trained with different OHC's signals.
 
@@
 
-This work aims to propose a simple game that can elicit the ErrP component and that can be used to train a gaming agent using the RL model.
+This work aims to propose a simple game that can use the ErrP component to train a gaming agent using a RL model.
 The collected data shows that ErrP signals can in fact be classified and used to train an agent effectively.
 
-This proposal tries to keep the system as simple as possible, emphasizing information flow from the subjective error perception of the human critic, through the reward generation using the signal processing and classification pipeline, and finally the Q-Table updating  to enhance the performance of the gaming agent.
+This proposal tries to keep the system as simple as possible, emphasizing information flow from the subjective error perception of the human critic.
+Rewards are generated using the signal processing and classification pipeline, and the Q-Table updates enhancing the performance of the gaming agent.
 
@@
 The obtained accuracy to discriminate ErrPs is low.
-However, even with such a lower accuracy values, the RL algorithm was able to extract meaningful information from rewards that were helpful to improve the agent performance.
+However, even with such low accuracy values, the RL algorithm was able to extract meaningful information from rewards that were helpful to improve, and often maximize, the agent's performance.
 Additionally, one important aspect of the classification results is the low percentage of false positives (Figure~\ref{fig:confusionmatrix}), showing a high specificity.
 On the other hand, the percentage of false negatives is generally higher.
-However, even though this implies that the agent misses frequently that an action taken is wrong, this is not hindering the overall performance and the agent is still learning.
-\textit{Though scarce, accurate rewards are very useful for the RL algorithm}.
+However, even though this implies that the agent misses frequently when a wrong action takes place, this is not hindering the overall performance and the agent is still learning.
+\textit{Even when scarce, accurate rewards are very useful for the RL algorithm}.
 %However, even though this imply that the agent misses frequently that an action taken is wrong, this do not seems to be a serious issue because the agent improves its performance.
@@
 
-At the same time, effective agent training depends on the OHC's data that was used to train it.
-Results confirm the futility or complexity of using Transfer Learning~\cite{Wu2016}: training a classifier with data obtained from one OHC, but using it to identify ErrPs to produce rewards for the brainwave session match of another OHC does not increases the performance of the agent.
-Despite that, the rewards generated from different subjects can be used to train the same Q-Table to improve its performance, which may lead to strategies where the overall performance is enhanced based on the information from different human critics at the same time.
+At the same time, effective agent training depends on the OHC's training data.
+Results confirm the futility or complexity of using Transfer Learning~\cite{Wu2016}: training a classifier with data obtained from one OHC, and using the same classifier to identify ErrPs for another OHC.
+Despite that, the rewards generated from different subject's classifiers can be used to train the same Q-Table to improve its performance, which may lead to strategies where the overall performance is enhanced based on the information from different human critics at the same time.
 There seems to be an agreement in terms of the subjective interpretation of what may be an appropriate movement to reach the goal.
 
-The simple setup of the grid-based game allows to further experimentation, using the reduction on the number of average steps to reach the goal as a validation of the achieved information transfer.
-It will be of research interest to verify if the smooth progression towards the end alter the shape of the ErrP response, how the ErrP response is triggered in relation with different shapes and colors of the board markers~\cite{EIMER1997143}, or if there is a differential ErrP signal component in relation to up,down, left and right movements.
+The simple setup of the grid-based game allows further experimentation, using the reduction on the number of average steps to reach the goal as a validation of the achieved information transfer.
+It will be of research interest to verify if the smooth progression towards the end alters the shape of the ErrP response, how the ErrP response is triggered in relation with different shapes and colors of the board markers~\cite{EIMER1997143}, or if there is a differential ErrP signal component in relation to up, down, left and right movements.
 In addition, the outcome of manipulating the stimulus could be further studied as well as the influence on the results if incentives are given to participants.
 
-Further work will be conducted in order to increase the complexity of the game to allow the possibility that the target position be dynamically changed.
-Although we found that the better performing classifier is Logistic Regression, there is  more room from improvement.
-The classifier could be enhanced to recognize more effectively the Error Potential~\cite{Iwane2017}, or pre-trained to allow higher accuracy~\cite{Spuler2012}.
+Further work will be conducted in order to increase the complexity of the game to allow the possibility that the target position is dynamically changed.
+Although we found that the better performing classifier is Logistic Regression, there is room for improvement.
+The classifier could be enhanced to recognize the Error Potential~\cite{Iwane2017} more effectively or could be pre-trained to allow higher accuracy~\cite{Spuler2012}.
 

### 2020-08-23 ErrP.tex
Up with the modified file.

@@
 
-Given the scenario, Reinforcement Learning (RL)~\cite{Sutton2018} stands out as a natural method to train the agent.
+Given the scenario, Reinforcement Learning (RL)~\cite{Sutton2018} stands out as a viable method to train the agent.
 Reinforcement Learning refers to an algorithmic learning strategy inspired on how biological agents learn by exploring their environment while getting negative or positive feedback rewards.
@@
 \end{subfigure}
-\caption{Heatmap for the transfer learning experiment.  }
+\caption{Heatmap for the transfer learning experiment.}
 \label{fig:transferlearning}

### 2020-08-23 ErrP.tex
Add minor format change to paper
Subo los cambios tomando las modificaciones que subió Natalia.

--- 2020-08-23 ErrP.tex
@@
 We perform an experiment where rewards are obtained from the ErrP signals from observational human critics watching an agent randomly play a game.
-An agent is iteratively trained by receiving these rewards and updating its policy, improving its overall performance.
+The agent is iteratively trained by receiving these rewards and updating its policy, improving its overall performance.
 Our results are expressed in threefold: (i) the structure of a simple grid-based game that can elicit the ErrP signal component; (ii) the verification that low classification accuracy of just above chance level that produces noisy rewards is enough to allow an agent to learn the optimal policy; (iii) collaborative rewards from multiple observational human critics can compensate the lack of accuracy or the limited scope of transfer learning schemes.
@@
 
-In this work, we aim to use the information extracted from brainwaves to enhance the performance of a gaming agent.
-The three contributions are (1) a simple game that can elicit the ErrP potential, (2) results that confirm that even when ErrP classification accuracy is low and produces a noisy reward signal, enough information is generated as for an agent to learn the optimal policy and solve a simple game and (3) collaborative rewards from multiple observational human observers can compensate the lack of classification accuracy or the inefficacy of transfer learning procedures for brainwaves signals.
+Therefore,  we aim to use the information extracted from brainwaves to enhance the performance of a gaming agent.
+The three contributions are (1) a simple game that can elicit the ErrP potential, (2) results that confirm that even when ErrP classification accuracy is low and produces a noisy reward signal, enough information is generated for an agent to learn the optimal policy and solve a simple game and (3) collaborative rewards from multiple observational human observers can compensate the lack of classification accuracy or the inefficacy of transfer learning procedures for brainwaves signals.
 
@@
 The gaming agent starts with a Q-Table initialized with zeros, so the initial policy for the agent is randomized.
-For the agent to learn from the feedback generated by the OHC, the next step, given a current state, will be determined by the agent's actions taken from one brainwave session match.
+For the agent to learn from the feedback generated by the OHC movement actions are determined by the agent's actions that are taken from one brainwave session match.
 This allows the Q-Table to be built based on the OHC's feedback from the movements the agent took, which are executed pseudo-randomly while executing the brainwave session.
@@
 
-Figure~\ref{fig:classifiers} shows the binary classification accuracy obtained for the eight OHCs using the five different classification algorithms using a 10-fold cross-validation procedure.
+Figure~\ref{fig:classifiers} shows the binary classification accuracy obtained for the eight OHCs using five different classification algorithms and using a 10-fold cross-validation procedure.
 The best overall performance is obtained using Logistic Regression.
 In addition, the classification accuracy obtained averaging 5 epochs is shown as well.
-Although the signal averaging procedures improves the Signal-To-Noise-Radio (SNR) of the ErrP response, it reduces the number of data samples, only producing a clear improvement for the OHCs that contain more samples (1, 3 and 7).
+Although the signal averaging procedures improves the Signal-To-Noise-Radio (SNR) of the ErrP response, it reduces the number of data samples, producing a clear improvement only for the OHCs that contain more samples (1, 3 and 7).
 
@@
 \end{subfigure}
-\caption{Heatmap for the transfer learning experiment.  }
+\caption{Heatmap for the transfer learning experiment. Values represent the reduction in the average number of steps required to reach the goal.  Negative values represent net improvements.}
 \label{fig:transferlearning}
@@
 This proposal tries to keep the system as simple as possible, emphasizing information flow from the subjective error perception of the human critic.
-Rewards are generated using the signal processing and classification pipeline, and the Q-Table updates enhancing the performance of the gaming agent.
+Rewards are generated using the signal processing and classification pipeline, and the Q-Table updates, enhancing the performance of the gaming agent.
 
@@
 However, even though this implies that the agent misses frequently when a wrong action takes place, this is not hindering the overall performance and the agent is still learning.
-\textit{Even when scarce, accurate rewards are very useful for the RL algorithm}.
+Though scarce, accurate rewards are very useful for the RL algorithm.
 %However, even though this imply that the agent misses frequently that an action taken is wrong, this do not seems to be a serious issue because the agent improves its performance.
@@
 At the same time, effective agent training depends on the OHC's training data.
-Results confirm the futility or complexity of using Transfer Learning~\cite{Wu2016}: training a classifier with data obtained from one OHC, and using the same classifier to identify ErrPs for another OHC.
+Results confirm the futility or complexity of using Transfer Learning~\cite{Wu2016}: training a classifier with data obtained from one OHC, and using the same classifier to identify ErrPs for another OHC does not increases the performance of the agent.
 Despite that, the rewards generated from different subject's classifiers can be used to train the same Q-Table to improve its performance, which may lead to strategies where the overall performance is enhanced based on the information from different human critics at the same time.

### 2020-08-24 ErrP.tex
Some minor fixes.

@@
 This phase is divided into a sequence of run sessions and a gaming agent training match.
-During the run session, the agent plays 200 matches guided by a specific Q-Table with a 5\% chance of a randomly selecting a movement, to reduce deadlocks and loops.
+During the run session, the agent plays 200 matches guided by a specific Q-Table with a 5\% chance of randomly selecting a movement, to reduce deadlocks and loops.
 Following the run session, the agent performs a single gaming agent training match.
-The gaming agent starts with a Q-Table initialized with zeros, so the initial policy for the agent is randomized.
-For the agent to learn from the feedback generated by the OHC movement actions are determined by the agent's actions that are taken from one brainwave session match.
+The gaming agent starts first with a Q-Table initialized with zeros, so the initial policy for the agent is randomized.
+For the agent to learn from the feedback generated by the OHC, movement actions are determined by the agent's actions that are taken from one brainwave session match.
 This allows the Q-Table to be built based on the OHC's feedback from the movements the agent took, which are executed pseudo-randomly while executing the brainwave session.
@@
 In addition, the classification accuracy obtained averaging 5 epochs is shown as well.
-Although the signal averaging procedures improves the Signal-To-Noise-Radio (SNR) of the ErrP response, it reduces the number of data samples, producing a clear improvement only for the OHCs that contain more samples (1, 3 and 7).
+Although the signal averaging procedure improves the Signal-To-Noise-Radio (SNR) of the ErrP response, it reduces the number of data samples, producing a clear improvement only for the OHCs that contain more samples (1, 3 and 7).
 

### 2020-08-25 review/response.letter.tex
Subo la version que finalmente mandamos a ScholarOne.  En 6 meses charlamos.

@@
 reduction) on the average number of steps, required to reach the target in 200 plays, is achieved when a classifier is trained with ErrP signals from the same subject that is used to identify the ErrP.
-This is added in Section IV and in Figure 7.
+This is added in Section III and in Figure 7.
 On the other hand, the structure of the game scenario allows to easily extend the experiments to verify what is the outcome of manipulating the stimulus, their presentation or the influence on the results if incentives are given to participants.
@@
 {\color{blue}
-Historically MNE standed for Minimum Error Estimate, a software package developed in Martinos Center of Harvard University.
+Historically MNE stands for Minimum Error Estimate, a software package developed in Martinos Center of Harvard University.
 Now MNE  is the name of a entire software platform to perform analysis of several type of brain signals like Magnetoencephalograpy and Electroencephalography.
@@
 {\color{blue}
-Excellent.  We added that information.
+Excellent.  We added that information on Page 3.
 }
@@
 So far we didn't test if the Error Potential is affected by the smooth progression toward the end, which is indeed something interesting to verify in this simple scenario.
-We added this very interesting extension in Section IV.
+We added this very appealing extension in Section IV.
 
@@
 Yes, the Reviewer is correct.
-We modified this sentence to state more clearly the message that we wanted to convey, which is, that results are completely subject dependent.
-But that even when many action should be tagged as "wrong" (triggering an ErrP) only with a few of them right, it is enough to train the agent towards the optimal solution.
+We modified this sentence to state more clearly the message that we wanted to convey, which is, that results are completely subject dependent, and that even when many actions should be tagged as "wrong" (triggering an ErrP) only with a few of them accurate, it is enough to train the agent towards the optimal solution.
 }
@@
 The statement is absolutely right.
-We extended this experience per Reviewer's suggestion and we verified that effectively the only combination of training/testing in the recognition of ErrP that produces an improvement on the performance of the agent is the one that uses information from the same subject (check new Figure 7).
+We extended this experience per Reviewer's suggestion and we verified that effectively the only combination of training/testing in the identification of ErrP that produces an improvement on the performance of the agent is the one that uses information from the same subject (check new Figure 7).
 We think a generic-classifier to identify ErrP potentials for any subject (i.e.
@@
 We wanted to emphasize the finding that even with such low levels of identification, it was possible for the agent to learn an efficient strategy.
+The accuracy obtained in each single subject is representing the ability of the classifier to identify the ErrP response and to produce accurate rewards for the reinforcement learning scheme.
 }
@@
 The classification accuracy obtained for all subject is now being shown on Figure 5 with ROC curves.
-What is shown progressively is the experiment itself, where after each gaming agent training match, a new Q-Table is generated based on the rewards tagged from the brainwave session.
+We shown progressively the experiment itself, where after each gaming agent training match, a new Q-Table is generated based on the rewards tagged from the brainwave session.
 The agent improves their efficiency by reaching the target in a progressively less number of steps on average for each run session.
@@
 {\color{blue}
-The ratio hit/no-hit segments is 50/50, so for each brainwave session match, as the average number of steps is around 100, it will be 50 segments of hit (moving further from the target) and 50 of no-hit (moving closer).
+The ratio hit/no-hit segments is 50/50, so for each brainwave session match, as the average number of steps is around 100, it will be 50 segments of hit (moving farther from the target) and 50 of no-hit (moving closer).
 }

### 2020-08-25 ErrP.tex
Subo la version que finalmente mandamos a ScholarOne.  En 6 meses charlamos.

@@
 e-mail: rramele@itba.edu.ar.}% <-this % stops a space
-\thanks{Manuscript received December 9, 2019; revised August 20, 2020.}}
+\thanks{Manuscript received December 9, 2019; revised August 25, 2020.}}
 
@@
 These rewards are obtained by implementing a Brain-Computer Interface (BCI) system that identifies signal components called Error-related Potentials (ErrP), which occur when a person witnesses a recognizable error.
-We perform an experiment where rewards are obtained from the ErrP signals from observational human critics watching an agent randomly play a game.
+We perform an experiment where rewards are obtained from the ErrP signals from observational human critics watching an agent playing randomly a game.
 The agent is iteratively trained by receiving these rewards and updating its policy, improving its overall performance.
@@
 The gaming agent starts first with a Q-Table initialized with zeros, so the initial policy for the agent is randomized.
-For the agent to learn from the feedback generated by the OHC, movement actions are determined by the agent's actions that are taken from one brainwave session match.
-This allows the Q-Table to be built based on the OHC's feedback from the movements the agent took, which are executed pseudo-randomly while executing the brainwave session.
+For the agent to learn from the feedback generated by the OHC, movement actions are determined by the reply of the agent's actions that were taken during one brainwave session match, in an offline reinforcement learning scheme~\cite{Levine2020}.
+This allows the Q-Table to be built based on the OHC's feedback from the movements the agent took, which were executed pseudo-randomly during the brainwave session.
 The previously mentioned feedback is not explicit as it comes from the interpreted brain signal data.
@@
 \includegraphics[scale=0.4]{Images/Average_steps/all.eps}
-\caption{Average steps using Q-Table trained with brainwave session matches from six different OHCs.}
+\caption{Average steps using Q-Table trained with brainwave session matches from six different OHCs. X axis show the progressive number of gaming agent training matches used to train the Q-Table.}
 \label{fig:avg_steps_all}
@@
 Further work will be conducted in order to increase the complexity of the game to allow the possibility that the target position is dynamically changed.
-Although we found that the better performing classifier is Logistic Regression, there is room for improvement.
+Although we found that the best performing classifier is Logistic Regression, there is room for improvement.
 The classifier could be enhanced to recognize the Error Potential~\cite{Iwane2017} more effectively or could be pre-trained to allow higher accuracy~\cite{Spuler2012}.

### 2020-09-25 review2/response.letter.tex
Info for Review round 2

--- 2020-08-25 review/response.letter.tex
@@
 
-We are grateful to all the reviewers for their tremendously helpful feedback.
+We appreciate a lot all the comments and feedback provided by the AE and the Reviewers.
 
-In the following, we discuss how we dealt with each raised issue.
+In the following, we discuss all the changes with each raised issue.
 
@@
 
+\section*{\fbox{AE Transcript:}}
+
+AE's Comments to Author:
+
+Associate Editor
+Comments to the Author:
+The paper is improved but would benefit from a further update to
+- improve abstract
+- provide further interpretation/discussion of findings
+- fix minor errors/typos
+- address the grand average recommendation
+
 \section*{\fbox{Reviewer \#1 Transcript:}}
 
-This paper proposes the use of a gaming agent to be trained using Reinforcement Learning (RL) as well as the feedback obtained from EEG brainwaves of human critic observers.
-The idea of using brain patterns for boosting ML is highly interesting and well suited for the journal.
-Although it is not a new concept, it is nicely re-purposed for online use-case.
+Comments to the Author
+The paper is improved. The contribution is clearer. Thank you for the reply to comments. I attach some further comments.
 
-However, I am not sure if there is something new in the paper compared to the 2010 proof-of-concept (Iturrate et al.: Robot Reinforcement Learning using EEG-based reward signals).
-The presentation style seems a bit confusing and needs serious improvements.
-Background is very limited (some are incorporated in the introduction) and substantial work is required.
-There has been a lot of work in BCIs over the past decade and some in the area of games.
+Training a Gaming Agent on Brainwaves
+The paper has been improved. IMO, there are still areas that need further attention to improve the paper further.
+Page 1
+The abstract still reads like an introduction until the last sentence.
+I would begin with sentence: “Error-related potential (ErrP) are a particular type of ERP that can be elicited by a person who attends a recognizable error.”
 
-From the scientific part, the results are not so convincing.
-In particular, the proposed idea does not seem to be too practical method.
-The classification does not provide something significant as it stands at the moment.
-The sample used is also quite small and the complexity of the game is limited.
+\begin{quotation}
+{\color{blue}
+fdsjlfjldksj
+}
+\end{quotation}
 
-Nevertheless, the paper could be improved in many ways.
-An obvious point would be to improve the classifiers.
-Apart from this, I would suggest that authors would look at ways of manipulating the stimulus, stimulus presentation or giving out incentives to participants.
+Expand the results of the paper as this is the contribution.
+“Results show that there is an effective transfer of information and that the agent learns successfully to solve the game efficiently.
+Both the underlined terms need to cite evidence from the paper.
+
+\begin{quotation}
+{\color{blue}
+fdsjlfjldksj
+}
+\end{quotation}
+
+Line 40 “This information is used to make a gaming agent <that> improves ....”
+
+\begin{quotation}
+{\color{blue}
+fdsjlfjldksj
+}
+\end{quotation}
+
+Line 11 col 2 “how biological agents learn from its <their> environment by exploring it and getting feedback rewards, either negative or positive.”
+
+\begin{quotation}
+{\color{blue}
+fdsjlfjldksj
+}
+\end{quotation}
+
+Line 17 col2 “Nonneglected is the influence of DeepBrain’s AlphaGo project,” // Re-word
+
+\begin{quotation}
+{\color{blue}
+fdsjlfjldksj
+}
+\end{quotation}
+
+Line 24 col 2 “The papers [8], [9], [10] have successfully demonstrated that a robot can be controlled by obtaining a reward signal from a person’s brain activity, which who is observing the robot, <to> solve a task.”
+
+\begin{quotation}
+{\color{blue}
+fdsjlfjldksj
+}
+\end{quotation}
+
+Line 58 Put in a reference number from ethics committee from which approval was sough (e.g. University committee)
+
+\begin{quotation}
+{\color{blue}
+fdsjlfjldksj
+}
+\end{quotation}
+
+Page 2
+Line 56 “Data is <are> handled and processed with the OpenVibe Designer,” // datum-data
+
+\begin{quotation}
+{\color{blue}
+fdsjlfjldksj
+}
+\end{quotation}
+
+Line 37 col 2 “This dataset has been published on the IEEE DataPort initiative [15].” // I would move this to the end of next paragraph (or possibly end of paper)
+
+\begin{quotation}
+{\color{blue}
+fdsjlfjldksj
+}
+\end{quotation}
+
+Page 4
+Lin 24 This allows to learn the Q-Table <to learn> based on the subject’s feedback from the movements the agent
+took, which are chosen pseudo-randomly, while executing the brainwave session.
+
+\begin{quotation}
+{\color{blue}
+fdsjlfjldksj
+}
+\end{quotation}
+
+Line 50 “The best overall performance is obtained using Logistic Regression.” // also need to discuss the significance of the overall levels of accuracy in Discussion.
+Is a best performance of 0.672 useful/acceptable?
+How does it compare to other researchers (if a comparison is possible).
+
+\begin{quotation}
+{\color{blue}
+fdsjlfjldksj
+}
+\end{quotation}
+
+Line 42 col 2 “These results are also consistent with their classification ROC curves, shown on <in> Figures 6 obtained for both subjects, where the area under the curve are close to chance level.” // Why didn’t you show one good ROC curve and one bad one.
+This would provide the basis for comparison.
+
+\begin{quotation}
+{\color{blue}
+fdsjlfjldksj
+}
+\end{quotation}
+
+Page 5
+Figure 5 “Y axis shows the averaged number of steps, while x axis show the number of
+experiences used to cumulative train the Q-Table.”
+// Why does Fig5 E only have 2 sets of data? Some discussion of the (smaller) change from 1 – 2 would be appropriate (e.g. I Discussion)
+Line 51 “Not performance gain is evidenced, the agents learn nothing which implies that the reward information is useless.” // useless is not a good choice of wording –provides no value
+
+\begin{quotation}
+{\color{blue}
+fdsjlfjldksj
+}
+\end{quotation}
+
+Line 55 “It can be seen that the overall performance of the agent improves as long as there are more experiences to be used to train it, regardless if they were generated from the brainwaves classification from different subjects.” // more explanation/discussion needed.
+Is this an average effect from positive learners?
+
+\begin{quotation}
+{\color{blue}
+fdsjlfjldksj
+}
+\end{quotation}
+
+This work aims to state whether ErrP signals could be used to train a gaming agent using reinforcement learning.
+The collected data show that ErrP signals can in fact be classified and used to train an agent effectively.
+// Can you link these findings to confirm/challenge other recent research in Err potentials
+
+\begin{quotation}
+{\color{blue}
+fdsjlfjldksj
+}
+\end{quotation}
+
+Page 6
+Fig 8 – why use data from subject 6 (a non-learner)?
+
+\begin{quotation}
+{\color{blue}
+fdsjlfjldksj
+}
+\end{quotation}
+
+Line 42 “However, even though this implies that the agent misses frequently that an action taken is wrong, this is not hindering the overall performance and the agent is still learning” //
+
+\begin{quotation}
+{\color{blue}
+fdsjlfjldksj
+}
+\end{quotation}
+
+Line 20 col 2 Despite that, the rewards generated from different subjects can be used to train the same Q- Table to improve its performance, which may lead to strategies where the overall performance is improved based on the information from different human critics at the same time.
+//These are key findings, worth more discussion/interpretation and inclusion in abstract.
+
+\begin{quotation}
+{\color{blue}
+fdsjlfjldksj
+}
+\end{quotation}
 
@@
 
-The paper is interesting and relevant. However in my opinion it needs revision for purposes of clarification and to improve the contribution.
-Please see attached document for my comments.
+Comments to the Author
+The authors have satisfactorily addressed my concerns.
+I have a minor comment regarding Figure 3.
+It is unclear what the brown bar labelled GrandAvg represents since there is one for each participant.
+Please clarify.
+I suggest having another set of bars (a ninth) for the grand average (average over participants) for each of the algorithms used.
 
-Training a Gaming Agent on Brainwaves
-There are too many grammatical errors to list individually.
-//Does the header refer to a general template?
-JOURNAL OF LATEX CLASS FILES, VOL. 14, NO. 8, AUGUST 2015
-//The abstract read more like an introduction, rather than an indication of the work undertaken for the paper.
-25 “Results show that there is an effective transfer of information and that
-the agent learns successfully to solve the game efficiently.”
-//This is too vague. What are the outcomes of the study?
-39 This information is used to make a gaming agent improves its operational performance using electroencephalography (EEG) signals as feedback of the performed task, obtained from an observational human critic.
-//There is a grammar issue. I don’t understand this sentence.
-54 RL should be defined in main body of the paper. Also the term ‘agent’ needs to be defined/clarified. How does it relate to the Game Manager from Figure 1?
-17 col 2 Recently, this technique has seen a come-back. //this is not scientific language
-58 col 3 The precision of 25.125 is inappropriate P2, 46 col 2 What is “state information”?
-P3, 2 red normally indicates an error
-P3, 11 I assume that the “observational human critic” is the player/participant/subject/human observer. This role should be clarified and terminology used consistently.
-P3, 41 define MNE
-P3, 56 Thus, each epoch is composed of a matrix 500 x 8. // add channels
-P4, 32 Hence, following the iterative procedure based on Equation 1, the Q-Table is updated in each iteration.
-After the algorithm finishes iterating through all the training episodes, the Q-Table is stored to test the performance of the agent.
-// Will the game always terminate? How long does the game take? Does smooth progression toward finish affect the err potential?
-P4 Fig 3. Is the chance score = 0.5?
-P4 the labels referred to in Fig 5 should correlate with the test here, i.e., A= subject 1 etc.
-P4 referring to Fig 6; a comparison ROC curve with subject 1 would be more interesting
+\subsection*{\ovalbox{Reviewer 1 General Comments}}
+AE's Comments to Author:
 
-P5, 34 what is meant by “experiences”?
-P5, 29 col 2 – remove Average steps per Q-Table legend.
-P5 50, col 2 The collected data show that ErrP signals can in fact be classified and used to train an agent effectively.
-// how has effectiveness been determined here?
-Page 6 Fig 10 the text is not legible, it should be improved.
-Page 6, 40
-“However, even though this implies that the agent misses frequently that an action taken is wrong, this is not hindering the overall performance and the agent is still learning.”
-// Your results show that this is subject dependent
-P6, 56
-Results show that training a classifier with data of one subject, but using it
-to classify the events of experiences of another subject does
-not lead to an improvement on the performance of the agent.
-// could a pre-trained generic classifier provide a better initial state, subsequently trained with observer data to converge more quickly?
-Are there differential err potential for up, down, left, right?
+Associate Editor
+Comments to the Author:
+The paper is improved but would benefit from a further update to
+- improve abstract
 
-\section*{\fbox{Reviewer \#3 Transcript:}}
+\begin{quotation}
+{\color{blue}
+We conducted a new BCI and games literature review and updated the Introduction accordingly, adding more updated background.
+We highlight now what we think is our contribution, which is a simple game that can be used to trigger the ErrP response in a simple scenario that can be used to train an agent.
+We were unable to find a similar work from that same perspective.
+}
+\end{quotation}
 
-Comments to the Author
-The following work shows the usage of ErrPs for training a gaming agent using reinforcement learning.
-Authors attempt different conventional classification approaches, as well as intersubject classification.
+- provide further interpretation/discussion of findings
 
-It is unclear to me the benefit of evaluating single subject to single subject offline classification accuracy.
-Please elaborate on this.
-Since different subjects attained different performance, all combinations of subjects used for training and testing should be inspected for the 1:1 evaluation setup.
-Maybe classification accuracy could be reported at different steps (depending on the amount of training data – gradual increasing the number of subjects)
-What is the ratio of hit/no hit segments of action (epochs)?
-Page 3, column 2, lines 4-9. It is unclear at this stage what action from the starting point would generate an ErrP.
-moves-> move
-Page 3, column 2, lines 11-13. Has the MinMax Scaler been applied in any other BCI related study or elsewhere? I think including a reference would be useful.
-Page 4. Figure 3. I would suggest adding another set of bars for the grand average classification scores.
-Page 4, Figure 4. This figure is redundant and could be removed.
-Page 5, Figure 5. The titles of the subplots would be more descriptive when replacing the letters with the corresponding subjects number.
-Page 5, column 1, line 52, Not ->no
-Page 5, column1, line 55, accumulative->cumulative
-Page 6, Figure 8. It is unclear to me what is the benefit of showing both A and B. Since the behavior is similar in both cases.
-Page 6, Figure 10. This figure is, in my opinion, incomplete. What is the reason for showing this subset of subjects? I suggest showing the confusion matrices of all subjects and/or their average.
-Page 6, column 2, line 40. show -> shows
+\begin{quotation}
+{\color{blue}
+BLA BLA BLA
+}
+\end{quotation}
+
+- fix minor errors/typos
+
+\begin{quotation}
+{\color{blue}
+BLA BLA BLA
+}
+\end{quotation}
+
+- address the grand average recommendation
+
+\begin{quotation}
+{\color{blue}
+BLA BLA BLA
+}
+\end{quotation}
 

### 2020-09-25 review2/ErrP.1.tex
Info for Review round 2

--- 2020-08-23 ErrP.tex
@@
 e-mail: rramele@itba.edu.ar.}% <-this % stops a space
-\thanks{Manuscript received December 9, 2019; revised August 20, 2020.}}
+\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}
 
@@
 % The paper headers
-\markboth{IEEE Transactions on Games}%
+\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
 {Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}
@@
 \begin{abstract}
-In this study, we propose a simple game scenario that can be used to trigger a feedback response embedded in Electroencephalographic (EEG) signals of an observation human critic that observes an agent playing a game.
-Based on a Reinforcement Learning (RL) model, the gaming agent receives rewards for their actions on the game and learns its optimal policy.
-These rewards are obtained by implementing a Brain-Computer Interface (BCI) system that identifies signal components called Error-related Potentials (ErrP), which occur when a person witnesses a recognizable error.
-We perform an experiment where rewards are obtained from the ErrP signals from observational human critics watching an agent randomly play a game.
-The agent is iteratively trained by receiving these rewards and updating its policy, improving its overall performance.
-Our results are expressed in threefold: (i) the structure of a simple grid-based game that can elicit the ErrP signal component; (ii) the verification that low classification accuracy of just above chance level that produces noisy rewards is enough to allow an agent to learn the optimal policy; (iii) collaborative rewards from multiple observational human critics can compensate the lack of accuracy or the limited scope of transfer learning schemes.
+The field of Brain Computer Interfaces (BCI) has seen a bloom in the past few years.
+One of its applications is the training of systems using signals originated from the human brain.
+Out of all the methods used to acquire information from the central nervous system, the one that has gained most popularity is Electroencephalography (EEG), mainly because of its effectiveness, low cost and its noninvasive characteristic.
+Event-related potential (ERP) are brain signals found on EEG that are time-locked to a particular event.
+Error-related potential (ErrP) are a particular type of ERP that  can be elicited by a person who attends a recognizable error.
+When subjects observe an agent who makes a mistake this potential can be discerned by analyzing the signals which are directly related with the cognitive interpretation of an erroneous outcome or decision.
+Reinforcement Learning (RL) is an Artificial Intelligence approach where an agent tries to maximize rewards obtained while interacting with an unknown environment.
+In this work, a gaming agent is trained using RL, and the feedback obtained from brainwaves of human critic observers.
+Results show that there is an effective transfer of information and that the agent learns successfully to solve the game efficiently.
 \end{abstract}
-
-%When subjects observe the agent making a mistake this potential can be discerned by analyzing the signals which are directly related with the cognitive interpretation of an erroneous outcome or decision.
 
@@
 \end{IEEEkeywords}
-
-%n this study into the player’s emotional theory of mind (ToM) of gameplaying agents, we investigate how an agent’s behaviour and the player’s own performance and emotions shape the recognition of a frustrated behaviour.
-We focus on the perception of frustration as it is a prevalent affective experience in human-computer interaction.
-We present a testbed game tailored towards this end, in which a player competes against an agent with a frustration model based on theory.
-We collect gameplay data, an annotated ground truth about the player’s appraisal of the agent’s frustration, and apply face recognition to estimate the player’s emotional state.
-We examine the collected data through correlation analysis and predictive machine learning models, and find that the player’s observable emotions are not correlated highly with the perceived frustration of the agent.
-This suggests that our subject’s ToM is a cognitive process based on the gameplay context.
-Our predictive models—using ranking support vector machines—corroborate these results, yielding moderately accurate predictors of players’ ToM.
-
-%In this work, we propose a Dynamic Difficulty Adjustment methodology to achieve automatic video game balance.
-The balance task is modeled as a meta game, a game where actions change the rules of another base game.
-Based on the model of Reinforcement Learning (RL), an agent assumes the role of a game master and learns its optimal policy by playing the meta game.
-In this new methodology we extend traditional RL by adding the existence of a meta environment whose state transition depends on the evolution of a base environment.
-In addition, we propose a Multi Agent System training model for the game master agent, where it plays against multiple agent opponents, each with a distinct behavior and proficiency level while playing the base game.
-Our experiment is conducted on an adaptive grid-world environment in singleplayer and multiplayer scenarios.
-Our results are expressed in twofold: (i) the resulting decision making by the game master through gameplay, which must comply in accordance to an established balance objective by the game designer; (ii) the initial conception of a framework for automatic game balance, where the balance task design is reduced to the modulation of a reward function (balance reward), an action space (balance strategies) and the definition of a balance space state.
-
-%In this study, we propose a simple game scenario that can be used to trigger a feedback response embedded in the Electroencephalographic (EEG) signals of an observation human critic that observes an agent playing a game.
-Based on the model of Reinforcement Learning (RL), a gaming agent receives rewards based on their actions on the game and learns its optimal policy.
-These rewards are obtained by implementing a Brain-Computer Interface (BCI) system that identifies signal components called Error-related Potentials (ErrP).
-These are brain signals found on EEG that can be elicited by a person who attends a recognizable error.
-When subjects observe the agent making a mistake this potential can be discerned by analyzing the signals which are directly related with the cognitive interpretation of an erroneous outcome or decision.
-Our experiment
-
-%In addition, we verified that the effective tagging of rewards could only be performed by using information from the same subject.
-
-%Our results are expressed in threefold: (i) a simple grid-based game can elicit the ErrP signal component; (ii) though ErrP identification accuracy is low and produces a noisy reward, an agent can learn the optimal policy and solve the simple game; (iii) collaborative rewards from multiple observational human observers can compensate the lack of accuracy obtained from specific subjects.
-
-%Therefore, in this work, we aim to use the information extracted from brainwaves to enhance the performance of a gaming agent.
-The three contributions  are (1) a very simple game that can elicit the ErrP potential, (2) results that confirm that even when ErrP classification accuracy is low and produces a noisy reward signal, that provides enough information for an agent to learn the optimal policy and solve the simple game and (3) that collaborative rewards from multiple observational human observers can compensate the lack of accuracy obtained from specific subjects.
-
-%Each time the gaming agent plays this simple game, it takes on average around 100 steps to reach the target spot.
-We asked an observational human critic to watch the gaming agent play the game, while we recorded their brainwaves.
-We trained first a classifier to be able to recognize Error Potentials from these brainwaves.
-We started the game again, and the gaming agent started to move around the board, but this time once an Error Potential was identified from the brainwaves, it was used as a negative reward to train a new Q-Table for the agent.
-The game was iteratively repeated, but the gaming agent used the Q-Table that was updated in the previous experience.
-%We verified that by doing this experiment, the agent required less and less steps on average to reach the goal until it arrives to the optimal number of around 10 steps.
-We found that although the number of training sessions depended on the accuracy of the classifier, even with very low values (just above chance level), the agent learns and the number of average number of steps is reduced.
-%We verified that if trained the agent with noise signals, completely uncorrelated with the reward, the agent learned nothing, and the average number of steps was not reduced at all.
-%Finally, we also verified that if we train a classifier with Error Potentials from one subject and used that classifier to provide the rewards for the experiment, the number of steps is not reduced, and that do not depend on the subjects, is an intrinsic result which is produced when mixing the classifiers.
-Only the usage of a classifier from the same subject produces this improvement.
-%Finally, we verified that rewards obtained from different subjects, can be used to improve the performance of the gaming agent collaboratively.
 
@@
 
-%This work tackles this problem by exploring the use of brain signals as an interface between humans and computers, trying to provide information to the system without explicit communication from the user.
-
 % You must have at least 2 lines in the paragraph with the drop letter
 % (should never be an issue)
-\IEEEPARstart{T}{he} effectiveness of today's human–machine interaction and artificial intelligence is limited by a communication bottleneck, as humans are required to translate high-level concepts into a machine-mandated sequence of instructions~\cite{Xu2020,CURSOR-CONTROL-PAPER}.
-Hence, new interaction methods are required to increase the communication bandwidth between computers and humans or to produce alternative communications systems to increase the efficiency of this channel.
-In this respect, video games have been widely used as test tools to assess new means of interactions~\cite{Carter2014,Barr2007}.
-Video gaming agents are computer programs that can sense the computer game environment, process information, and react accordingly within the environment.
-They are used in the context of testing and evaluating artificial intelligence algorithms that aim to win the game or to behave like a real user player~\cite{Zhao2020}.
-In this work, the feedback obtained from an observational human critic (OHC) in the form of electroencephalographic (EEG) signals is used to evaluate the operational performance of a gaming agent.
-Observational human critics are silent subjects observing a computer gaming agent playing the game.
-
-% Reescribí la primera oración porque el sujeto no tenía sentido con el predicado.  TODO
-The feasibility of a distinct non-biological communication channel between the Central Nervous System (CNS) and a computer device has been previously proven with Brain Computer Interfaces (BCI) or Brain Machine Interfaces (BMI).~\cite{Vasiljevic2020}.
-BCI systems provide a new input modality that can be used in the context of a computer game~\cite{Scherer2012,Nijholt2007}.
-This advancement is relevant in the context of the accessibility for video games~\cite{Aguado-Delgado2020} and the growing area of e-sports~\cite{Yakovlev2020}.
-
-% Observation human critic? Suena raro acá, puse Subject pero chequear! TODO
-In this study, gaming agents are trained using only signal components called Error-related Potentials (ErrP) that can be identified in the observer's brain signals.
-These types of signals can be found on EEG traces and are elicited when subjects are aware of the presence of an unexpected outcome, which they identify as an error.
-The analysis of ErrP signals is currently an extensive area of research in the neuroscience community~\cite{Holroyd2009}.
-Error-related Potentials can be detected by signal processing and machine learning techniques~\cite{EERP-PAPER} and are also used in Brain-Computer Interfaces to implement or enhance artificial communication channels~\cite{Chavarriaga2014}.
-
-Given the scenario, Reinforcement Learning (RL)~\cite{Sutton2018} stands out as a natural method to train the agent.
-Reinforcement Learning refers to an algorithmic learning strategy inspired on how biological agents learn by exploring their environment while getting negative or positive feedback rewards.
-The method aims to maximize positive rewards while minimizing negative feedback.
-Thus, the learning problem is posed as a stochastic optimization strategy~\cite{Santos1999}.
-Recently, this technique has been used extensively in the context of advances in artificial intelligence~\cite{Nguyen2020}.
-The influence of DeepBrain's AlphaGo project cannot be neglected, since it was the first to reach a very high proficiency when it won the complex game Go against several world champions~\cite{ALPHA-GO}.
+\IEEEPARstart{T}{he} effectiveness of today's human–machine interaction and artificial intelligence is limited by a communication bottleneck as humans are required to translate high-level concepts into a machine-mandated sequence of instructions~\cite{CURSOR-CONTROL-PAPER}.
+This work tackles this problem by exploring the use of brain signals as an interface between human and computer, trying to provide information to the system without explicit communication from the user.
+This information is used to make a gaming agent improves its operational performance using electroencephalography (EEG) signals as feedback of the performed task, obtained from an observational human critic.
+The idea is that subjects observing a computer game playing, can train the gaming agent using only signals components called Error-related Potentials (ErrP) that can be identified from their brain signals.
+These can be found on EEG traces and are elicited when a subject is aware of the presence of an unexpected outcome, which she/he identifies as an error.
+It is currently an extensive area of research in the neuroscience community~\cite{Holroyd2009}.
+Error-related Potentials can be detected by signal processing and machine learning techniques~\cite{EERP-PAPER} and they are also used in Brain-Computer Interfaces (BCI) to implement or enhance artificial communication channels~\cite{Chavarriaga2014}.
+
+In order to train the agent, RL~\cite{Santos1999} comes as a natural solution for this scenario from the field of Artificial Intelligence.
+RL is an algorithmic learning strategy that can be established by mimicking how biological agents learn from its environment by exploring it and getting feedback rewards, either negative or positive.
+This strategy aims to maximize the amount of positive rewards while keeping the number of negative feedback low.
+Thus, the learning problem is  posed as a mere stochastic optimization strategy~\cite{sutton2018reinforcement}.
+Recently, this technique has seen a come-back.
+Nonneglected is the influence of DeepBrain's AlphaGo project, which was the first to reach a very high proficiency when it won the complex game Go against several world champions~\cite{ALPHA-GO}.
 
@@
 Previous research has explored the usage of RL with reward signals based on brain activity, recorded by an EEG-based BCI system during task execution.
-The papers \cite{ROBOT-CONTROL-PAPER,Kim2017,Omedes2013} have successfully demonstrated that a robot can be controlled with brain signals from a person that is observing a robot solve a task.
-Moreover, a growing number of studies have demonstrated the feasibility of using ErrPs as rewards for RL schemes such as to enhance robotic behaviour~\cite{Luo2019}, to assess air traffic controller's decisions~\cite{Goh2019} or to categorize actions as errors~\cite{Wirth2020}.
-Other approaches have used these signals as important feedback for human-robot interaction or to implement shared-control strategies~\cite{Schiatti2018}.
-Additionally, ErrPs have also been used in the context of games as an additional feedback channel that can be explored to improve gaming experience~\cite{Plass-OudeBos2010,kober2018bci}.
-
-Therefore,  we aim to use the information extracted from brainwaves to enhance the performance of a gaming agent.
-The three contributions are (1) a simple game that can elicit the ErrP potential, (2) results that confirm that even when ErrP classification accuracy is low and produces a noisy reward signal, enough information is generated for an agent to learn the optimal policy and solve a simple game and (3) collaborative rewards from multiple observational human observers can compensate the lack of classification accuracy or the inefficacy of transfer learning procedures for brainwaves signals.
+The papers \cite{ROBOT-CONTROL-PAPER,Kim2017,Omedes2013} have successfully demonstrated that a robot can be controlled by obtaining a reward signal from a person's brain activity which is observing the robot solve a task.
+Other approaches have used the signal as an important feedback for human-robot interaction or to implement shared-control strategies~\cite{Schiatti2018}.
+Additionally, ErrPs have also been used in the context of games as an additional feedback channel that can be explored to enhance gaming experience~\cite{Plass-OudeBos2010,kober2018bci}.
+In this same line, the objective of this work is to use the information extracted from brainwaves to enhance the performance of a gaming agent, replicating and extending the usage of this signal.
 
@@
 In Section \ref{section:materials} the general layout of the cognitive game is described.
-Sections \ref{brainwavesession} and \ref{cognitive_experiment_details} outline the cognitive game procedure used to obtain rewards in the form of ErrP components.
-Section \ref{q_learning_step_alg} describes the gaming agent learning procedure.
-Lastly, results and conclusions are exposed in Sections \ref{results} and \ref{conclusions}.
+Section \ref{section:calibration} outlines the processing pipeline used to detect ErrP components.
+The following Section \ref{learning} describes the agent learning phase.
+Results and Conclusions are exposed in Sections \ref{results} and \ref{conclusions}.
 
@@
 
-The experimental procedure is summarized in Figure \ref{diag:complete_flow}.
-The proposed system has two distinct parts.
-This first part consists of the collection of brainwave signals from a person that is watching an agent play a game.
-The agent knows the game rules but not how to win it.
-The second part, the gaming agent learning phase, is where the agent can learn the winning strategy using the person's feedback to improve its own performance.
+This first part consists in collecting signals from a person's brainwaves while they are watching a game where the agent knows the game rules but not how to win it.
+Hence, the agent can learn the winning strategy using the person's feedback to improve its own performance.
+This section describes the process of obtaining the person's brain signals that are used to make the agent more efficient.
 
@@
 Brainwaves are obtained by the OpenVibe Acquisition Server.
-The Game Manager is responsible for generating the game screen, the game mechanics, and the game movements performed by the gaming agent.
-It is also connected to the Acquisition Server to send stimulus information.
+The Game Manager is responsible for generating the game screen and is connected to the Acquisition Server to send stimulus information.
 The captured information is stored by the OpenVibe Designer.
 Offline, EEG signals are classified and they are linked to each game movement calculated by the Game Manager to determine proper rewards for each action.
-This information is used by a Reinforcement Learning algorithm to learn iteratively a Q-Table to improve the performance of the agent that plays the game.}
+This information is used by a Reinforcement Learning algorithm to learn a Q-Table to improve the performance of the agent that plays the game.}
     \label{diag:complete_flow}
@@
 
-\subsection{Brainwave Session}
-\label{brainwavesession}
-
-The retrieval of the OHC's brain activity, called the brainwave session, is one of the most critical parts of the study.
-Subjects are recruited voluntarily and given a form with questions regarding their health (previous health issues and particular visual sensitivity), habits (sleeping hours, caffeine and alcohol consumption), and a consent petition to collect the required data.
-The brainwave sessions are performed with 8 subjects, 5 males and 3 females, with an average age of 25.12 years, a standard deviation of 1.54 years, and a range of 22-28 years.
-All subjects have normal vision, are right-handed and no history of neurological disorders.
+The experimental procedure is summarized in Figure \ref{diag:complete_flow}.
+The central part is the retrieval of the subject's brain activity.
+This process is called brainwave session.
+Subjects are recruited voluntarily.
+They are given a consent form with questions regarding their health (previous health issues and particular visual sensitivity), habits (sleeping hours, caffeine and alcohol consumption), as well as an approval petition to collect the required data.
+The brainwave sessions are performed with 8 subjects, 5 males and 3 females, average age 25.125 years, standard deviation 1.54 years, range of 22-28 years.
+All subjects have normal vision, are right-handed and have no history of neurological disorders.
 
@@
 When this concludes, the subject is introduced to the wireless digital EEG device (g.Nautilus, g.Tec, Austria) that she/he has to wear during the brainwave session.
-It has eight electrodes (g.LADYbird, g.Tec, Austria) on the positions Fz, Cz, Pz, Oz, P3, P4, PO7, and PO8, identified according to the 10-20 International System, with a reference set to the right ear lobe and ground set as the AFz position.
+It has eight electrodes (g.LADYbird, g.Tec, Austria) on the positions Fz, Cz, Pz, Oz, P3, P4, PO7 and PO8, identified according to the 10-20 International System, with a reference set to the right ear lobe and ground set as the AFz position.
 The electrode contact points are adjusted applying conductive gel until the impedance values displayed by the program g.NeedAccess (g.Tec, Austria) are within the desired range.
 This process takes between 10 to 15 minutes.
-After this step, the subject is instructed to close their eyes, make eye movements and muscle chew in order to check the program and guarantee that the live channel values are accurate.
+After this step, the subject is instructed to close their eyes and the same program is used to check the live channel values so that there are no dead ones and the expected values are displayed for eye movements or muscle chewing.
 
@@
 A $50$~Hz notch filter is applied to filter out power line noise.
-An additional bandpass filter between $0.5$~Hz and $60$~Hz is applied.
-Data is handled and processed with the OpenVibe Designer, from the same platform, using 8 channels for the brain data (one channel per electrode) and an additional channel to record the stimulus, which corresponds to a game movement performed by the agent.
-After everything is connected, the subject is seated in a comfortable chair in front of a computer screen.
+An additional bandpass filter between $0.5$~Hz and $60$~Hz is applied as well.
+Data is handled and processed with the OpenVibe Designer, from the same platform, using 8 channels for the brain data (one channel per electrode) and an additional channel for the stimulus, which corresponds to a game movement performed by the agent.
+After everything is connected, the subject seats in a comfortable chair in front of a computer screen.
 The brightness of the screen is set to the maximum setting to avoid any visual inconvenience in which the subject can not distinguish the components of the game that appear on the screen.
@@
 
-The Acquisition Server receives and synchronizes the signal data from the headset and any event information from the game, and transfers it to the OpenVibe Designer application.
+The Acquisition Server has the responsibility of receiving and synchronizing the signal data from the headset and any event information from the game, and transfers it to the OpenVibe Designer application.
 When the subject is ready, the Game Manager and the OpenVibe Designer programs are launched and configured to communicate with the previously mentioned Acquisition Server.
-A brainwave session consists of several matches, each one being a gameplay.
-In the end, the sequence of game movements and the signal data generated for each match are saved for offline processing.
+A brainwave session consists of several experiences, each one being a game run.
+At the end, the game state information and the signal data with the game event information of each run are saved for offline processing.
 
@@
 The game parsimoniously consists of a $5x5$ grid of grey circular spots with a black background.
-A blue spot indicates the current position of the agent and a green spot represents the goal, as shown in Figure  \ref{fig:game_representation}.
+A blue spot indicates current position of the agent whereas a green spot represents the goal, as shown in Figure  \ref{fig:game_representation}.
 The agent's objective is to reach the goal.
-The circular spot representing the goal remains static at the bottom-right position of the grid, while the one representing the position of the agent starts at the upper-left position of the grid and moves in each iteration.
-When the agent reaches the goal, the position where the agent and the goal are located turns red, showing that the match has ended.
-There are four possible movements that the agent can perform: it can go upwards, downwards, towards the left and the right, and those movements are bounded to avoid the agent from leaving the grid.
+The circular spot representing the goal remains static at the bottom-right position of the grid, while the one representing the position of the agent always starts at the upper-left position of the grid.
+When the agent reaches the goal, the position where the agent and the goal are located turns red, showing that the experience has ended.
+There are four possible movements that the agent can perform: it can go upwards, downwards, towards the left and towards the right, and those movements are bounded to avoid the agent from leaving the grid.
 The movement direction is selected randomly and is executed once every 2 seconds.
-After each gameplay, there is a pause of 5 seconds until the next match starts.
+At the end, there is a pause of 5 seconds before the next experience starts.
 Each time an agent moves, the Game Manager program sends an event marker to the Acquisition Server.
-This is considered a stimulus to the observational human critic.
-The game is designed as to be evident whenever there is an error (i.e.
+This is considered as a stimulus to the observational human critic.
+The experience is designed for it to be evident whenever there is an error (i.e.
 the agent moves away from the objective) so the subject can notice it immediately after the stimulus is presented, possibly triggering the expected cognitive response, which can be imprinted as an ErrP component within the EEG stream.
@@
 \centering 
-\caption{Grid system representation used in the cognitive game.
+\caption{Grid system representation used in the Cognitive Game Experience.
 The blue spot represents the initial location while the green spot represents the target location.
@@
 
-\subsection{Signal Processing, Segmentation and Classification}
+\section{Signal Processing, Segmentation and Classification}
 \label{section:calibration}
 
-To aid the detection of the ErrP response, an offline processing pipeline and classifier is constructed to identify whether the action taken by the agent is an error or not, from the human observer's point of view.
-It is developed in Python using the "MNE" software platform \cite{MNE-PYTHON}, which is a package designed specifically for processing EEG and Magnetoencephalography data, and built upon the machine learning library Scikit-Learn~\cite{scikit-learn}.
-
-This pipeline consists of the offline processing of the collected signals used to train a classifier that can decide whether an error potential is triggered.
-Firstly, the output of a brainwave session is read and an additional band-pass filter of 0.1-20.0 Hz is applied to the signal.
+To aid in detecting the ErrP response, an offline processing pipeline and classifier is constructed to identify whether the action taken by the agent is an error or not, from the human observer point of view.
+It is developed in Python using the MNE platform \cite{MNE-PYTHON}, which is a package designed specifically for processing EEG and Magnetoencephalography data, and built upon the machine learning library Scikit-Learn~\cite{scikit-learn}.
+
+This pipeline consists of the offline processing of the collected signals in order to train a classifier that can decide whether an error potential is triggered.
+Firstly, the output of a brainwave session is read and an additional band pass filter of 0.1-20.0Hz is applied to the signal.
 Samples that correspond to the start of an event are tagged using the data from the stimulus channel.
 
-After the raw data is loaded and tagged, epochs are extracted.
-Epochs consist of all the sample points that take place during the 2 seconds from the start of the event, 2 seconds corresponding to the time it takes for each action to take place, resulting in 500 samples per channel, as the sampling frequency is 250 Hz.
-Thus, each epoch is composed of a matrix $500$ x $8$ channels.
-
-Samples that do not correspond to an epoch (located beyond the 2 seconds frame after the onset of the event) are not used. Also, epochs referring to the start or finish of each match are excluded.
-
-In this way, the raw data of a brainwave session is processed into an array of matches where each element is an array of epochs tagged with a number specifying the prediction of the classifier, i.e.
-if the epoch corresponds to an action that made the agent move further from the goal (hit) or an action that made the agent moves closer to the goal (no-hit).
+After the data is loaded and tagged, epochs are extracted from the raw data.
+Epochs consist of all the sample points that take place between the start of the event and 2 seconds later (time for each action to take place), resulting in 500 samples per channel, as the sample frequency is 250 Hz.
+Thus, each epoch is composed of a matrix $500$ x $8$.
+
+Samples that do not correspond to an epoch (located beyond the 2 seconds frame after the onset of the event) are not used.
+Also, epochs referring to the start or finish of the experience are excluded.
+This is done because the start and the end of the experience doesn't involve the agent taking an action.
+
+In this way, the raw data of a brainwave session is processed into an array of experiences where each element is an array of epochs tagged with a number specifying the prediction of the classifier, i.e.
+if the epoch corresponds to an action that made the agent moves further from the goal (hit) or an action that made the agent moves closer to the goal (no-hit).
 The ErrP is expected to be found in hits.
-To get the data ready for classification, the stimulus channel is removed to classify the signals using only the EEG data.
+To get the data ready for classification, the stimulus channel is removed in order to classify the signals using only the EEG data.
 Each epoch is regularized using a MinMaxScaler, i.e.
-subtracting the minimum value in the epoch and dividing by the signal peak-to-peak amplitude~\cite{Zhou2019}.
-The eight channels are concatenated using the MNE Vectorizer function, which transforms the data matrix into a single array sample.
+substracting the minimun value in the epoch and dividing by the signal peak-to-peak amplitude.
+The eight channels are concatenated using the  MNE Vectorizer function to transform the data matrix into a single array sample.
 Lastly, this data is used by the classification module as information to train and test a classifier.
-Five different classification algorithms are used:  Logistic Regression, Multilayer Perceptron with a hidden layer of 100 neurons (i.e.
-default values for the Scikit-Learn MLPClassifier), Random Forest, KNeighbours with k=3 and finally a linear kernel Support Vector Classifier (i.e.
+Four different classification algorithms are used.
+Logistic Regression, Multi-layer Perceptron with a hidden layer of 100 neurons (i.e.
+default values for the Scikit-Learn MLPClassifier), Random Forest and finally a linear kernel Support Vector Classifier (i.e.
 SVM)~\cite{Lotte2018}.
@@
 
-\subsection{Reinforcement Learning}
+\section{Reinforcement Learning}
 \label{learning}
 
-Each match consists of a list of game movement configurations and the associated epochs obtained from OHC's brainwaves.
-The set of matches of each OHC is split into training and testing.
-Training matches are used to train the classifier to identify the ErrP signal.
-After a classifier is trained, the epochs extracted from the test matches are classified as hit or no-hit.
-A reward for each movement in the match is generated based on the prediction from the classifier for that movement.
+Each experience consists of a list of game movement configurations and the associated epochs obtained from subject's brainwaves.
+The set of experiences of each subject is split into training and testing.
+Training experiences are used to train the classifier, whereas test experiences are used to test its performance.
+After a classifier is trained, the epochs of the experience are classified as hit or no-hit.
+A reward for each movement in the game run is produced, based on the classification of the epoch that correspond to that movement.
 The reward can either be -1 when the event is classified as a hit or 0 when it is classified as a no-hit.
-The accuracy of these rewards depends on the performance of the classifier.
-The list of game movements and their associated reward information is used to train the agent by a variant of Reinforcement Learning called Q-Learning algorithm.
+The accuracy of this rewards depends on the performance of the classifier.
+The list of game movements and their associated reward information are used to train the agent by a variant of Reinforcement Learning called Q-Learning algorithm.
 
@@
 
-Q-Learning~\cite{Watkins1992} is a form of model-free reinforcement learning, where an agent tries an action at a particular state and evaluates its consequences in terms of the reward or penalty it receives.
-To represent rewards, a matrix $Q(s,a)$ is used, where rows correspond to all the possible states, and columns represent all possible actions.
-This matrix is known as the Q-Table.
-The algorithm proceeds by randomly choosing what action to do and iteratively updating the Q-Table based on the received reward $r$ by the following equation
+Q-Learning~\cite{Watkins1992} is a form of model-free reinforcement learning algorithm where an agent tries an action at a particular state and evaluate its consequences in terms of the reward or penalty it receives.
+In order to represent rewards, a matrix $Q(s,a)$ is used, where rows correspond to all the possible states, whereas columns represent all possible actions.
+This matrix is known as a Q-Table.
+The algorithm proceeds by randomly choosing what action to do and updating iteratively the Q-Table based on the received reward $r$ by the following equation
 
@@
 
-\noindent where $s$ is the current state, $a$ the action, $\alpha$ the learning rate and $\gamma$ the discount factor, a value between 0 and 1 that determines the importance of long term results versus immediate rewards.
+\noindent where $s$ is the current state, $a$ is the action, $\alpha$ represents the learning rate and $\gamma$ represents the discount factor, a value between 0 and 1 that determines the importance of long term results versus immediate rewards.
 Hence,  $Q(s,a)$  is the expected value of the sum of discounted rewards that the agent will receive if in the $s$ state, it takes the action $a$ according to this policy.
-Once the environment has been extensively explored and the Q-Table has been optimized, the action chosen for a given state is the one that maximizes the expected reward according to the Q-Table matrix.
+Once the environment has been extensively explored and the Q-Table has been obtained, the action chosen for a given state is the one that maximizes the expected reward according to the Q-Table matrix.
 
@@
 
-\subsection{Gaming Agent Learning Procedure}
+\subsection{Agent Learning}
 \label{q_learning_step_alg}
-
-The gaming agent learning procedure uses the testing matches from brainwave sessions produced during the cognitive game procedure phase, and their components are schematized in Figure~\ref{diag:complete_flow}.
-
-This phase is divided into a sequence of run sessions and a gaming agent training match.
-During the run session, the agent plays 200 matches guided by a specific Q-Table with a 5\% chance of a randomly selecting a movement, to reduce deadlocks and loops.
-Following the run session, the agent performs a single gaming agent training match.
-The gaming agent starts with a Q-Table initialized with zeros, so the initial policy for the agent is randomized.
-For the agent to learn from the feedback generated by the OHC movement actions are determined by the agent's actions that are taken from one brainwave session match.
-This allows the Q-Table to be built based on the OHC's feedback from the movements the agent took, which are executed pseudo-randomly while executing the brainwave session.
+The Q-Table is initialized with zeros, unless a preexisting Q-Table is passed as a parameter.
+For the agent, in order to learn from the feedback generated by the subject, the Q-Table is not used to determine the action to take at a given state.
+Instead, the policy which determines which action to take in a particular state is given by the agent's actions taken from the brainwave session results.
+This allows to learn the Q-Table based on the subject's feedback from the movements the agent took, which are chosen pseudo-randomly, while executing the brainwave session.
 The previously mentioned feedback is not explicit as it comes from the interpreted brain signal data.
-This implies that the reward is determined by the OHC's brain activity.
-
-Hence, following the iterative procedure based on Equation~\ref{equ:update_q_table}, the Q-Table is updated in each gaming agent training match.
-After the algorithm finishes replicating all the steps from the brainwave session match, the Q-Table is stored and used by the agent in the next run session.
+This implies that the reward is determined by the subject's brain activity.
+
+Hence, following the iterative procedure based on Equation~\ref{equ:update_q_table}, the Q-Table is updated in each iteration.
+After the algorithm finishes iterating through all the training episodes, the Q-Table is stored to test the performance of the agent.
 
@@
 
-Figure~\ref{fig:classifiers} shows the binary classification accuracy obtained for the eight OHCs using five different classification algorithms and using a 10-fold cross-validation procedure.
+Figures~\ref{fig:classifiers} and~\ref{fig:logisticregression} show the binary classification accuracy obtained for the eight subjects for the four different classification algorithms using a 10-fold cross validation procedure.
 The best overall performance is obtained using Logistic Regression.
-In addition, the classification accuracy obtained averaging 5 epochs is shown as well.
-Although the signal averaging procedures improves the Signal-To-Noise-Radio (SNR) of the ErrP response, it reduces the number of data samples, producing a clear improvement only for the OHCs that contain more samples (1, 3 and 7).
 
@@
     \centering
-    \includegraphics[scale=0.12]{revisedimages/cross_val.eps}
-    \caption{Binary single trial classification score using five different classifiers while recognizing ErrP potentials for the eight OHCs.
-The classification score using an ensemble average of 5 epochs is shown as well (GrandAvg).
-Chance Level is 0.5.}
+    \includegraphics[scale=0.4]{Images/algorithm_calibration/Total_calib.png}
+    \caption{Binary Classification Score using different classifiers while recognizing ErrP potentials for the eight subjects.}
     \label{fig:classifiers}
@@
 
-On the other hand, Figure \ref{fig:avg_steps} shows the average amount of steps it takes for the agent to reach the goal for each OHC, as the Q-Table is progressively trained using the reward information obtained from the prediction of the trained classifier.
-Each point corresponds to a run session where the average number of steps for the agent to reach the goal using a specific Q-Table is specified, for 200 repetitions.
-The first point, at the x-value 0, represents the number of steps the agent takes to reach the goal with an untrained Q-Table, where movements are decided randomly.
-The next point corresponds to the amount of steps it takes to reach the goal using a policy derived from a Q-Table trained after one brainwave session match, and so on.
+\begin{figure}[ht]
+    \centering
+    \includegraphics[scale=0.4]{Images/algorithm_calibration/LR_calib.png}
+    \caption{Binary Classification Score using Logistic Regression for the eight subjects.}
+    \label{fig:logisticregression}
+\end{figure}
+
+On the other hand, Figure \ref{fig:avg_steps} shows for each subject the average amount of steps the agent takes to reach the goal as the Q-Table is progressively trained using the reward information obtained from their classified experiences.
+Each point corresponds to the average number of steps in 200 repetitions that it takes for the agent to reach the goal for a specific Q-Table.
+The first point represents the amount of steps the agent takes to reach the goal for a Q-Table that hasn't been trained at all, where movements are decided randomly.
+The next point corresponds to the amount of steps it takes to reach the goal using a policy derived from a Q-Table trained with one experience, and so on.
 
@@
 \end{subfigure}
-\caption{Average number of steps for the agent to reach the goal when trained with rewards generated from brainwaves from OHCs 1-8.
-Y axis show the averaged number of steps for a run session, while x axis show the number of game matches used to cumulative train the Q-Table.}
+\caption{Average number of steps for the agent when trained with experiences from subjects 1(A)-8(H).
+Y axis show the averaged number of steps, while x axis show the number of experiences used to cumulative train the Q-Table.}
 \label{fig:avg_steps}
@@
 The results show that as the Q-Table is progressively trained the average amount of steps decreases, meaning that the agent learns.
-However, the rate at which it learns varies per OHC, depending on the classification accuracy of the extracted brainwaves.
-For example results for OHC 1 show faster learning than those of OHC 8 (Figure \ref{fig:avg_steps}).
-
-In the case for OHC 5 and 6, the reward information obtained from the brainwaves is not enough to train the agent effectively.
-Figures \ref{fig:avg_steps} for OHC 5 and 6 show no apparent learning, as the amount of steps to reach the goal doesn't decrease when trained.
-These results are also consistent with their classification ROC curves, shown on Figures~\ref{fig:rocsubjects} obtained for both OHCs, where the area under the curve are close to chance level.
-Both OHCs have less recorded data from the sessions in comparison to the rest of the OHCs.
-This variation in performance for different OHCs has been studied extensively in BCI~\cite{Chavarriaga2014}.
-Besides low data samples, there are other reasons affecting the classification accuracy:  cognitive reasons (i.e.
-the OHC not paying extensively attention to the game dynamics), very low SNR of the ErrP component or even the BCI-illiteracy phenomena where the specific OHC's signals do not contain the expected component response~\cite{Yousefi2019}.
+However, the rate at which it learns varies per subject, depending on the classification accuracy of the extracted brainwaves.
+For example results for subject 1 (Figure \ref{fig:avg_steps} A) show faster learning than those of subject 8 (Figure \ref{fig:avg_steps} H).
+
+In the case for subject 5 and 6, the reward information obtained from the brainwaves is not enough to train the agent effectively.
+Figures \ref{fig:avg_steps} E and \ref{fig:avg_steps} F show no apparent learning, as the amount of steps to reach the goal doesn't decrease when trained.
+These results are also consistent with their classification ROC curves, shown on Figures~\ref{fig:rocsubjects} obtained for both subjects, where the area under the curve are close to chance level.
+Both subjects have less recorded data from the sessions in comparison to the rest of the subjects.
+This variation in performance for different subjects has been studied extensively in BCI.
+Besides low data samples there are other reasons affecting the classification accuracy:  cognitive reasons, this being the subject not paying extensively attention to the game dynamics, very low Signal-To-Noise Ratio (SNR) of the ErrP component or even the BCI-illiteracy phenomena where the specific subject's signals do not contain the expected component response~\cite{Yousefi2019}.
 
@@
 \captionsetup[subfigure]{justification=centering}
-\begin{subfigure}{0.5\textwidth}
-\centering
-\includegraphics[scale=0.09]{revisedimages/roc_1.eps}   \hspace{-1.5em}
-\includegraphics[scale=0.09]{revisedimages/roc_2.eps} \\
-%\vspace{-1.3em}
-\centering
-\includegraphics[scale=0.09]{revisedimages/roc_3.eps}   \hspace{-1.5em}
- \includegraphics[scale=0.09]{revisedimages/roc_4.eps} \\
- \centering
-  \includegraphics[scale=0.09]{revisedimages/roc_5.eps}   \hspace{-1.5em}
-  \includegraphics[scale=0.09]{revisedimages/roc_6.eps} \\
-  \centering
-  \includegraphics[scale=0.09]{revisedimages/roc_7.eps}    \hspace{-1.5em}
-  \includegraphics[scale=0.09]{revisedimages/roc_8.eps} \\
+\begin{subfigure}{0.25\textwidth}
+    \centering
+    \includegraphics[scale=0.2]{Images/Classification_test/roc_e.png}
 \end{subfigure}
-\caption{ROC Curves for OHCs 1-8. True positive rate is on the vertical axis and false positive rate on the horizontal axis.}
+\begin{subfigure}{0.25\textwidth}
+    \centering
+    \includegraphics[scale=0.2]{Images/Classification_test/roc_f.png}  
+\end{subfigure}
+\caption{ROC Curves for subjects 5 (up) and 6 (down)}
 \label{fig:rocsubjects}
@@
 
-Figure~\ref{fig:avg_steps_noise} shows the result of an agent successively trained with brainwave session matches where the EEG is generated with random signals.
-In this case, random EEG signals are generated using OpenVibe Acquisition Server signal generator for all channels, as if they were produced by an OHC who doesn't pay attention to the game.
-The agent learns nothing, and regardless of the number of matches that are used to learn the Q-Table, the number of steps required to reach the goal does not decrease.
-This pattern is also obtained when the game matches from OHCs 5 and 6 are used, showing that the reward labeling predicted by the trained classifier for those cases worked like a random classifier.
+Figure~\ref{fig:avg_steps_noise} shows the result of an agent successively trained with experiences obtained from a brainwave session, generated with sham signals.
+In this case, random EEG signals were generated using OpenVibe Acquisition Server signal generator for all channels, as if they were generated from a human observer who doesn't pay attention to the game.
+As it can be seen, the agent learns nothing, and regardless of the amount of experiences that are used to learn the Q-Table, the number of steps required to reach the goal does not decrease.
+This pattern is also obtained when the experiences from subjects 5 and 6 are used, showing that the reward labeling predicted by the trained classifier for those subjects worked like a random classifier.
 
@@
 \centering
-\includegraphics[scale=0.4]{Images/Average_steps/noise.eps}
-\caption{Average number of steps for the agent to reach the goal when trained with a classifier produced from sham EEG signals.
-X axis show the number of gaming agent training matches used to train the Q-Table.}
+\includegraphics[scale=0.4]{Images/Average_steps/noise.png}
+\caption{Average steps using Q-Table trained with a noisy signal.}
 \label{fig:avg_steps_noise}
@@
 Electroencephalographic signals have high inter-subject variability~\cite{Chavarriaga2014}.
-This is evidenced in Figure~\ref{fig:transferlearning} where the agent training is performed with rewards obtained by classifying epochs from one Tester OHC and a classifier that was trained using the brainwaves from a different Trainer OHC.
-The figure shows the cumulative variation for all run sessions on the average number of steps required to reach the goal after training the agent with all the available matches from the brainwave session.
-Enhancements are shown as negative values.
-Only the diagonal of the heatmap matrix shows a clear improvement in terms of the reduction of the required number of steps to reach the goal (averaged per 200 runs) which corresponds to the same information for each OHC shown in Figure~\ref{fig:avg_steps}.
-For the transfer learning experiment~\cite{Wu2016}, no performance gain is evidenced, the agents learn nothing and this implies that the reward information is useless.
+This is evidenced in Figure~\ref{fig:transferlearning} where the agent training is performed by using rewards obtained by classifying epochs from one subject, but using a classifier which was trained using the brainwaves from a different subject.
+Not performance gain is evidenced, the agents learn nothing which implies that the reward information is useless.
 
@@
 \begin{subfigure}{0.5\textwidth}
-\includegraphics[scale=0.60]{revisedimages/transfer_learning_heatmap.eps}
+\includegraphics[scale=0.27]{Images/Average_steps/Ax.png}
+\includegraphics[scale=0.27]{Images/Average_steps/Bx.png}
 \end{subfigure}
-\caption{Heatmap for the transfer learning experiment. Values represent the reduction in the average number of steps required to reach the goal.  Negative values represent net improvements.}
+\caption{(A) Average steps using Q-table trained with experiences from subject 8 classified with a classifier trained with data from subject 6.
+(B) Average steps using Q-table trained with experiences from subject 1 classified with a classifier trained with data from subject 3.}
 \label{fig:transferlearning}
@@
 
-Finally, Figure~\ref{fig:avg_steps_all} shows the result of training an agent with cumulative brainwave session matches from OHCs 1, 2, 3, 4, 7, and 8.
-It can be seen that the overall performance of the agent improves as long as there is information to produce rewards, regardless of the fact that they were generated from classifiers trained with different OHC's signals.
+Finally, Figure~\ref{fig:avg_steps_all} shows the result of training an agent with accumulative experiences from subjects 1,2,3,4,7, and 8.
+It can be seen that the overall performance of the agent improves as long as there are more experiences to be used to train it, regardless if they were generated from the brainwaves classification from different subjects.
 
@@
 \centering
-\includegraphics[scale=0.4]{Images/Average_steps/all.eps}
-\caption{Average steps using Q-Table trained with brainwave session matches from six different OHCs.}
+\includegraphics[scale=0.4]{Images/Average_steps/all.png}
+\caption{Average steps using Q-Table trained with 6 experiences from different subjects.}
 \label{fig:avg_steps_all}
@@
 
-This work aims to propose a simple game that can use the ErrP component to train a gaming agent using a RL model.
-The collected data shows that ErrP signals can in fact be classified and used to train an agent effectively.
-
-This proposal tries to keep the system as simple as possible, emphasizing information flow from the subjective error perception of the human critic.
-Rewards are generated using the signal processing and classification pipeline, and the Q-Table updates, enhancing the performance of the gaming agent.
+This work aims to state whether ErrP signals could be used to train a gaming agent using reinforcement learning.
+The collected data show that ErrP signals can in fact be classified and used to train an agent effectively.
+
+This proposal tries to keep the system as simple as possible, emphasizing information flow from the subjective error perception of the human critic, through the reward generation using the signal processing and classification pipeline, and finally the Q-Table updating  to enhance the performance of the gaming agent.
+
+%Enfatizar la idea de que la mejor métrica de la propia detección está dada por la propia capacidad del agente de minimizar su tarea, que hay un flujo de información que involucra la propia percepción de la persona.
+
+%While classifying, the better performing classifier is Logistic Regression.
+One important aspect of the classification results is the low percentage of false positives (Figure~\ref{fig:confusionmatrix}), showing a high specificity.
+It is not common that the agent learns that an action is wrong when in fact it is an action that takes it closer to the goal.
+On the other hand, the percentage of false negatives is generally higher, but this is not a serious issue since missing out on learning that an action is wrong does not lower the performance of the agent, but only means it will take more experiences to learn a correct path.
+
+While classifying, the better performing classifier is Logistic Regression.
+One important aspect of the classification results is the low percentage of false positives (Figure~\ref{fig:confusionmatrix}), showing a high specificity.
+It is not common that the agent learns that an action is wrong when in fact it is an action that takes it closer to the goal.
+On the other hand, the percentage of false negatives is generally higher.
+However, even though this implies that the agent misses frequently that an action taken is wrong, this is not hindering the overall performance and the agent is still learning.
+
+%However, even though this imply that the agent misses frequently that an action taken is wrong, this do not seems to be a serious issue because the agent improves its performance.
+
+\begin{figure}[h!]
+\begin{subfigure}{0.5\textwidth}
+\centering
+\includegraphics[scale=0.12]{Images/Classification_test/matrix_a.png}
+\includegraphics[scale=0.12]{Images/Classification_test/matrix_c.png}\\
+\includegraphics[scale=0.12]{Images/Classification_test/matrix_d.png}
+\includegraphics[scale=0.12]{Images/Classification_test/matrix_h.png}
+\end{subfigure}
+\caption{Confusion Matrix for subjects 1,3,4 and 8. Darker colors show higher values.  It can be seen the lower percentage of false positives (upper right corner of each chart).}
+\label{fig:confusionmatrix}
+\end{figure}
+
+Once ErrP signals are identified they can be used to train an agent using a reinforcement learning algorithm.
+Brainwave sessions have a low amount of experiences in order to reduce fatigue from subjects.
+However data suggests that longer sessions are required in order to reach better classification scores, since more data is available in order to train the classifier.
+It can be seen that subjects with the largest amounts of data have the best classification.
+This can also be achieved designing a bigger game system that generates more samples with every session.
+
+At the same time, effective agent training depends on the subject's data that was used to train it.
+Results show that training a classifier with data of one subject, but using it to classify the events of experiences of another subject does not lead to an improvement on the performance of the agent.
+Despite that, the rewards generated from different subjects can be used to train the same Q-Table to improve its performance, which may lead to strategies where the overall performance is improved based on the information from different human critics at the same time.
 
@@
 The obtained accuracy to discriminate ErrPs is low.
-However, even with such low accuracy values, the RL algorithm was able to extract meaningful information from rewards that were helpful to improve, and often maximize, the agent's performance.
-Additionally, one important aspect of the classification results is the low percentage of false positives (Figure~\ref{fig:confusionmatrix}), showing a high specificity.
-On the other hand, the percentage of false negatives is generally higher.
-However, even though this implies that the agent misses frequently when a wrong action takes place, this is not hindering the overall performance and the agent is still learning.
-Though scarce, accurate rewards are very useful for the RL algorithm.
-%However, even though this imply that the agent misses frequently that an action taken is wrong, this do not seems to be a serious issue because the agent improves its performance.
-
-\begin{figure}[h!]
-\begin{subfigure}{0.5\textwidth}
-\centering
-\includegraphics[scale=0.14]{revisedimages/matrix_1.eps}
-\includegraphics[scale=0.14]{revisedimages/matrix_2.eps}\\
-\includegraphics[scale=0.14]{revisedimages/matrix_3.eps}
-\includegraphics[scale=0.14]{revisedimages/matrix_4.eps}\\
-\includegraphics[scale=0.14]{revisedimages/matrix_5.eps}
-\includegraphics[scale=0.14]{revisedimages/matrix_6.eps}\\
-\includegraphics[scale=0.14]{revisedimages/matrix_7.eps}
-\includegraphics[scale=0.14]{revisedimages/matrix_8.eps}\\
-\end{subfigure}
-\caption{Confusion Matrix for OHCs 1-8. Darker colors show higher values.  It can be seen the lower percentage of false positives (upper right corner of each chart).}
-\label{fig:confusionmatrix}
-\end{figure}
-
-%Brainwave sessions have a low amount of matches in order to reduce fatigue from OHCs.
-However data suggests that longer sessions are required in order to reach better classification scores, since more data is available in order to train the classifier.
-Matches from OHCs with the largest amounts of data have the best classification scores and produced more accurate rewards.
-This can also be achieved designing a bigger game system that generates more samples with every session.
-While classifying, the better performing classifier is Logistic Regression.
-
-At the same time, effective agent training depends on the OHC's training data.
-Results confirm the futility or complexity of using Transfer Learning~\cite{Wu2016}: training a classifier with data obtained from one OHC, and using the same classifier to identify ErrPs for another OHC does not increases the performance of the agent.
-Despite that, the rewards generated from different subject's classifiers can be used to train the same Q-Table to improve its performance, which may lead to strategies where the overall performance is enhanced based on the information from different human critics at the same time.
-There seems to be an agreement in terms of the subjective interpretation of what may be an appropriate movement to reach the goal.
-
-The simple setup of the grid-based game allows further experimentation, using the reduction on the number of average steps to reach the goal as a validation of the achieved information transfer.
-It will be of research interest to verify if the smooth progression towards the end alters the shape of the ErrP response, how the ErrP response is triggered in relation with different shapes and colors of the board markers~\cite{EIMER1997143}, or if there is a differential ErrP signal component in relation to up, down, left and right movements.
-In addition, the outcome of manipulating the stimulus could be further studied as well as the influence on the results if incentives are given to participants.
-
-Further work will be conducted in order to increase the complexity of the game to allow the possibility that the target position is dynamically changed.
-Although we found that the better performing classifier is Logistic Regression, there is room for improvement.
-The classifier could be enhanced to recognize the Error Potential~\cite{Iwane2017} more effectively or could be pre-trained to allow higher accuracy~\cite{Spuler2012}.
-
-%Concluding, this research shows evidence that brain signals can be used as an interface between human and a gaming computer enabling an alternative communication with the system without explicit input from the user.
+However, even with such a lower accuracy values, the RL algorithm was able to extract meaningful information from rewards that were helpful to improve the agent performance.
+
+Further work will be conducted in order to increase the complexity of the game to allow the possibility that the target position be dynamically changed.
+In that case the agent would start to learn to follow the target, instead of learning to go to a specific static destination spot.
+Additionally, the classifier could be enhanced to recognize more effectively the Error Potential~\cite{Iwane2017}.
+
+Concluding, this research show evidence that brain signals can be used as an interface between human and a gaming computer enabling an alternative communication with the system without explicit input from the user.
 

### 2020-09-27 review2/response.letter.tex
Commit the response.

@@
 
+Expand the results of the paper as this is the contribution.
+“Results show that there is an effective transfer of information and that the agent learns successfully to solve the game efficiently.
+Both the underlined terms need to cite evidence from the paper.
+
+Line 40 “This information is used to make a gaming agent <that> improves ....”
+
+Line 11 col 2 “how biological agents learn from its <their> environment by exploring it and getting feedback rewards, either negative or positive.”
+
+Line 17 col2 “Nonneglected is the influence of DeepBrain’s AlphaGo project,” // Re-word
+
+Line 24 col 2 “The papers [8], [9], [10] have successfully demonstrated that a robot can be controlled by obtaining a reward signal from a person’s brain activity, which who is observing the robot, <to> solve a task.”
+
+Line 58 Put in a reference number from ethics committee from which approval was sough (e.g. University committee)
+
+Page 2
+Line 56 “Data is <are> handled and processed with the OpenVibe Designer,” // datum-data
+
+Line 37 col 2 “This dataset has been published on the IEEE DataPort initiative [15].” // I would move this to the end of next paragraph (or possibly end of paper)
+
+Page 4
+Lin 24 This allows to learn the Q-Table <to learn> based on the subject’s feedback from the movements the agent
+took, which are chosen pseudo-randomly, while executing the brainwave session.
+
+Line 50 “The best overall performance is obtained using Logistic Regression.” // also need to discuss the significance of the overall levels of accuracy in Discussion.
+Is a best performance of 0.672 useful/acceptable?
+How does it compare to other researchers (if a comparison is possible).
+
+Line 42 col 2 “These results are also consistent with their classification ROC curves, shown on <in> Figures 6 obtained for both subjects, where the area under the curve are close to chance level.” // Why didn’t you show one good ROC curve and one bad one.
+This would provide the basis for comparison.
+
+Page 5
+Figure 5 “Y axis shows the averaged number of steps, while x axis show the number of
+experiences used to cumulative train the Q-Table.”
+// Why does Fig5 E only have 2 sets of data? Some discussion of the (smaller) change from 1 – 2 would be appropriate (e.g. I Discussion)
+Line 51 “Not performance gain is evidenced, the agents learn nothing which implies that the reward information is useless.” // useless is not a good choice of wording –provides no value
+
+Line 55 “It can be seen that the overall performance of the agent improves as long as there are more experiences to be used to train it, regardless if they were generated from the brainwaves classification from different subjects.” // more explanation/discussion needed.
+Is this an average effect from positive learners?
+
+This work aims to state whether ErrP signals could be used to train a gaming agent using reinforcement learning.
+The collected data show that ErrP signals can in fact be classified and used to train an agent effectively.
+// Can you link these findings to confirm/challenge other recent research in Err potentials
+
+Page 6
+Fig 8 – why use data from subject 6 (a non-learner)?
+
+Line 42 “However, even though this implies that the agent misses frequently that an action taken is wrong, this is not hindering the overall performance and the agent is still learning” //
+
+Line 20 col 2 Despite that, the rewards generated from different subjects can be used to train the same Q- Table to improve its performance, which may lead to strategies where the overall performance is improved based on the information from different human critics at the same time.
+//These are key findings, worth more discussion/interpretation and inclusion in abstract.
+
+\section*{\fbox{Reviewer \#2 Transcript:}}
+
+Comments to the Author
+The authors have satisfactorily addressed my concerns.
+I have a minor comment regarding Figure 3.
+It is unclear what the brown bar labelled GrandAvg represents since there is one for each participant.
+Please clarify.
+I suggest having another set of bars (a ninth) for the grand average (average over participants) for each of the algorithms used.
+
+\subsection*{\ovalbox{AE General Comments}}
+AE's Comments to Author:
+
+Associate Editor
+Comments to the Author:
+The paper is improved but would benefit from a further update to
+- improve abstract
+
+\begin{quotation}
+{\color{blue}
+We conducted a new BCI and games literature review and updated the Introduction accordingly, adding more updated background.
+We highlight now what we think is our contribution, which is a simple game that can be used to trigger the ErrP response in a simple scenario that can be used to train an agent.
+We were unable to find a similar work from that same perspective.
+}
+\end{quotation}
+
+- provide further interpretation/discussion of findings
+
+\begin{quotation}
+{\color{blue}
+BLA BLA BLA
+}
+\end{quotation}
+
+- fix minor errors/typos
+
+\begin{quotation}
+{\color{blue}
+BLA BLA BLA
+}
+\end{quotation}
+
+- address the grand average recommendation
+
+\begin{quotation}
+{\color{blue}
+BLA BLA BLA
+}
+\end{quotation}
+
+\subsection*{\ovalbox{Reviewer 1 General Comments}}
+
+Comments to the Author
+The paper is improved. The contribution is clearer. Thank you for the reply to comments. I attach some further comments.
+
+Training a Gaming Agent on Brainwaves
+The paper has been improved. IMO, there are still areas that need further attention to improve the paper further.
+Page 1
+The abstract still reads like an introduction until the last sentence.
+I would begin with sentence: “Error-related potential (ErrP) are a particular type of ERP that can be elicited by a person who attends a recognizable error.”
+
 \begin{quotation}
@@
 Expand the results of the paper as this is the contribution.
-“Results show that there is an effective transfer of information and that the agent learns successfully to solve the game efficiently.
+“Results show that there is an  \underline{effective} transfer of information and that the agent learns \underline{successfully} to solve the game efficiently.
 Both the underlined terms need to cite evidence from the paper.
@@
 
-Line 40 “This information is used to make a gaming agent <that> improves ....”
+Line 40 “This information is used to make a gaming agent $<$that$>$ improves ....”
 
@@
 
-Line 11 col 2 “how biological agents learn from its <their> environment by exploring it and getting feedback rewards, either negative or positive.”
+Line 11 col 2 “how biological agents learn from its $<$their$>$ environment by exploring it and getting feedback rewards, either negative or positive.”
 
@@
 
-Line 17 col2 “Nonneglected is the influence of DeepBrain’s AlphaGo project,” // Re-word
+Line 17 col2 "\sout{Nonneglected} is the influence of DeepBrain’s AlphaGo project,” // Re-word
 
@@
 
-Line 24 col 2 “The papers [8], [9], [10] have successfully demonstrated that a robot can be controlled by obtaining a reward signal from a person’s brain activity, which who is observing the robot, <to> solve a task.”
+Line 24 col 2 “The papers [8], [9], [10] have successfully demonstrated that a robot can be controlled by obtaining a reward signal from a person’s brain activity, \sout{which} who is observing the robot, $<$to$>$ solve a task.”
 
@@
 Page 2
-Line 56 “Data is <are> handled and processed with the OpenVibe Designer,” // datum-data
+Line 56 “Data \sout{is} $<$are$>$ handled and processed with the OpenVibe Designer,” // datum-data
 
@@
 Page 4
-Lin 24 This allows to learn the Q-Table <to learn> based on the subject’s feedback from the movements the agent
+Lin 24 This allows \sout{to learn} the Q-Table $<$to learn$>$ based on the subject’s feedback from the movements the agent
 took, which are chosen pseudo-randomly, while executing the brainwave session.
@@
 
-Line 42 col 2 “These results are also consistent with their classification ROC curves, shown on <in> Figures 6 obtained for both subjects, where the area under the curve are close to chance level.” // Why didn’t you show one good ROC curve and one bad one.
+Line 42 col 2 “These results are also consistent with their classification ROC curves, shown \sout{on} $<$in$>$ Figures 6 obtained for both subjects, where the area under the curve are close to chance level.” // Why didn’t you show one good ROC curve and one bad one.
 This would provide the basis for comparison.
@@
 // Why does Fig5 E only have 2 sets of data? Some discussion of the (smaller) change from 1 – 2 would be appropriate (e.g. I Discussion)
-Line 51 “Not performance gain is evidenced, the agents learn nothing which implies that the reward information is useless.” // useless is not a good choice of wording –provides no value
+Line 51 “No\sout{t} performance gain is evidenced, the agents learn nothing which implies that the reward information is useless.” // useless is not a good choice of wording –provides no value
 
@@
 
-\section*{\fbox{Reviewer \#2 Transcript:}}
+\subsection*{\ovalbox{Reviewer 2 General Comments}}
 
 Comments to the Author
+The paper is improved. The contribution is clearer. Thank you for the reply to comments. I attach some further comments.
+
 The authors have satisfactorily addressed my concerns.
@@
 
-\subsection*{\ovalbox{Reviewer 1 General Comments}}
-AE's Comments to Author:
-
-Associate Editor
-Comments to the Author:
-The paper is improved but would benefit from a further update to
-- improve abstract
-
 \begin{quotation}
 {\color{blue}
-We conducted a new BCI and games literature review and updated the Introduction accordingly, adding more updated background.
-We highlight now what we think is our contribution, which is a simple game that can be used to trigger the ErrP response in a simple scenario that can be used to train an agent.
-We were unable to find a similar work from that same perspective.
-}
-\end{quotation}
-
-- provide further interpretation/discussion of findings
-
-\begin{quotation}
-{\color{blue}
-BLA BLA BLA
-}
-\end{quotation}
-
-- fix minor errors/typos
-
-\begin{quotation}
-{\color{blue}
-BLA BLA BLA
-}
-\end{quotation}
-
-- address the grand average recommendation
-
-\begin{quotation}
-{\color{blue}
-BLA BLA BLA
-}
-\end{quotation}
-
-\subsection*{\ovalbox{Reviewer 1 General Comments}}
-
-This paper proposes the use of a gaming agent to be trained using Reinforcement Learning (RL) as well as the feedback obtained from EEG brainwaves of human critic observers.
-The idea of using brain patterns for boosting ML is highly interesting and well suited for the journal.
-Although it is not a new concept, it is nicely re-purposed for online use-case.
-
-However, I am not sure if there is something new in the paper compared to the 2010 proof-of-concept (Iturrate et al.: Robot Reinforcement Learning using EEG-based reward signals).
-The presentation style seems a bit confusing and needs serious improvements.
-Background is very limited (some are incorporated in the introduction) and substantial work is required.
-There has been a lot of work in BCIs over the past decade and some in the area of games.
-
-\begin{quotation}
-{\color{blue}
-We conducted a new BCI and games literature review and updated the Introduction accordingly, adding more updated background.
-We highlight now what we think is our contribution, which is a simple game that can be used to trigger the ErrP response in a simple scenario that can be used to train an agent.
-We were unable to find a similar work from that same perspective.
-}
-\end{quotation}
-
-From the scientific part, the results are not so convincing.
-In particular, the proposed idea does not seem to be too practical method.
-The classification does not provide something significant as it stands at the moment.
-The sample used is also quite small and the complexity of the game is limited.
-
-\begin{quotation}
-{\color{blue}
-Issues raised by the Reviewer are accurate and timely described.
-We aimed to find a suitable game that at the same time can be trained with a Reinforcement Learning technique and that triggered the ErrP response as well.
-We modified the manuscript, emphasized three results of our experiments.
-First we show that the basic Q-Learning algorithm is robust to noisy signals.
-Additionally,  we show the futility of transfer learning approaches using the brainwave signals, and finally that the cumulative contribution of the rewards obtained from different subjects enhances the performance of an agent.
-}
-\end{quotation}
-
-Nevertheless, the paper could be improved in many ways.
-An obvious point would be to improve the classifiers.
-Apart from this, I would suggest that authors would look at ways of manipulating the stimulus, stimulus presentation or giving out incentives to participants.
-
-\begin{quotation}
-{\color{blue}
-We added a new classifier and performed two more experiments.
-First we included kNeighbours as a new classification algorithm.
-This can be seen in Section C and in Figure 3.
-In that same Figure, we also added results obtained while performing signal averaging to enhance the SNR of the ErrP component.
-Moreover, we performed a complete transfer learning experiment, verifying if it was possible to improve the efficiency of the gaming agent and verified that the best results for the improvement (i.e.
-reduction) on the average number of steps, required to reach the target in 200 plays, is achieved when a classifier is trained with ErrP signals from the same subject that is used to identify the ErrP.
-This is added in Section III and in Figure 7.
-On the other hand, the structure of the game scenario allows to easily extend the experiments to verify what is the outcome of manipulating the stimulus, their presentation or the influence on the results if incentives are given to participants.
-We added this compelling ideas to the Section IV.
-}
-\end{quotation}
-
-\subsection*{\ovalbox{Reviewer 2 General Comments}}
-The paper is interesting and relevant. However in my opinion it needs revision for purposes of clarification and to improve the contribution.
-Please see attached document for my comments.
-
-Training a Gaming Agent on Brainwaves
-There are too many grammatical errors to list individually.
-
-\vspace{2em}
-\begin{quotation}
-{\color{blue}
-We truly appreciate this level of detail in all the comments and the requests for information. 
-}
-\end{quotation}
-\vspace{2em}
-
-//Does the header refer to a general template?
-JOURNAL OF LATEX CLASS FILES, VOL. 14, NO. 8, AUGUST 2015
-
-\vspace{2em}
-\begin{quotation}
-{\color{blue}
-This error has been fixed.  Thanks for pointing it out.
-}
-\end{quotation}
-\vspace{2em}
-
-//The abstract read more like an introduction, rather than an indication of the work undertaken for the paper.
-25 “Results show that there is an effective transfer of information and that
-the agent learns successfully to solve the game efficiently.”
-//This is too vague. What are the outcomes of the study?
-
-\vspace{2em}
-\begin{quotation}
-{\color{blue}
-We performed several changes in the manuscript.  We modified the Introduction describing those changes and emphasizing what we think may be our main contributions.  We rewrote the Abstract completely.
-}
-\end{quotation}
-\vspace{2em}
-
-39 This information is used to make a gaming agent improves its operational performance using electroencephalography (EEG) signals as feedback of the performed task, obtained from an observational human critic.
-//There is a grammar issue. I don’t understand this sentence.
-
-\vspace{2em}
-\begin{quotation}
-{\color{blue}
-We modified the sentence.  We thanks the reviewer for pointing out this issue.
-}
-\end{quotation}
-\vspace{2em}
-
-54 RL should be defined in main body of the paper. Also the term ‘agent’ needs to be defined/clarified. How does it relate to the Game Manager from Figure 1?
-
-\vspace{2em}
-\begin{quotation}
-{\color{blue}
-The acronym was revised and we also verified all the other acronyms used in the text.
-The term "agent" was defined and presented in the Introduction, and their relation with the Game Manager in Figure 1 was established.
-}
-\end{quotation}
-\vspace{2em}
-
-17 col 2 Recently, this technique has seen a come-back. // this is not scientific language
-
-\vspace{2em}
-\begin{quotation}
-{\color{blue}
-This mistake has been corrected.  We apologize for the bad choice of words.
-}
-\end{quotation}
-\vspace{2em}
-
-58 col 3 The precision of 25.125 is inappropriate P2, 46 col 2 What is “state information”?
-
-\vspace{2em}
-\begin{quotation}
-{\color{blue}
-The precision was adjusted to two decimals for the age mean and the standard deviation.
-We removed  "state information" and replaced the wording of the phrase in order to clarify more clearly the information that we wanted to convey:  we refer to state information to the sequence of movements that the gaming agent performs on the game.
-}
-\end{quotation}
-\vspace{2em}
-
-P3, 2 red normally indicates an error
-
-\vspace{2em}
-\begin{quotation}
-{\color{blue}
-We understand the Reviewer's point, and we agree with her/him that red is not the right color to represent the completion of a task in the game, and in this case it may have cognitive implications regarding the generalized concept that red indicates an error.
-It is known that the ErrP response may be affected by colors and shapes (Eimer 1997, \textit{An event-related potential (ERP) study of transient and sustained visual attention to color and form}).
-The experiments that we performed were implemented with the board showed on Figure 2 of the manuscript.
-We added this very important issue at the conclusions in relation with possible future works.
-}
-\end{quotation}
-\vspace{2em}
-
-P3, 11 I assume that the “observational human critic” is the player/participant/subject/human observer. This role should be clarified and terminology used consistently.
-
-\vspace{2em}
-\begin{quotation}
-{\color{blue}
-Absolutely.
-We preferred to use OHC "observational human critic" to emphasize what the subject is actually doing while using the system.
-We clarified this notation at the Introduction and along the manuscript.
-}
-\end{quotation}
-\vspace{2em}
-
-P3, 41 define MNE
-
-\vspace{2em}
-\begin{quotation}
-{\color{blue}
-Historically MNE stands for Minimum Error Estimate, a software package developed in Martinos Center of Harvard University.
-Now MNE  is the name of a entire software platform to perform analysis of several type of brain signals like Magnetoencephalograpy and Electroencephalography.
-We added a clarification about this on Section II.C.
-}
-\end{quotation}
-\vspace{2em}
-
-P3, 56 Thus, each epoch is composed of a matrix 500 x 8. // add channels
-
-\vspace{2em}
-\begin{quotation}
-{\color{blue}
-Excellent.  We added that information on Page 3.
-}
-\end{quotation}
-\vspace{2em}
-
-P4, 32 Hence, following the iterative procedure based on Equation 1, the Q-Table is updated in each iteration.
-After the algorithm finishes iterating throughout all the training episodes, the Q-Table is stored to test the performance of the agent.
-// Will the game always terminate? How long does the game take? Does smooth progression toward finish affect the err potential?
-
-\vspace{2em}
-\begin{quotation}
-{\color{blue}
-
-When the gaming agent moves randomly on the board of Figure 2, it takes on average 100 steps to arrive to the final location on the grid.
-Each step, the movement direction is performed once every 2 seconds, so on average it takes around 200 seconds to finish the game.
-After training during \textit{run sessions} (check new Section II.F), the agent starts to use the Q-Table to decide the next movement.
-However, the Q-Table could potentially end up producing endless loops or deadlocks so if the steps count arrives to 200 the game is interrupted and it starts all over again.
-So far we didn't test if the Error Potential is affected by the smooth progression toward the end, which is indeed something interesting to verify in this simple scenario.
-We added this very appealing extension in Section IV.
-
-}
-\end{quotation}
-\vspace{2em}
-
-P4 Fig 3. Is the chance score = 0.5?
-
-\vspace{2em}
-\begin{quotation}
-{\color{blue}
-Yes, it is.  We added that information in the Figure's caption.
-}
-\end{quotation}
-\vspace{2em}
-
-P4 the labels referred to in Fig 5 should correlate with the test here, i.e., A= subject 1 etc.
-
-\vspace{2em}
-\begin{quotation}
-{\color{blue}
-The figure labels on Figure 4(now) were modified to reflect which subfigure references which subject.  Additionally, we use the same notation on the new Figure 5.
-} 
-\end{quotation}
-\vspace{2em}
-
-P4 referring to Fig 6; a comparison ROC curve with subject 1 would be more interesting
-
-\vspace{2em}
-\begin{quotation}
-{\color{blue}
-We added on Figure 5(now) all the ROC curves that we obtained for all the different subjects, including the one for Subject 1.  
-}
-\end{quotation}
-\vspace{2em}
-
-P5, 34 what is meant by “experiences”?
-
-\vspace{2em}
-\begin{quotation}
-{\color{blue}
-We added a new Section II.F to clarify this part of the experiment which was not explained at all.
-First we rewrote how we separated the two parts of the experiment, the "Cognitive Game Procedure" and the "Gaming Agent Learning Procedure".
-We replaced "experiences" with \textit{run session}.
-This all is explained in the above-mentioned section.
-}
-\end{quotation}
-\vspace{2em}
-
-P5, 29 col 2 – remove Average steps per Q-Table legend.
-
-\vspace{2em}
-\begin{quotation}
-{\color{blue}
-This was modified in all the Figures, adjusting fonts and labels.  We appreciate a lot the time to point out this issue.
-}
-\end{quotation}
-\vspace{2em}
-
-P5 50, col 2 The collected data show that ErrP signals can in fact be classified and used to train an agent effectively.
-// how has effectiveness been determined here?
-
-\vspace{2em}
-\begin{quotation}
-{\color{blue}
-Each time the gaming agent plays this simple game, it takes on average around 100 steps to reach the target spot.
-We asked an observational human critic to watch the gaming agent play the game, while we recorded their brainwaves.
-We trained first a classifier to be able to recognize Error Potentials from these brainwaves.
-We started the game again, and the gaming agent started to move around the board, but this time once an Error Potential was identified from the brainwaves, it was used as a negative reward to train a new Q-Table for the agent.
-The game was iteratively repeated, but the gaming agent used the Q-Table that was updated in the previous run session.
-We verified that by doing this experiment, the agent required less and less steps on average to reach the goal until it arrives to the optimal number of around 10 steps.
-We found that although the effectiveness of this improvement depended on the accuracy of the classifier, even with very low values (just above chance level), the agent learns and the number of average number of steps is reduced.
-We verified that if trained the agent with sham signals, completely uncorrelated with the reward, the agent learned nothing, and the average number of steps was not reduced at all.
-Finally, we also verified that if we train a classifier with Error Potentials from one subject and used that classifier to provide the rewards for the experiment, the number of steps is not reduced, and that do not depend on the subjects, is an intrinsic result which is produced when intermixing the OHCs.
-Only the usage of a trained classifier from the same OHC produces this improvement.
-Finally, we verified that rewards obtained from different OHCs, can be used to improve the performance of the gaming agent collaboratively.
-}
-\end{quotation}
-\vspace{2em}
-
-Page 6 Fig 10 the text is not legible, it should be improved.
-
-\vspace{2em}
-\begin{quotation}
-{\color{blue}
-This is now Figure 9, we increased the fontsize, added a colormap and included the confusion matrices for all the subjects.
-}
-\end{quotation}
-\vspace{2em}
-
-Page 6, 40
-“However, even though this implies that the agent misses frequently that an action taken is wrong, this is not hindering the overall performance and the agent is still learning.”
-// Your results show that this is subject dependent
-
-\vspace{2em}
-\begin{quotation}
-{\color{blue}
-Yes, the Reviewer is correct.
-We modified this sentence to state more clearly the message that we wanted to convey, which is, that results are completely subject dependent, and that even when many actions should be tagged as "wrong" (triggering an ErrP) only with a few of them accurate, it is enough to train the agent towards the optimal solution.
-}
-\end{quotation}
-\vspace{2em}
-
-P6, 56
-Results show that training a classifier with data of one subject, but using it
-to classify the events of experiences of another subject does
-not lead to an improvement on the performance of the agent.
-
-// could a pre-trained generic classifier provide a better initial state, subsequently trained with observer data to converge more quickly?
-Are there differential err potential for up, down, left, right?
-
-\vspace{2em}
-\begin{quotation}
-{\color{blue}
-The statement is absolutely right.
-We extended this experience per Reviewer's suggestion and we verified that effectively the only combination of training/testing in the identification of ErrP that produces an improvement on the performance of the agent is the one that uses information from the same subject (check new Figure 7).
-We think a generic-classifier to identify ErrP potentials for any subject (i.e.
-without calibration) is a research goal of the BCI community because this will allow to have more robust, easier to use, with shorter setups  BCI devices (Suller 2012,\textit{Online use of error-related potentials in healthy users and people with severe motor impairment increases performance of a P300-BCI}).
-If such a generic pre-trained classifier could be conceived, this simple game can be used to verify if the number of training sessions required is reduced and this will confirm that the pre-trained classifier is helping to do it more quickly.
-We didn't verify if the error potential for up, down, left, right per se produces a different error potential, though we verified that in general getting farther from the target (in Manhattan distance) produces a signal which is slightly different from the one that is produced when the gaming agent moves closer to the target.
-We added these very interesting lines of further exploration in Section IV.
-}
-\end{quotation}
-\vspace{2em}
-
-\vskip+1ex
-\noindent \dotfill
-\vskip+1ex
-
-\subsection*{\ovalbox{Reviewer 3 General Comments}}
-
-Comments to the Author
-The following work shows the usage of ErrPs for training a gaming agent using reinforcement learning.
-Authors attempt different conventional classification approaches, as well as intersubject classification.
-
-\begin{quotation}
-{\color{blue}
-We appreciate a lot the time dedicated to review our manuscript.
-}
-\end{quotation}
-
-It is unclear to me the benefit of evaluating single subject to single subject offline classification accuracy. Please elaborate on this.
-
-\begin{quotation}
-{\color{blue}
-We tested many variants of simple games and we found that only the one proposed here produced a distinctive  ErrP response.
-The single subject accuracy that is presented on Figure 5(now) shows the level of ErrP single trial identification that we achieved for different subjects (which is low).
-We wanted to emphasize the finding that even with such low levels of identification, it was possible for the agent to learn an efficient strategy.
-The accuracy obtained in each single subject is representing the ability of the classifier to identify the ErrP response and to produce accurate rewards for the reinforcement learning scheme.
-}
-\end{quotation}
-
-Since different subjects attained different performance, all combinations of subjects used for training and testing should be inspected for the 1:1 evaluation setup.
-
-\begin{quotation}
-{\color{blue}
-This is an excellent idea that we now explored with a new experiment.
-We showed the results on Figure 7, where a classifier is trained to recognize ErrP signals using the information obtained from one Trainer subject and used to generate rewards for a gaming agent on a different Tester subject.
-We added information about this on Section IV.
-}
-\end{quotation}
-
-Maybe classification accuracy could be reported at different steps (depending on the amount of training data – gradual increasing the number of subjects)
-
-\begin{quotation}
-{\color{blue}
-The classification accuracy obtained for all subject is now being shown on Figure 5 with ROC curves.
-We shown progressively the experiment itself, where after each gaming agent training match, a new Q-Table is generated based on the rewards tagged from the brainwave session.
-The agent improves their efficiency by reaching the target in a progressively less number of steps on average for each run session.
-}
-\end{quotation}
-
-What is the ratio of hit/no hit segments of action (epochs)?
-
-\begin{quotation}
-{\color{blue}
-The ratio hit/no-hit segments is 50/50, so for each brainwave session match, as the average number of steps is around 100, it will be 50 segments of hit (moving farther from the target) and 50 of no-hit (moving closer).
-}
-\end{quotation}
-
-Page 3, column 2, lines 4-9. It is unclear at this stage what action from the starting point would generate an ErrP.
-moves-> move
-
-\begin{quotation}
-{\color{blue}
-The Reviewer is absolutely right in that there isn't any possible action that the gaming agent can perform at the beginning of the experience (the game agent is located at the upper-left corner) that may trigger an ErrP response.
-We modified the phrase to emphasize the message that we wanted to convey.
-Additionally, there is a very important caveat of the experiment.
-The gaming agent always has a 5\% chance of wandering and selecting an action randomly, regardless of their Q-Train.
-This is precisely to avoid loops or deadlocks situations.
-
-On the other hand, we fixed the pointed out grammatical error as well.
-}
-\end{quotation}
-
-Page 3, column 2, lines 11-13. Has the MinMax Scaler been applied in any other BCI related study or elsewhere? I think including a reference would be useful.
-
-\begin{quotation}
-{\color{blue}
-We added a reference where the MinMaxScaler is used in a BCI application (new page 3, second column).
-}
-\end{quotation}
-
-Page 4. Figure 3. I would suggest adding another set of bars for the grand average classification scores.
-
-\begin{quotation}
-{\color{blue}
-We added a new bar on the Figure 3 where we included the obtained classification accuracy when 5 segments are ensemble averaged to produce an averaged signal (with an improved SNR in terms of the ErrP).
-These scores are reported in the Figure 4 as "GrandAvg".
-There is a balance to be considered because adding more segments to the averaged signal reduces the number of available samples used for training the classifier.
-}
-\end{quotation}
-
-Page 4, Figure 4. This figure is redundant and could be removed.
-
-\begin{quotation}
-{\color{blue}
-The figure was removed, thank you very much for your comment.
-}
-\end{quotation}
-
-Page 5, Figure 5. The titles of the subplots would be more descriptive when replacing the letters with the corresponding subjects number.
-
-\begin{quotation}
-{\color{blue}
-We agree with Reviewer's comment.  We removed the letters and replace them with subject's numbers in Figures 4 and 5.
-}
-\end{quotation}
-
-Page 5, column 1, line 52, Not ->no
-
-\begin{quotation}
-{\color{blue}
-Fixed.  Thank you very much !
-}
-\end{quotation}
-
-Page 5, column1, line 55, accumulative->cumulative
-
-\begin{quotation}
-{\color{blue}
-Fixed.
-}
-\end{quotation}
-
-Page 6, Figure 8. It is unclear to me what is the benefit of showing both A and B. Since the behavior is similar in both cases.
-
-\begin{quotation}
-{\color{blue}
-We included now all the ROC curves for all the subjects.
-}
-\end{quotation}
-
-Page 6, Figure 10. This figure is, in my opinion, incomplete. What is the reason for showing this subset of subjects? I suggest showing the confusion matrices of all subjects and/or their average.
-
-\begin{quotation}
-{\color{blue}
-Absolutely right.
-We included all the confusion matrices for all the subjects.
-The reason for this is that we wanted to convey the message that our hypothesis is that as false positives are low, those ErrP that are triggered are indeed good "rewards" that are useful for the training algorithm and the gaming agent is using that information, tough scarce, in a useful way to learn and improve it performance.
-}
-\end{quotation}
-
-Page 6, column 2, line 40. show -> shows
-
-\begin{quotation}
-{\color{blue}
-Fixed.
+fdsjlfjldksj
 }

### 2020-09-28 review2/response.letter.tex
Fix to the response letter.

@@
 Expand the results of the paper as this is the contribution.
-“Results show that there is an effective transfer of information and that the agent learns successfully to solve the game efficiently.
+“Results show that there is an  \underline{effective} transfer of information and that the agent learns \underline{successfully} to solve the game efficiently.
 Both the underlined terms need to cite evidence from the paper.
 
-Line 40 “This information is used to make a gaming agent <that> improves ....”
+Line 40 “This information is used to make a gaming agent $<$that$>$ improves ....”
 
-Line 11 col 2 “how biological agents learn from its <their> environment by exploring it and getting feedback rewards, either negative or positive.”
+Line 11 col 2 “how biological agents learn from its $<$their$>$ environment by exploring it and getting feedback rewards, either negative or positive.”
 
-Line 17 col2 “Nonneglected is the influence of DeepBrain’s AlphaGo project,” // Re-word
+Line 17 col2 "\sout{Nonneglected} is the influence of DeepBrain’s AlphaGo project,” // Re-word
 
-Line 24 col 2 “The papers [8], [9], [10] have successfully demonstrated that a robot can be controlled by obtaining a reward signal from a person’s brain activity, which who is observing the robot, <to> solve a task.”
+Line 24 col 2 “The papers [8], [9], [10] have successfully demonstrated that a robot can be controlled by obtaining a reward signal from a person’s brain activity, \sout{which} who is observing the robot, $<$to$>$ solve a task.”
 
@@
 {\color{blue}
-We conducted a new BCI and games literature review and updated the Introduction accordingly, adding more updated background.
-We highlight now what we think is our contribution, which is a simple game that can be used to trigger the ErrP response in a simple scenario that can be used to train an agent.
-We were unable to find a similar work from that same perspective.
+bal bla bal
 }

### 2020-10-11 review2/response.letter.tex
Add grammatical fixes to paper and included an improved version of the abstract

@@
 {\color{blue}
-bal bla bal
+Rewrote the abstract talking in further detail obtained results.
 }
@@
 {\color{blue}
-fdsjlfjldksj
+Rewrote the abstract talking in further detail obtained results.
 }
@@
 {\color{blue}
-fdsjlfjldksj
+This was solved in a previous version.
 }
@@
 {\color{blue}
-fdsjlfjldksj
+Fixed issue.
 }
@@
 {\color{blue}
-fdsjlfjldksj
+TODO: No entiendo esto bien a que se refiere
 }
@@
 {\color{blue}
-fdsjlfjldksj
+Fixed issue for all appeareances of "data is".
 }
@@
 {\color{blue}
-fdsjlfjldksj
+Added information in the form of a footnote.
 }
@@
 {\color{blue}
-fdsjlfjldksj
+AC'a hablar que es aceptable porqeu alcanza para aprender el optimal policy. Buscar una comparaci'on?
 }
@@
 {\color{blue}
-fdsjlfjldksj
+TODO: Arregle error gramatical pero no agregu'e la ROC mala.
 }
@@
 {\color{blue}
-fdsjlfjldksj
+Subject 5 and 6 aren't used to train the algorithm in this instance. Added this information in the figure caption.
 }
@@
 Comments to the Author
+
 The paper is improved. The contribution is clearer. Thank you for the reply to comments. I attach some further comments.

### 2020-10-11 ErrP.tex
Add grammatical fixes to paper and included an improved version of the abstract

@@
 \begin{abstract}
-In this study, we propose a simple game scenario that can be used to trigger a feedback response embedded in Electroencephalographic (EEG) signals of an observation human critic that observes an agent playing a game.
+%objective
+Error-related potential (ErrP) are a particular type of ERP elicited by a person attending a recognizable error.
+The purpose of this study is to determine if these signals can be used to train a Reinforcement Learning (RL) algorithm to learn an optimal policy.
+A game scenario is used to trigger the feedback response embedded in Electroencephalographic (EEG) signals of an observation human critic (OHC) that observes an agent playing a game.
+ErrP signals are captured using a Brain-Computer Interface (BCI) system.
+%method
+The experimental process consists of an individual observing a simple game scenario while their brain signals are captured.
+The game consists of a grid, where the object has to reach a desired target in the fewest amount of steps.
+Initially the object moves randomly within the grid,
+and a RL algorithm is trained for it to learn the optimal policy, in order to know how to reach the target in the least amount of steps.
+%Results
+% Expand the results of the paper as this is the contribution.
+“Results show that there is an effective transfer of information and that the agent learns successfully to solve the game eﬀiciently.
+Both the underlined terms need to cite evidence from the paper.
+% The rewards generated from different subjects can be used to train the same Q- Table to improve its performance, which may lead to strategies where the overall performance is improved based on the information from different human critics at the same time.
+//These are key findings, worth more discussion/interpretation and inclusion in abstract.
+Results show that there is an effective transfer of information and that the agent successfully learns to solve the game efficiently.
+Initially when the game is simulated with random movements it takes the agent an average of 97 steps to reach the objective, whereas when the trained Q-Table is used to reach the objective, the agent can reach the goal in the optimal number of steps, which is 8 steps.
+The algorithm can be trained with information from different OHCs, since the resulting dataset is composed of rewards for each corresponding step, independent of who they were generated from.
+This shows that the error classification accuracy (approximately 0.67) is good enough for the algorithm to learn.
+The reward function only penalizes wrong steps, which means that type II error (not properly identifying a wrong movement) does not affect the accuracy, they only make the learning process slower.
+%conclusions
+This study shows that: (i) the structure of a simple grid-based game that can elicit the ErrP signal component; (ii) the verification that low classification accuracy of just above chance level that produces noisy rewards is enough to allow an agent to learn the optimal policy; (iii) collaborative rewards from multiple observational human critics can compensate the lack of accuracy or the limited scope of transfer learning schemes.
+
+% In this study, we propose a simple game scenario that can be used to trigger a feedback response embedded in Electroencephalographic (EEG) signals of an observation human critic that observes an agent playing a game.
 Based on a Reinforcement Learning (RL) model, the gaming agent receives rewards for their actions on the game and learns its optimal policy.
@@
 Previous research has explored the usage of RL with reward signals based on brain activity, recorded by an EEG-based BCI system during task execution.
-The papers \cite{ROBOT-CONTROL-PAPER,Kim2017,Omedes2013} have successfully demonstrated that a robot can be controlled with brain signals from a person that is observing a robot solve a task.
+The papers \cite{ROBOT-CONTROL-PAPER,Kim2017,Omedes2013} have successfully demonstrated that a robot can be controlled with brain signals from a person who is observing a robot solve a task.
 Moreover, a growing number of studies have demonstrated the feasibility of using ErrPs as rewards for RL schemes such as to enhance robotic behaviour~\cite{Luo2019}, to assess air traffic controller's decisions~\cite{Goh2019} or to categorize actions as errors~\cite{Wirth2020}.
@@
 Offline, EEG signals are classified and they are linked to each game movement calculated by the Game Manager to determine proper rewards for each action.
-This information is used by a Reinforcement Learning algorithm to learn iteratively a Q-Table to improve the performance of the agent that plays the game.}
+This information is used by a Reinforcement Learning algorithm that iteratively trains a Q-Table in order to improve the performance of the agent that plays the game.}
     \label{diag:complete_flow}
@@
 An additional bandpass filter between $0.5$~Hz and $60$~Hz is applied.
-Data is handled and processed with the OpenVibe Designer, from the same platform, using 8 channels for the brain data (one channel per electrode) and an additional channel to record the stimulus, which corresponds to a game movement performed by the agent.
+Data are handled and processed with the OpenVibe Designer, from the same platform, using 8 channels for the brain data (one channel per electrode) and an additional channel to record the stimulus, which corresponds to a game movement performed by the agent.
 After everything is connected, the subject is seated in a comfortable chair in front of a computer screen.
 The brightness of the screen is set to the maximum setting to avoid any visual inconvenience in which the subject can not distinguish the components of the game that appear on the screen.
-This dataset has been published on the IEEE DataPort initiative~\cite{6emh-wb46-19}.
 
@@
 A brainwave session consists of several matches, each one being a gameplay.
-In the end, the sequence of game movements and the signal data generated for each match are saved for offline processing.
+In the end, the sequence of game movements and the signal data generated for each match are saved for offline processing \footnote{The brainwave dataset has been published on the IEEE DataPort initiative~\cite{6emh-wb46-19}.}.
 
@@
 In order to do this different parameters are tested for a set of algorithms and for each individual subject.
-Initially a sub-selection of experiments is used to define a subset of parameters to test with, and then all the data is tested with this subset of parameters.
+Initially a sub-selection of experiments is used to define a subset of parameters to test with, and then all the data are tested with this subset of parameters.
 
@@
 
-After the raw data is loaded and tagged, epochs are extracted.
+After the raw data are loaded and tagged, epochs are extracted.
 Epochs consist of all the sample points that take place during the 2 seconds from the start of the event, 2 seconds corresponding to the time it takes for each action to take place, resulting in 500 samples per channel, as the sampling frequency is 250 Hz.
@@
 The eight channels are concatenated using the MNE Vectorizer function, which transforms the data matrix into a single array sample.
-Lastly, this data is used by the classification module as information to train and test a classifier.
+Lastly, this data are used by the classification module as information to train and test a classifier.
 Five different classification algorithms are used:  Logistic Regression, Multilayer Perceptron with a hidden layer of 100 neurons (i.e.
@@
 Figures \ref{fig:avg_steps} for OHC 5 and 6 show no apparent learning, as the amount of steps to reach the goal doesn't decrease when trained.
-These results are also consistent with their classification ROC curves, shown on Figures~\ref{fig:rocsubjects} obtained for both OHCs, where the area under the curve are close to chance level.
+These results are also consistent with their classification ROC curves, shown in Figures~\ref{fig:rocsubjects} obtained for both OHCs, where the area under the curve are close to chance level.
 Both OHCs have less recorded data from the sessions in comparison to the rest of the OHCs.
@@
 \includegraphics[scale=0.4]{Images/Average_steps/all.eps}
-\caption{Average steps using Q-Table trained with brainwave session matches from six different OHCs. X axis show the progressive number of gaming agent training matches used to train the Q-Table.}
+\caption{Average steps using Q-Table trained with brainwave session matches from six different OHCs.
+X axis show the progressive number of gaming agent training matches used to train the Q-Table.
+These matches correspond to all subjects, excluding subjects 5 and 6 which individually show no significant learning progress.}
 \label{fig:avg_steps_all}
@@
 %Brainwave sessions have a low amount of matches in order to reduce fatigue from OHCs.
-However data suggests that longer sessions are required in order to reach better classification scores, since more data is available in order to train the classifier.
+However data suggests that longer sessions are required in order to reach better classification scores, since more data are available in order to train the classifier.
 Matches from OHCs with the largest amounts of data have the best classification scores and produced more accurate rewards.

### 2020-10-12 ErrP.tex
Subo la versión del PDF con todo integrado.  Fijense que el archivo 5-Segments Average.eps ahora se llama avg_5_segments.eps porque a veces chilla Latex si tienen espacios los nombres.  Lo mismo el archivo cross_val (1).eps lo deje con el nombre final de cross_val.eps que era el que tenía originalmente.

@@
 
-\author{Bartolomé Francisco, Moreno Juan,  Navas Natalia, Vitali José, \\
+\author{
+\IEEEauthorblockN{%
+  Bartolomé~Francisco\textsuperscript{\textsection}, 
+  Moreno~Juan\textsuperscript{\textsection},  
+  Navas~Natalia\textsuperscript{\textsection}, 
+  Vitali~José\textsuperscript{\textsection}, \\
   Ramele~Rodrigo,~\IEEEmembership{Member,~IEEE,}
   Santos~Juan~Miguel% <-this % stops a space
+  }%
+
 \thanks{R. Ramele and J.M.Santos are with the Department
@@
 \maketitle
+\begingroup\renewcommand\thefootnote{\textsection}
+\footnotetext{Equal contribution}
+\endgroup
 
@@
 
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.6\textwidth]{revisedimages/avg_closer.eps}
+    \includegraphics[width=0.6\textwidth]{revisedimages/avg_further.eps}
+    \caption{Grand Average for all OHCs for the closer and further condition.  It can be seen the bump around 300 ms.}
+    \label{fig:classifiers}
+\end{figure}
+
 Figure~\ref{fig:classifiers} shows the binary classification accuracy obtained for the eight OHCs using five different classification algorithms and using a 10-fold cross-validation procedure.
@@
     \centering
-    \includegraphics[scale=0.12]{revisedimages/cross_val.eps}
+    \includegraphics[scale=0.11]{revisedimages/cross_val.eps}
+    \includegraphics[height=40pt,width=1.20\textwidth]{revisedimages/avg_5_segments.eps}
     \caption{Binary single trial classification score using five different classifiers while recognizing ErrP potentials for the eight OHCs.

### 2020-10-12 review2/response.letter.tex
Agrego una referencia en base a una pregunta del revisor 1.

@@
 {\color{blue}
-TODO: No entiendo esto bien a que se refiere
+We added the missing information on Section II.A.  Thanks for pointing out this important issue.
 }
@@
 {\color{blue}
-Added information in the form of a footnote.
+Added information in the form of a footnote on Section II.B.
 }
@@
 {\color{blue}
-AC'a hablar que es aceptable porqeu alcanza para aprender el optimal policy. Buscar una comparaci'on?
+On Section IV, third paragraph we tackled this issue.
+The overall performance of 0.672 is low.
+Although a comparison can be misleading in the context of the experiment, because it is not clear at which extent the nature of the experiment can elicit a different ErrP response which will inevitable produce different level of accuracies for detection.
+A comparison was added.
 }

### 2020-10-12 ErrP.tex
Agrego una referencia en base a una pregunta del revisor 1.

@@
 The retrieval of the OHC's brain activity, called the brainwave session, is one of the most critical parts of the study.
-Subjects are recruited voluntarily and given a form with questions regarding their health (previous health issues and particular visual sensitivity), habits (sleeping hours, caffeine and alcohol consumption), and a consent petition to collect the required data.
+Subjects are recruited voluntarily and given a form with questions regarding their health (previous health issues and particular visual sensitivity), habits (sleeping hours, caffeine and alcohol consumption), and a written informed consent petition to collect the required data.
+The experiment is conducted anonymously in accordance with the Declaration of Helsinki published by the World Health Organization.
+No monetary compensation is handed out.
+This study is approved by the Departamento de Investigación y Doctorado, Instituto Tecnológico de Buenos Aires (ITBA).
 The brainwave sessions are performed with 8 subjects, 5 males and 3 females, with an average age of 25.12 years, a standard deviation of 1.54 years, and a range of 22-28 years.
@@
 One additional aspect to remark is the robustness of the learning strategy based on Q-Learning~\cite{Bauer2015,Rubin2012}.
-The obtained accuracy to discriminate ErrPs is low.
+
+The obtained accuracy to discriminate ErrPs is low, similar results were obtained in  \cite{Ehrlich2016}.
+
 However, even with such low accuracy values, the RL algorithm was able to extract meaningful information from rewards that were helpful to improve, and often maximize, the agent's performance.

### 2020-10-12 review2/response.letter.tex
Completé la respuesta a casi todas las preguntas, modifiqué el texto en concordancia.  Hice unos cambios para enfatizar que la contribución es la mecánica y el agente del juego.

@@
 {\color{blue}
-Rewrote the abstract talking in further detail obtained results.
+We started the abstract as suggested, thank you very much for it.  We rewrote the abstract detailing the obtained results.
 }
@@
 {\color{blue}
-This was solved in a previous version.
+We included this information in the abstract and added it in the Conclusions Section (IV).
 }
@@
 {\color{blue}
-This was solved in a previous version.
+This text is no longer contained in the manuscript.  We verified along the Manuscript to avoid similar mistakes.
 }
@@
 {\color{blue}
-This was solved in a previous version.
+This was already solved in a previous version, and the manuscript no longer contains this line.  We appreciate a lot for your suggestion.
 }
@@
 {\color{blue}
-Fixed issue for all appeareances of "data is".
+Fixed issue for every appearances of \textbf{data is}.
 }
@@
 {\color{blue}
-Fixed issue.
+Fixed issue.  We appreciate a lot the level of detail in the comments.
 }
@@
 The overall performance of 0.672 is low.
-Although a comparison can be misleading in the context of the experiment, because it is not clear at which extent the nature of the experiment can elicit a different ErrP response which will inevitable produce different level of accuracies for detection.
-A comparison was added.
+Although a comparison can be misleading in the context of the ErrP experiment, we added a brief comparison to other similar works.
+We also emphasized this point in future works where there is room for improvement in terms of the classification and processing pipeline.
 }
@@
 {\color{blue}
-TODO: Arregle error gramatical pero no agregu'e la ROC mala.
+We emphasize on the Figure 6 caption which ROC curves where good which were not so good.
+We added this in the text and the important finding that we could not provide an enhencement of the agent for those subjects where the obtained ROC curves were not good.
 }
@@
 {\color{blue}
-fdsjlfjldksj
+We fixed the inappropriate wording, and appreciate the Reviewer for pointing this out.  
+Figure 5, for Subject 5 (in the first version of the manuscript it was labeled E) has only two sets of data because that Participant (OHC) couldn't complete more sessions.
+Hence we used two training sessions to calculate the Q-Table and subsequently performed the run session (i.e.
+the agent performs movements randomly based on the trained QTable for 200 iterations).
 }
@@
 {\color{blue}
-fdsjlfjldksj
+This is a great question.
+Traditional Transfer Learning strategies focus on the procedure to enrich a classifier training it with a vast dataset and using it to generalize to new data or unseen scenarios.
+While deaing with EEG data, this strategy tends to fail, and other approaches are required.
+We found in this work, that even when that strategy fails, if the system is coupled with a basic reinforcement learning algorithm, the cumulative rewards from different subjects, can be used to effectively transmit information and improve the agent performance.
+We agree with the Reviewer that this may be due to the average effect of positive or learners with a higher accuracy, but we think it may be related to the fact that the RL algorithm is quite robust and if we can get a higher specificity it will lead to eventually learn, and the usage of various OHCs help to increase the available data to do so.
 }
@@
 {\color{blue}
-fdsjlfjldksj
+We believe this result is quite supported in the literature.
+You can check here here here here here.
+Our novel approach is to use the rewards to train an agent that can perform on its own after the training has been performed, and the game mechanics to verify the flow of information.
+This information was added in the Conclusion Section IV.
 }
@@
 {\color{blue}
-Subject 5 and 6 aren't used to train the algorithm in this instance. Added this information in the figure caption.
+Subject 5 and 6 aren't used to train the algorithm in this instance. This information was emphasized on the Figure's caption and on the main text in the Result Section.
 }
@@
 Line 42 “However, even though this implies that the agent misses frequently that an action taken is wrong, this is not hindering the overall performance and the agent is still learning” //
-
-\begin{quotation}
-{\color{blue}
-fdsjlfjldksj
-}
-\end{quotation}
 
@@
 {\color{blue}
-fdsjlfjldksj
+We added it because is a very interesting results to overcome issues in transfer learning while dealing with biological data.  We appreciate the reviewer for this very important point.
 }

### 2020-10-12 ErrP.tex
Completé la respuesta a casi todas las preguntas, modifiqué el texto en concordancia.  Hice unos cambios para enfatizar que la contribución es la mecánica y el agente del juego.

@@
 Additionally, ErrPs have also been used in the context of games as an additional feedback channel that can be explored to improve gaming experience~\cite{Plass-OudeBos2010,kober2018bci}.
+The game is similar to this one \cite{Iturrate2013}.
 
 Therefore,  we aim to use the information extracted from brainwaves to enhance the performance of a gaming agent.
-The three contributions are (1) a simple game that can elicit the ErrP potential, (2) results that confirm that even when ErrP classification accuracy is low and produces a noisy reward signal, enough information is generated for an agent to learn the optimal policy and solve a simple game and (3) collaborative rewards from multiple observational human observers can compensate the lack of classification accuracy or the inefficacy of transfer learning procedures for brainwaves signals.
+The three contributions are (1) a simple game mechanics and agent that can elicit the ErrP potential, (2) results that confirm that even when ErrP classification accuracy is low but with a high specificity and produces a noisy reward signal, enough information is generated for an agent to learn the optimal policy and solve a simple game and (3) collaborative rewards from multiple observational human observers can compensate the lack of classification accuracy or the inefficacy of transfer learning procedures for brainwaves signals.
+
+%However, even though this implies that the agent misses frequently that an action taken is wrong, this is not hindering the overall performance and the agent is still learning
 
@@
 The game parsimoniously consists of a $5x5$ grid of grey circular spots with a black background.
+It is similar to the one proposed by~\cite{Iturrate2013}.
 A blue spot indicates the current position of the agent and a green spot represents the goal, as shown in Figure  \ref{fig:game_representation}.
@@
     \centering
-    \includegraphics[width=0.6\textwidth]{revisedimages/avg_closer.eps}
-    \includegraphics[width=0.6\textwidth]{revisedimages/avg_further.eps}
+    \includegraphics[width=0.5\textwidth]{revisedimages/avg_closer.eps}
+    \includegraphics[width=0.5\textwidth]{revisedimages/avg_further.eps}
     \caption{Grand Average for all OHCs for the closer and further condition.  It can be seen the bump around 300 ms.}
@@
     \includegraphics[scale=0.11]{revisedimages/cross_val.eps}
-    \includegraphics[height=40pt,width=1.20\textwidth]{revisedimages/avg_5_segments.eps}
+    \includegraphics[scale=0.21]{revisedimages/avg_5_segments.eps}
     \caption{Binary single trial classification score using five different classifiers while recognizing ErrP potentials for the eight OHCs.
@@
 Only the diagonal of the heatmap matrix shows a clear improvement in terms of the reduction of the required number of steps to reach the goal (averaged per 200 runs) which corresponds to the same information for each OHC shown in Figure~\ref{fig:avg_steps}.
-For the transfer learning experiment~\cite{Wu2016}, no performance gain is evidenced, the agents learn nothing and this implies that the reward information is useless.
+For the transfer learning experiment~\cite{Wu2016}, no performance gain is evidenced, the agents learn nothing and this implies that the reward information provides no value.
 
@@
 
-This work aims to propose a simple game that can use the ErrP component to train a gaming agent using a RL model.
-The collected data shows that ErrP signals can in fact be classified and used to train an agent effectively.
+This work aims to propose a simple game mechanics that can use the ErrP component to train a gaming agent using a RL model.
+The collected data and the shows that ErrP signals can in fact be classified and used to train an agent effectively.
 
@@
 One additional aspect to remark is the robustness of the learning strategy based on Q-Learning~\cite{Bauer2015,Rubin2012}.
-
-The obtained accuracy to discriminate ErrPs is low, similar results were obtained in  \cite{Ehrlich2016}.
-
+The obtained accuracy to discriminate ErrPs is low, though on the same level to other similar results~\cite{Iturrate2013,Ehrlich2016}.
+In this regard, dispite of the subjectivity of the ErrP response in terms of the proposed experiment, levels of 90\% of accuracy are reported~\cite{Chavarriaga2014}.
 However, even with such low accuracy values, the RL algorithm was able to extract meaningful information from rewards that were helpful to improve, and often maximize, the agent's performance.

### 2020-10-13 review2/response.letter.tex
Más respuestas.  Finalmente decidí volar el gráfico de los promedios.  En un punto no es lo que el revisor exactamente pide y lo que el pide no me parece, y creo comparten ustedes, tenga mucho sentido hacerlo.  Prefiero ir por el lado de ofrecerle alternativas y presentar el gráfico del grand average que es lo que quizás aporte más info (además ese gráfico salió perfecto).

@@
 {\color{blue}
-Rewrote the abstract talking in further detail obtained results.
+We rewrote the abstract explaining in further details the obtained results.  
 }
@@
 {\color{blue}
-BLA BLA BLA
+We included extra information and verified the contributions/findings.
 }
@@
 {\color{blue}
-BLA BLA BLA
+We fixed the carefully reported issues gently provided by Reviewers.
 }
@@
 {\color{blue}
-BLA BLA BLA
+We addressed this issue.
+We think there must a missunderstanding from our side of the suggestion/recommendation of the Reviewer.
+We added additional information in this response letter, and apologize for this.
 }
@@
 {\color{blue}
-fdsjlfjldksj
+We think we misunderstood previous Reviewer suggestions.
+We added the brown bar on the previous Figure 3 (now Figure 5) because we assumed the Reviewer was referring to perform a classification using epoched averaged signal segments.
+We used 5-segments to obtain an averaged signal with an enhanced signal-to-noise ratio (Wim van Drongelen, 4 - Signal Averaging, Editor(s): Wim van Drongelen, Signal Processing for Neuroscientists, Academic Press, 2007, Pages 55-70,) per Participant, and perfomed the classification of ErrP components based on those averaged signals for each Participant.
+We used only Logistic Regression as classificiaton algorithm, as it was the one where we achieved better performance for single signal segments.
+We think this is now confusing and decided to remove those brown bars.
+We have now included a new Figure 3, where we plotted the Grand Average signals over participants for the two experimental conditions.
+The top subfigure shows the signals for the "move closer to the target" condition, whereas the bottom subfigure represents the grand average for the "move closer" condition.
+On the other hand, Figure 9 shows the results of using information to train a classifier with data from one Participant and use it to identify rewards for another participant.
+This is performed in a single-trial, without any signal averaging.
+We apologize for the Reviewer for our misunderstanding and ask back for more information if it feels like the misunderstanding persisted.
 }
@@
 \bibliographystyle{IEEEtran}
-\bibliography{Reference}
+%\bibliography{Reference}
 

### 2020-10-13 review2/response.letter.tex
Una vuelta de rosca.

--- 2020-10-12 review2/response.letter.tex
@@
 {\color{blue}
-We started the abstract as suggested, thank you very much for it.  We rewrote the abstract detailing the obtained results.
+We started the abstract as suggested, and rewrote it detailing the obtained results.   Thank you very much for your suggestion.
 }
@@
 {\color{blue}
-We included this information in the abstract and added it in the Conclusions Section (IV).
+We included the following information in the abstract and added it in the Conclusions Section (IV), showing evidence from the paper.
+
+Each time the gaming agent plays this simple game, it takes on average around 100 steps to reach the target spot.
+We trained a classifier to recognize Error Potential from observational human critics that watch the agent playing the game.
+We let the agent play again and we mark movements that trigger an error potential from the human critic.
+We used those movements as rewards in a Reinforcement Learning scheme, and use them to train a Q-Table.
+When we let the agent plays the game again, the number of steps that requires to solve the game is now reduced.
+If we provide feedback based on random signals, we verified that no reduction is achieved and the average number of steps does not change.
+This shows that there is an effective transfer of information from the brainwaves to the agent.
+As this process is repeated, the agent keeps improving solving the game effectively, i.e.
+performing the minimum number of required steps to reach the goal.
+
 }
@@
 {\color{blue}
-This text is no longer contained in the manuscript.  We verified along the Manuscript to avoid similar mistakes.
+This text is no longer contained in the manuscript.  We verified throughout the Manuscript to avoid similar mistakes.
 }
@@
 {\color{blue}
-Fixed issue for every appearances of \textbf{data is}.
+Fixed issue for every appearances of \textbf{data}.
 }
@@
 Although a comparison can be misleading in the context of the ErrP experiment, we added a brief comparison to other similar works.
-We also emphasized this point in future works where there is room for improvement in terms of the classification and processing pipeline.
+We also emphasized this point in future  works at the end of the Conclusions section.
 }
@@
 {\color{blue}
-We emphasize on the Figure 6 caption which ROC curves where good which were not so good.
-We added this in the text and the important finding that we could not provide an enhencement of the agent for those subjects where the obtained ROC curves were not good.
+Due to previous Reviewer's requests, we added all the ROC curves on the new Figure 7.
+We now emphasized on this figure's caption which ROC curves where showing an effective identification of the ErrP potential and which did not.
+We added this in the text emphasizing the important finding that we could not provide an enhancement of the agent performance based on the rewards from subjects where the obtained ROC curves were not good.
 }
@@
 {\color{blue}
-fdsjlfjldksj
+We think we misunderstood previous Reviewer's suggestions.
+We added the brown bar on the previous Figure 3 (now Figure 5) because we assumed the Reviewer was referring to perform a classification using epoched averaged signal segments.
+We used 5-segments to obtain an averaged signal with an enhanced signal-to-noise ratio (Wim van Drongelen, 4 - Signal Averaging, Editor(s): Signal Processing for Neuroscientists, Academic Press, 2007, Pages 55-70,) per Participant, and performed the classification of ErrP components based on those averaged signals for each Participant.
+We used only Logistic Regression as classification algorithm, as it was the one with which we achieved better performance for single signal segments.
+It is clear now that the brown bars were confusing and we have decided to remove them.
+Instead, we have now included a new Figure 3, where we plotted the \textbf{Grand Average} signals over all the participants for the two experimental conditions.
+The top subfigure shows the signals for the "move closer to the target" condition, whereas the bottom subfigure represents the grand average for the "move further" condition.
+On the other hand, Figure 9 shows the results of using information to train a classifier with data from one Participant and use it to identify rewards for another participant.
+This is performed in a single-trial approach from individual segments without any signal averaging.
+We apologize to the Reviewer for our misunderstanding and ask back for more information if it feels like the misunderstanding persisted.
 }

### 2020-10-13 ErrP.tex
Más respuestas.  Finalmente decidí volar el gráfico de los promedios.  En un punto no es lo que el revisor exactamente pide y lo que el pide no me parece, y creo comparten ustedes, tenga mucho sentido hacerlo.  Prefiero ir por el lado de ofrecerle alternativas y presentar el gráfico del grand average que es lo que quizás aporte más info (además ese gráfico salió perfecto).
Una vuelta de rosca.

@@
 Moreover, a growing number of studies have demonstrated the feasibility of using ErrPs as rewards for RL schemes such as to enhance robotic behaviour~\cite{Luo2019}, to assess air traffic controller's decisions~\cite{Goh2019} or to categorize actions as errors~\cite{Wirth2020}.
-Other approaches have used these signals as important feedback for human-robot interaction or to implement shared-control strategies~\cite{Schiatti2018}.
+Other approaches have used these signals as important feedback for human-robot interaction or to implement shared-control strategies~\cite{Schiatti2018,Iturrate2013}.
 Additionally, ErrPs have also been used in the context of games as an additional feedback channel that can be explored to improve gaming experience~\cite{Plass-OudeBos2010,kober2018bci}.
-The game is similar to this one \cite{Iturrate2013}.
 
@@
     \includegraphics[width=0.5\textwidth]{revisedimages/avg_further.eps}
-    \caption{Grand Average for all OHCs for the closer and further condition.  It can be seen the bump around 300 ms.}
+        \includegraphics[scale=1.0]{revisedimages/electrodes.png}
+    \caption{Grand Average of 2-seconds segments for all OHCs for the "move closer" (top) and "move further" (middle) condition.
+The increased height of the first peak around 0.4 seconds reflects the Error Potential response particularly on Pz, based on the electrode layout (bottom).}
     \label{fig:classifiers}
@@
 The best overall performance is obtained using Logistic Regression.
-In addition, the classification accuracy obtained averaging 5 epochs is shown as well.
-Although the signal averaging procedure improves the Signal-To-Noise-Radio (SNR) of the ErrP response, it reduces the number of data samples, producing a clear improvement only for the OHCs that contain more samples (1, 3 and 7).
 
@@
     \centering
-    \includegraphics[scale=0.11]{revisedimages/cross_val.eps}
-    \includegraphics[scale=0.21]{revisedimages/avg_5_segments.eps}
-    \caption{Binary single trial classification score using five different classifiers while recognizing ErrP potentials for the eight OHCs.
-The classification score using an ensemble average of 5 epochs is shown as well (GrandAvg).
-Chance Level is 0.5.}
+    \includegraphics[width=0.5\textwidth,height=70pt]{revisedimages/cross_val.eps}
+    %\includegraphics[width=290pt,height=90pt]{revisedimages/avg_5_segments.eps}
+    \caption{Binary single trial classification score using five different classifiers while recognizing ErrP potentials for the eight OHCs.   Chance Level is 0.5.}
     \label{fig:classifiers}
@@
 \end{subfigure}
-\caption{ROC Curves for OHCs 1-8. True positive rate is on the vertical axis and false positive rate on the horizontal axis.}
+\caption{ROC Curves for OHCs 1-8.
+True positive rate is on the vertical axis and false positive rate on the horizontal axis.
+The ROC curves for ErrP identification for Subjects 5 and 6 show low classification scores.}
 \label{fig:rocsubjects}
@@
 \label{conclusions}
+
+Each time the gaming agent plays this simple game, it takes on average around 100 steps to reach the target spot.
+We trained a classifier to recognize Error Potential from observational human critics that watch the agent playing the game.
+We let the agent play again and we mark movements that trigger an error potential from the human critic.
+We used those movements as rewards in a Reinforcement Learning scheme, and use them to train a Q-Table.
+When we let the agent plays the game again, the number of steps that requires to solve the game is now reduced.
+If we provide feedback based on random signals, we verified that no reduction is achieved and the average number of steps does not change.
+This shows that there is an effective transfer of information from the brainwaves to the agent.
+As this process is repeated, the agent keeps improving solving the game effectively, i.e.
+performing the minimum number of required steps to reach the goal.
 

### 2020-10-14 ErrP.tex
Subo una versión nueva del abstract reducido.

@@
 Error-related potential (ErrP) are a particular type of ERP elicited by a person attending a recognizable error.
-The purpose of this study is to determine if these signals can be used to train a Reinforcement Learning (RL) algorithm to learn an optimal policy.
-A game scenario is used to trigger the feedback response embedded in Electroencephalographic (EEG) signals of an observation human critic (OHC) that observes an agent playing a game.
-ErrP signals are captured using a Brain-Computer Interface (BCI) system.
-%method
-The experimental process consists of an individual observing a simple game scenario while their brain signals are captured.
-The game consists of a grid, where the object has to reach a desired target in the fewest amount of steps.
-Initially the object moves randomly within the grid,
-and a RL algorithm is trained for it to learn the optimal policy, in order to know how to reach the target in the least amount of steps.
+These signals can be used to train a gaming agent by a Reinforcement Learning (RL) algorithm to learn an optimal policy.
+The experimental process consists of an observational human critic (OHC) observing a simple game scenario while their Electroencephalographic (EEG) brain signals are captured.
+The game consists of a grid, where a green spot has to reach a desired target in the fewest amount of steps.
 %Results
@@
 //These are key findings, worth more discussion/interpretation and inclusion in abstract.
-Results show that there is an effective transfer of information and that the agent successfully learns to solve the game efficiently.
-Initially when the game is simulated with random movements it takes the agent an average of 97 steps to reach the objective, whereas when the trained Q-Table is used to reach the objective, the agent can reach the goal in the optimal number of steps, which is 8 steps.
-The algorithm can be trained with information from different OHCs, since the resulting dataset is composed of rewards for each corresponding step, independent of who they were generated from.
+Results show that there is an effective transfer of information and that the agent successfully learns to solve the game efficiently, from the initial 97 steps on average required to reach the target to the optimal number of 8 steps.
+Our results are expressed in threefold: (i) the structure of a simple grid-based game that can elicit the ErrP signal component, (ii) the verification that the reward function only penalizes wrong steps, which means that type II error (not properly identifying a wrong movement) does not affect significantly the agent learning process; (iii) collaborative rewards from multiple observational human critics can be used to train the algorithm effectively and can compensate the lack of low accuracy (approximately 67\%) or the limited scope of transfer learning schemes.
+
+%The algorithm can be trained with information from different OHCs, since the resulting dataset is composed of rewards for each corresponding step, independent of who they were generated from.
 This shows that the error classification accuracy (approximately 0.67) is good enough for the algorithm to learn.
@@
 %conclusions
-This study shows that: (i) the structure of a simple grid-based game that can elicit the ErrP signal component; (ii) the verification that low classification accuracy of just above chance level that produces noisy rewards is enough to allow an agent to learn the optimal policy; (iii) collaborative rewards from multiple observational human critics can compensate the lack of accuracy or the limited scope of transfer learning schemes.
-
-% In this study, we propose a simple game scenario that can be used to trigger a feedback response embedded in Electroencephalographic (EEG) signals of an observation human critic that observes an agent playing a game.
-Based on a Reinforcement Learning (RL) model, the gaming agent receives rewards for their actions on the game and learns its optimal policy.
-These rewards are obtained by implementing a Brain-Computer Interface (BCI) system that identifies signal components called Error-related Potentials (ErrP), which occur when a person witnesses a recognizable error.
-We perform an experiment where rewards are obtained from the ErrP signals from observational human critics watching an agent playing randomly a game.
-The agent is iteratively trained by receiving these rewards and updating its policy, improving its overall performance.
-Our results are expressed in threefold: (i) the structure of a simple grid-based game that can elicit the ErrP signal component; (ii) the verification that low classification accuracy of just above chance level that produces noisy rewards is enough to allow an agent to learn the optimal policy; (iii) collaborative rewards from multiple observational human critics can compensate the lack of accuracy or the limited scope of transfer learning schemes.
+%Our results are expressed in threefold (i) the structure of a simple grid-based game that can elicit the ErrP signal component; (ii) the verification that low classification accuracy of just above chance level that produces noisy rewards is enough to allow an agent to learn the optimal policy; (iii) collaborative rewards from multiple observational human critics can compensate the lack of accuracy or the limited scope of transfer learning schemes.
+
 \end{abstract}

### 2020-10-15 review2/response.letter.tex
Subo una versión nueva del abstract reducido.
Le doy una vuelta más de rosca. Ya casi está.

@@
 Comments to the Author:
+
 The paper is improved but would benefit from a further update to
-- improve abstract
-- provide further interpretation/discussion of findings
-- fix minor errors/typos
-- address the grand average recommendation
+
+\begin{itemize}
+\item improve abstract
+\item provide further interpretation/discussion of findings
+\item fix minor errors/typos
+\item address the grand average recommendation
+\end{itemize}
 
@@
 The paper is improved but would benefit from a further update to
+
 - improve abstract
@@
 {\color{blue}
-We rewrote the abstract explaining in further details the obtained results.  
+We have rewrote the abstract explaining in further details the obtained results.  
 }
@@
 {\color{blue}
-We included extra information and verified the contributions/findings.
+We included extra information and verified the contributions/findings.  This information was included in the abstract as well as in the Conclusion (Section IV).
 }
@@
 We addressed this issue.
-We think there must a missunderstanding from our side of the suggestion/recommendation of the Reviewer.
+We think there could be a misunderstanding from our side about the suggestion/recommendation of the Reviewer.
 We added additional information in this response letter, and apologize for this.
@@
 
-Training a Gaming Agent on Brainwaves
 The paper has been improved. IMO, there are still areas that need further attention to improve the paper further.
@@
 {\color{blue}
-This text is no longer contained in the manuscript.  We verified throughout the Manuscript to avoid similar mistakes.
+We fixed this grammatical error.  Thank you very much for noticing it.
 }
@@
 The overall performance of 0.672 is low.
-Although a comparison can be misleading in the context of the ErrP experiment, we added a brief comparison to other similar works.
+Although a straightforward comparison could be misleading in the context of the ErrP experiment, we added a brief recount of the values obtained for other similar works.
 We also emphasized this point in future works at the end of the Conclusions section.
@@
 {\color{blue}
-Due to previous Reviewer's requests, we added all the ROC curves on the new Figure 7.
+Due to previous Reviewer's requests, we added all the ROC curves on the new Figure 6.
 We now emphasized on this figure's caption which ROC curves where showing an effective identification of the ErrP potential and which did not.
-We added this in the text emphasizing the important finding that we could not provide an enhancement of the agent performance based on the rewards from subjects where the obtained ROC curves were not good.
+We added this in the text highlighting the important finding that we could not provide an enhancement of the agent performance based on the rewards from subjects where the obtained ROC curves were not good (Section III, page 5).
 }
@@
 This is a great question.
-Traditional Transfer Learning strategies focus on the procedure to enrich a classifier training it with a vast dataset and using it to generalize to new data or unseen scenarios.
-While deaing with EEG data, this strategy tends to fail, and other approaches are required.
+Traditional transfer learning strategies focus on the procedure to enrich a classifier training it with a vast dataset and using it to generalize to new data from unseen scenarios.
+While dealing with EEG data, this strategy tends to fail, and other approaches are required.
 We found in this work, that even when that strategy fails, if the system is coupled with a basic reinforcement learning algorithm, the cumulative rewards from different subjects, can be used to effectively transmit information and improve the agent performance.
-We agree with the Reviewer that this may be due to the average effect of positive or learners with a higher accuracy, but we think it may be related to the fact that the RL algorithm is quite robust and if we can get a higher specificity it will lead to eventually learn, and the usage of various OHCs help to increase the available data to do so.
+We agree with the Reviewer that this may be due to the average effect of positive or learners with a higher accuracy, but we think it may be related to the fact that the RL algorithm is quite robust and if we can get a higher specificity it will lead to eventually learn, and the cumulative usage of data from various OHCs help to overcome this issue and improve the agent performance.
 }
@@
 {\color{blue}
-We believe this result is quite supported in the literature.
-You can check here here here here here.
-Our novel approach is to use the rewards to train an agent that can perform on its own after the training has been performed, and the game mechanics to verify the flow of information.
-This information was added in the Conclusion Section IV.
+
+These results are supported by the literature.
+As we mention in the Introduction, similar experiments have been performed (R.
+Chavarriaga, A.
+Sobolewski, and J.
+d.
+R.
+Millán, "Errare machinale est: The use of error-related potentials in brain-machine interfaces," Frontiers in Neuroscience,2014).
+Our novel approach is to use the rewards to train a gaming agent.
+We have added this confirmation in the Conclusion Section IV.
 }
@@
 {\color{blue}
-Subject 5 and 6 aren't used to train the algorithm in this instance. This information was emphasized on the Figure's caption and on the main text in the Result Section.
+The experiment that we performed to generate the Figure 9 doesn't include data from Subject 5 and 6.
+This is emphasized on the Figure's caption and on the main text in the Result Section.
+In the Figure 9, the X axis show the progressive number of gaming agent training matches used to update the Q-Table (in this case they are from different subjects).
 }
@@
 {\color{blue}
-We added it because is a very interesting results to overcome issues in transfer learning while dealing with biological data.  We appreciate the reviewer for this very important point.
+We included the both finding in the abstract and we emphasized them  in Section IV. 
 }

### 2020-10-15 ErrP.tex
Le doy una vuelta más de rosca. Ya casi está.

@@
 Error-related potential (ErrP) are a particular type of ERP elicited by a person attending a recognizable error.
-These signals can be used to train a gaming agent by a Reinforcement Learning (RL) algorithm to learn an optimal policy.
-The experimental process consists of an observational human critic (OHC) observing a simple game scenario while their Electroencephalographic (EEG) brain signals are captured.
+These Electroencephalographic (EEG)  signals can be used to train a gaming agent by a Reinforcement Learning (RL) algorithm to learn an optimal policy.
+The experimental process consists of an observational human critic (OHC) observing a simple game scenario while their brain signals are captured.
 The game consists of a grid, where a green spot has to reach a desired target in the fewest amount of steps.
+Results show that there is an effective transfer of information and that the agent successfully learns to solve the game efficiently, from the initial 97 steps on average required to reach the target to the optimal number of 8 steps.
+Our results are expressed in threefold: (i) the mechanics of a simple grid-based game that can elicit the ErrP signal component, (ii) the verification that the reward function only penalizes wrong steps, which means that type II error (not properly identifying a wrong movement) does not affect significantly the agent learning process; (iii) collaborative rewards from multiple observational human critics can be used to train the algorithm effectively and can compensate low classification accuracies (around 67\%) or the limited scope of transfer learning schemes.
 %Results
@@
 //These are key findings, worth more discussion/interpretation and inclusion in abstract.
-Results show that there is an effective transfer of information and that the agent successfully learns to solve the game efficiently, from the initial 97 steps on average required to reach the target to the optimal number of 8 steps.
-Our results are expressed in threefold: (i) the structure of a simple grid-based game that can elicit the ErrP signal component, (ii) the verification that the reward function only penalizes wrong steps, which means that type II error (not properly identifying a wrong movement) does not affect significantly the agent learning process; (iii) collaborative rewards from multiple observational human critics can be used to train the algorithm effectively and can compensate the lack of low accuracy (approximately 67\%) or the limited scope of transfer learning schemes.
-
 %The algorithm can be trained with information from different OHCs, since the resulting dataset is composed of rewards for each corresponding step, independent of who they were generated from.
@@
 Therefore,  we aim to use the information extracted from brainwaves to enhance the performance of a gaming agent.
-The three contributions are (1) a simple game mechanics and agent that can elicit the ErrP potential, (2) results that confirm that even when ErrP classification accuracy is low but with a high specificity and produces a noisy reward signal, enough information is generated for an agent to learn the optimal policy and solve a simple game and (3) collaborative rewards from multiple observational human observers can compensate the lack of classification accuracy or the inefficacy of transfer learning procedures for brainwaves signals.
+The three contributions are (1) a simple game mechanics and agent that can elicit the ErrP potential, (2) results that confirm that even when ErrP classification accuracy is low but with a high specificity, enough information is generated for an agent to learn the optimal policy and solve a simple game and (3) collaborative rewards from multiple observational human observers can compensate the lack of classification accuracy or the inefficacy of transfer learning procedures for brainwaves signals.
 
@@
 
-In Section \ref{section:materials} the general layout of the cognitive game is described.
+This work unfold as follows: in Section \ref{section:materials} the general layout of the cognitive game is described.
 Sections \ref{brainwavesession} and \ref{cognitive_experiment_details} outline the cognitive game procedure used to obtain rewards in the form of ErrP components.
@@
 
-This phase is divided into a sequence of run sessions and a gaming agent training match.
+This phase is divided into a sequence of run sessions and gaming agent training matches.
 During the run session, the agent plays 200 matches guided by a specific Q-Table with a 5\% chance of randomly selecting a movement, to reduce deadlocks and loops.
@@
 For the agent to learn from the feedback generated by the OHC, movement actions are determined by the reply of the agent's actions that were taken during one brainwave session match, in an offline reinforcement learning scheme~\cite{Levine2020}.
-This allows the Q-Table to be built based on the OHC's feedback from the movements the agent took, which were executed pseudo-randomly during the brainwave session.
+This allows the Q-Table to be learned based on the OHC's feedback from the movements the agent took, which were executed pseudo-randomly during the brainwave session.
 The previously mentioned feedback is not explicit as it comes from the interpreted brain signal data.
@@
 \label{results}
+
+Grand averaged signal segments of 2-seconds length for all the OHCs can be seen on Figure~\ref{fig:grandaverage}.
+The ErrP can be noticed more clearly on Pareto-central areas (Pz electrode), around 0.4~s with a more prominent positive peak.
 
@@
         \includegraphics[scale=1.0]{revisedimages/electrodes.png}
-    \caption{Grand Average of 2-seconds segments for all OHCs for the "move closer" (top) and "move further" (middle) condition.
+    \caption{Grand average of 2-seconds segments for all OHCs for the "move closer" (top) and "move further" (middle) condition.
 The increased height of the first peak around 0.4 seconds reflects the Error Potential response particularly on Pz, based on the electrode layout (bottom).}
-    \label{fig:classifiers}
+    \label{fig:grandaverage}
 \end{figure}
 
-Figure~\ref{fig:classifiers} shows the binary classification accuracy obtained for the eight OHCs using five different classification algorithms and using a 10-fold cross-validation procedure.
+Figure~\ref{fig:classifiers}, on the other hand, shows the binary classification accuracy obtained for the eight OHCs using five different classification algorithms and using a 10-fold cross-validation procedure.
 The best overall performance is obtained using Logistic Regression.
@@
 
-On the other hand, Figure \ref{fig:avg_steps} shows the average amount of steps it takes for the agent to reach the goal for each OHC, as the Q-Table is progressively trained using the reward information obtained from the prediction of the trained classifier.
+Complementary, Figure \ref{fig:avg_steps} shows the average amount of steps it takes for the agent to reach the goal for each OHC, as the Q-Table is progressively trained using the reward information obtained from the prediction of the trained classifier.
 Each point corresponds to a run session where the average number of steps for the agent to reach the goal using a specific Q-Table is specified, for 200 repetitions.
@@
 Each time the gaming agent plays this simple game, it takes on average around 100 steps to reach the target spot.
-We trained a classifier to recognize Error Potential from observational human critics that watch the agent playing the game.
-We let the agent play again and we mark movements that trigger an error potential from the human critic.
-We used those movements as rewards in a Reinforcement Learning scheme, and use them to train a Q-Table.
-When we let the agent plays the game again, the number of steps that requires to solve the game is now reduced.
-If we provide feedback based on random signals, we verified that no reduction is achieved and the average number of steps does not change.
+We trained a classifier to recognize Error Potential from observational human critics that observe the agent playing the game.
+The gaming agent plays randomly and movements are marked triggered by the identification of an error potential from the human critic.
+Those movements are used as rewards in a Reinforcement Learning scheme to train a Q-Table.
+The gaming agent plays the game again, but this time the number of required steps to solve the game is reduced.
+If rewards are provided based on random signals,  no reduction is achieved and the average number of steps does not change.
 This shows that there is an effective transfer of information from the brainwaves to the agent.
@@
 This work aims to propose a simple game mechanics that can use the ErrP component to train a gaming agent using a RL model.
-The collected data and the shows that ErrP signals can in fact be classified and used to train an agent effectively.
-
+As described in the literature~\cite{Chavarriaga2014}, ErrPs can be used to transmit subjective feedback to a computer.
+The collected data shows that ErrP signals can in fact be classified and used to train an agent effectively.
 This proposal tries to keep the system as simple as possible, emphasizing information flow from the subjective error perception of the human critic.
@@
 The obtained accuracy to discriminate ErrPs is low, though on the same level to other similar results~\cite{Iturrate2013,Ehrlich2016}.
-In this regard, dispite of the subjectivity of the ErrP response in terms of the proposed experiment, levels of 90\% of accuracy are reported~\cite{Chavarriaga2014}.
-However, even with such low accuracy values, the RL algorithm was able to extract meaningful information from rewards that were helpful to improve, and often maximize, the agent's performance.
+In this regard, despite the subjectivity of the ErrP response in terms of the proposed experiment, levels of 90\%  accuracy are reported~\cite{Chavarriaga2014} as well.
+Despite the low accuracy  in ErrP identification, the RL algorithm was able to extract meaningful information from rewards that were helpful to improve, and often maximize, the agent's performance.
 Additionally, one important aspect of the classification results is the low percentage of false positives (Figure~\ref{fig:confusionmatrix}), showing a high specificity.
 On the other hand, the percentage of false negatives is generally higher.
-However, even though this implies that the agent misses frequently when a wrong action takes place, this is not hindering the overall performance and the agent is still learning.
-Though scarce, accurate rewards are very useful for the RL algorithm.
-%However, even though this imply that the agent misses frequently that an action taken is wrong, this do not seems to be a serious issue because the agent improves its performance.
+Even though this implies that the agent misses frequently when a wrong action takes place, this is not hindering the overall performance and the agent is still learning.
+Although they may be scarce, accurate rewards are very useful for the RL algorithm.
 

### 2020-10-18 review2/response.letter.tex
Pequeños ajustes al leer el texto.

@@
 We now emphasized on this figure's caption which ROC curves where showing an effective identification of the ErrP potential and which did not.
-We added this in the text highlighting the important finding that we could not provide an enhancement of the agent performance based on the rewards from subjects where the obtained ROC curves were not good (Section III, page 5).
+We added this in the text, highlighting the important finding that we could not provide an enhancement of the agent performance based on the rewards from subjects where the obtained ROC curves were not good (Section III, page 5).
 }
@@
 We fixed the inappropriate wording, and appreciate the Reviewer for pointing this out.
-Figure 5, for Subject 5 (in the first version of the manuscript it was labeled E) has only two sets of data because that Participant (OHC) couldn't complete more sessions.
+
+Figure 5, for Subject 5 (in the first version of the manuscript it was labeled E) has only two sets of testing data because that Participant (OHC) couldn't complete more sessions.
 Hence we used two training sessions to calculate the Q-Table and subsequently performed the run session (i.e.
 the agent performs movements randomly based on the trained QTable for 200 iterations).
+On the other hand, we hypothesize that the smaller change obtained from 1-2 for Subject 5 (as well as for Subject 6), may be due to the fact that the ROC curves for those Subjects also display very low classification accuracy.
+This could be for reasons related to BCI-illeteracy issues, or the Participant (OHC) not being  concentrated at all during the experiment.
+This information was explained in Section III, page 5.
 }
@@
 We found in this work, that even when that strategy fails, if the system is coupled with a basic reinforcement learning algorithm, the cumulative rewards from different subjects, can be used to effectively transmit information and improve the agent performance.
-We agree with the Reviewer that this may be due to the average effect of positive or learners with a higher accuracy, but we think it may be related to the fact that the RL algorithm is quite robust and if we can get a higher specificity it will lead to eventually learn, and the cumulative usage of data from various OHCs help to overcome this issue and improve the agent performance.
+We agree with the Reviewer that this may be due to the average effect of positive or learners with a higher accuracy, but we think it may be related to the fact that the RL algorithm is quite robust and if we can get a higher specificity, the cumulative usage of data from various OHCs help to overcome this issue and improve the agent performance.
 }
@@
 {\color{blue}
-We included the both finding in the abstract and we emphasized them  in Section IV. 
+We included both finding in the abstract and we emphasized them  in Section IV. 
 }
@@
 We think we misunderstood previous Reviewer's suggestions.
-We added the brown bar on the previous Figure 3 (now Figure 5) because we assumed the Reviewer was referring to perform a classification using epoched averaged signal segments.
+We added the brown bar on the previous Figure 3 (now Figure 4) because we assumed the Reviewer was referring to a classification performed using epoched averaged signal segments.
 We used 5-segments to obtain an averaged signal with an enhanced signal-to-noise ratio (Wim van Drongelen, 4 - Signal Averaging, Editor(s): Signal Processing for Neuroscientists, Academic Press, 2007, Pages 55-70,) per Participant, and performed the classification of ErrP components based on those averaged signals for each Participant.
@@
 The top subfigure shows the signals for the "move closer to the target" condition, whereas the bottom subfigure represents the grand average for the "move further" condition.
-On the other hand, Figure 9 shows the results of using information to train a classifier with data from one Participant and use it to identify rewards for another participant.
+On the other hand, Figure 9 shows the results, in terms of the decrease in the number of steps for the agent to reach the goal, of using information to train a classifier with data from one Participant and use it to identify rewards for another participant.
 This is performed in a single-trial approach from individual segments without any signal averaging.

### 2020-10-18 ErrP.tex
Pequeños ajustes al leer el texto.

@@
 %objective
-Error-related potential (ErrP) are a particular type of ERP elicited by a person attending a recognizable error.
+Error-related potential (ErrP) are a particular type of Event-Related Potential (ERP) elicited by a person attending a recognizable error.
 These Electroencephalographic (EEG)  signals can be used to train a gaming agent by a Reinforcement Learning (RL) algorithm to learn an optimal policy.
@@
 Results show that there is an effective transfer of information and that the agent successfully learns to solve the game efficiently, from the initial 97 steps on average required to reach the target to the optimal number of 8 steps.
-Our results are expressed in threefold: (i) the mechanics of a simple grid-based game that can elicit the ErrP signal component, (ii) the verification that the reward function only penalizes wrong steps, which means that type II error (not properly identifying a wrong movement) does not affect significantly the agent learning process; (iii) collaborative rewards from multiple observational human critics can be used to train the algorithm effectively and can compensate low classification accuracies (around 67\%) or the limited scope of transfer learning schemes.
+Our results are expressed in threefold: (i) the mechanics of a simple grid-based game that can elicit the ErrP signal component, (ii) the verification that the reward function only penalizes wrong steps, which means that type II error (not properly identifying a wrong movement) does not affect significantly the agent learning process; (iii) collaborative rewards from multiple observational human critics can be used to train the algorithm effectively and can compensate low classification accuracies and a limited scope of transfer learning schemes.
 %Results
@@
 The feasibility of a distinct non-biological communication channel between the Central Nervous System (CNS) and a computer device has been previously proven with Brain Computer Interfaces (BCI) or Brain Machine Interfaces (BMI).~\cite{Vasiljevic2020}.
-BCI systems provide a new input modality that can be used in the context of a computer game~\cite{Scherer2012,Nijholt2007}.
+BCI systems provide a new input modality that can be used in computer game~\cite{Scherer2012,Nijholt2007}.
 This advancement is relevant in the context of the accessibility for video games~\cite{Aguado-Delgado2020} and the growing area of e-sports~\cite{Yakovlev2020}.
@@
 % Observation human critic? Suena raro acá, puse Subject pero chequear! TODO
-In this study, gaming agents are trained using only signal components called Error-related Potentials (ErrP) that can be identified in the observer's brain signals.
+In this study, gaming agents are trained using only signal components called Error-related Potentials (ErrP) that can be identified in the observer's brainwaves.
 These types of signals can be found on EEG traces and are elicited when subjects are aware of the presence of an unexpected outcome, which they identify as an error.
@@
 Other approaches have used these signals as important feedback for human-robot interaction or to implement shared-control strategies~\cite{Schiatti2018,Iturrate2013}.
-Additionally, ErrPs have also been used in the context of games as an additional feedback channel that can be explored to improve gaming experience~\cite{Plass-OudeBos2010,kober2018bci}.
+Additionally, ErrPs have also been used in games as an additional feedback channel that can be explored to improve gaming experience~\cite{Plass-OudeBos2010,kober2018bci}.
 
@@
 
-Grand averaged signal segments of 2-seconds length for all the OHCs can be seen on Figure~\ref{fig:grandaverage}.
-The ErrP can be noticed more clearly on Pareto-central areas (Pz electrode), around 0.4~s with a more prominent positive peak.
+Grand averaged time-locked signal segments of 2-seconds length for all the OHCs can be seen in Figure~\ref{fig:grandaverage}.
+The ErrP can be noticed more clearly on parieto-central areas (Pz electrode), around 0.4~s with a more prominent positive peak.
 
@@
         \includegraphics[scale=1.0]{revisedimages/electrodes.png}
-    \caption{Grand average of 2-seconds segments for all OHCs for the "move closer" (top) and "move further" (middle) condition.
-The increased height of the first peak around 0.4 seconds reflects the Error Potential response particularly on Pz, based on the electrode layout (bottom).}
+    \caption{Grand average of 2-seconds time-locked segments for all OHCs for the "move closer" (top) and "move further" (middle) condition.
+Zero corresponds to the onset of the stimulus, i.e.
+when the gaming agent moves.
+The increased height of the first peak around 0.4 seconds reflects the ErrP response particularly on Pz, based on the electrode layout (bottom).}
     \label{fig:grandaverage}
@@
 Complementary, Figure \ref{fig:avg_steps} shows the average amount of steps it takes for the agent to reach the goal for each OHC, as the Q-Table is progressively trained using the reward information obtained from the prediction of the trained classifier.
-Each point corresponds to a run session where the average number of steps for the agent to reach the goal using a specific Q-Table is specified, for 200 repetitions.
+Each point corresponds to a run session of 200 game play repetitions.
+The y-value represent the average number of steps the agent takes to reach the goal using a specific Q-Table for a run session.
 The first point, at the x-value 0, represents the number of steps the agent takes to reach the goal with an untrained Q-Table, where movements are decided randomly.
@@
 Only the diagonal of the heatmap matrix shows a clear improvement in terms of the reduction of the required number of steps to reach the goal (averaged per 200 runs) which corresponds to the same information for each OHC shown in Figure~\ref{fig:avg_steps}.
-For the transfer learning experiment~\cite{Wu2016}, no performance gain is evidenced, the agents learn nothing and this implies that the reward information provides no value.
+For this transfer learning experiment~\cite{Wu2016}, no performance gain is evidenced, the agents learn nothing and this implies that the reward information provides no value.
 
@@
 Each time the gaming agent plays this simple game, it takes on average around 100 steps to reach the target spot.
-We trained a classifier to recognize Error Potential from observational human critics that observe the agent playing the game.
+A classifier can be trained to recognize Error Potential from observational human critics that observe the agent playing the game.
 The gaming agent plays randomly and movements are marked triggered by the identification of an error potential from the human critic.
@@
 As described in the literature~\cite{Chavarriaga2014}, ErrPs can be used to transmit subjective feedback to a computer.
-The collected data shows that ErrP signals can in fact be classified and used to train an agent effectively.
+The collected data show that ErrP signals can in fact be classified and used to train an agent effectively.
 This proposal tries to keep the system as simple as possible, emphasizing information flow from the subjective error perception of the human critic.
@@
 The obtained accuracy to discriminate ErrPs is low, though on the same level to other similar results~\cite{Iturrate2013,Ehrlich2016}.
-In this regard, despite the subjectivity of the ErrP response in terms of the proposed experiment, levels of 90\%  accuracy are reported~\cite{Chavarriaga2014} as well.
+In this regard, despite the subjectivity of the ErrP response in terms of the proposed experiment, levels of 90\%  accuracy are reported~\cite{Chavarriaga2014}.
 Despite the low accuracy  in ErrP identification, the RL algorithm was able to extract meaningful information from rewards that were helpful to improve, and often maximize, the agent's performance.

### 2020-10-19 review2/response.letter.tex
Last version ?

@@
 Comments to the Author:
-The paper is improved but would benefit from a further update to
+The paper is improved
+
+\begin{quotation}
+{\color{blue}
+We thanks the AE and all the Reviewers for all the information provided in the comments and for thoughtfully reviewing our manuscript.
+}
+\end{quotation}
+
+but would benefit from a further update to
 
@@
 {\color{blue}
-Due to previous Reviewer's requests, we added all the ROC curves on the new Figure 6.
-We now emphasized on this figure's caption which ROC curves where showing an effective identification of the ErrP potential and which did not.
+Based on a previous Reviewer's requests, we added all the ROC curves on the new Figure 6.
+We think it is better to allow comparisons between Figures 5,6 and 8.
+We are now emphasizing on this figure's caption which ROC curves were showing an effective identification of the ErrP potential and which did not.
 We added this in the text, highlighting the important finding that we could not provide an enhancement of the agent performance based on the rewards from subjects where the obtained ROC curves were not good (Section III, page 5).
@@
 Hence we used two training sessions to calculate the Q-Table and subsequently performed the run session (i.e.
-the agent performs movements randomly based on the trained QTable for 200 iterations).
+the agent performs movements randomly based on the trained Q-Table for 200 iterations).
 On the other hand, we hypothesize that the smaller change obtained from 1-2 for Subject 5 (as well as for Subject 6), may be due to the fact that the ROC curves for those Subjects also display very low classification accuracy.
@@
 We agree with the Reviewer that this may be due to the average effect of positive or learners with a higher accuracy, but we think it may be related to the fact that the RL algorithm is quite robust and if we can get a higher specificity, the cumulative usage of data from various OHCs help to overcome this issue and improve the agent performance.
+We have added this information in Section IV.
 }

### 2020-10-19 ErrP.tex
Last version ?

@@
 Previous research has explored the usage of RL with reward signals based on brain activity, recorded by an EEG-based BCI system during task execution.
-The papers \cite{ROBOT-CONTROL-PAPER,Kim2017,Omedes2013} have successfully demonstrated that a robot can be controlled with brain signals from a person who is observing a robot solve a task.
+The papers \cite{ROBOT-CONTROL-PAPER,Kim2017,Omedes2013} have successfully demonstrated that a robot can be controlled with brain signals from a person who is observing a robot to solve a task.
 Moreover, a growing number of studies have demonstrated the feasibility of using ErrPs as rewards for RL schemes such as to enhance robotic behaviour~\cite{Luo2019}, to assess air traffic controller's decisions~\cite{Goh2019} or to categorize actions as errors~\cite{Wirth2020}.
@@
 
-In this way, the raw data of a brainwave session is processed into an array of matches where each element is an array of epochs tagged with a number specifying the prediction of the classifier, i.e.
+In this way, the raw data of a brainwave session are processed into an array of matches where each element is an array of epochs tagged with a number specifying the prediction of the classifier, i.e.
 if the epoch corresponds to an action that made the agent move further from the goal (hit) or an action that made the agent moves closer to the goal (no-hit).
@@
 The eight channels are concatenated using the MNE Vectorizer function, which transforms the data matrix into a single array sample.
-Lastly, this data are used by the classification module as information to train and test a classifier.
+Lastly, these data are used by the classification module as information to train and test a classifier.
 Five different classification algorithms are used:  Logistic Regression, Multilayer Perceptron with a hidden layer of 100 neurons (i.e.
@@
 Figures \ref{fig:avg_steps} for OHC 5 and 6 show no apparent learning, as the amount of steps to reach the goal doesn't decrease when trained.
-These results are also consistent with their classification ROC curves, shown in Figures~\ref{fig:rocsubjects} obtained for both OHCs, where the area under the curve are close to chance level.
+These results are also consistent with the classification ROC curves, shown in Figures~\ref{fig:rocsubjects}, where the area under the curve for OHCs 5 and 6 are close to chance level.
 Both OHCs have less recorded data from the sessions in comparison to the rest of the OHCs.
@@
 Electroencephalographic signals have high inter-subject variability~\cite{Chavarriaga2014}.
-This is evidenced in Figure~\ref{fig:transferlearning} where the agent training is performed with rewards obtained by classifying epochs from one Tester OHC and a classifier that was trained using the brainwaves from a different Trainer OHC.
+This is evidenced in Figure~\ref{fig:transferlearning} where the agent training is performed with rewards obtained by classifying epochs from one Tester OHC with a classifier that was trained using the brainwaves from a different Trainer OHC.
 The figure shows the cumulative variation for all run sessions on the average number of steps required to reach the goal after training the agent with all the available matches from the brainwave session.
@@
 This proposal tries to keep the system as simple as possible, emphasizing information flow from the subjective error perception of the human critic.
-Rewards are generated using the signal processing and classification pipeline, and the Q-Table updates, enhancing the performance of the gaming agent.
 
@@
 The obtained accuracy to discriminate ErrPs is low, though on the same level to other similar results~\cite{Iturrate2013,Ehrlich2016}.
-In this regard, despite the subjectivity of the ErrP response in terms of the proposed experiment, levels of 90\%  accuracy are reported~\cite{Chavarriaga2014}.
+In this regard, despite the variability of the ErrP response in terms of different experiments, levels of 90\%  accuracy in identifying it are reported~\cite{Chavarriaga2014}.
 Despite the low accuracy  in ErrP identification, the RL algorithm was able to extract meaningful information from rewards that were helpful to improve, and often maximize, the agent's performance.
-Additionally, one important aspect of the classification results is the low percentage of false positives (Figure~\ref{fig:confusionmatrix}), showing a high specificity.
+Additionally,  classification results show a low percentage of false positives (Figure~\ref{fig:confusionmatrix}), entailing a high specificity.
 On the other hand, the percentage of false negatives is generally higher.
@@
 Despite that, the rewards generated from different subject's classifiers can be used to train the same Q-Table to improve its performance, which may lead to strategies where the overall performance is enhanced based on the information from different human critics at the same time.
-There seems to be an agreement in terms of the subjective interpretation of what may be an appropriate movement to reach the goal.
+We hypothesize that as long as there are accurate rewards obtained from high specificity classifiers, there is extra information that can be used by the agent to get an improved Q-Table.
+Additionally, it seems to be an agreement in terms of the subjective interpretation of what may be an appropriate movement to reach the goal, and different OHCs produce rewards for the same type of movements.
 

### 2020-10-20 ErrP.tex
Correcciones minimas

@@
 The experimental process consists of an observational human critic (OHC) observing a simple game scenario while their brain signals are captured.
-The game consists of a grid, where a green spot has to reach a desired target in the fewest amount of steps.
+The game consists of a grid, where a blue spot has to reach a desired target in the fewest amount of steps.
 Results show that there is an effective transfer of information and that the agent successfully learns to solve the game efficiently, from the initial 97 steps on average required to reach the target to the optimal number of 8 steps.
@@
 The proposed system has two distinct parts.
-This first part consists of the collection of brainwave signals from a person that is watching an agent play a game.
+This first part consists of the collection of brainwave signals from an OHC that is watching an agent play a game.
 The agent knows the game rules but not how to win it.
-The second part, the gaming agent learning phase, is where the agent can learn the winning strategy using the person's feedback to improve its own performance.
+The second part, the gaming agent learning phase, is where the agent can learn the winning strategy using the OHC's feedback to improve its own performance.
 
@@
 After everything is connected, the subject is seated in a comfortable chair in front of a computer screen.
-The brightness of the screen is set to the maximum setting to avoid any visual inconvenience in which the subject can not distinguish the components of the game that appear on the screen.
+The brightness of the screen is set to the maximum setting to avoid any visual inconvenience in which the subject cannot distinguish the components of the game that appear on the screen.
 
@@
 In this way, the raw data of a brainwave session are processed into an array of matches where each element is an array of epochs tagged with a number specifying the prediction of the classifier, i.e.
-if the epoch corresponds to an action that made the agent move further from the goal (hit) or an action that made the agent moves closer to the goal (no-hit).
+if the epoch corresponds to an action that made the agent move further from the goal (hit) or an action that made the agent move closer to the goal (no-hit).
 The ErrP is expected to be found in hits.
@@
 Each point corresponds to a run session of 200 game play repetitions.
-The y-value represent the average number of steps the agent takes to reach the goal using a specific Q-Table for a run session.
+The y-values represent the average number of steps the agent takes to reach the goal using a specific Q-Table for a run session.
 The first point, at the x-value 0, represents the number of steps the agent takes to reach the goal with an untrained Q-Table, where movements are decided randomly.
@@
 Besides low data samples, there are other reasons affecting the classification accuracy:  cognitive reasons (i.e.
-the OHC not paying extensively attention to the game dynamics), very low SNR of the ErrP component or even the BCI-illiteracy phenomena where the specific OHC's signals do not contain the expected component response~\cite{Yousefi2019}.
+the OHC not paying extensive attention to the game dynamics), very low SNR of the ErrP component or even the BCI-illiteracy phenomena where the specific OHC's signals do not contain the expected component response~\cite{Yousefi2019}.
 
@@
 Each time the gaming agent plays this simple game, it takes on average around 100 steps to reach the target spot.
-A classifier can be trained to recognize Error Potential from observational human critics that observe the agent playing the game.
-The gaming agent plays randomly and movements are marked triggered by the identification of an error potential from the human critic.
+A classifier can be trained to recognize Error Potential from OHCs that observe the agent playing the game.
+The gaming agent plays randomly and movements are marked triggered by the identification of an error potential from the OHC.
 Those movements are used as rewards in a Reinforcement Learning scheme to train a Q-Table.
@@
 The collected data show that ErrP signals can in fact be classified and used to train an agent effectively.
-This proposal tries to keep the system as simple as possible, emphasizing information flow from the subjective error perception of the human critic.
+This proposal tries to keep the system as simple as possible, emphasizing information flow from the subjective error perception of the OHC.
 
@@
 At the same time, effective agent training depends on the OHC's training data.
-Results confirm the futility or complexity of using Transfer Learning~\cite{Wu2016}: training a classifier with data obtained from one OHC, and using the same classifier to identify ErrPs for another OHC does not increases the performance of the agent.
-Despite that, the rewards generated from different subject's classifiers can be used to train the same Q-Table to improve its performance, which may lead to strategies where the overall performance is enhanced based on the information from different human critics at the same time.
+Results confirm the futility or complexity of using Transfer Learning~\cite{Wu2016}: training a classifier with data obtained from one OHC, and using the same classifier to identify ErrPs for another OHC does not increase the performance of the agent.
+Despite that, the rewards generated from different subject's classifiers can be used to train the same Q-Table to improve its performance, which may lead to strategies where the overall performance is enhanced based on the information from different OHCs at the same time.
 We hypothesize that as long as there are accurate rewards obtained from high specificity classifiers, there is extra information that can be used by the agent to get an improved Q-Table.

### 2020-12-03 final/ErrP.tex
Subo la versión final del paper aceptado.

--- 2020-10-20 ErrP.tex
@@
 Hence, new interaction methods are required to increase the communication bandwidth between computers and humans or to produce alternative communications systems to increase the efficiency of this channel.
-In this respect, video games have been widely used as test tools to assess new means of interactions~\cite{Carter2014,Barr2007}.
+In this respect, video games have been widely used as test tools to assess new means of interactions~\cite{Carter2014,Frey2014,Barr2007}.
 Video gaming agents are computer programs that can sense the computer game environment, process information, and react accordingly within the environment.
@@
 The feasibility of a distinct non-biological communication channel between the Central Nervous System (CNS) and a computer device has been previously proven with Brain Computer Interfaces (BCI) or Brain Machine Interfaces (BMI).~\cite{Vasiljevic2020}.
-BCI systems provide a new input modality that can be used in computer game~\cite{Scherer2012,Nijholt2007}.
+BCI systems provide a new input modality that can be used in computer games~\cite{Scherer2012,Marshall2013,Nijholt2007}.
 This advancement is relevant in the context of the accessibility for video games~\cite{Aguado-Delgado2020} and the growing area of e-sports~\cite{Yakovlev2020}.
@@
 Thus, the learning problem is posed as a stochastic optimization strategy~\cite{Santos1999}.
-Recently, this technique has been used extensively in the context of advances in artificial intelligence~\cite{Nguyen2020}.
+Recently, this technique has been used extensively in artificial intelligence~\cite{Nguyen2020}.
 The influence of DeepBrain's AlphaGo project cannot be neglected, since it was the first to reach a very high proficiency when it won the complex game Go against several world champions~\cite{ALPHA-GO}.
@@
 
-This work unfold as follows: in Section \ref{section:materials} the general layout of the cognitive game is described.
+This work unfolds as follows: in Section \ref{section:materials} the general layout of the cognitive game is described.
 Sections \ref{brainwavesession} and \ref{cognitive_experiment_details} outline the cognitive game procedure used to obtain rewards in the form of ErrP components.
@@
     \centering
-    \includegraphics[width=\textwidth]{Images/complete_flow.png}
+    \includegraphics[width=\textwidth]{images/figure1.png}
     \caption{Overview of the experimental procedure.
@@
 \centering
-\includegraphics[scale=0.2]{Images/grid_initial_state.png}
-\includegraphics[scale=0.2]{Images/grid_end_state.png}
+\includegraphics[scale=0.2]{images/figure2a.png}
+\includegraphics[scale=0.2]{images/figure2b.png}
 \end{subfigure}
@@
 The gaming agent starts first with a Q-Table initialized with zeros, so the initial policy for the agent is randomized.
-For the agent to learn from the feedback generated by the OHC, movement actions are determined by the reply of the agent's actions that were taken during one brainwave session match, in an offline reinforcement learning scheme~\cite{Levine2020}.
+For the agent to learn from the feedback generated by the OHC, movement actions are determined by the replay of the agent's actions that were taken during one brainwave session match, in an offline reinforcement learning scheme~\cite{Levine2020}.
 This allows the Q-Table to be learned based on the OHC's feedback from the movements the agent took, which were executed pseudo-randomly during the brainwave session.
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{revisedimages/avg_closer.eps}
-    \includegraphics[width=0.5\textwidth]{revisedimages/avg_further.eps}
-        \includegraphics[scale=1.0]{revisedimages/electrodes.png}
+    \includegraphics[width=0.5\textwidth]{images/figure3a.eps}
+    \includegraphics[width=0.5\textwidth]{images/figure3b.eps}
+    \includegraphics[scale=1.0]{images/figure3c.png}
     \caption{Grand average of 2-seconds time-locked segments for all OHCs for the "move closer" (top) and "move further" (middle) condition.
-Zero corresponds to the onset of the stimulus, i.e.
+Zero time on x-axis corresponds to the onset of the stimulus, i.e.
 when the gaming agent moves.
@@
     \centering
-    \includegraphics[width=0.5\textwidth,height=70pt]{revisedimages/cross_val.eps}
+    \includegraphics[width=0.5\textwidth,height=70pt]{images/figure4.eps}
     %\includegraphics[width=290pt,height=90pt]{revisedimages/avg_5_segments.eps}
@@
 \centering
-\includegraphics[scale=0.27]{Images/Average_steps/a.png}
-\includegraphics[scale=0.27]{Images/Average_steps/b.png}
-\centering
-\includegraphics[scale=0.27]{Images/Average_steps/c.png}
- \includegraphics[scale=0.27]{Images/Average_steps/d.png}
- \centering
-  \includegraphics[scale=0.27]{Images/Average_steps/e.png}
-  \includegraphics[scale=0.27]{Images/Average_steps/f.png}
-  \centering
-  \includegraphics[scale=0.27]{Images/Average_steps/g.png}
-  \includegraphics[scale=0.27]{Images/Average_steps/h.png}
+\includegraphics[scale=0.27]{images/figure5a.png}
+\includegraphics[scale=0.27]{images/figure5b.png}
+\centering
+\includegraphics[scale=0.27]{images/figure5c.png}
+ \includegraphics[scale=0.27]{images/figure5d.png}
+ \centering
+  \includegraphics[scale=0.27]{images/figure5e.png}
+  \includegraphics[scale=0.27]{images/figure5f.png}
+  \centering
+  \includegraphics[scale=0.27]{images/figure5g.png}
+  \includegraphics[scale=0.27]{images/figure5h.png}
 \end{subfigure}
@@
 \centering
-\includegraphics[scale=0.09]{revisedimages/roc_1.eps}   \hspace{-1.5em}
-\includegraphics[scale=0.09]{revisedimages/roc_2.eps} \\
+\includegraphics[scale=0.09]{images/figure6a.eps}   \hspace{-1.5em}
+\includegraphics[scale=0.09]{images/figure6b.eps} \\
 %\vspace{-1.3em}
 \centering
-\includegraphics[scale=0.09]{revisedimages/roc_3.eps}   \hspace{-1.5em}
- \includegraphics[scale=0.09]{revisedimages/roc_4.eps} \\
- \centering
-  \includegraphics[scale=0.09]{revisedimages/roc_5.eps}   \hspace{-1.5em}
-  \includegraphics[scale=0.09]{revisedimages/roc_6.eps} \\
-  \centering
-  \includegraphics[scale=0.09]{revisedimages/roc_7.eps}    \hspace{-1.5em}
-  \includegraphics[scale=0.09]{revisedimages/roc_8.eps} \\
+\includegraphics[scale=0.09]{images/figure6c.eps}   \hspace{-1.5em}
+ \includegraphics[scale=0.09]{images/figure6d.eps} \\
+ \centering
+  \includegraphics[scale=0.09]{images/figure6e.eps}   \hspace{-1.5em}
+  \includegraphics[scale=0.09]{images/figure6f.eps} \\
+  \centering
+  \includegraphics[scale=0.09]{images/figure6g.eps}    \hspace{-1.5em}
+  \includegraphics[scale=0.09]{images/figure6h.eps} \\
 \end{subfigure}
@@
 \centering
-\includegraphics[scale=0.4]{Images/Average_steps/noise.eps}
+\includegraphics[scale=0.4]{images/figure7.eps}
 \caption{Average number of steps for the agent to reach the goal when trained with a classifier produced from sham EEG signals.
@@
 \begin{subfigure}{0.5\textwidth}
-\includegraphics[scale=0.60]{revisedimages/transfer_learning_heatmap.eps}
+\includegraphics[scale=0.60]{images/figure8.eps}
 \end{subfigure}
@@
 \centering
-\includegraphics[scale=0.4]{Images/Average_steps/all.eps}
+\includegraphics[scale=0.4]{images/figure9.eps}
 \caption{Average steps using Q-Table trained with brainwave session matches from six different OHCs.
@@
 A classifier can be trained to recognize Error Potential from OHCs that observe the agent playing the game.
-The gaming agent plays randomly and movements are marked triggered by the identification of an error potential from the OHC.
+The gaming agent plays randomly and movements are marked based on the identification of an error potential from the OHC.
 Those movements are used as rewards in a Reinforcement Learning scheme to train a Q-Table.
@@
 The obtained accuracy to discriminate ErrPs is low, though on the same level to other similar results~\cite{Iturrate2013,Ehrlich2016}.
-In this regard, despite the variability of the ErrP response in terms of different experiments, levels of 90\%  accuracy in identifying it are reported~\cite{Chavarriaga2014}.
-Despite the low accuracy  in ErrP identification, the RL algorithm was able to extract meaningful information from rewards that were helpful to improve, and often maximize, the agent's performance.
+In this regard, considering the variability of the ErrP response in terms of different cognitive experiments, levels of 90\%  accuracy in identifying it, are reported~\cite{Chavarriaga2014}.
+In this work, despite the low accuracy in ErrP identification, the RL algorithm was able to extract meaningful information from rewards that were helpful to improve, and often maximize, the agent's performance.
 Additionally,  classification results show a low percentage of false positives (Figure~\ref{fig:confusionmatrix}), entailing a high specificity.
@@
 \centering
-\includegraphics[scale=0.14]{revisedimages/matrix_1.eps}
-\includegraphics[scale=0.14]{revisedimages/matrix_2.eps}\\
-\includegraphics[scale=0.14]{revisedimages/matrix_3.eps}
-\includegraphics[scale=0.14]{revisedimages/matrix_4.eps}\\
-\includegraphics[scale=0.14]{revisedimages/matrix_5.eps}
-\includegraphics[scale=0.14]{revisedimages/matrix_6.eps}\\
-\includegraphics[scale=0.14]{revisedimages/matrix_7.eps}
-\includegraphics[scale=0.14]{revisedimages/matrix_8.eps}\\
+\includegraphics[scale=0.14]{images/figure10a.eps}
+\includegraphics[scale=0.14]{images/figure10b.eps}\\
+\includegraphics[scale=0.14]{images/figure10c.eps}
+\includegraphics[scale=0.14]{images/figure10d.eps}\\
+\includegraphics[scale=0.14]{images/figure10e.eps}
+\includegraphics[scale=0.14]{images/figure10f.eps}\\
+\includegraphics[scale=0.14]{images/figure10g.eps}
+\includegraphics[scale=0.14]{images/figure10h.eps}\\
 \end{subfigure}
